### 2016-03-03 paper/paper.tex

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{times}
\usepackage{latexsym}
\usepackage{color}

\newcommand{\secref}[1]{Section~\ref{sec:#1}}
\newcommand{\figref}[1]{Figure~\ref{fig:#1}}
\newcommand{\algref}[1]{Algorithm~\ref{alg:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
\newcommand{\mattnote}[1]{\textcolor{red}{NOTE: #1}}
\newcommand{\blank}{\_\_\_}
\newcommand{\predicate}[1]{\ensuremath{\textsc{#1}}}
\newcommand{\entity}[1]{\ensuremath{\mathrm{#1}}}

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

\title{Combining formal and distributional models of predicate semantics}

\author{}%Matt Gardner and Jayant Krishnamurthy\\
%Allen Institute for Artificial Intelligence\\
%Seattle, Washington, USA\\
%{\tt \{mattg,jayantk\}@allenai.org}}

\date{}

\begin{document}

\maketitle

\begin{abstract}

  We consider the problem of learning models of predicate (category and
  relation) semantics using both distributional information and structured
  information contained in a formal knowledge base.  Most previous approaches
  to modeling predicate semantics have either been purely distributional (such
  as word2vec and knowledge base embedding methods) or purely formal (such as
  most semantic parsers).  Distributional approaches have very broad coverage,
  but lack the compositional, logical semantics used by semantic parsers, and
  it has so far been difficult to combine the benefits of both of these
  techniques.

  In this paper, we present a method that incorporates logical statements
  derived from a knowledge base into distributional models of categories and
  relations.  Instead of mapping a phrase to a single logical statement, as
  done by semantic parsers, our method uses logical statements as features
  added to distributional models of words, allowing the model to learn that
  Freebase entities that are "honchos" are people, not buildings, and that they
  are frequently CEOs or film producers.  We use these models in an
  open-vocabulary semantic parsing task, showing a 63\% relative improvement in
  mean average precision over a distributional-only model, and a X\%
  improvement over a formal-only approach.

\end{abstract}

\section{Introduction}

How should a computer program represent the meaning of a word or a phrase?  The
answer to this question has a long and rich history.  Motivated by
Harris's distributional
hypothesis~\cite{harris-1954-distributional-hypothesis}, much work has been put
into representing words as collections of the contexts in which they appear.
Recent work with neural networks and word embeddings have shown that these
representations can be very useful for a number of natural language processing
tasks. \mattnote{cite something here}

At the same time, other researchers have found Montague's ideas about English
as a formal language to be useful~\cite{montague-1974-english-formal-language}.
Modern semantic parsers make use of a model-theoretic semantics that represents
words and phrases as formal predicates.  These predicates are then typically
mapped onto a query over a structured knowledge base, such as
Freebase~\cite{freebase-2008-bollacker}.  This kind of modeling allows semantic
parsers to handle the compositional structure of natural language and to
leverage large, curated knowledge sources to perform various natural language
processing tasks.  \mattnote{cite some semantic parsing papers}

Both of these approaches to modeling predicate semantics have aspects that are
very appealing.  It is relatively straightforward to learn a distributional
vector for every word or phrase in a corpus, allowing easy generalization from
words labeled with part of speech tags or dependency information to other words
that are distributionally similar.  Yet distributional approaches struggle to
make good use of the structured information contained in curated knowledge
sources like Freebase and WordNet~\cite{wordnet-1995}.  On the other hand,
because formal approaches to semantics typically model word meaning in terms of
a structured knowledge source, their applicability is limited to the set of
concepts represented in that knowledge source---a semantic parser trained with
Freebase cannot even represent words whose meaning has no correlate in the
Freebase ontology, such as ``front-runner'' and ``honcho''.

In this work we introduce models of predicate semantics that combine the
benefits of both distributional and formal approaches.  While there is no
Freebase predicate that corresponds exactly to the meaning of ``honcho'',
Freebase \emph{does} contain many predicates that can \emph{partially}
represent the word.  Our models extract features from Freebase that are
correlated with words and phrases seen in natural language text, and learns
weights for those features as additional components of a distributional model
of the word's meaning.

To demonstrate these models, we focus on the task of fill-in-the-blank natural
language queries, such as ``Italian architect \blank{}''.  Similar to many
current semantic parsers, we first convert this natural language query into a
logical form: $\lambda(\entity{x}) \predicate{architect}(\entity{x}) \land
\predicate{architect\_N/N}(\entity{Italian}, \entity{x})$.  A typical semantic
parser (e.g., that of Kwiatkowski et
al.~\shortcite{kwiatkowski-2013-ontology-matching}) would then try to map this
logical form to a Freebase query, matching \entity{Italian} to
(\predicate{/people/person/nationality}, \entity{Italy}) and
\predicate{architect} to (\predicate{/type/object/type},
\entity{/architecture/architect}).  In contrast, we follow Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} in learning a
model for each predicate that can give a \emph{score} to potential arguments.
However, while the models of Krishnamurthy and Mitchell are purely
distributional, using Freebase only as a means of finding entities in text, we
inject additional information from Freebase into the models for each predicate.
The model we learn for \predicate{architect} has a \emph{feature} capturing the
fact that an entity has the type \entity{/architecture/architect} in Freebase,
and the model for \predicate{architect\_N/N} has a \emph{feature} capturing
whether the first argument is the country of nationality of the second
argument.

This is a fundamentally new kind of predicate semantics.  It is
distributional---part of the model is still trained in a manner very similar to
word2vec---yet it is also formal.  However, instead of committing to a single
Freebase query to represent a phrase, as traditional formal approaches do, our
models are flexible, encoding many possible Freebase queries as features that
can give hints to the model.  Thus words that would be impossible to represent
as a single Freebase query can still benefit from the information contained in
Freebase---our model for ``front-runner'' learns that acceptable entities are
politicians, even though there is no exact encoding of ``front-runner'' in
Freebase.

The rest of this paper is organized as follows.  In \secref{background}, we
describe the relevant background necessary to understand the models we propose,
and we situate our model in the context of related work.  In \secref{method},
we give a formal description of our models of predicate semantics.  In
\secref{experiments}, we present experimental results on fill-in-the-blank
natural language query task.  Using web text linked to Freebase as our training
and test data, we show a 63\% relative improvement over prior work, giving a
new state-of-the-art result on this dataset.  In \secref{discussion}, we give a
detailed discussion of the benefits and drawbacks of the models we have
proposed.  We then conclude in \secref{conclusion}.

\section{Background}
\label{sec:background}

Our proposed method is best viewed as the addition of SFE
features~\cite{gardner-2015-sfe} to Krishnamurthy and
Mitchell's~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}
open-vocabulary semantic parser.  Accordingly, in this section we briefly
describe both of these techniques, as well as give a short overview of other
closely related work.

\subsection{Open-vocabulary semantic parsing}

\mattnote{TODO - Jayant will write this}

\subsection{Subgraph feature extraction}

\mattnote{TODO}

\section{Method}
\label{sec:method}

\mattnote{TODO}

\section{Experiments}
\label{sec:experiments}

\mattnote{TODO}

\section{Discussion}
\label{sec:discussion}

\mattnote{TODO}

\section{Conclusion}
\label{sec:conclusion}

\mattnote{TODO}

%\section*{Acknowledgments}

\bibliography{bib}
\bibliographystyle{acl2016}

\end{document}

### 2016-03-03 paper/paper.tex
A little work on SFE description
Former-commit-id: 3d025ff526ef20e1c2e19bfdf9eb23eda687a75b
Former-commit-id: 557af611d39c17216e9de7ab5c463a54ed6189ed

@@
 
-\mattnote{TODO}
+Subgraph feature extraction (SFE) is a technique introduced by Gardner and
+Mitchell~\shortcite{gardner-2015-sfe} for generating feature matrices over node
+pairs in a graph with labeled edges.  Given a pair of nodes in a graph, SFE
+performs a search to characterize a subgraph around those two nodes, then
+extracts various kinds of features from that subgraph, such as the set of edge
+sequences that connect the two nodes.  \mattnote{Give an example graph with
+features.}  Gardner and Mitchell used these features to perform link
+prediction in the graph, using characteristics of the subgraph around two nodes
+to determine if an edge of a particular type should exist between those nodes
+(when the graph corresponds to a knowledge base like Freebase, this task is
+also known as knowledge base completion). Gardner and Mitchell only used these
+features to model formal KB relations, however.
+
+We differ from the work done by Gardner and Mitchell in two ways.  First, we
+apply these features to models of natural language, instead of formal KB
+relations.  There are some non-trivial problems that need to be solved in order
+to make this work, which will be discussed in \secref{method}.  Second, Gardner
+and Mitchell only considered generating feature matrices over node \emph{pairs}
+in a graph, with which one can model binary relations.  The natural language
+queries we wish to answer also involve unary predicates, or categories.  We
+thus extend SFE to also generate feature matrices over \emph{nodes} in a graph,
+an extension that is straightforward and is also discussed in more detail in
+\secref{method}.
+
+\subsection{Other related work}
+
+Manaal's retrofitting semantic lexicons, Sebastian Riedel's ``Injecting Logical
+Background Knowledge into Embeddings for Relation Extraction'', work on PRA and
+KBC more generally\ldots
 

### 2016-03-03 paper/paper.tex
writing background section
Former-commit-id: 5bb9d830736c482fd42cb272f37ddebbdfdf29c5
Former-commit-id: 0736fea577294a02f29dd7c4c39cf06135a1cc70

--- 2016-03-03 paper/paper.tex
@@
 \usepackage{acl2016}
+\usepackage{amsmath}
 \usepackage{times}
@@
 \newcommand{\entity}[1]{\ensuremath{\mathrm{#1}}}
+
+\newcommand{\true}[0]{\predicate{true}}
+\newcommand{\false}[0]{\predicate{false}}
 
@@
 
-\mattnote{TODO - Jayant will write this}
+This system predicts a denotation $\gamma$, i.e., a set of Freebase
+entities, for a natural language text $s$, using the following
+probabilistic model:
+
+\begin{align*}
+P(\gamma | s) & = \sum_w \sum_\ell P(\gamma | \ell, w) P(w ; \theta, \phi) P(\ell | s)
+\end{align*}
+
+In this equation, $P(\ell | s)$ represents a semantic parser that
+produces a logical form $\ell$ given the text $s$. This logical form
+contains open-vocabulary predicates, as in the ``architect'' example
+above. This factor is deterministic, meaning that it assigns
+probability one to a single logical form. The second factor $P(w)$
+represents a distribution over possible worlds $w$, where a world is
+an assignment of truth values to all possible predicate
+instances. This distribution can be efficiently represented using a
+probabilistic database because each predicate instance is treated as
+an independent random variable. The truth probabilities of these
+variables are predicted using a matrix factorization approach similiar
+to that of Riedel et al., \shortcite{riedel-2013-mf-universal-schema};
+$\theta$ and $\phi$ represent the parameters of the matrix
+factorization. Finally, $P(\gamma | \ell, w)$ represents the
+deterministic evaluation of the logical form $\ell$ on the world $w$
+to produce a denotation $\gamma$. This factor is similar to other
+semantic parsing work, where it represents the deterministic
+evaluation of a query against a given database. Algorithms from the
+probabilistic databases community enable us to efficiently compute the
+marginal probability that an entity $e$ is in the denotation of a
+sentence, $\sum_\gamma P(e \in \gamma | s)$, for a large number of
+queries; we refer the reader to (TODO).
+
+The training problem in this model is to learn the parameters $\theta$
+and $\phi$ of the probabilistic database. The probability of a
+category instance $c(e)$ and relation instance $r(e_1, e_2)$ in the
+database is given by:
+
+\begin{align*}
+  P(c(e) & = \true{}) & = & \sigma ( \theta_c^T \phi_e ) \\
+  P(r(e_1, e_2) & = \true{}) & = & \sigma ( \theta_r^T \phi_{(e_1, e_2)} )
+\end{align*}
+
+The parameters $\theta$ represent $k$-dimensional embeddings of each
+category and relation predicate, and the parameters $\phi$ represent
+$k$-dimensional embeddings of each Freebase entity and entity
+pair. The probability of a predicate instance is the inner product of
+the corresponding predicate and entity embeddings. Thus, predicates
+with nearby embeddings will have similar distributions over the
+entities in their denotation.
+
+The parameters $\theta$ and $\phi$ are learned from predicate/entity
+co-occurrence counts collected from a large corpus. The training data
+consists of query/entity pairs, $\{(\ell^i, e^i)\}$, where the entity
+$e^i$ is observed to be an element of $\ell^i$'s denotation. These
+pairs are collected by semantically parsing entity-linked sentences
+and simplifying the resulting logical forms to identify conjunctions
+of predicates where all arguments are bound to specific
+entities. Extracting an entity from this conjunction results in a
+query/entity pair. The model is trained using a ranking objective that
+learns to rank the observed entities for each query above unobserved
+entities.
 

### 2016-03-03 paper/paper.tex
A bit more work on the paper
Former-commit-id: d1ba10d3d7acfd0db4b1ed2ff812cf82cd01e264
Former-commit-id: d27feb8d09883d0e8b5101ff89ab7a5216e8f1be

--- 2016-03-03 paper/paper.tex
@@
 we give a formal description of our models of predicate semantics.  In
-\secref{experiments}, we present experimental results on fill-in-the-blank
+\secref{evaluation}, we present experimental results on fill-in-the-blank
 natural language query task.  Using web text linked to Freebase as our training
@@
 \subsection{Open-vocabulary semantic parsing}
+\label{sec:jayant-semparse}
 
@@
 
-Manaal's retrofitting semantic lexicons, Sebastian Riedel's ``Injecting Logical
-Background Knowledge into Embeddings for Relation Extraction'', work on PRA and
-KBC more generally\ldots
+Some related work on including structured information in distributional
+representations: Manaal's retrofitting semantic lexicons, Sebastian Riedel's
+``Injecting Logical Background Knowledge into Embeddings for Relation
+Extraction'', work on PRA and KBC more generally\ldots Also, the whole line of
+work on knowledge base embeddings (RESCAL, TransE, etc.) is at least slightly
+relevant here, as is PRA.  \mattnote{Actually write
+this section}.
 
@@
 
+\subsection{Adding SFE features to Jayant's models}
+\label{sec:formal-and-distributional}
+
 \mattnote{TODO}
 
-\section{Experiments}
-\label{sec:experiments}
+\subsection{Finding relevant features for each predicate}
+\label{sec:computing-pmi}
 
 \mattnote{TODO}
+
+\subsection{Improved logical forms}
+\label{sec:better-lfs}
+
+\mattnote{TODO}
+
+\section{Evaluation}
+\label{sec:evaluation}
+
+We evaluate our models of predicate semantics on a fill-in-the-blank natural
+language query task.  Each test example is a natural language phrase containing
+at least two Freebase entities, one of which is held out.  The system must
+propose Freebase entities to fill in the blank left by the held out entity, and
+the predicted entities are then judged manually for correctness.  We compare
+our proposed models, which combine distributional and formal elements, with
+distributional-only and formal-only baselines.
+
+\subsection{Data}
+
+We use the dataset introduced by Krishnamurthy and
+Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}, which
+consists of the ClueWeb09 web
+corpus\footnote{http://www.lemuproject.org/clueweb09.php} along with Google's
+FACC entity linking of that corpus to
+Freebase~\cite{gabrilovich-2013-clueweb-entity-linking}.  3 million webpages
+from this corpus were processed with a CCG parser to produce logical forms, as
+described in \secref{jayant-semparse}.  This produced 2.1m predicate instances
+involving 142k entity pairs and 184k entities.  After removing
+infrequently-seen predicates (seen fewer than 6 times), there were 25k
+categories and 4.2k relations.\footnote{The differences in numbers reported
+here versus those reported by Krishnamurthy and
+Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} are due to the
+improved logical form generation, discussed in \secref{better-lfs}.}
+
+\subsection{Methodology}
+
+\subsection{Models}
+
+\subsection{Results}
 

### 2016-03-03 tacl2015_paper/decision.tex
adding tacl2015 paper
Former-commit-id: 0d96938966b2ba3d3b01c8b2bbda93814689193d

\documentclass{article}[11pt,oneside]

\begin{document}

\begin{verbatim}

As TACL action editor for submission 548, "Learning a Compositional
Semantics for Freebase with an Open Predicate Vocabulary",   I am happy to
tell you that I am accepting your paper subject (conditional) to your making
specific revisions within two months.

LIST OF MANDATORY REVISIONS:
The following issues were particularly prominent in the reviews below:

* There is a recent paper that seems closely related, "Large-scale semantic
parsing without Question-Answer Pairs", TACL 2014, Reddy, Lapata, and
Steedman. Please do a thorough comparison to this.

* Please add more discussion on the coverage and expressivity of the
approach: Which language phenomena are addressed by the representation in
this paper? How is negation handled, and which cases of negation are covered
by the current set of rules?

* Please do a comparison of probabilistic databases to Markov Logic
Networks, and more generally to probabilistic logic with a probability
distribution over
possible worlds.

But please also take into account all other reviewer comments.

Note that the reviewers asked for changes to the explanations of your model,
but not any additional experiments.

Generally, your revised version will be handled by the same action editor
(me) and the same reviewers (if necessary) in making the final decision ---
which, *if* all requested revisions are made, will be final acceptance.

You are allowed one to two extra pages of content to accommodate these
revisions.  To submit your revised version, follow the instructions in the
"Revision and Resubmission Policy for TACL Submissions" section of the
Author Guidelines at
https://tacl2013.cs.columbia.edu/ojs/index.php/tacl/about/submissions#authorGuidelines
.

Thank you for submitting to TACL, and I look forward to your revised
version!

Katrin Erk
University of Texas, Austin
katrin.erk@mail.utexas.edu
------------------------------------------------------
------------------------------------------------------
....THE REVIEWS....
------------------------------------------------------
------------------------------------------------------
Reviewer A:

CLARITY: For the reasonably well-prepared reader, is it clear what was done
and why? Is the paper well-written and well-structured?:
        5. Very clear.

ORIGINALITY/INNOVATIVENESS: How original is the approach? Does this paper
break new ground in topic, methodology, or content? How exciting and
innovative is the research it describes?
Note that a paper could score high for originality even if the results do
not show a convincing benefit.
:
        4. Creative: An intriguing problem, technique, or approach that is
substantially different from previous research.

SOUNDNESS/CORRECTNESS: First, is the technical approach sound and
well-chosen? Second, can one trust the claims of the paper -- are they
supported by properexperiments and are the results of the experiments
correctlyinterpreted?:
        4. Generally solid work, although there are some aspects of the approach or
evaluation I am not sure about.

MEANINGFUL COMPARISON: Does the author make clear where the presented system
sits with respect to existing literature? Are the references adequate?:
        4. Mostly solid bibliography and comparison, but there are a few additional
references that should be included. Discussion of benefits and limitations
is acceptable but not enlightening.

SUBSTANCE: Does this paper have enough substance (in terms of the amount of
work), or would it benefit from more ideas or analysis?:
        4. Represents an appropriate amount of work for a publication in this
journal. (most submissions)

IMPACT OF IDEAS OR RESULTS: How significant is the work described? If the
ideas are novel, will they also be useful or inspirational? If the results
are sound, are they also important? Does the paper bring new insights into
the nature of the problem?:
        4. Some of the ideas or results will substantially help other people's
ongoing research.

REPLICABILITY Will members of the ACL community be able to reproduce or
verify the results in this paper?
Members of the ACL community:
:
        3. could reproduce the results with some difficulty. The settings of
parameters are underspecified or subjectively determined; the
training/evaluation data are not widely available.

IMPACT OF ACCOMPANYING SOFTWARE: If software was submitted along with the
paper, what is the expected impact of the software package?:
        1. No usable software released.

IMPACT OF ACCOMPANYING DATASET: If a dataset was submitted along with the
paper, what is its expected impact? Will it be valuable to others in the
form in which they are released?:
        1. No usable datasets submitted.

RECOMMENDATION: Should the paper be accepted or rejected? In deciding on
your ultimate recommendation, please think over all your scores above. If a
paper has some weaknesses, but you really got a lot out of it, feel free to
reccommend it. If a paper is solid but you could live without it, let us
know that you're ambivalent.:
        4. Worthy: A good paper that is worthy of being published in TACL.

Detailed Comments for the Authors:
        This is one of the best papers in the recent literature on combining formal
and distributional semantics. The model maps CCG parses to logical forms,
then learns an embedding for the property and relation symbols based on
their denotations. These embeddings are used to construct a probabilistic
database, in a similar way to universal schema. The approach allows them to
capture compositional semantics whilst retaining the 'softness' of
distributional semantics.

Most of my comments are minor.

The paper introduces a new ranking function which allows compositional
expressions to be added to the database - which I think is an important
contribution. The paper claims that their model represents "arbitrary
natural language phrases" (end of section 2) - but later it suggests that
only expressions in which all variables are bound to Freebase entities are
added. For example, I think that this restriction means that a sentence like
"Every president is a person" wouldn't be added to the database (c.f.
Rochtaschel et al. 2014, who are interested in adding first-order knowledge
to probabilistic databases). The paper should be more clear about exactly
what knowledge is being represented in their database.

I also think that the paper would benefit from a discussion of the
strengths/weaknesses of using a probabilistic database for knowledge
representation, compared to alternatives such as Markov logic networks (as
used by Beltagy et al. 2013). For example, I think that adding a single new
fact to the database would require it to be retrained?

In the evaluation, they find that manually-annotated Freebase queries
outperform their model. One approach would be to also include Freebase
predicates in the database (as in universal schema), and see if the
combination outperforms Freebase alone. If this isn't possible, explain why.
Also, I'd be interested to see a result using parsed Freebase queries
(rather than gold queries), e.g. using Berant's parser.

A clustering baseline performs weakly on the task - it's perhaps worth
mentioning what kinds of errors it's making (e.g. over-clustering,
under-clustering, etc.) Lewis and Steedman (2013) use some additional
techniques, such as modeling ambiguity and dropping weak links in the
clustering, which may explain the difference in performance.

The authors suggest that recall could be improved by training on a larger
corpus. The amount of training data they use actually seems relatively small
by recent standards - is the bottleneck in syntactic parsing times, or in
the learning?

Some of the post-processing CCG parses sounds very similar to that used by
Lewis and Steedman (such as converting verbal adjuncts to arguments, adding
word features to prepositions). If so, this should be referenced.

The related work should discuss the recent Reddy, Lapata and Steedman paper
(TACL 2014). Like the submission, they learn a semantics for predicates in a
CCG-derived logical form based on their Freebase-entity arguments. There are
several important differences, but they're worth discussing.

The paper is generally very well-written, but I think Figure 1 could be made
more clear. Also, Figure 3 should use human-readable constants rather than
Freebase IDs.

REVIEWER CONFIDENCE:
        4. Quite sure. I tried to check the important points carefully. It's
unlikely, though conceivable, that I missed something that should affect my
ratings.

------------------------------------------------------

------------------------------------------------------
Reviewer B:

CLARITY: For the reasonably well-prepared reader, is it clear what was done
and why? Is the paper well-written and well-structured?:
        3. Mostly understandable to me with some effort.

ORIGINALITY/INNOVATIVENESS: How original is the approach? Does this paper
break new ground in topic, methodology, or content? How exciting and
innovative is the research it describes?
Note that a paper could score high for originality even if the results do
not show a convincing benefit.
:
        3. Respectable: A nice research contribution that represents a notable
extension of prior approaches or methodologies.

SOUNDNESS/CORRECTNESS: First, is the technical approach sound and
well-chosen? Second, can one trust the claims of the paper -- are they
supported by properexperiments and are the results of the experiments
correctlyinterpreted?:
        4. Generally solid work, although there are some aspects of the approach or
evaluation I am not sure about.

MEANINGFUL COMPARISON: Does the author make clear where the presented system
sits with respect to existing literature? Are the references adequate?:
        4. Mostly solid bibliography and comparison, but there are a few additional
references that should be included. Discussion of benefits and limitations
is acceptable but not enlightening.

SUBSTANCE: Does this paper have enough substance (in terms of the amount of
work), or would it benefit from more ideas or analysis?:
        4. Represents an appropriate amount of work for a publication in this
journal. (most submissions)

IMPACT OF IDEAS OR RESULTS: How significant is the work described? If the
ideas are novel, will they also be useful or inspirational? If the results
are sound, are they also important? Does the paper bring new insights into
the nature of the problem?:
        4. Some of the ideas or results will substantially help other people's
ongoing research.

REPLICABILITY Will members of the ACL community be able to reproduce or
verify the results in this paper?
Members of the ACL community:
:
        3. could reproduce the results with some difficulty. The settings of
parameters are underspecified or subjectively determined; the
training/evaluation data are not widely available.

IMPACT OF ACCOMPANYING SOFTWARE: If software was submitted along with the
paper, what is the expected impact of the software package?:
        1. No usable software released.

IMPACT OF ACCOMPANYING DATASET: If a dataset was submitted along with the
paper, what is its expected impact? Will it be valuable to others in the
form in which they are released?:
        1. No usable datasets submitted.

RECOMMENDATION: Should the paper be accepted or rejected? In deciding on
your ultimate recommendation, please think over all your scores above. If a
paper has some weaknesses, but you really got a lot out of it, feel free to
reccommend it. If a paper is solid but you could live without it, let us
know that you're ambivalent.:
        4. Worthy: A good paper that is worthy of being published in TACL.

Detailed Comments for the Authors:
        Summary of paper: The goal of this paper is to extend compositional
semantic parsing to open-domain predicates, as not to be bound by knowledge
bases such as Freebase. Specifically, a huge number of sentences are parsed
into logical forms using a simple rule-based semantic parser, where the
predicates (categories and relations) used are words.  These words are
embedded into a vector space via matrix factorization (like in universal
schema).  Experiments demonstrate the value of using matrix factorization
and training on compositional utterances.

Summary of assessment: Overall, I thought this was a decent paper.  The goal
of extending semantic parsing to more realistic settings is definitely a
worthwhile one.  The paper presents a reasonable and natural approach, and
the experiments demonstrate some promise in this approach.  There are,
however, several improvements that could be made that would turn this into a
strong paper:

1) I'd like to see a more rigorous treatment of the semantics.  This paper
has the opporunity to lay out a foundation for how compositional semantics
should be handled, but it comes across currently as rather ad-hoc.  Several
things about the exposition could be improved, as detailed below.

2) At some level, I'm not convinced by the practical utility of learning
these matrix factorization models based on the particular restricted
compositional utterances used in the paper, because at the end of the day,
you're just trying to model a set of relations.  For example, the utterance
"Tom Cruise plays Maverick in the movie Top Gun" is really just "Tom Cruise
plays Maverick" and "Tom Cruise plays in the movie Top Gun", which are both
just triples.  More complex utterances "Top Gun played in 5 movies" couldn't
be represented with triples and would actually require semantic parsing, but
this is not handled in the paper.  I understand that there is a 1\%
improvement by learning from compositional parses, but there's no analysis
of this.

More detailed comments:

Figure 2: the treatment of appositive constructions seems inappropriate.
Rather than stringing together a huge conjunction, the appositive
construction should be an independent conventional implicature statement,
whose validity is independent of the main statement.

Page 5: when presenting the probabilistic denotations, it would be clearer
to define things more rigorously.  For example, does this corresponds to a
world model where each ground predicate is true with some probability
independently? I believe the answer is no, and that there's some
approximation in the recursive definition of denotations, which should be
made clearer.  Comparing with what one gets from Markov logic would be
helpful.

I would have liked the paper to be more explicit early on about the exact
set of logical forms handled in two senses: (i) the formal logical
restrictions (e.g., only conjunctions and existential quantification is
allowed), and (ii) the practical sizes of the logical forms (e.g., do they
include 5 predicates or 50 predicates)?  I know statistics are given later
(in Table 1), but I think it really helps the reader understand the
motivation and design decisions if this appeared earlier.

5.1: the description of extracting simplified logical forms is not clear to
me. The examples help, but I didn't get a sense of what the general recipe
is on an arbitrarily logical form.  This seems like an important part of the
paper.

Perhaps state in 5.2 that this only handles simple predicate-entity queries
(the third example in Figure 3)?  Also, is $t_j'$ sampled based on $t_j$ so
that they share one entity in common.  In general, this part should be
spelled out in more detail: random from what distribution?

I found the ranking objective in 5.3 to be confusing.  In particular, in the
definition of $C(\ell)$ and $R_L(\ell)$, and $R_R(\ell)$, it's not clear
what this set is and that $y$ stands in for a concrete entity (?) in $\ell$,
but that $x$ is a variable (which doesn't even appear in $\ell$)?  This
definition also doesn't seem to generalize to all logical forms $\ell$.
What if the entity $e_i$ was embedded deeply in some large logical form
$\ell$ with lots of other existentially quantified variables?  I don't see
how the construction in the paper works for that, or is that outside the
scope of the paper?  Either way, being explicit would be useful.

At a higher-level note, the ranking objective seems rather ad-hoc.  Since
you already have defined a probabilistic denotation for a logical form
$\ell$ (section 4.2), why not just maximize the probability that the
denotation $\ell_i$ contains $e_i$, and the probability that denotation
$\ell_i$ does not contain random $e_i'$ that get sampled (appropriately
weighting the two terms)? I suppose the gradient updates would be more
involved and require some backpropagation, but conceptually, this would be a
lot cleaner, and the treatment of probabilistic semantics would be handled
in one place rather than two.

I was surprised that the Freebase semantic parsing method actually has more
complete coverage given that the folklore assumption (and indeed the
motivation for relation extraction) is that there is more data in text.

I would have liked to see much more error analysis of concrete examples of
compositional utterances that that system gets right and wrong.  What do the
examples in the test set look like?

REVIEWER CONFIDENCE:
        4. Quite sure. I tried to check the important points carefully. It's
unlikely, though conceivable, that I missed something that should affect my
ratings.

------------------------------------------------------

------------------------------------------------------
Reviewer C:

CLARITY: For the reasonably well-prepared reader, is it clear what was done
and why? Is the paper well-written and well-structured?:
        5. Very clear.

ORIGINALITY/INNOVATIVENESS: How original is the approach? Does this paper
break new ground in topic, methodology, or content? How exciting and
innovative is the research it describes?
Note that a paper could score high for originality even if the results do
not show a convincing benefit.
:
        4. Creative: An intriguing problem, technique, or approach that is
substantially different from previous research.

SOUNDNESS/CORRECTNESS: First, is the technical approach sound and
well-chosen? Second, can one trust the claims of the paper -- are they
supported by properexperiments and are the results of the experiments
correctlyinterpreted?:
        5. The approach is very apt, and the claims are convincingly supported.

MEANINGFUL COMPARISON: Does the author make clear where the presented system
sits with respect to existing literature? Are the references adequate?:
        3. Bibliography and comparison are somewhat helpful, but it could be hard
for a reader to determine exactly how this work relates to previous work or
what its benefits and limitations are.

SUBSTANCE: Does this paper have enough substance (in terms of the amount of
work), or would it benefit from more ideas or analysis?:
        4. Represents an appropriate amount of work for a publication in this
journal. (most submissions)

IMPACT OF IDEAS OR RESULTS: How significant is the work described? If the
ideas are novel, will they also be useful or inspirational? If the results
are sound, are they also important? Does the paper bring new insights into
the nature of the problem?:
        4. Some of the ideas or results will substantially help other people's
ongoing research.

REPLICABILITY Will members of the ACL community be able to reproduce or
verify the results in this paper?
Members of the ACL community:
:
        4. could mostly reproduce the results, but there may be some
variation because of sample variance or minor variations in their
interpretation of the protocol or method.

IMPACT OF ACCOMPANYING SOFTWARE: If software was submitted along with the
paper, what is the expected impact of the software package?:
        1. No usable software released.

IMPACT OF ACCOMPANYING DATASET: If a dataset was submitted along with the
paper, what is its expected impact? Will it be valuable to others in the
form in which they are released?:
        1. No usable datasets submitted.

RECOMMENDATION: Should the paper be accepted or rejected? In deciding on
your ultimate recommendation, please think over all your scores above. If a
paper has some weaknesses, but you really got a lot out of it, feel free to
reccommend it. If a paper is solid but you could live without it, let us
know that you're ambivalent.:
        5. Strong: I'd like to see it accepted; it will be one of the better papers
in TACL.

Detailed Comments for the Authors:
        Beautifully written paper describing an extension to the Freebase semantic
parsing problem, incorporating matrix factorisation borrowed from the ideas
on universal schema. The authors have worked hard to compare against
ompetitive baselines, and argue convincingly for the open nature of the
represenation. Careful thought has been given to the machine learning side,
with extensions to previous objective functions used for similar work.

The only grumble I have relates to an apparent lack of awareness of a highly
relevant existing TACL paper. It is perhaps generous to suggest an oversight
on the part of the authors in not citing the following paper which came out
in October 2014:

Large-scale Semantic Parsing without Question-Answer Pairs
Siva Reddy, Mirella Lapata, Mark Steedman

The submitted paper must position itself with respect to this paper, since
both use CCG for freebase semantic parsing. (The Reddy paper does not use an
"open" representation, so I can see this crucial difference.)

More minor comments follow.

Try this piece of tex to get your CCG categories looking much cleaner
(without the extraneous space):

\newcommand{\cf}[1]{\mbox{$\it{#1}$}}   % category font, e.g. \cf{NP}

Modifiers of verbs are changed to complements using PP. What if there are
lots of modifiers? That implies lots of PPs? eg (...((S\NP)/PP/PP)...)?
Maybe this doesn't matter if the change is only done in post-processing
before the semantic rules are applied, but it might be a bad idea to have
this representation as part of the supertagger and/or parser.

Special rules are used to deal with negation. How is this dealt with in the
semantics. Eg, off the top of my head, what about a query like "All the
James Bond actors that did *not* appear in Bond movies before 1980?" Is it
possible to take set complements? Is that how it's handled?

Footnote 2 is a little opaque. I understand the difference between the
marginal and conditional prob (I think); something like P(entity|query) vs.
P(entity, query), so in the marginal case there's no distribution over
possible answers. But why one works better than the other is mysterious, and
footnote 2 didn't help much.

Just one typo (!): "as opposed tuples in general"

Section 6.2: "Each system predicts..." - which systems? It's not clear at
this point what the systems are providing the pool.

I'm also not entirely convinced by the use of the pooling methodology here.
My understanding of pooling in IR is that experiments have been run showing
that, with enough diversity in the systems making up the pool, the recall in
the pooled answers is extremely high, making them a good basis for manual
annotation (since no relevant documents or correct answers are missed). If
the systems you use are just the handful you evaluate, it's not clear
pooling has the same guarantees.

I was also puzzled by the idea that there can be more than one answer to a
query, so a couple of examples here would really help. (I guess there could
be more than one CEO of a company, for example?)

It also wasn't obvious to me that MAP is the right evaluation, if there are
so few possible answers. Why not just rank of the first correct answer? What
do they do in, eg, TREC QA track here?

The last line of table 1 (> 1 answer 116) confused me. Is this the number of
questions with more than one answer? In the text it says at least one (so
>=) *system* able to produce the correct answer.

lambda = 10^-4, 300 dimensions: were these parameters tuned? If so, on what
data? (I guess I'm wondering whether additional tuning was done for your
system compared to the baselines, and on what data...)

I would change the title of section 7 (Discussion) to Conclusion, since
there's very little discussion.

REVIEWER CONFIDENCE:
        4. Quite sure. I tried to check the important points carefully. It's
unlikely, though conceivable, that I missed something that should affect my
ratings.

\end{verbatim}

\end{document}

### 2016-03-03 tacl2015_paper/naaclhlt2015/naaclhlt2015.tex
adding tacl2015 paper
Former-commit-id: 0d96938966b2ba3d3b01c8b2bbda93814689193d

%
% File naaclhlt2015.tex
%

\documentclass[11pt,letterpaper]{article}
\usepackage{naaclhlt2015}
\usepackage{times}
\usepackage{latexsym}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

\title{Instructions for NAACL HLT 2015 Proceedings\Thanks{This
    document has been adapted from the instructions for earlier ACL
    and NAACL proceedings, including those for 
    NAACL-HLT-12 by Nizar Habash and William Schuler,
    NAACL-HLT-10 by Claudia Leacock and Richard Wicentowski,
    NAACL-HLT-09 by Joakim Nivre and Noah Smith, 
    for ACL-05 by Hwee Tou Ng and Kemal Oflazer,
    for ACL-02 by Eugene Charniak and Dekang Lin, and earlier ACL and
    EACL formats.  Those versions were written by several people,
    including John Chen, Henry S. Thompson and Donald Walker.
    Additional elements were taken from the formatting instructions of
    the {\em International Joint Conference on Artificial Intelligence}.  
    This second version clarifies the procedure for 
    submitting for double-blind reviewing.}}

\author{Author 1\\
	    XYZ Company\\
	    111 Anywhere Street\\
	    Mytown, NY 10000, USA\\
	    {\tt author1@xyz.org}
	  \And
	Author 2\\
  	ABC University\\
  	900 Main Street\\
  	Ourcity, PQ, Canada A1A 1T2\\
  {\tt author2@abc.ca}}

\date{}

\begin{document}
\maketitle
\begin{abstract}
  This document contains the instructions for preparing a camera-ready
  manuscript for the proceedings of NAACL HLT 2015.  The document itself conforms
  to its own specifications, and is therefore an example of what
  your manuscript should look like.  Papers are required to conform to
  all the directions reported in this document.  Also included are instructions for
  submission to the conference, which are similar to the camera-ready instructions
  but remove author-identifying information.
\end{abstract}

\section{Introduction}

The following instructions are directed to authors of papers accepted
for publication in the NAACL HLT 2015 proceedings.  All authors are required
to adhere to these specifications. Authors are required to provide 
a Portable Document Format (PDF) version of
their papers.  The proceedings will be printed on US-Letter paper.
Authors from countries in which access to word-processing systems is
limited should contact the publication chairs as soon as possible.

\indent\paragraph{Note} Grayscale readability of all figures and
graphics will be enforced for all accepted papers
(\S\ref{ssec:accessibility}).  Apart from this, the style files and
camera-ready requirements are unchanged from last year.

\section{General Instructions}

Manuscripts must be in two-column format.  Exceptions to the
two-column format include the title, as well as the 
authors' names and complete
addresses (only in the final version, not in the version submitted for review), 
which must be centered at the top of the first page (see
the guidelines in Subsection~\ref{ssec:first}), and any full-width
figures or tables.  Type single-spaced.  Do not number the pages.
Start all pages directly under the top margin.  See the guidelines
later regarding formatting the first page.

%% If the paper is produced by a printer, make sure that the quality
%% of the output is dark enough to photocopy well.  It may be necessary
%% to have your laser printer adjusted for this purpose.  Papers that are too
%% faint to reproduce well may not be included.

%% {\bf Do not print page numbers on the manuscript.}  Write them lightly
%% on the back of each page in the upper left corner along with the
%% (first) author's name.

The maximum length of a manuscript is eight (8) pages for the main
conference, printed single-sided, plus two (2) pages for references
(see Section~\ref{sec:length} for additional information on the
maximum number of pages).  Do not number the pages.

The review process is double-blind, so do not include any author information (names, addresses) when submitting a paper for review.  However, you should allocate space for the names and addresses so that they will fit in the final (accepted) version.  This is best done by either providing fake or blank names and addresses (as shown in this paper).

\subsection{Electronically-available resources}

NAACL HLT provides this description in \LaTeX2e{} ({\tt naaclhlt2015.tex}) and PDF
format ({\tt naaclhlt2015.pdf}), along with the \LaTeX2e{} style file used to
format it ({\tt naaclhlt2015.sty}) and an ACL bibliography style ({\tt naaclhlt2015.bst}).
These files are all available at
{\tt http://naacl2015.naacl.org}.  A Microsoft Word
template file ({\tt naaclhlt2015.dot}) is also available at the same URL. We
strongly recommend the use of these style files, which have been
appropriately tailored for the NAACL HLT 2015 proceedings.

\subsection{Format of Electronic Manuscript}
\label{sect:pdf}

For the production of the electronic manuscript you must use Adobe's
Portable Document Format (PDF). This format can be generated from
postscript files: on Unix systems, you can use {\tt ps2pdf} for this
purpose; under Microsoft Windows, you can use Adobe's Distiller, or
if you have cygwin installed, you can use {\tt dvipdf} or
{\tt ps2pdf}.  Note 
that some word processing programs generate PDF which may not include
all the necessary fonts (esp. tree diagrams, symbols). When you print
or create the PDF file, there is usually an option in your printer
setup to include none, all or just non-standard fonts.  Please make
sure that you select the option of including ALL the fonts.  {\em
  Before sending it, test your {\/\em PDF} by printing it from a
  computer different from the one where it was created}. Moreover,
some word processor may generate very large postscript/PDF files,
where each page is rendered as an image. Such images may reproduce
poorly.  In this case, try alternative ways to obtain the postscript
and/or PDF.  One way on some systems is to install a driver for a
postscript printer, send your document to the printer specifying
``Output to a file'', then convert the file to PDF.

For reasons of uniformity, Adobe's {\bf Times Roman} font should be
used. In \LaTeX2e{} this is accomplished by putting

\begin{quote}
\begin{verbatim}
\usepackage{times}
\usepackage{latexsym}
\end{verbatim}
\end{quote}
in the preamble.

Additionally, it is of utmost importance to specify the {\bf
  US-Letter format} (8.5in $\times$ 11in) when formatting the paper.
When working with {\tt dvips}, for instance, one should specify {\tt
  -t letter}.

Print-outs of the PDF file on US-Letter paper should be identical to the
hardcopy version.  If you cannot meet the above requirements about the
production of your electronic submission, please contact the
publication chairs above  as soon as possible.

\subsection{Layout}
\label{ssec:layout}

Format manuscripts two columns to a page, in the manner these
instructions are formatted. The exact dimensions for a page on US-letter
paper are:

\begin{itemize}
\item Left and right margins: 1 inch
\item Top margin: 1 inch
\item Bottom margin: 1 inch
\item Column width: 3.15 inches
\item Column height: 9 inches
\item Gap between columns: 0.2 inches
\end{itemize}

\noindent Papers should not be submitted on any other paper size. Exceptionally,
authors for whom it is \emph{impossible} to format on US-Letter paper,
may format for \emph{A4} paper. In this case, they should keep the \emph{top}
and \emph{left} margins as given above, use the same column width,
height and gap, and modify the bottom and right margins as necessary.
Note that the text will no longer be centered.

\subsection{The First Page}
\label{ssec:first}

Center the title, author's name(s) and affiliation(s) across both
columns (or, in the case of initial submission, space for the names). 
Do not use footnotes for affiliations.  Do not include the
paper ID number assigned during the submission process. 
Use the two-column format only when you begin the abstract.

{\bf Title}: Place the title centered at the top of the first page, in
a 15 point bold font.  (For a complete guide to font sizes and styles, see Table~\ref{font-table}.)
Long title should be typed on two lines without
a blank line intervening. Approximately, put the title at 1in from the
top of the page, followed by a blank line, then the author's names(s),
and the affiliation on the following line.  Do not use only initials
for given names (middle initials are allowed). Do not format surnames
in all capitals (e.g., ``Bangalore,'' not ``BANGALORE'').  The affiliation should
contain the author's complete address, and if possible an electronic
mail address. Leave about 0.75in between the affiliation and the body
of the first page.

{\bf Abstract}: Type the abstract at the beginning of the first
column.  The width of the abstract text should be smaller than the
width of the columns for the text in the body of the paper by about
0.25in on each side.  Center the word {\bf Abstract} in a 12 point
bold font above the body of the abstract. The abstract should be a
concise summary of the general thesis and conclusions of the paper.
It should be no longer than 200 words.  The abstract text should be in 10 point font.

{\bf Text}: Begin typing the main body of the text immediately after
the abstract, observing the two-column format as shown in 
the present document.  Do not include page numbers.

{\bf Indent} when starting a new paragraph. For reasons of uniformity,
use Adobe's {\bf Times Roman} fonts, with 11 points for text and 
subsection headings, 12 points for section headings and 15 points for
the title.  If Times Roman is unavailable, use {\bf Computer Modern
  Roman} (\LaTeX2e{}'s default; see section \ref{sect:pdf} above).
Note that the latter is about 10\% less dense than Adobe's Times Roman
font.

\subsection{Sections}

{\bf Headings}: Type and label section and subsection headings in the
style shown on the present document.  Use numbered sections (Arabic
numerals) in order to facilitate cross references. Number subsections
with the section number and the subsection number separated by a dot,
in Arabic numerals.

{\bf Citations}: Citations within the text appear
in parentheses as~\cite{Gusfield:97} or, if the author's name appears in
the text itself, as Gusfield~\shortcite{Gusfield:97}. In \LaTeX2e, the former is accomplished using
\verb|\cite| and the latter with \verb|\shortcite| or \verb|\newcite|.
Append lowercase letters to the year in cases of ambiguities.  
Treat double authors as in~\cite{Aho:72}, but write as 
in~\cite{Chandra:81} when more than two authors are involved. 
Collapse multiple citations as in~\cite{Gusfield:97,Aho:72}.

\textbf{References}: Gather the full set of references together under
the heading {\bf References}; place the section before any Appendices,
unless they contain references. Arrange the references alphabetically
by first author, rather than by order of occurrence in the text.
Provide as complete a citation as possible, using a consistent format,
such as the one for {\em Computational Linguistics\/} or the one in the 
{\em Publication Manual of the American 
Psychological Association\/}~\cite{APA:83}.  Use of full names for
authors rather than initials is preferred.  A list of abbreviations
for common computer science journals can be found in the ACM 
{\em Computing Reviews\/}~\cite{ACM:83}.

The \LaTeX{} and Bib\TeX{} style files provided roughly fit the
American Psychological Association format, allowing regular citations, 
short citations and multiple citations as described above.

{\bf Appendices}: Appendices, if any, directly follow the text and the
references (but see above).  Letter them in sequence and provide an
informative title: {\bf Appendix A. Title of Appendix}.

\textbf{Acknowledgment} sections should go as a last (unnumbered) section immediately
before the references.

\subsection{Footnotes}

{\bf Footnotes}: Put footnotes at the bottom of the page. They may
be numbered or referred to by asterisks or other
symbols.\footnote{This is how a footnote should appear.} Footnotes
should be separated from the text by a line.\footnote{Note the
line separating the footnotes from the text.}  Footnotes should be in 9 point font.

\subsection{Graphics}

{\bf Illustrations}: Place figures, tables, and photographs in the
paper near where they are first discussed, rather than at the end, if
possible.  Wide illustrations may run across both columns and should be placed at
the top of a page. Color illustrations are discouraged, unless you have verified that 
they will be understandable when printed in black ink.

\begin{table}
\begin{center}
\begin{tabular}{|l|rl|}
\hline \bf Type of Text & \bf Font Size & \bf Style \\ \hline
paper title & 15 pt & bold \\
author names & 12 pt & bold \\
author affiliation & 12 pt & \\
the word ``Abstract'' & 12 pt & bold \\
section titles & 12 pt & bold \\
document text & 11 pt  &\\
abstract text & 10 pt & \\
captions & 10 pt & \\
bibliography & 10 pt & \\
footnotes & 9 pt & \\
\hline
\end{tabular}
\end{center}
\caption{\label{font-table} Font guide. }
\end{table}

{\bf Captions}: Provide a caption for every illustration; number each one
sequentially in the form:  ``Figure 1. Caption of the Figure.'' ``Table 1.
Caption of the Table.''  Type the captions of the figures and 
tables below the body, using 10 point text.

\subsection{Accessibility}
\label{ssec:accessibility}

In an effort to accommodate the color-blind (as well as those printing
to paper), grayscale readability for all accepted papers will be
enforced.  Color is not forbidden, but authors should ensure that
tables and figures do not rely solely on color to convey critical
distinctions.

\section{Length of Submission}
\label{sec:length}

The NAACL HLT 2015 main conference accepts submissions of long papers
and short papers.  The maximum length of a long paper manuscript is
eight (8) pages of content and two (2) additional pages of references
\emph{only} (appendices count against the eight pages, not the
additional two pages).  The maximum length of a short paper manuscript
is four (4) pages and two (2) additional pages of references.
Accepted papers will be granted an additional content page. For both
long and short papers, all illustrations, references, and appendices
must be accommodated within these page limits, observing the
formatting instructions given in the present document.  Papers that do
not conform to the specified length and formatting requirements are
subject to be rejected without review.

\section{Double-blind review process}
\label{sec:blind}

As the reviewing will be blind, the paper must not include the
authors' names and affiliations.  Furthermore, self-references that
reveal the author's identity, e.g., ``We previously showed (Smith,
1991) ...'' must be avoided. Instead, use citations such as ``Smith
previously showed (Smith, 1991) ...'' Papers that do not conform to
these requirements will be rejected without review. In addition,
please do not post your submissions on the web until after the
review process is complete (in special cases this is permitted: see 
the multiple submission policy below).

We will reject without review any papers that do not follow the
official style guidelines, anonymity conditions and page limits.

\section{Multiple Submission Policy}

Papers that have been or will be submitted to other meetings or
publications must indicate this at submission time. Authors of
papers accepted for presentation at NAACL HLT 2015 must notify the
program chairs by the camera-ready deadline as to whether the paper
will be presented. All accepted papers must be presented at the
conference to appear in the proceedings. We will not accept for
publication or presentation papers that overlap significantly in
content or results with papers that will be (or have been) published
elsewhere.

Preprint servers such as arXiv.org and ACL-related workshops that
do not have published proceedings in the ACL Anthology are not
considered archival for purposes of submission. Authors must state
in the online submission form the name of the workshop or preprint
server and title of the non-archival version.  The submitted version
should be suitably anonymized and not contain references to the
prior non-archival version. Reviewers will be told: ``The author(s)
have notified us that there exists a non-archival previous version
of this paper with significantly overlapping text. We have approved
submission under these circumstances, but to preserve the spirit
of blind review, the current submission does not reference the
non-archival version.'' Reviewers are free to do what they like with
this information.

Authors submitting more than one paper to NAACL HLT must ensure
that submissions do not overlap significantly ($>25\%$) with each other
in content or results. Authors should not submit short and long
versions of papers with substantial overlap in their original
contributions.

\section*{Acknowledgments}

Do not number the acknowledgment section.

\begin{thebibliography}{}

\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
Alfred~V. Aho and Jeffrey~D. Ullman.
\newblock 1972.
\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
\newblock Prentice-{Hall}, Englewood Cliffs, NJ.

\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
{American Psychological Association}.
\newblock 1983.
\newblock {\em Publications Manual}.
\newblock American Psychological Association, Washington, DC.

\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
{Association for Computing Machinery}.
\newblock 1983.
\newblock {\em Computing Reviews}, 24(11):503--512.

\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
\newblock 1981.
\newblock Alternation.
\newblock {\em Journal of the Association for Computing Machinery},
  28(1):114--133.

\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
Dan Gusfield.
\newblock 1997.
\newblock {\em Algorithms on Strings, Trees and Sequences}.
\newblock Cambridge University Press, Cambridge, UK.

\end{thebibliography}

\end{document}

### 2016-03-03 tacl2015_paper/our-cover-letter.tex
adding tacl2015 paper
Former-commit-id: 0d96938966b2ba3d3b01c8b2bbda93814689193d

\title{Cover Letter: \\ Learning a Compositional Semantics for Freebase \\ with an Open
  Predicate Vocabulary}

\documentclass[10pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{mdwlist}

\begin{document}
\maketitle

We appreciate the helpful comments from the reviewers. Our responses
to the three specific changes are listed below:

\begin{itemize*}

\item {\bf Comparison to Reddy et al. (2014):} We have added a
  discussion comparing our approach to this one in Section 8 (Related
  Work). This work is similar to ours in its training data
  generation. It differs from our work in that it uses a closed
  predicate vocabulary -- as do all semantic parsers to
  Freebase. (This difference was acknowledged by the reviewers in
  their original reviews.)

\item {\bf Coverage and Expressivity of Approach:} We have added a
  Discussion (Section 3.4) to the semantic parsing portion of the
  paper describing our system's coverage of linguistic phenomena. Note
  that we have chosen to drop negation from the description of the
  semantic parsing system, as it is (1) confusing to the readers, and
  (2) irrelevant for both the training and evaluation.

\item {\bf Comparing Probabilistic Databases to Possible Worlds
  Semantics:} We have changed our description of the system to use
  possible worlds semantics throughout. Section 2 (System Overview)
  sets up a probabilistic model for the whole system, and Section 4
  (Probabilistic Database) explains how a probabilistic database
  represents a probability distribution over possible worlds. Section
  5 (Inference) has also been improved to explain how the recursive
  query evaluation algorithm is consistent with the possible worlds
  semantics. Finally, Section 8 briefly compares probabilistic
  databases to Markov Logic Networks -- we believe the relationship
  does not require much explanation, given the improved presentation.

\end{itemize*}

We have also made changes based on the additional suggestions of the
reviewers. These are fairly minor changes, but we point them out to
assist in the re-review:

{\bf Reviewer 1}

The changes mentioned above address the comments about the knowledge
represented in the probabilistic database, and the relationship of
probabilistic databases to MLNs. The discussion of
coverage/expressivity also cites Lewis and Steedman (2013). Finally,
Figure 3 now uses human-readable IDs.

% We have not changed the text describing the clustering baseline,
% because the clusters look reasonable on manual inspection. Also, note
% that our training set is approximately 10x larger than the comparable
% work of Riedel et al. (2013).

{\bf Reviewer 2}

The new presentation of the probabilistic database and explicit
discussion of the coverage of our semantic parsing approach should
address many of your concerns. This presentation lays out a general
probabilistic model for thinking about compositional semantics with an
open predicate vocabulary, even though our system only implements a
small piece of it. We also explain the extraction of simplified
logical forms, which we believe also clarifies the ranking objective
explanation. Footnote 4 addresses your suggestion of training with
randomly-generated negative examples (which we tried, and found
performed poorly). Finally, the discussion section now includes a
high-level error analysis.

{\bf Reviewer 3}

Most of your comments should be addressed by the 3 changes
above. Additionally, Table 1 has been clarified as suggested, and the
evaluation discusses how the hyperparameters were selected. Finally,
the discussion section has been considerably improved.

(Also, thanks for the LaTeX tip.)

\end{document}

### 2016-03-03 tacl2015_paper/paper.tex
adding tacl2015 paper
Former-commit-id: 0d96938966b2ba3d3b01c8b2bbda93814689193d

\documentclass[11pt]{article}

\usepackage{acl2012}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage[pdf]{pstricks}
\usepackage{pst-pdf}
\usepackage{pst-plot}
\usepackage{times}
\usepackage{multirow}
\usepackage{latexsym}
\usepackage{soul}
\usepackage{subfig}
\usepackage{stmaryrd}
\usepackage{url}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

\title{Learning a Compositional Semantics for Freebase \\ with an Open
  Predicate Vocabulary}

\author{Jayant Krishnamurthy\\
        Carnegie Mellon University\\
        5000 Forbes Avenue\\
        Pittsburgh, PA 15213\\
	{\tt jayantk@cs.cmu.edu}
	  \And
	Tom M. Mitchell\\
        Carnegie Mellon University\\
        5000 Forbes Avenue\\
        Pittsburgh, PA 15213\\
        {\tt tom.mitchell@cmu.edu}}

\date{}

% Contributions:
% - compositional model of semantics based on universal schema (cite old work)
% - new training objective
% - experimental evaluation
% 
% Introduction:
% 
% - Fixed schema is inherently limiting
% - open / universal is good
%   - need techniques for composition / compositional semantics
% -

\newcommand{\pred}[1]{\textsc{#1}}
% TODO: make this look cleaner!
\newcommand{\ccgsyn}[1]{\mbox{$\it{#1}$}}
\newcommand{\true}{\pred{True}}

\newcommand{\clb}{\textsc{CorpusLookup}}
\newcommand{\cb}{\textsc{Clustering}}
\newcommand{\uspr}{\textsc{Factorization} (\ensuremath{O_P})}
\newcommand{\usqr}{\textsc{Factorization} (\ensuremath{O_Q})}
\newcommand{\epr}{\textsc{Ensemble} (\ensuremath{O_P})}
\newcommand{\eqr}{\textsc{Ensemble} (\ensuremath{O_Q})}
\newcommand{\pden}[1]{\ensuremath{\llbracket #1 \rrbracket_{P}}}

\DeclareMathOperator{\precision}{Prec}
\DeclareMathOperator{\correct}{Correct}

\begin{document}
\maketitle
\begin{abstract}
We present an approach to learning a model-theoretic semantics for
natural language tied to Freebase. Crucially, our approach uses an
open predicate vocabulary, enabling it to produce denotations for
phrases such as ``Republican front-runner from Texas'' whose semantics
cannot be represented using the Freebase schema. Our approach directly
converts a sentence's syntactic CCG parse into a logical form
containing predicates derived from the words in the sentence,
assigning each word a consistent semantics across sentences. This
logical form is evaluated against a learned probabilistic database
that defines a distribution over denotations for each textual
predicate. A training phase produces this probabilistic database using
a corpus of entity-linked text and probabilistic matrix factorization
with a novel ranking objective function. We evaluate our approach on a
compositional question answering task where it outperforms several
competitive baselines. We also compare our approach against manually
annotated Freebase queries, finding that our open predicate vocabulary
enables us to answer many questions that Freebase cannot.

% This approach allows us to learn denotations for tricky words (e.g.,
% ``front-runner'') and compose them to produce denotations for phrases
% (e.g., ``Republican front-runner from Texas''). The use of CCG also
% enables us to model linguistic phenomena such as negation. 
\end{abstract}

\section{Introduction}

Traditional knowledge representation assumes that world knowledge can
be encoded using a closed vocabulary of formal predicates. In recent
years, semantic parsing has enabled us to build compositional models
of natural language semantics using such a closed predicate vocabulary
\cite{zelle1996,zettlemoyer05}. These semantic parsers map natural
language statements to database queries, enabling applications such as
answering questions using a large knowledge base
\cite{yahya12,krishnamurthy2012,cai2013acl,kwiatkowski2013,berant2013,berant2014,reddy2014}. Furthermore,
the model-theoretic semantics provided by such parsers have the
potential to improve performance on other tasks, such as information
extraction and coreference resolution.

However, a closed predicate vocabulary has inherent
limitations. First, its coverage will be limited, as such vocabularies
are typically manually constructed. Second, it may abstract away
potentially relevant semantic differences. For example, the semantics
of ``Republican front-runner'' cannot be adequately encoded in the
Freebase schema because it lacks the concept of a ``front-runner.''
We could choose to encode this concept as ``politician'' at the cost
of abstracting away the distinction between the two. As this example
illustrates, these two problems are prevalent in even the largest
knowledge bases.

\begin{figure*}
\small
\begin{minipage}{0.23\linewidth}\textbf{Input Text}\\Republican front-runner \\ from Texas\end{minipage} ~~ $\rightarrow$ ~~
\begin{minipage}{0.3\linewidth}
\textbf{Logical Form}\\
$\lambda x.\exists y,z. \pred{front-runner}(x) \wedge y=\pred{/en/republican} \wedge \pred{nn}(y,x) \wedge z=\pred{/en/texas} \wedge \pred{from}(x,z)$
\end{minipage} ~~ $\rightarrow$ ~~
\begin{minipage}{0.3\linewidth}
\begin{tabular}{ll}
\textbf{Entity} & \textbf{Prob.} \\
$\pred{/en/george\_bush}$ & 0.57 \\
$\pred{/en/rick\_perry}$ & 0.45 \\
... & \\
\end{tabular}
\end{minipage}

\vspace{-.35in}
\begin{minipage}{0.15\linewidth}
\begin{pspicture}(-0.25,-0.4)(4.2,3.6)
\scalebox{0.8}{

\psframe(1,0)(2,2)
\psframe(2.2,1)(4.2,2)
\rput(1.5, 1){$\phi$}
\rput(3.2, 1.5){$\theta$}

\rput[rt](0.95,1.85){{\small \pred{ texas}}}
\rput[rt](0.95,1.35){{\small \pred{ repub.}}}
\rput[rt](0.95,0.85){{\small \pred{ g.\_bush}}}
\rput[rt](0.95,0.35){{\small \pred{ ...}}}

\rput[lb]{60}(2.4,2){{\small \pred{f.-run.}}}
\rput[lb]{60}(2.9,2){{\small \pred{pol.}}}
\rput[lb]{60}(3.4,2){{\small \pred{state}}}
\rput[lb]{60}(3.9,2){{\small \pred{...}}}

\rput[l](0,-0.3){\large \textbf{Entity/Predicate Embeddings}}
}
\end{pspicture}
\end{minipage}
\begin{minipage}{0.35\linewidth}
\begin{pspicture}(-2.7,-0.4)(4.7,3.6)
\scalebox{0.8}{

\psframe(1,0)(2,2)
\psframe(2.2,1)(4.2,2)
\rput(1.5, 1){$\phi$}
\rput(3.2, 1.5){$\theta$}

\rput[rt](0.95,1.85){{\small (\pred{g.\_bush}, \pred{ texas})}}
\rput[rt](0.95,1.35){{\small (\pred{g.\_bush}, \pred{ repub.})}}
\rput[rt](0.95,0.85){{\small (\pred{repub.}, \pred{ g.\_bush})}}
\rput[rt](0.95,0.35){{\small \pred{...}}}

\rput[lb]{60}(2.4,2){{\small \pred{from}}}
\rput[lb]{60}(2.9,2){{\small \pred{lives\_in}}}
\rput[lb]{60}(3.4,2){{\small \pred{nn}}}
\rput[lb]{60}(3.9,2){{\small \pred{...}}}

\rput(4.6,1.5){$\rightarrow$}
}
\end{pspicture}
\end{minipage}
\begin{minipage}{0.15\linewidth}
\begin{pspicture}(-1,-0.4)(8,3.6)
\scalebox{0.8}{

\psframe(1,0)(3,2)
\psline(1,0.5)(3,0.5)
\psline(1,1)(3,1)
\psline(1,1.5)(3,1.5)
\psline(1.5,0)(1.5,2)
\psline(2,0)(2,2)
\psline(2.5,0)(2.5,2)

\rput[rt](0.95,1.85){{\small \pred{ texas}}}
\rput[rt](0.95,1.35){{\small \pred{ repub.}}}
\rput[rt](0.95,0.85){{\small \pred{ g.\_bush}}}
\rput[rt](0.95,0.35){{\small \pred{ ...}}}

\rput[lb]{60}(1.3,2){{\small \pred{f.-run.}}}
\rput[lb]{60}(1.8,2){{\small \pred{pol.}}}
\rput[lb]{60}(2.3,2){{\small \pred{state}}}
\rput[lb]{60}(2.8,2){{\small \pred{...}}}

\rput[c](1.25,1.75){{\small .1}}
\rput[c](1.25,1.25){{\small .1}}
\rput[c](1.25,0.75){{\small .9}}

\rput[c](1.75,1.75){{\small .1}}
\rput[c](1.75,1.25){{\small .1}}
\rput[c](1.75,0.75){{\small .9}}

\rput[c](2.25,1.75){{\small .8}}
\rput[c](2.25,1.25){{\small .1}}
\rput[c](2.25,0.75){{\small .1}}

\rput[l](0,-0.3){\large \textbf{Probabilistic Database}}

% \psline[linewidth=0.5pt](3.4,1.5)(6.5,1.5)
% \psline[linewidth=0.5pt]{->}(6.5,1.5)(6.5,3.7)
}
\end{pspicture}
\end{minipage}
\begin{minipage}{0.2\linewidth}
\begin{pspicture}(-2.5,-0.4)(8,3.6)
\scalebox{0.8}{

\psframe(1,0)(3,2)
\psline(1,0.5)(3,0.5)
\psline(1,1)(3,1)
\psline(1,1.5)(3,1.5)
\psline(1.5,0)(1.5,2)
\psline(2,0)(2,2)
\psline(2.5,0)(2.5,2)

\rput[rt](0.95,1.85){{\small (\pred{g.\_bush}, \pred{ texas})}}
\rput[rt](0.95,1.35){{\small (\pred{g.\_bush}, \pred{ repub.})}}
\rput[rt](0.95,0.85){{\small (\pred{repub.}, \pred{ g.\_bush})}}
\rput[rt](0.95,0.35){{\small \pred{ ...}}}

\rput[lb]{60}(1.3,2){{\small \pred{from}}}
\rput[lb]{60}(1.8,2){{\small \pred{lives\_in}}}
\rput[lb]{60}(2.3,2){{\small \pred{nn}}}
\rput[lb]{60}(2.8,2){{\small \pred{...}}}

\rput[c](1.25,1.75){{\small .9}}
\rput[c](1.25,1.25){{\small .1}}
\rput[c](1.25,0.75){{\small .1}}

\rput[c](1.75,1.75){{\small .9}}
\rput[c](1.75,1.25){{\small .1}}
\rput[c](1.75,0.75){{\small .1}}

\rput[c](2.25,1.75){{\small .1}}
\rput[c](2.25,1.25){{\small .1}}
\rput[c](2.25,0.75){{\small .7}}

% \psline[linewidth=0.5pt](3.4,1.5)(6.5,1.5)
% \psline[linewidth=0.5pt]{->}(6.5,1.5)(6.5,3.7)
\psline[linewidth=0.5pt]{->}(-0.5,2.8)(-0.5,3.2)

}
\end{pspicture}
\end{minipage}
\vspace{-.1in}
\caption{Overview of our approach. Top left: the text is converted to
  logical form by CCG syntactic parsing and a collection of
  manually-defined rules. Bottom: low-dimensional embeddings of each
  entity (entity pair) and category (relation) are learned from an
  entity-linked web corpus. These embeddings are used to construct a
  probabilistic database. The labels of these matrices are shortened
  for space reasons. Top right: evaluating the logical form on the
  probabilistic database computes the marginal probability that each
  entity is an element of the text's denotation.}
\label{fig:overview}
\vspace{-.1in}
\end{figure*}

An alternative paradigm is an \emph{open} predicate vocabulary, where
each natural language word or phrase is given its own formal
predicate. This paradigm is embodied in both open information
extraction \cite{banko2007} and universal schema
\cite{riedel2013}. Open predicate vocabularies have the potential to
capture subtle semantic distinctions and achieve high
coverage. However, we have yet to develop compelling approaches to
compositional semantics within this paradigm.

% An alternative approach is \emph{open information extraction}, which
% treats every natural language word or phrase as its own formal
% predicate \cite{banko2007}. Another closely related approach is
% \emph{universal schema}, which joins these natural language predicates
% with formal predicates \cite{riedel2013}. 
% In these approaches, the knowledge representation has an open
% predicate vocabulary that is determined by the textual expressions in
% a corpus.

This paper takes a step toward compositional semantics with an open
predicate vocabulary. Our approach defines a distribution over
denotations (sets of Freebase entities) given an input text.  The
model has two components, shown in Figure \ref{fig:overview}. The
first component is a rule-based semantic parser that uses a syntactic
CCG parser and manually-defined rules to map entity-linked texts to
logical forms containing predicates derived from the words in the
text. The second component is a probabilistic database with a possible
worlds semantics that defines a distribution over denotations for each
textually-derived predicate. This database assigns independent
probabilities to individual predicate instances, such as
$P(\pred{front-runner}(\pred{/en/george\_bush})) = 0.9$. Together,
these components define an exponentially-large distribution over
denotations for an input text; to simplify this output, we compute the
marginal probability, over all possible worlds, that each entity is an
element of the text's denotation.

% A training phase estimates parameters for the probabilistic database
% using probabilistic matrix factorization with a novel query/answer
% ranking objective. The training data is derived by analyzing a corpus
% of entity-linked sentences with the rule-based semantic analysis
% system, producing a collection logical form queries with observed
% entity answers. The query/answer ranking objective, when optimized,
% trains the database to rank the observed answers for each query above
% unobserved answers. The matrix factorization learns a low-dimensional
% embedding of each entity (entity pair) and category (relation) such
% that the denotation of a predicate is likely to contain entities or
% entity pairs with nearby vectors.

The learning problem in our approach is to train the probabilistic
database to predict a denotation for each predicate. We pose this
problem as probabilistic matrix factorization with a novel
query/answer ranking objective. This factorization learns a
low-dimensional embedding of each entity (entity pair) and category
(relation) such that the denotation of a predicate is likely to
contain entities or entity pairs with nearby vectors. To train the
database, we first collect training data by analyzing entity-linked
sentences in a large web corpus with the rule-based semantic
parser. This process generates a collection of logical form queries
with observed entity answers. The query/answer ranking objective, when
optimized, trains the database to rank the observed answers for each
query above unobserved answers.

% Given a learned probabilistic database, Figure \ref{fig:overview}
% illustrates the process of predicting a denotation for a text. First,
% the semantic analysis system produces a logical form for the given
% text (top left). Next, this logical form is evaluated against the
% learned probabilistic database to produce a list of entities ranked by
% probability, similar to existing semantic parsing techniques (top
% right). Each predicate instance's probability in the database is
% determined by the low-dimensional embeddings learned by matrix
% factorization (bottom left).

% pose this problem as
% probabilistic matrix factorization with a novel ranking
% objective. First, we collect training data, in the form of true
% assertions about Freebase entities found in a large web corpus. We
% then automatically generate query-answer pairs from these assertions
% and train the database to rank  Training produces a vector embedding of each
% predicate and entity such that the denotation of a predicate is likely
% to contain entities with nearby vectors.
% 
% 
% An initial training phase uses the semantic analysis component and a
% large entity-linked corpus to learn parameters for the probabilistic
% database,  The set of categories and
% relations is automatically derived from the words in the training
% data.

% The denotation of a text is computed in three
% steps.  (Embeddings of entity pairs and relation
% predicates are also learned, but not shown in the Figure for space
% reasons.) Second, given a text, a rule based-semantic analysis system
% produces a logical form. 
% 
% Our approach represents world knowledge in a
% probabilistic database over textually-derived predicates and Freebase
% entities. To semantically analyze a natural language statement, we use a
% rule-based approach to transform its syntactic CCG parse into a query
% against this database. Evaluating the query produces a ranked list of
% Freebase entity answers,

% We train the database using a data set of true assertions about
% Freebase entities collected from a large web corpus. , or learning
% embeddings for each predicated and entity that assign high probability
% to the observed assertions.

%  Our approach first uses a CCG-based semantic analysis system
% to identify assertions about Freebase entities, resulting in a sparse
% collection of observed predicate instances. Our approach then
% generalizes from the observed predicate instances using probabilistic
% matrix factorization (TODO: cite). We introduce a novel training
% objective that encourages the learned parameters to correctly answer
% compositional natural language queries.

We evaluate our approach on a question answering task, finding that
our approach outperforms several baselines and that our new training
objective improves performance over a previously-proposed
objective. We also evaluate the trade-offs between open and closed
predicate vocabularies by comparing our approach to a
manually-annotated Freebase query for each question. This comparison
reveals that, when Freebase contains predicates that cover the
question, it achieves higher precision and recall than our
approach. However, our approach can correctly answer many questions
not covered by Freebase.

% The contributions of this work are threefold:
% \begin{enumerate} 
% \item An approach to compositional semantics with an open predicate
%   vocabulary that uses probabilistic matrix factorization to produce
%   the underlying knowledge representation.
% 
% \item A novel query/answer ranking objective for the matrix
%   factorization that improves performance over a previously-proposed
%   objective.
% 
% \item An experimental evaluation on a question answering task that
%   highlights the advantages and disadvantages of open and closed
%   predicate vocabularies.
% \end{enumerate}

% (TODO: key challenges to semantic analysis: (1) ability to represent
% phenomena like negation, etc. (2) synonymy)

% \section{Overview}
% 
% This paper is structured as follows. Section \ref{sec:rule} describes
% the rule-based semantic analysis system, which is used to generate
% training data for the probabilistic database. Section \ref{sec:probdb}
% describes the probabilistic database, our matrix factorization model
% and our training algorithm. Section \ref{sec:evaluation} describes our
% experimental evaluation, Section \ref{sec:priorwork} describes prior
% work, and Section \ref{sec:discussion} concludes.

\section{System Overview}

The purpose of our system is to predict a denotation $\gamma$ for a
given natural language text $s$. The denotation $\gamma$ is the set of
Freebase entities that $s$ refers to; for example, if
$s=\mbox{``president of the US,''}$ then $\gamma = \{\pred{/en/Obama},
\pred{/en/Bush}, ... \}$.\footnote{This paper uses a simple
  model-theoretic semantics where the denotation of a noun phrase is a
  set of entities and the denotation of a sentence is either true or
  false. However, for notational convenience, denotations $\gamma$
  will be treated as sets of entities throughout.} Our system
represents this prediction problem using the following probabilistic
model:
\begin{eqnarray*}
P(\gamma | s) = \sum_w \sum_\ell P(\gamma | \ell, w) P(w) P(\ell | s) 
\end{eqnarray*}

The first term in this factorization, $P(\ell | s)$, is a distribution
over logical forms $\ell$ given the text $s$. This term
corresponds to the rule-based semantic parser (Section
\ref{sec:rule}). This semantic parser is deterministic, so this term
assigns probability 1 to a single logical form for each text. The
second term, $P(w)$, represents a distribution over possible worlds,
where each world is an assignment of truth values to all possible
predicate instances. The distribution over worlds is represented by a
probabilistic database (Section \ref{sec:probdb}). The final term,
$P(\gamma | \ell, w)$, deterministically evaluates the logical form
$\ell$ on the world $w$ to produce a denotation $\gamma$. This term
represents query evaluation against a fixed database, as in other work
on semantic parsing.

Section \ref{sec:inference} describes inference in our model. To
produce a ranked list of entities (Figure \ref{fig:overview}, top
right) from $P(\gamma | s)$, our system computes the marginal
probability that each entity is an element of the denotation
$\gamma$. This problem corresponds to query evaluation in a
probabilistic database, which is known to be tractable in many cases
\cite{suciu2011probabilistic}.

Section \ref{sec:training} describes training, which estimates
parameters for the probabilistic database $P(w)$. This step first
automatically generates training data using the rule-based semantic
parser. This data is used to formulate a matrix factorization problem
that is optimized to estimate the database parameters.

% In our approach, only
% the probabilistic database $P(w)$ must be learned. Training data, in
% the form of logical forms with fully-observed entity arguments, is
% automatically generated by applying the open-vocabulary semantic
% parser to entity-linked text. The probabilistic database is
% parameterized as a matrix factorization model, and is trained by
% optimizing a ranking objective using stochastic gradient descent.

% Note that this probabilistic model is the exact opposite of the
% traditional semantic parsing model. Traditionally, $P(\ell | s)$ is
% learned, and $P(W)$ is a point distribution. Our system is exactly the
% opposite, using a \emph{deterministic} semantic parser and a
% \emph{learned} database.

\section{Rule-Based Semantic Parser}
\label{sec:rule}

The first part of our compositional semantics system is a rule-based
system that deterministically computes a logical form $\ell$ for a
text $s$. This component is used during inference to analyze the
logical structure of text, and during training to generate training
data (see Section \ref{sec:trainingdata}).  Several input/output pairs
for this system are shown in Figure \ref{fig:examplesem}.

The conversion to logical form has 3 phases:

\begin{enumerate}
\item \textbf{CCG syntactic parsing} parses the text and applies
  several deterministic syntactic transformations to facilitate
  semantic analysis.
\item \textbf{Entity linking} marks known Freebase entities in the
  text.
\item \textbf{Semantic analysis} assigns a logical form to each word,
  then composes them to produce a logical form for the complete text.
\end{enumerate}

\subsection{Syntactic Parsing}

The first step in our analysis is to syntactically parse the text. We
use the \textsc{ASP-SYN} parser \cite{krishnamurthy2014} trained on
CCGBank \cite{hockenmaier02ccgbank}. We then automatically transform
the resulting syntactic parse to make the syntactic structure more
amenable to semantic analysis. This step marks \ccgsyn{NP}s in
conjunctions by replacing their syntactic category with
\ccgsyn{NP[\mbox{conj}]}. This transformation allows semantic analysis to
distinguish between appositives and comma-separated lists. It also
transforms all verb arguments to core arguments, i.e., using the
category \ccgsyn{PP/NP} as opposed to \ccgsyn{((S\backslash
  NP)\backslash (S\backslash NP))/NP}. This step simplifies the
semantic analysis of verbs with prepositional phrase arguments. The
final transformation adds a word feature to each \ccgsyn{PP} category,
e.g., mapping \ccgsyn{PP} to \ccgsyn{PP[\mbox{by}]}. These features are used
to generate verb-preposition relation predicates, such as
$\pred{directed\_by}$.

\subsection{Entity Linking}

The second step is to identify mentions of Freebase entities in the
text. This step could be performed by an off-the-shelf entity linking
system \cite{ratinov2011,milne2008} or string matching. However, our
training and test data is derived from Clueweb 2009, so we rely on the
entity linking for this corpus provided by Gabrilovich et. al
\shortcite{gabrilovich2013}.

Our system incorporates the provided entity links into the syntactic
parse provided that they are consistent with the parse
structure. Specifically, we require that each mention is either (1) a
constituent in the parse tree with syntactic category $N$ or $NP$ or
(2) a collection of $N/N$ or $NP/NP$ modifiers with a single head
word. The first case covers noun and noun phrase mentions, while the
second case covers noun compounds. In both cases, we substitute a
single multi-word terminal into the parse tree spanning the mention
and invoke special semantic rules for mentions described in the next
section.

\subsection{Semantic analysis}

The final step uses the syntactic parse and entity links to produce a
logical form for the text. The system induces a logical form for every
word in the text based on its syntactic CCG category. Composing these
logical forms according to the syntactic parse produces a logical form
for the entire text.

\begin{figure}
{\small
\ul{Dan Hesse}, CEO of \ul{Sprint} \\
$\lambda x.\exists y.x = \pred{/en/dan\_hesse} \wedge \pred{ceo}(x) \wedge \pred{of}(x, y) \wedge y = \pred{/en/sprint}$ \\

\ul{Yankees} pitcher \\
$\lambda x.\exists y.\pred{pitcher}(x) \wedge \pred{nn}(y, x) \wedge y = \pred{/en/yankees}$ \\

\ul{Tom Cruise} plays \ul{Maverick} in the movie \ul{Top Gun}. \\
$\exists x,y,z. x = \pred{/en/tom\_cruise} \wedge \pred{plays}(x,
y) \wedge y = \pred{/en/maverick\_(character)} \wedge \pred{plays\_in}(x, z) \wedge z
= \pred{/en/top\_gun} $
}
\vspace{-.1in}
\caption{Example input/output pairs for our semantic analysis
  system. Mentions of Freebase entities in the text are indicated by
  underlines.}
\vspace{-.1in}
\label{fig:examplesem}
\end{figure}

Our semantic analyses are based on a relatively na\"ive
model-theoretic semantics. We focus on language whose semantics can be
represented with existentially-quantified conjunctions of unary and
binary predicates, ignoring, for example, temporal scope and
superlatives. Generally, our system models nouns and adjectives as
unary predicates, and verbs and prepositions as binary
predicates. Special multi-word predicates are generated for
verb-preposition combinations. Entity mentions are mapped to the
mentioned entity in the logical form. We also created special rules
for analyzing conjunctions, appositives, and relativizing
conjunctions. The complete list of rules used to produce these logical
forms is available
online.\footnote{\url{http://rtw.ml.cmu.edu/tacl2015_csf}}

We made several notable choices in designing this component. First,
multi-argument verbs are analyzed using pairwise relations, as in the
third example in Figure \ref{fig:examplesem}. This analysis allows us
to avoid reasoning about entity triples (quadruples, etc.), which are
challenging for the matrix factorization due to sparsity. Second,
noun-preposition combinations are analyzed as a category and relation,
as in the first example in Figure \ref{fig:examplesem}. We empirically
found that combining the noun and preposition in such instances
resulted in worse performance, as it dramatically increased the
sparsity of training instances for the combined relations.
% Furthermore, in many
% cases our analysis is more reasonable than the combined analysis; for
% example, ``Dan Hesse of Sprint'' is an acceptable statement given the
% first example in Figure \ref{fig:examplesem}.
Third, entity mentions with the $\ccgsyn{N/N}$ category are analyzed
using a special noun-noun relation, as in the second example in Figure
\ref{fig:examplesem}. Our intuition is that this relation shares
instances with other relations (e.g., ``city in Texas'' implies
``Texan city''). Finally, we lowercased each word to create its
predicate name, but performed no lemmatization or other normalization.

\subsection{Discussion}

The scope of our semantic analysis system is somewhat limited relative
to other similar systems \cite{bos2008,lewis2013} as it only outputs
existentially-quantified conjunctions of predicates. Our goal in
building this system was to analyze noun phrases and simple sentences,
for which this representation generally suffices. The reason for this
focus is twofold. First, this subset of language is sufficient to
capture much of the language surrounding Freebase entities. Second,
for various technical reasons, this restricted semantic representation
is easier to use (and more informative) for training the probabilistic
database (see Section \ref{sec:qro}).

% This semantic analysis system may appear somewhat na\"ive in
% comparison to other similar systems \cite{bos2008,lewis2013}, as it
% does not even attempt to model many linguistic phenomena (TODO:
% example). Our goal in building this system was to analyze noun phrases
% and simple sentences, for which it produces reasonable analyses.
% There are many reasons for this emphasis. First, these are the kinds
% of constructions in which Freebase entities appear. Second, it makes
% sense to evaluate a new approach to compositional semantics on
% (relatively) simple language. Third, complex logical forms are less
% useful for training. Fourth, the current version of our probabilistic
% database learning is restricted to categories and relations. TODO:
% existentially quantified conjunctions of predicates.

Note that this system can be straightforwardly extended to model
additional linguistic phenomena, such as additional logical operators
and generalized quantifiers, by writing additional rules. The
semantics of logical forms including these operations are well-defined
in our model, and the system does not even need to be re-trained to
incorporate these additions.

% We demonstrate this capability by adding additional rules for
% negation (TODO).

% TODO: Describe the scope / intended coverage of this system. Cite
% BOxer / lewis and steedman. Explicitly discuss quantifiers (e.g., 5
% movies). Formal logical restrictions and size of l.f.s (can reference
% later table).

% The
% semantics of more complex logical forms,  are well-defined by the probabilistic database
% 
% The
% focus of this paper, however, is on evaluating the combination of a
% compositional semantics
% 
% Prior work has clearly demonstrated that more sophisticated systems
% are possible.
% 
% Thus,  If 
% 
% Our goal in building this system is not to produce a complete,
% logically accurate semantic analysis of language, but rather a good
% enough analysis for the purpose of evaluating our compositional
% semantics approach.
% 
% This semantic analysis system is somewhat na\"ive
% 
% The focus of this semantic analysis system is on analyzing noun
% phrases and simple sentences. 
% 
% The output of this semantic analysis system is, typically, an
% existentially-quantified conjunction of predicates. Although this
% representation may seem fairly limited, it is sufficient for the types
% of language we expect to be able to analyze. 
% 
% Despite the open predicate vocabulary, the
% denotations of many words cannot be accurately represented as sets of
% Freebase entities.
% 
% Note that this system can be extended quite easily with additional
% rules for generalized quantifiers (e.g, ``5 movies''). To verify this,
% we annotated a rule for a simple kind of negation (TODO: demo?).
% 
% The design of this semantic analysis system is influenced by the kinds
% of language we expect to encounter 
% 
% Our goals in designing this semantic analysis system were 
% 
% 
%  A simple form of negation was included for the sole purpose
% of demonstrating that
% 
% The intended scope of this semantic analysis system is quite limited:
% it focuses on analyzing noun phrases and simple sentences with
% verbs. 
% 
% Generalized quantifiers
% 
% Although this semantic analysis system is not very sophisticated, it
% is sufficient for the purposes of this paper. Specifically, not all
% language can be semantically represented using
% 
% During training, it is much more efficient to 
% 
% Other systems for converting syntactic CCG parses to logical form are
% considerably more sophisticated than ours \cite{bos2008,lewis2013}.
%

% Note that we make no attempt to analyze negation or quantifiers
% (outside of conjunctions). These phenomena could be included in our
% analysis by annotating special logical forms for a small subset of
% words, such as ``not.'' We found that such quantifiers were
% empirically not very common in our evaluation, and thus we chose not
% to annotate them. Complexly quantified statements would also be
% omitted from the probabilistic database training, so there is little
% consequence in omitting these entries.

\section{Probabilistic Database}
\label{sec:probdb}

The second part of our compositional semantics system is a
probabilistic database. This database represents a distribution over
\emph{possible worlds}, where each world is an assignment of truth
values to every predicate instance. Equivalently, the probabilistic
database can be viewed as a distribution over databases or knowledge
bases.

    % In traditional semantic parsing, a
   % logical form can be evaluated against a world to produce a
  % denotation. Evaluating a logical form against a probabilistic database
 % produces a \emph{distribution} over denotations.

Formally, a probabilistic database is a collection of random
variables, each of which represents the truth value of a single
predicate instance. Given entities $e \in E$, categories $c \in C$,
and relations $r \in R$ the probabilistic database contains boolean
random variables $c(e)$ and $r(e_1, e_2)$ for each category and
relation instance, respectively. All of these random variables are
assumed to be independent. Let a world $w$ represent an assignment of
truth values to all of these random variables, where $c(e) = w_{c,e}$
and $r(e_1, e_2) = w_{r, e_1, e_2}$. By independence, the probability
of a world can be written as:
\begin{eqnarray*}
P(w) & = & \prod_{e \in E} \prod_{c \in C} P( c(e) = w_{c,e}) \times \\
 & & \prod_{e_1\in E} \prod_{e_2 \in E} \prod_{r \in R} P(r(e_1, e_2) = w_{r, e_1, e_2})
\end{eqnarray*}

The next section discusses how probabilistic matrix factorization is
used to model the probabilities of these predicate instances.

\subsection{Matrix Factorization Model}

The probabilistic matrix factorization model treats the truth of each
predicate instance as an independent boolean random variable that is
true with probability:
\begin{eqnarray*}
P( c(e) = \true{}) & = & \sigma ( \theta_c^T \phi_e ) \\
P( r(e_1,e_2) = \true{}) & = & \sigma ( \theta_r^T \phi_{(e_1,e_2)} )
\end{eqnarray*}

Above, $\sigma (x) = \frac{e^x}{1 + e^x}$ is the logistic function. In
these equations, $\theta_c$ and $\theta_r$ represent $k$-dimensional
vectors of per-predicate parameters, while $\phi_e$ and $\phi_{(e_1,
  e_2)}$ represent $k$-dimensional vector embeddings of each entity
and entity pair. This model contains a low-dimensional embedding of
each predicate and entity such that each predicate's denotation has a
high probability of containing entities with nearby vectors. The
probability that each variable is false is simply 1 minus the
probability that it is true.

This model can be viewed as matrix factorization, as depicted in
Figure \ref{fig:overview}. The category and relation instance
probabilities can be arranged in a pair of matrices of dimension $|E|
\times |C|$ and $|E|^2 \times |R|$. Each row of these matrices
represents an entity or entity pair, each column represents a category
or relation, and each value is between 0 and 1 and represents a truth
probability (Figure \ref{fig:overview}, bottom right). These two
matrices are factored into matrices of size $|E| \times k$ and $k
\times |C|$, and $|E|^2 \times k$ and $k \times |R|$, respectively,
containing $k$-dimensional embeddings of each entity, category, entity
pair and relation (Figure \ref{fig:overview}, bottom left). These
low-dimensional embeddings are represented by the parameters $\phi$
and $\theta$.

% In the first equation above, $\theta$ is a $|C| \times k$ matrix
% containing a $k$-dimensional vector embedding $\theta_c$ for each
% category $c$, and $\phi$ an $|E| \times k$ matrix containing a
% $k$-dimensional vector embedding $\phi_e$ for each entity $e$. The
% $\theta$ and $\phi$ matrices are defined analogously for relations and
% entity pairs in the second equation.

\section{Inference: Computing Marginal Probabilities}
\label{sec:inference}

Inference computes the marginal probability, over all possible worlds,
that each entity is an element of a text's denotation. In many cases
-- depending on the text -- these marginal probabilities can be
computed exactly in polynomial time.

The inference problem is to calculate $P(e \in \gamma | s)$ for each
entity $e$. Because both the semantic parser $P(\ell | s)$ and query
evaluation $P(\gamma | \ell, w)$ are deterministic, this problem can
be rewritten as:
\begin{eqnarray*}
P(e \in \gamma | s) & = & \sum_\gamma \textbf{1}(e \in \gamma) P(\gamma | s) \\
% & = & \sum_\gamma \sum_w \textbf{1}(e \in \gamma) P(\gamma | \ell, w) P(w)  \\
& = & \sum_w \textbf{1}(e \in \llbracket \ell \rrbracket_w) P(w) 
\end{eqnarray*}

Above, $\ell$ represents the logical form for the text $s$ produced by
the rule-based semantic parser, and \textbf{1} represents the
indicator function. The notation $\llbracket \ell \rrbracket_w$
represents denotation produced by (deterministically) evaluating the
logical form $\ell$ on world $w$. This inference problem corresponds
to query evaluation in a probabilistic database, which is \#P-hard in
general. Intuitively, this problem can be difficult because $P(\gamma
| s)$ is a joint distribution over sets of entities that can be
exponentially large in the number of entities.

However, a large subset of probabilistic database queries, known as
\emph{safe} queries, permit polynomial time evaluation
\cite{dalvi2007}. Safe queries can be evaluated extensionally using a
probabilistic notion of a denotation that treats each entity as
independent. Let $\pden{ \ell }$ denote a probabilistic denotation,
which is a function from entities (or entity pairs) to probabilities,
i.e., $\pden{ \ell }(e) \in [0, 1]$. The denotation of a
logical form is then computed recursively, in the same manner as a
non-probabilistic denotation, using probabilistic extensions of the
typical rules, such as:
\begin{eqnarray*}
\pden{c}(e) & = & \sum_w P(w) \textbf{1}(w_{c,e}) \\
\pden{r}(e_1, e_2) & = & \sum_w P(w) \textbf{1}(w_{r,e_1,e_2}) \\
\pden{c_1(x) \wedge c_2(x)}(e) & = & \pden{ c_1 }(e) \times \pden{ c_2 }(e) \\
\pden{\exists y.r(x, y)}(e) & = & 1 - \prod_{y \in E} (1 - \pden{r}(e, y)) \\
% P_{ext}(c_1(e_1) \wedge r(e_1, e_2)) & = & P(c(e_1)) \times P(r(e_1, e_2)) \\
% P_{ext}(\exists y.r(e, y)) & = & ( 1 - \prod_{y \in E} [1 -  P(\pred{of}(e, y)) \times P(\pred{company}(y))]) \\
\end{eqnarray*}

The first two rules are base cases that simply retrieve predicate
probabilities from the probabilistic database. The remaining rules
compute the probabilistic denotation of a logical form from the
denotations of its parts.\footnote{This listing of rules is partial as
  it does not include, e.g., negation or joins between one-argument
  and two-argument logical forms. However, the corresponding rules are
  easy to derive.} The formula for the probabilistic computation on
the right of each of these rules is a straightforward consequence of
the (assumed) independence of entities. For example, the last rule
computes the probability of an \pred{or} of a set of independent
random variables (indexed by $y$) using the identity $A \vee B = \neg
(\neg A \wedge \neg B)$. For safe queries, $\pden{ \ell }(e) = P(e \in
\gamma | s)$, that is, the probabilistic denotation computed according
to the above rules \emph{is equal to} the marginal probability
distribution. In practice, all of the queries in the experiments are
safe, because they contain only one query variable and do not contain
repeated predicates. For more information on query evaluation in
probabilistic databases, we refer the reader to Suciu et
al. \shortcite{suciu2011probabilistic}.

% To evaluate a safe query, one first creates a query
% plan that determines the intermediate sets of entities to create. For
% example, to evaluate, $\lambda x. \exists y. \pred{ceo}(x) \wedge
% \pred{of}(x, y) \wedge \pred{company}(y)$, we can first evaluate
% $\lambda x,y.\pred{of}(x, y) \wedge \pred{company}(y)$ to get a set of
% entity pairs. Next, we quantify out $y$ to get the set of entities for
% $\lambda x.\exists y.\pred{of}(x, y) \wedge
% \pred{company}(y)$. Finally, we join this with $\lambda
% x.\pred{ceo}(x)$ to get the final result.
% 
% The fundamental idea of safe query evaluation is to approximate the
% joint distributions over sets of entities with
% 
% 
% 
% Evaluating a probabilistic database query can be
% intractable because $P(\gamma | s)$ is a distribution over \emph{sets}
% of entities, which can be exponentially large in the number of
% entities. However, this distribution often factors such that the set
% membership of each entity is independent. Safe queries are those for
% which treating this distribution as if it factors results in the
% correct marginal probabilities.
% 
% \begin{figure}
% \begin{pspicture}(0,0)(7,5)
% \psframe(0.5,3.5)(1,4.5)
% \psframe(0.5,3.5)(1,4.5)
% \end{pspicture}
% \end{figure}
% 
% Safe queries can be evaluated similarly to standard database queries
% by maintaining additional probability tables for each intermediate
% result. Consider the logical form $\lambda x. \exists y. \pred{ceo}(x)
% \wedge \pred{of}(x, y) \wedge \pred{company}(y)$. The probabilistic
% database gives us a table of probabilities for each predicate,
% $P_{ext}(\pred{company}(e))$, etc.
% 
% for each predicate
% and intermediate result in the computation. , for each predicate or
% intermediate recursively by maintaining a list of probabilities
%

% TODO: marginal probabilities can also be approximated quite accurately for unsafe queries.

% These queries can be
% evaluated using simple recursive probability computations. For
% example, an entity $e$ is in the denotation of $\lambda
% x.\pred{ceo}(x) \wedge \pred{of}(x, \pred{/en/sprint})$ with
% probability $P(\pred{ceo}(e)) \times P(\pred{of}(e,
% \pred{/en/sprint}))$. Queries with existential (universal) quantifiers
% can also be handled by computing an \pred{or} (\pred{and}) over all
% possible entity values of the quantified variable. For example, an
% entity $e$ is in the denotation of $\lambda x. \exists
% y. \pred{ceo}(x) \wedge \pred{of}(x, y) \wedge \pred{company}(y)$ with
% probability $P(\pred{ceo}(e)) \times ( 1 - \prod_{y \in E} [1 -
%   P(\pred{of}(e, y)) \times P(\pred{company}(y))])$; this expression
% computes the \pred{or} over entities $y$ using the identity $A \vee B
% = \neg (\neg A \wedge \neg B)$.

Note that inference does not compute the most probable denotation,
$\max_\gamma P(\gamma | s)$. In some sense, the most probable
denotation is the correct output for a model-theoretic
semantics. However, it is highly sensitive to the probabilities in the
database, and in many cases it is empty (because a conjunction of
independent boolean random variables is unlikely to be
true). Producing a ranked list of entities is also useful for
evaluation purposes.

% 
% 
% \begin{eqnarray*}
% P(\gamma | s) = \sum_w \sum_\ell P(\gamma | \ell, w) P(w) P(\ell | s) 
% \end{eqnarray*}
% 
% 
% Consider query evaluation against a fixed world (database) $W$ as in
% traditional semantic parsing. A logical form $\ell$ can be
% deterministically evaluated against this world to return a denotation
% $\gamma$. This process is traditionally written as 
% 
% In the probabilistic case, there is no longer a single world, but
% rather a distribution $P(W)$ over possible worlds. However, logical
% forms can be evaluated against each possible world in the same fashion
% as above, producing a distribution over denotations:
% 
% \begin{eqnarray*}
% P(\gamma | \ell ; \theta, \phi) & = & \sum_W P( \gamma | \ell, W) P(W ; \theta, \phi) \\
%  & = & \sum_W \textbf{1}(\gamma = \llbracket \ell \rrbracket_W) P(W ; \theta, \phi) \\
% \end{eqnarray*}
% 
% Above, \textbf{1} represents the indicator function. The conditional
% probability distribution can be replaced with this indicator because
% evaluation is deterministic.
% 
% At first glance, the highest probability denotation appears to be the
% correct output for the model. However, this denotation is highly
% sensitive to the probabilities in the database, and in many cases is
% completely empty. Instead, for the evaluation, we compute the marginal
% probability that each entity is an element of the denotation:
% 
% \begin{eqnarray*}
% P(e \in \gamma | \ell; \theta, \phi) = \sum_\gamma \textbf{1}(e \in \gamma) P(\gamma | \ell ; \theta, \phi)
% \end{eqnarray*}

% This probability is a score for each entity that allows us to produce
% a ranked list of answers for each query. As it turns out, there is a
% considerable amount of work on computing these marginal probabilities
% in probabilistic databases; for more information, we refer the reader
% to Suciu et al. \shortcite{suciu2011probabilistic}.  Computing
% marginal probabilities for probabilistic database queries is \#P-hard
% in general, but many queries permit tractable evaluation
% \cite{dalvi2007}.
% 
% For example, an entity $e$ is in the denotation of $\lambda
% x.\pred{ceo}(x) \wedge \pred{of}(x, \pred{/en/sprint})$ with
% probability $P(\pred{ceo}(e)) \times P(\pred{of}(e,
% \pred{/en/sprint}))$. Queries with existential (universal) quantifiers
% can also be handled by computing an \pred{or} (\pred{and}) over all
% possible entity values of the quantified variable. For example, an
% entity $e$ is in the denotation of $\lambda x. \exists
% y. \pred{ceo}(x) \wedge \pred{of}(x, y) \wedge \pred{company}(y)$ with
% probability $P(\pred{ceo}(e)) \times ( 1 - \prod_{y \in E} [1 -
%   P(\pred{of}(e, y)) \times P(\pred{company}(y))])$; this expression
% computes the \pred{or} over entities $y$ using the identity $A \vee B
% = \neg (\neg A \wedge \neg B)$. For more information about query
% evaluation in probabilistic databases, we refer the reader to .

\section{Training}
\label{sec:training}

The training problem in our approach is to learn parameters $\theta$
and $\phi$ for the probabilistic database. We consider two different
objective functions for learning these parameters that use slightly
different forms of training data. In both cases, training has two
phases. First, we generate training data, in the form of observed
assertions or query-answer pairs, by applying the rule-based semantic
parser to a corpus of entity-linked web text. Second, we optimize the
parameters of the probabilistic database to rank observed assertions
or answers above unobserved assertions or answers.

% We work around the
% requirement for negative training data by using a novel ranking
% objective that trains the system to rank observed answers to queries
% above unobserved answers.

\subsection{Training Data}
\label{sec:trainingdata}

\begin{figure*}
\small

\textbf{Original sentence and logical form} \\
General \ul{Powell}, appearing Sunday on \ul{CNN} 's \ul{Late Edition}, said ... \\
{\small $\exists w,x,y,z. ~~~ w = \pred{/en/powell} \wedge \pred{general}(w) \wedge \pred{appearing}(w, x) \wedge \pred{sunday}(x) \wedge \pred{appearing\_on}(w, y) \wedge y = \pred{/en/late} \wedge \pred{'s}(z, y) \wedge z = \pred{/en/cnn} \wedge \pred{said}(w, ...)$ } \\

\textbf{Simplified logical form} \\
{\small $\exists w,y,z. ~~ w = \pred{/en/powell}  \wedge \pred{general}(w) \wedge \pred{appearing\_on}(w, y) \wedge y = \pred{/en/late} \wedge \pred{'s}(z, y) \wedge z = \pred{/en/cnn}$ } \\

{
\renewcommand{\tabcolsep}{0.1cm}
\begin{tabular}{l|ll}
\textbf{Instances} & \textbf{Queries} & \textbf{Answers} \\
{\small $\pred{general}(\pred{/en/powell})$ }& {\small $\lambda w.\pred{general}(w) \wedge \pred{appearing\_on}(w, \pred{/en/late})$ } & {\small $\pred{/en/powell}$ }\\
{\small $\pred{appearing\_on}(\pred{/en/powell}, \pred{/en/late})$ } & {\small $\lambda y.\pred{appearing\_on}(\pred{/en/powell}, y) \wedge \pred{'s}(\pred{/en/cnn}, y) $ } & {\small  $\pred{/en/late}$ }\\
{\small $\pred{'s}(\pred{/en/cnn}, \pred{/en/late})$ } & {\small $\lambda z.\pred{'s}(z, \pred{/en/late})$}& {\small $\pred{/en/cnn}$ }\\
\end{tabular}
}
\vspace{-.15in}
\caption{Illustration of training data generation applied to a single
  sentence. We generate two types of training data, predicate
  instances and queries with observed answers, by semantically parsing
  the sentence and extracting portions of the generated logical form
  with observed entity arguments. The predicate instances are
  extracted from the conjuncts in the simplified logical form, and the
  queries are created by removing a single entity from the simplified
  logical form.}
\label{fig:trainingdata}
\vspace{-.1in}
\end{figure*}

Training data is generated by applying the process illustrated in
Figure \ref{fig:trainingdata} to each sentence in an entity-linked web
corpus. First, we apply our rule-based semantic parser to the sentence
to produce a logical form. Next, we extract portions of this logical
form where every variable is bound to a particular Freebase entity,
resulting in a simplified logical form. Because the logical forms are
existentially-quantified conjunctions of predicates, this step simply
discards any conjuncts in the logical form containing a variable that
is not bound to a Freebase entity. From this simplified logical form,
we generate two types of training data: (1) predicate instances, and
(2) queries with known answers (see Figure \ref{fig:trainingdata}). In
both cases, the corpus consists entirely of assumed-to-be-true
statements, making obtaining negative examples a major challenge for
training.\footnote{A seemingly simple solution to this problem is to
  randomly generate negative examples; however, we empirically found
  that this approach performs considerably worse than both of the
  proposed ranking objectives.}

\subsection{Predicate Ranking Objective}
\label{sec:pro}

Riedel et al. \shortcite{riedel2013} introduced a ranking objective to
work around the lack of negative examples in a similar matrix
factorization problem. Their objective is a modified version of
Bayesian Personalized Ranking \cite{rendle2009} that aims to rank
observed predicate instances above unobserved instances.

This objective function uses observed predicate instances (Figure
\ref{fig:trainingdata}, bottom left) as training data. This data
consists of two collections, $\{(c_i, e_i)\}_{i=1}^n$ and $\{(r_j,
t_j)\}_{j=1}^m$, of observed category and relation instances. We use
$t_j$ to denote a tuple of entities, $t_j = (e_{j,1}, e_{j,2})$, to
simplify notation. The predicate ranking objective is:
\begin{eqnarray*}
O_P(\theta, \phi) & = & \sum_{i=1}^n \log \sigma( \theta_{c_i}^T (\phi_{e_i} - \phi_{e_i^\prime})) + \\
& & \sum_{j=1}^m \log \sigma( \theta_{r_j}^T (\phi_{t_j} - \phi_{t_j^\prime}))
\end{eqnarray*}

where $e_i^\prime$ is a randomly sampled entity such that $(c_i,
e_i^\prime)$ does not occur in the training data. Similarly,
$t_j^\prime$ is a random entity tuple such that $(r_j, t_j^\prime)$
does not occur. Maximizing this function attempts to find
$\theta_{c_i}$, $\phi_{e_i}$ and $\phi_{e_i^\prime}$ such that
$P(c_i(e_i))$ is larger than $P(c_i(e_i^\prime))$ (and similarly for
relations). During training, $e_i^\prime$ and $t_j^\prime$ are
resampled on each pass over the data set according to each entity or
tuple's empirical frequency.

\subsection{Query Ranking Objective}
\label{sec:qro}

The previous objective aims to rank the entities within each predicate
well. However, such within-predicate rankings are insufficient to
produce correct answers for queries containing multiple predicates --
the scores for each predicate must further be calibrated to work well
with each other given the independence assumptions of the
probabilistic database.

We introduce a new training objective that encourages good rankings
for entire queries instead of single predicates. The data for this
objective consists of tuples, $\{(\ell_i, e_i)\}_{i=1}^n$, of a query
$\ell_i$ with an observed answer $e_i$ (Figure \ref{fig:trainingdata},
bottom right). Each $\ell_i$ is a function with exactly one entity
argument, and $\ell_i(e)$ is a conjunction of predicate instances. For
example, the last query in Figure \ref{fig:trainingdata} is a function
of one argument $z$, and $\ell(e)$ is a single predicate instance,
$\pred{'s}(e, \pred{/en/late})$. The new objective aims to rank the
observed entity answer above unobserved entities for each query: {
% \setlength{\abovedisplayskip}{-5pt}
\setlength{\belowdisplayskip}{-10pt}
% \setlength{\abovedisplayshortskip}{0pt}
% \setlength{\belowdisplayshortskip}{0pt}
\begin{eqnarray*}
O_{Q}(\theta, \phi) & = & \sum_{i=1}^n \log P_{rank}(\ell_i, e_i, e_i^\prime)  \\
\end{eqnarray*}
}
% The expression $\theta_{c}^T (\phi_{e} - \phi_{e^\prime})$ in the
% predicate ranking objective can be viewed as an approximation of the
% probability that $e$ is ranked above $e^\prime$ in category $c$. Our
% goal is to extend this approximation to work for complete logical
% expressions. Our approach is to can define a new probabilistic
% database, $\pred{DB}_{e^\prime}$, where the random variable for each
% predicate instance $c(e)$ defines the (approximate) probability. Then the
% predicate ranking objective is simply:
% 
% $P_{\pred{DB}_{e^\prime}}(c(e))$
%% For example,
%% given the phrase ``Dan Hesse, CEO of Sprint'', we would produce the
%% logical form $\pred{ceo}(\pred{/en/dan\_hesse}) \wedge
%% \pred{of}(\pred{/en/dan\_hesse}, \pred{/en/sprint})$, and the training
%% example $(\ell = \lambda x.\pred{ceo}(x) \wedge \pred{of}(x,
%% \pred{/en/sprint}), e = \pred{/en/dan\_hesse})$.

$P_{rank}$ generalizes the approximate ranking probability defined by
the predicate ranking objective to more general queries. The
expression $\sigma (\theta_{c}^T (\phi_{e} - \phi_{e^\prime}))$ in the
predicate ranking objective can be viewed as an approximation of the
probability that $e$ is ranked above $e^\prime$ in category
$c$. $P_{rank}$ uses this approximation for each individual predicate
in the query. For example, given the query $\ell = \lambda x.c(x)
\wedge r(x, y)$ and entities $(e, e^\prime)$, $P_{rank}(\ell, e,
e^\prime) = \sigma( \theta_c (\phi_e - \phi_{e^\prime})) \times
\sigma( \theta_r (\phi_{(e,y)} - \phi_{(e^\prime, y)}))$. For this
objective, we sample $e^\prime_i$ such that $(\ell_i, e^\prime_i)$
does not occur in the training data.

When $\ell$'s body consists of a conjunction of predicates, the query
ranking objective simplifies considerably. In this case, $\ell$ can be
described as three sets of one-argument functions: categories
$C(\ell)= \{\lambda x.c(x)\}$, left arguments of relations $R_L(\ell)
= \{\lambda x.r(x, y)\}$, and right arguments of relations $R_R(\ell)
= \{\lambda x.r(y, x)\}$. Furthermore, $P_{rank}$ is a product so we
can distribute the log:
\begin{eqnarray*}
O_{Q}(\theta, \phi) & = & \sum_{i=1}^n \sum_{\lambda x.c(x) \in C(\ell_i)} \hspace{-.2in} \log
\sigma (\theta_{c} (\phi_{e_i} - \phi_{e^\prime_i})) \\
& & \hspace{-.2in} + \hspace{-.2in} \sum_{\lambda x.r(x, y) \in R_L(\ell_i)} \hspace{-.2in} \log \sigma (\theta_{r} ( \phi_{(e_i,y)} - \phi_{(e^\prime_i, y)} )) \\
& & \hspace{-.2in} + \hspace{-.2in} \sum_{\lambda x.r(y, x) \in R_R(\ell_i)} \hspace{-.2in} \log \sigma (\theta_{r} ( \phi_{(y, e_i)} - \phi_{(y, e^\prime_i)} )) 
\end{eqnarray*}

This simplification reveals that the main difference between $O_{Q}$
and $O_{P}$ is the sampling of the unobserved entities $e^\prime$ and
tuples $t^\prime$. $O_{P}$ samples them in an unconstrained fashion
from their empirical distributions for every predicate. $O_{Q}$
considers the larger context in which each predicate occurs, with two
major effects. First, more negative examples are generated for
categories because the logical forms $\ell$ are more specific. For
example, both ``president of Sprint'' and ``president of the US''
generate instances of the $\pred{president}$ predicate; $O_Q$ will use
entities that only occur with one of these as negative examples for
the other. Second, the relation parameters are trained to rank tuples
with a shared argument, as opposed to tuples in general.

Note that, although $P_{rank}$ generalizes to more complex logical
forms than existentially-quantified conjunctions, training with these
logical forms is more difficult because $P_{rank}$ is no longer a
product. In these cases, it becomes necessary to perform inference
within the gradient computation, which can be expensive. The
restriction to conjunctions makes inference trivial, enabling the
factorization above.

\section{Evaluation}
\label{sec:evaluation}

We evaluate our approach to compositional semantics on a question
answering task. Each test example is a (compositional) natural
language question whose answer is a set of Freebase entities. We
compare our open domain approach to several baselines based on prior
work, as well as a human-annotated Freebase query for each example.

\subsection{Data}

We used Clueweb09 web
corpus\footnote{\url{http://www.lemurproject.org/clueweb09.php}} with the
corresponding Google FACC entity linking \cite{gabrilovich2013} to
create the training and test data for our experiments. The training
data is derived from 3 million webpages, and contains 1.7m predicate
instances, 1.1m queries, 150k entities and 130k entity
pairs. Predicates that appeared fewer than 6 times in the training
data were replaced with the predicate \pred{UNK}, resulting in 16k
categories and 1.4k relations.

Our test data consists of fill-in-the-blank natural language questions
such as ``Incan emperor \underline{\quad{}}'' or ``Cunningham directed
Auchtre's second music video \underline{\quad{}}.'' These questions
were created by applying the training data generation process (Section
\ref{sec:trainingdata}) to a collection of held-out webpages. Each
natural language question has a corresponding logical form query
containing at least one category and relation.

We chose not to use existing data sets for semantic parsing into
Freebase as our goal is to model the semantics of language that cannot
necessarily be modelled using the Freebase schema. Existing data sets,
such as Free917 \cite{cai2013acl} and WebQuestions \cite{berant2013},
would not allow us to evaluate performance on this subset of
language. Consequently, we evaluate our system on a new data set with
unconstrained language. However, we do compare our approach against
manually-annotated Freebase queries on our new data set (Section
\ref{sec:spfb}).

All of the data for our experiments is available online at {\small
  \url{http://rtw.ml.cmu.edu/tacl2015_csf}}.

\begin{table}
\centering
{\small
\begin{tabular}{lc}  \toprule
\# of questions & 220 \\
\quad{} Avg. \# of predicates / query & 2.77 \\
\quad{} Avg. \# of categories / query & 1.75 \\
\quad{} Avg. \# of relations / query & 1.02 \\  
\quad{} Avg. \# of answers / query & 1.92 \\ \midrule % \quad{} mean \# of answers & 3.63 \\ % 422 correct answers overall.  
\# of questions with $\geq 1$ answer & \multirow{2}{*}{116} \\
(found by at least one system) & \\
% \quad{} Avg. \# of answers / query with $>1$ answer & 3.63 \\
\bottomrule
\end{tabular}
}
\vspace{-.1in}
\caption{Statistics of the test data set.}
\label{table:statistics}
\vspace{-.15in}
\end{table}

\subsection{Methodology}

Our evaluation methodology is inspired by information retrieval
evaluations \cite{manning2008}. Each system predicts a ranked list of
100 answers for each test question. We then pool the top 30 answers of
each system and manually judge their correctness. The correct answers
from the pool are then used to evaluate the precision and recall of
each system. In particular, we compute average precision (AP) for each
question and report the mean average precision (MAP) across all
questions. We also report a weighted version of MAP, where each
question's AP is weighted by its number of annotated correct
answers. Average precision is computed as $\frac{1}{m}
\sum_{k=1}^m\precision(k) \times \correct(k)$, where $\precision(k)$
is the precision at rank $k$, $\correct(k)$ is an indicator function
for whether the $k$th answer is correct, and $m$ is the number of
returned answers (at most 100).

Statistics of the annotated test set are shown in Table
\ref{table:statistics}. A consequence of our unconstrained data
generation approach is that some test questions are difficult to
answer: of the 220 queries, at least one system was able to produce a
correct answer for 116. The remaining questions are mostly
unanswerable because they reference rare entities unseen in the
training data.

\subsection{Models and Baselines}

\begin{table}
\centering
{\small
\begin{tabular}{lcc} \toprule
 & MAP & Weighted MAP \\ \midrule
\cb{} & 0.224 & 0.266 \\
\clb{} & 0.246 & 0.296 \\ \midrule
\uspr{} & 0.299 & 0.473 \\
\usqr{} & 0.309 & 0.492 \\ \midrule
\epr{} & 0.391 & 0.614 \\ 
\eqr{} & 0.406 & 0.645 \\ \midrule
Upper bound & 0.527 & 1.0 \\ \bottomrule
\end{tabular}
}
\vspace{-.08in}
\caption{Mean average precision for our question answering task. The
  difference in MAP between each pair of adjacent models is
  statistically significant ($p < .05$) via the sign test.}
\label{table:results}
\vspace{-.15in}
\end{table}

We implemented two baseline models based on existing techniques. The
\pred{CorpusLookup} baseline answers test questions by directly using
the predicate instances in the training data as its knowledge
base. For example, given the query $\lambda x.\pred{ceo}(x) \wedge
\pred{of}(x, \pred{/en/sprint})$, this model will return the set of
entities $e$ such that $\pred{ceo}(e)$ and $\pred{of}(e,
\pred{/en/sprint})$ both appear in the training data. All answers
found in this fashion are assigned probability 1.

The \pred{Clustering} baseline first clusters the predicates in the
training corpus, then answers questions using the clustered
predicates. The clustering aggregates predicates with similar
denotations, ideally identifying synonyms to smooth over sparsity in
the training data. Our approach is closely based on Lewis and Steedman
\shortcite{lewis2013}, though is also conceptually related to
approaches such as DIRT \cite{lin2001} and USP
\cite{poon2009unsupervised}. We use the Chinese Whispers clustering
algorithm \cite{biemann2006} and calculate the similarity between
predicates as the cosine similarity of their TF-IDF weighted entity
count vectors. The denotation of each cluster is the union of the
denotations of the clustered predicates, and each entity in the
denotation is assigned probability 1.

We also trained two probabilistic database models, \uspr{} and
\usqr{}, using the two objective functions described in Sections
\ref{sec:pro} and \ref{sec:qro}, respectively. We optimized both
objectives by performing 100 passes over the training data with
AdaGrad \cite{duchi2011} using an L2 regularization parameter of
$\lambda=10^{-4}$. The predicate and entity embeddings have 300
dimensions. These parameters were selected on the basis of preliminary
experiments with a small validation set.

Finally, we observed that \clb{} has high precision but low recall,
while both matrix factorization models have high recall with somewhat
lower precision. This observation suggested that an ensemble of
\pred{CorpusLookup} and \pred{Factorization} could outperform either
model individually. We created two ensembles, \epr{} and \eqr{}, by
calculating the probability of each predicate as a 50/50 mixture of
each model's predicted probability.

\subsection{Results}

Table \ref{table:results} shows the results of our MAP evaluation, and
Figure \ref{fig:pr-curve} shows a precision/recall curve for each
model. The MAP numbers are somewhat low because almost half of the
test questions have no correct answers and all models get an average
precision of 0 on these questions. The upper bound on MAP is the
fraction of questions with at least 1 correct answer. Note that the
models perform well on the answerable questions, as reflected by the
ratio of the achieved MAP to the upper bound. The weighted MAP metric
also corrects for these unanswerable questions, as they are assigned 0
weight in the weighted average.

\begin{figure}
\vspace{-.15in}
\center
\begin{pspicture}(-1.25,0.7)(7,6.5)

\rput[c](2.5,1){{\small Recall}}
\rput[c](-1.1,3.9){\rotateleft{{\small Precision}}}

% \psframe(3.7,6.3)(6.5,4.3)
\psline[linecolor=red](4.5,6)(3.8,6)
\rput[l](4.6,6){{\footnotesize \pred{Ens. ($O_Q$)}}}
\psline[linecolor=blue](4.5,5.7)(3.8,5.7)
\rput[l](4.6,5.7){{\footnotesize \pred{Ens. ($O_P$)}}}
\psline[linecolor=green](4.5,5.4)(3.8,5.4)
\rput[l](4.6,5.4){{\footnotesize \pred{Fact. ($O_Q$)}}}
\psline[linecolor=orange](4.5,5.1)(3.8,5.1)
\rput[l](4.6,5.1){{\footnotesize \pred{Fact. ($O_P$)}}}
\psline[linecolor=gray,linestyle=dashed,dash=5pt 3pt](4.5,4.8)(3.8,4.8)
\rput[l](4.6,4.8){{\footnotesize \pred{C.Lookup}}}
\psline[linecolor=black,linestyle=dashed,dash=5pt 3pt](4.5,4.5)(3.8,4.5)
\rput[l](4.6,4.5){{\footnotesize \pred{Clustering}}}

\psset{xunit=5\psunit,yunit=6\psunit}
\psaxes[dx=.2,Dx=.2,dy=.1,Dy=.1,Oy=0.3,labels=all]{-}(0,0.3)(0,0.3)(1,1.01)
\fileplot[plotstyle=dots,linecolor=red]{curvedata/map_answerable/ensemble_joint.txt}
\fileplot[plotstyle=line,linecolor=red]{curvedata/map_answerable/ensemble_joint.txt}
\fileplot[plotstyle=dots,dotstyle=+,linecolor=blue]{curvedata/map_answerable/ensemble_ranking.txt}
\fileplot[linecolor=blue]{curvedata/map_answerable/ensemble_ranking.txt}

\fileplot[plotstyle=dots,dotstyle=square*,linecolor=green]{curvedata/map_answerable/joint.txt}
\fileplot[linecolor=green]{curvedata/map_answerable/joint.txt}
\fileplot[plotstyle=dots,dotstyle=triangle*,linecolor=orange]{curvedata/map_answerable/ranking.txt}
\fileplot[linecolor=orange]{curvedata/map_answerable/ranking.txt}

\fileplot[plotstyle=dots,linecolor=gray,linestyle=dashed]{curvedata/map_answerable/corpus_lookup.txt}
\fileplot[linecolor=gray,linestyle=dashed]{curvedata/map_answerable/corpus_lookup.txt}
\fileplot[plotstyle=dots,dotstyle=+,linecolor=black,linestyle=dashed]{curvedata/map_answerable/clustering.txt}
\fileplot[linecolor=black,linestyle=dashed]{curvedata/map_answerable/clustering.txt}
\end{pspicture}

\vspace{-.2in}
\caption{Averaged 11-point precision/recall curves for the 116
  answerable test questions.}
\vspace{-.2in}
\label{fig:pr-curve}
\end{figure}

% TODO: example queries and answers. Make a figure

These results demonstrate several findings. First, we find that both
\pred{Factorization} models outperform the baselines in both MAP and
weighted MAP. The performance improvement seems to be most significant
in the high recall regime (right side of Figure
\ref{fig:pr-curve}). Second, we find that the query ranking objective
$O_Q$ improves performance over the predicate ranking objective $O_P$
by 2-4\% on the answerable queries. The precision/recall curves show
that this improvement is concentrated in the low recall
regime. Finally, the ensemble models are considerably better than
their component models; however, even in the ensembled models, we find
that $O_Q$ outperforms $O_P$ by a few percent.

%% The results in Table \ref{table:results} also
%% show that both ensembles dramatically outperform their constituent
%% models. In both the \pred{Factorization} and \pred{Ensemble} models,
%% the query ranking objective improves performance over the predicate
%% ranking objective.

%%  presents an 11-point precision/recall curve
%% for each model. These curves show that both \pred{Factorization}
%% approaches uniformly outperform \clb{} and \cb{}, but the most
%% dramatic difference is in the high recall regime. We also see that the
%% query ranking objective $O_Q$ provides a consistent performance
%% improvement over the predicate ranking objective $O_P$.

\subsection{Comparison to Semantic Parsing to Freebase}
\label{sec:spfb}

A natural question is whether our open vocabulary approach outperforms
a closed approach for the same problem, such as semantic parsing to
Freebase (e.g., Reddy et al. \shortcite{reddy2014}). In order to
answer this question, we compared our best performing model to a
manually-annotated Freebase query for each test question. This
comparison allows us to understand the relative advantages of open and
closed predicate vocabularies.

The first author manually annotated a Freebase MQL query for each
natural language question in the test data set. This annotation is
somewhat subjective, as many of the questions can only be inexactly
mapped on to the Freebase schema. We used the following guidelines in
performing the mapping: (1) all relations in the text must be mapped
to one or more Freebase relations, (2) all entities mentioned in the
text must be included in the query, (3) adjective modifiers can be
ignored and (4) entities not mentioned in the text may be included in
the query. The fourth condition is necessary because many one-place
predicates, such as $\pred{mayor}(x)$, are represented in Freebase
using a binary relation to a particular entity, such as
$\pred{government\_office/title}(x, \pred{/en/mayor})$.

\begin{table}
\centering
{\small
\begin{tabular}{lc}  \toprule
\# of questions w/ an annotated MQL query & 142 \\
\quad{} query returns $>1$ answer & 95 \\
\quad{} query returns no answers & 47 \\  \midrule
\# of questions w/o an MQL query & 78 \\ \bottomrule
\end{tabular}
}
\vspace{-.1in}
\caption{Statistics of the Freebase MQL queries annotated for the test data set.}
\label{table:fbstatistics}
\vspace{-.1in}
\end{table}

\begin{table}
\centering
\vspace{-.04in}
{\small
\begin{tabular}{lcc} \toprule
 & MAP  \\ \midrule
\eqr{} & 0.263  \\
Freebase & 0.385 \\ \bottomrule
\end{tabular}
}
\vspace{-.1in}
\caption{Mean average precision of our best performing model compared
  to a manually annotated Freebase query for each test question.}
\label{table:fbresults}
\vspace{-.1in}
\end{table}

Statistics of the annotated queries are shown in Table
\ref{table:fbstatistics}. Coverage is reasonably high: we were able to
annotate a Freebase query for 142 questions (65\% of the test set). The
remaining unannotatable questions are due to missing predicates in
Freebase, such as a relation defining the emperor of the Incan
empire. Of the 142 annotated Freebase queries, 95 of them return at
least one entity answer. The queries with no answers typically
reference uncommon entities which have few or no known relation
instances in Freebase. The annotated queries contain an average of
2.62 Freebase predicates.

We compared our best performing model, \eqr{}, to the manually
annotated Freebase queries using the same pooled evaluation
methodology. The set of correct answers contains the correct
predictions of \eqr{} from the previous evaluation along with all
answers from Freebase. 
% (That is, we assume that Freebase has perfect precision.)

Results from this evaluation are shown in Table
\ref{table:fbresults}.\footnote{The numbers in this table are not
  comparable to the numbers in Table \ref{table:results} as the
  correct answers for each question are different.} In terms of
overall MAP, Freebase outperforms our approach by a fair
margin. However, this initial impression belies a more complex
reality, which is shown in Table \ref{table:fbresults2}. This table
compares both approaches by their relative performance on each test
question. On approximately one-third of the questions, Freebase has a
higher AP than our approach. On another third, our approach has a
higher AP than Freebase. On the final third, both approaches perform
equally well -- these are typically questions where neither approach
returns any correct answers (67 of the 75). Freebase outperforms in
the overall MAP evaluation because it tends to return more correct
answers to each question.

Note that the annotated Freebase queries have several advantages in
this evaluation. First, Freebase contains significantly more predicate
instances than our training data, which allows it to produce more
complete answers. Second, the Freebase queries correspond to the
performance of a perfect semantic parser, while current semantic
parsers achieve accuracies around 68\% \cite{berant2014}.

The results from this experiment suggest that closed and open
predicate vocabularies are complementary. Freebase produces high
quality answers when it covers a question. However, many of the
remaining questions can be answered correctly using an open vocabulary
approach like ours. This evaluation also suggests that recall is a
limiting factor of our approach; in the future, recall can be improved
by using a larger corpus or including Freebase instances during
training.

\begin{table}
\centering
{\small
\begin{tabular}{lcc} \toprule
 & \# of queries  \\ \midrule
Freebase higher AP & 75 (34\%)  \\
equal AP & 75 (34\%) \\
\eqr{} higher AP & 70 (31\%) \\ \bottomrule
\end{tabular}
}
\vspace{-.1in}
\caption{Question-by-question comparison of model performance. Each
  test question is placed into one of the three buckets above,
  depending on whether Freebase or \eqr{} achieves a better average
  precision (AP) for the question.}
\label{table:fbresults2}
\vspace{-.1in}
\end{table}

% \subsection{Examples}
% TODO

\section{Related Work}
\label{sec:priorwork}

\subsubsection*{Open Predicate Vocabularies}

There has been considerable work on generating semantic
representations with an open predicate vocabulary. Much of the work is
non-compositional, focusing on identifying similar predicates and
entities. DIRT \cite{lin2001}, Resolver \cite{yates07resolver} and
other systems \cite{yao2012} cluster synonymous expressions in a
corpus of relation triples. Matrix factorization is an alternative
approach to clustering that has been used for relation extraction
\cite{riedel2013,yao2013} and finding analogies
\cite{turney2008,speer2008}. All of this work is closely related to
distributional semantics, which uses distributional information to
identify semantically similar words and phrases
\cite{turney2010,griffiths2007}.

Some work has considered the problem of compositional semantics with
an open predicate vocabulary. Unsupervised semantic parsing
\cite{poon2009unsupervised,titov2011} is a clustering-based approach
that incorporates composition using a generative model for each
sentence that factors according to its parse tree. Lewis and Steedman
\shortcite{lewis2013} also present a clustering-based approach that
uses CCG to perform semantic composition. This approach is similar to
ours, except that we use matrix factorization and Freebase entities.

Finally, some work has focused on the problem of textual inference
within this paradigm. Fader et al. \shortcite{fader2013} present a
question answering system that learns to paraphrase a question so that
it can be answered using a corpus of Open IE triples \cite{fader2011}.
Distributional similarity has also been used to learn weighted logical
inference rules that can be used for recognizing textual entailment or
identifying semantically similar text
\cite{garrette2011,garrette2013,beltagy2013}. This line of work
focuses on performing inference between texts, whereas our work
computes a text's denotation.

% Our  These works combine natural language and
% knowledge base predicates in a single matrix factorization to predict
% new instances of the knowledge base predicates. However, they do not
% define a compositional semantics for longer natural language phrases,
% as we do in our work. We also introduce a novel objective function
% that improves performance on compositional queries. Note that our work
% does not use a universal schema in the sense that it does not combine
% textual predicates and Freebase predicates in the same schema.

% Several systems have attempted to automatically generalize semantic
% representations using an open predicate vocabulary. However, existing
% approaches such as DIRT, USP, Resolver, Lewis and Steedman (TODO:
% cite) are based on clustering synonyms. Our dimensionality reduction
% approach is more flexible than clustering, as the learned embedding of
% predicates can represent (e.g.,) near-synonyms or synonyms in a
% particular context. Furthermore, the expressive power of CCG enables
% our approach to represent negation and other linguistic phenomena that
% cannot be represented in these existing systems (barring Lewis and
% Steedman).

A significant difference between our work and most of the related work
above is that our work computes denotations containing Freebase
entities. Using these entities has two advantages: (1) it enables us
to use entity linking to disambiguate textual mentions, and (2) it
facilitates a comparison against alternative approaches that rely on a
closed predicate vocabulary. Disambiguating textual mentions is a
major challenge for previous approaches, so an entity-linked corpus is
a much cleaner source of data. However, our approach could also work
with automatically constructed entities, for example, created by
clustering mentions in an unsupervised fashion \cite{singh11}.

% There is an interesting connection between this work and compositional
% semantics with vector space models
% \cite{socher2011,hermann2013,krishnamurthy2013vssp}. In both cases,
% the meanings of individual words are represented as vectors. However,
% vector space models perform semantic composition directly in the space
% of vectors (or matrices, etc.), while our approach first maps these
% vectors to sets of entities, then performs composition using logical
% operations on these sets. Our approach has the advantage of being able
% to straightforwardly model phenomena that are challenging for vector
% space models, such as the action of subordinating conjunctions, e.g.,
% ``that'' in ``car that I drive.''

\subsubsection*{Semantic Parsing}

Several semantic parsers have been developed for Freebase
\cite{cai2013acl,kwiatkowski2013,berant2013,berant2014}. Our approach
is most similar to that of Reddy et al. \shortcite{reddy2014}, which
uses fixed syntactic parses of unlabeled text to train a Freebase
semantic parser. Like our approach, this system
automatically-generates query/answer pairs for training. However, this
system, like all Freebase semantic parsers, uses a closed predicate
vocabulary consisting of only Freebase predicates. In contrast, our
approach uses an open predicate vocabulary and can learn denotations
for words whose semantics cannot be represented using Freebase
predicates. Consequently, our approach can answer many questions that
these Freebase semantic parsers cannot (see Section \ref{sec:spfb}).

The rule-based semantic parser used in this paper is very similar to
several other rule-based systems that produce logical forms from
syntactic CCG parses \cite{bos2008,lewis2013}. We developed our own
system in order to have control over the particulars of the analysis;
however, our approach is compatible with these systems as well.

\subsubsection*{Probabilistic Databases}

Our system assigns a model-theoretic semantics to statements in
natural language \cite{dowty81} using a learned distribution over
possible worlds. This distribution is concisely represented in a
probabilistic database, which can be viewed as a simple Markov Logic
Network \cite{richardson2006} where all of the random variables are
independent. This independence simplifies query evaluation:
probabilistic databases permit efficient exact inference for safe
queries \cite{suciu2011probabilistic}, and approximate inference for
the remainder \cite{gatterbauer2010,gatterbauer2015}.

\section{Discussion}
\label{sec:discussion}

This paper presents an approach for compositional semantics with an
open predicate vocabulary. Our approach defines a probabilistic model
over denotations (sets of Freebase entities) conditioned on an input
text. The model has two components: a rule-based semantic parser that
produces a logical form for the text, and a probabilistic database
that defines a distribution over denotations for each predicate. A
training phase learns the probabilistic database by applying
probabilistic matrix factorization with a query/answer ranking
objective to logical forms derived from a large, entity-linked web
corpus. An experimental analysis demonstrates that this approach
outperforms several baselines and can answer many questions that
cannot be answered by semantic parsing into Freebase.

Our approach learns a model-theoretic semantics for natural language
text tied to Freebase, as do some semantic parsers, except with an
open predicate vocabulary. This difference influences several other
aspects of the system's design. First, because no knowledge base with
the necessary knowledge exists, the system is forced to \emph{learn}
its knowledge base (in the form of a probabilistic database). Second,
the system can directly map syntactic CCG parses to logical forms, as
it is no longer necessary to map words to a closed vocabulary of
knowledge base predicates. In some sense, our approach is the exact
opposite of the typical semantic parsing approach: usually, the
semantic parser is learned and the knowledge base is fixed; here, the
knowledge base is learned and the semantic parser is fixed. From a
machine learning perspective, training a probabilistic database via
matrix factorization is easier than training a semantic parser, as
there are no difficult inference problems. However, it remains to be
seen whether a learned knowledge base can achieve similar recall as a
fixed knowledge base on the subset of language it covers.

There are two limitations of this work. The most obvious limitation is
the restriction to existentially quantified conjunctions of
predicates. This limitation is not inherent to the approach, however,
and can be removed in future work by using a system like Boxer
\cite{bos2008} for semantic parsing. A more serious limitation is the
restriction to one- and two-argument predicates, which prevents our
system from representing events and $n$-ary relations. Conceptually, a
similar matrix factorization approach could be used to learn
embeddings for $n$-ary entity tuples; however, in practice, the
sparsity of these tuples makes learning challenging. Developing
methods for learning $n$-ary relations is an important problem for
future work.

% In our evaluation, we noticed two common sources of error. The first
% is noisy training data due to entity linking and syntactic parsing
% errors. For example, processing a comma-separated list often results
% in noun-noun relations between its elements. The consequences of these
% errors are noticeable in the output of test questions as well. An
% improved semantic parsing component or a denoising step could improve
% performance. The second is that the matrix factorization tends to
% assign more extreme probabilities to more frequent entities as their
% vector embeddings have greater norms. This can occasionally produce
% oddly-ranked results. Normalizing the embeddings in some fashion may
% help.

% TODO: discussion of coverage / expressivity of the approach. Which
% language phenomena are covered by the representation? What kinds of
% negation?

A direction for future work is scaling up the size of the training
corpus to improve recall. Low recall is the main limitation of our
current system as demonstrated by the experimental analysis. Both
stages of training, the data generation and matrix factorization, can
be parallelized using a cluster. All of the relation instances in
Freebase can also be added to the training corpus. It should be
feasible to increase the quantity of training data by a factor of
10-100, for example, to train on all of ClueWeb. Scaling up the
training data may allow a semantic parser with an open predicate
vocabulary to outperform comparable closed vocabulary systems.

% An important open problem is extending the matrix factorization
% approach used here to learn denotations for higher-arity (e.g.,
% ternary) predicates. Such predicates are necessary to represent
% events. This problem is challenging due to sparsity in the
% co-occurrences of entity triples (quadruples, etc.), and because many
% event mentions will only reference a subset of the event's
% arguments. One possible approach is to introduce latent event
% variables and binary relations between events and their arguments.

% Another conclusion from this work is that there are complementary
% roles for both open and closed predicate vocabularies. An elegant way
% to combine these approaches would be to construct a semantic parser
% that is capable of using both Freebase predicates as well as
% open-domain predicates. This semantic parser would have higher
% coverage than current approaches, while still obtaining the advantages
% of Freebase. Another advantage is the ability to learn the semantic
% analysis component, which may improve the semantic analyses for tricky
% phenomena like quantifier scoping. These integrated methods are a
% promising direction for future work.

\section*{Acknowledgments}
This research was supported in part by DARPA under contract number
FA8750-13-2-0005, and by a generous grant from Google. We additionally
thank Matt Gardner, Ndapa Nakashole, Amos Azaria and the anonymous
reviewers for their helpful comments.

\bibliography{semantic_parsing}{}
\bibliographystyle{acl2012}

\end{document}

### 2016-03-03 paper/paper.tex
adding tacl2015 paper
Former-commit-id: 0d96938966b2ba3d3b01c8b2bbda93814689193d
Former-commit-id: ebd9e90a03480ed7f01706ac6735016816934591
Wrote the evaluation section.
Mostly just the method and discussion sections left for the initial draft.


Former-commit-id: 5c44bff5d621f101c472a1832e1ee5e1156ee9a6
Former-commit-id: 03a29a4634ebf13fc62f936d117861489d88b87b

@@
 
+\subsection{Candidate entity generation}
+\label{sec:better-candidates}
+
+\mattnote{TODO}
+
 \section{Evaluation}
@@
 FACC entity linking of that corpus to
-Freebase~\cite{gabrilovich-2013-clueweb-entity-linking}.  3 million webpages
-from this corpus were processed with a CCG parser to produce logical forms, as
-described in \secref{jayant-semparse}.  This produced 2.1m predicate instances
-involving 142k entity pairs and 184k entities.  After removing
-infrequently-seen predicates (seen fewer than 6 times), there were 25k
+Freebase~\cite{gabrilovich-2013-clueweb-entity-linking}.  For training data, 3
+million webpages from this corpus were processed with a CCG parser to produce
+logical forms, as described in \secref{jayant-semparse}.  This produced 2.1m
+predicate instances involving 142k entity pairs and 184k entities.  After
+removing infrequently-seen predicates (seen fewer than 6 times), there were 25k
 categories and 4.2k relations.\footnote{The differences in numbers reported
@@
 
+We also used the test set created by Krishnamurthy and Mitchell, which contains
+220 queries generated in the same fashion as the training data from a separate
+section of ClueWeb.  However, we used this set for intermediate evaluations
+while developing our models, and so we also generated another, similar test set
+from a different held out section of ClueWeb.  This final test set contains 307
+queries.  We report results on both of these test sets below.  All of the data
+used in these experiments is available at [url withheld for review].
+
+\subsection{Experiments}
+
+We compare three models in our experiments: a distributional-only model, a
+formal-only model, and our proposed model, which is both distributional and
+formal.  The distributional-only model is the model proposed by Krishnamurthy
+and Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} and
+described in \secref{jayant-semparse}.  The combined model is the model
+described in \secref{sec:formal-and-distributional}, while the formal-only
+model removes the distributional component from the combined model (i.e., all
+parameters $\theta$ and $\phi$ from the distributional portion of the model are
+fixed at zero during training and test).  Note that this formal-only baseline
+is also new to this work---we are not aware of any other work that models
+language in terms of features derived from a formal knowledge base.
+
+In addition to running experiments comparing these three models on the two test
+sets described above, we also evaluated the improvement gained by using our
+modified logical forms (\secref{better-lfs}), and our entity proposal mechanism
+(\secref{better-candidates}).
+
 \subsection{Methodology}
 
-\subsection{Models}
+Given a fill-in-the-blank query such as ``Italian architect \blank{}'', each
+system produces a ranked list of 100 candidate entities.  To compare the output
+of the systems, we follow a pooled evaluation protocol commonly used in
+relation extraction and information
+retrieval~\cite{west-2014-kbc-via-qa,riedel-2013-mf-universal-schema}.  We take
+the top 30 predictions from each system and manually annotate whether they are
+correct, and use those annotations to compute the average precision (AP) and
+reciprocal rank (RR) of each system on the query.  Average precision is defined
+as $\frac{1}{m}\sum^m_{k=1} \mathrm{Prec}(k) \times \mathrm{Correct}(k)$, where
+$\mathrm{Prec}(k)$ is the recision at rank $k$, $\mathrm{Correct}(k)$ is an
+indicator function for whether the $k$th answer is correct, and $m$ is number
+of returned answers (up to 100, in this evaluation).  Reciprocal rank is
+computed by first finding the rank $r$ of the first correct prediction made by a
+system.  Reciprocal rank is then $\frac{1}{r}$, ranging from 1 (if the first
+prediction is correct) to 0 (if there is no correct answer returned).  In the
+tables below we report \emph{mean} average precision (MAP) and reciprocal rank
+(MRR), averaged over all of the queries in the test set.  We also report a
+weighted version of MAP, where the AP of each query is scaled by the number of
+annotated correct answers to the query.
 
 \subsection{Results}
+
+\begin{table}
+  \centering
+  \begin{tabular}{|l|r|r|}
+    \hline
+    Method & MAP & MRR \\
+    \hline
+    Distributional-only & .239 & ?? \\
+    Distributional-only (old lfs) & ?? & ?? \\
+    \hline
+    Formal-only & ?? & ?? \\
+    Formal-only (old lfs) & ?? & ?? \\
+    \hline
+    Combined model & \textbf{.340} & ?? \\
+    Combined model (old lfs) & ?? & ?? \\
+    \hline
+  \end{tabular}
+  \caption{Results on the development set for our fill-in-the-blank task.  The
+  combined model improves MAP by 42\% compared to the distributional-only
+  baseline.  Additionally, the improved logical forms presented in
+  \secref{better-lfs} significantly improve all models.}
+  \label{tab:dev-results}
+\end{table}
+
+\tabref{dev-results} shows the results of our experiments on the development
+set (the same as the test set used by Krishnamurthy and
+Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}).  As can be
+seen, the combined model significantly improves performance, giving a 42\%
+relative increase in MAP over the distributional-only baseline.  This table
+also shows the benefit of using our modified logical forms (see
+\secref{better-lfs}); by being able to better model the relations between
+entities, MAP of all of the models is significantly improved.
+
+\begin{table}
+  \centering
+  \begin{tabular}{|l|r|r|}
+    \hline
+    Method & MAP & MRR \\
+    \hline
+    Distributional-only & .231 & ?? \\
+    \ \ \ -related entities & .170 & ?? \\
+    \hline
+    Formal-only & ?? & ?? \\
+    \hline
+    Combined model & \textbf{.376} & ?? \\
+    \hline
+  \end{tabular}
+  \caption{Results on the final test set for our fill-in-the-blank task.  The
+  combined model improves MAP by 63\% relative to the distributional-only
+  baseline.  Additionally, allowing the distributional-only model to use
+  Freebase to propose candidates improves MAP by 6 points absolute due to
+  improved recall.}
+  \label{tab:final-results}
+\end{table}
+
+\tabref{final-results} shows that these improvements are consistent on the
+final test set, as well.  The performance improvement seen by the combined
+model is actually larger on this set, going from a MAP of .231 to .376, a 63\%
+relative improvement.  In this table, we also show the improvement gained by
+allowing the distributional-only model to propose candidate entities that are
+related in Freebase (see \secref{better-candidates}).  Even though these
+candidates are always ranked at the bottom of the list of predictions (with a
+score of 0), the additional recall provided by being able to propose more
+entities raises MAP of the distributional-only model from .170 to .231.
 

### 2016-03-03 papers/tacl2015/resubmission-pkg.tex
Moved the papers a bit
Former-commit-id: 52737d10d068126b1d127ac960df72f8ac9e9a99

\documentclass{article}[11pt,oneside]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INPUTS FOR THE NEW PAPER
\newcommand{\subtitle}{Learning a Compositional Semantics for Freebase \\ with an Open
  Predicate Vocabulary}
\title{Resubmission of TACL \#548, \\ \subtitle.   \\}

\newcommand{\resubmission}{paper.pdf}  %% revised version
\newcommand{\origdecision}{decision.pdf}  %% name of anonymized original-decision-letter file
\newcommand{\coverfile}{our-cover-letter.pdf}  %% name of anonymized cover-letter file

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{hyperref}
% \hypersetup{
%     colorlinks=true, %set true if you want colored links
%     linktoc=all,     %set to all if you want both sections and subsections linked
%     linkcolor=blue,  %choose some color if you want links to stand out
% }
\usepackage{ifthen}
\usepackage{xspace}

\usepackage{times}
\usepackage{fullpage}
\usepackage{pdfpages}

\special{papersize=8.5in,11in}
\pdfpageheight\paperheight
\pdfpagewidth\paperwidth
\setlength\topmargin{-7mm} \setlength\oddsidemargin{-0cm}
\setlength\textheight{22cm} \setlength\textwidth{15.8cm}
\setlength\columnsep{0.25in}  \newlength\titlebox \setlength\titlebox{2.00in}
\setlength\headheight{5pt}   \setlength\headsep{0pt}
\setlength\footskip{1.9cm}
\setlength\leftmargin{0.0in}
\pagestyle{plain}

\setlength{\footskip}{55pt}

\begin{document}
\maketitle

\tableofcontents

\section{Author(s) cover letter responding to the original reviews} Starts on next page.
\includepdf[pages=-,offset=0mm 6mm]{\coverfile}
\section{Revised submission} Starts on next page.
\includepdf[pages=-,offset=0mm 6mm]{\resubmission}
\section{Original decision letter and reviews} Starts on next page.
\includepdf[pages=-,offset=0mm 6mm]{\origdecision}

\end{document}

### 2016-03-03 src/main/scala/org/allenai/semparse/Evaluator.scala
Let the distributional model use the graph to propose entities
This really needs to be made modular, so I can change a parameter to switch
between these two, but this will do for now.


Former-commit-id: 93a7ff594b1657afa229ff7c84bd1caf440c374c
Former-commit-id: 039bc37378e452a7be0673c71e0c2959498f18c0

@@ -47,10 +47,12 @@ class Evaluator(
     val wholeJson = parse(fileUtil.readLinesFromFile(queryFile).mkString("\n"))
     for (json <- wholeJson.extract[Seq[JValue]]) {
       val sentence = (json \ "sentence").extract[String]
+      println(s"Scoring queries for sentence: $sentence")
       val queries = (json \ "queries").extract[Seq[JValue]]
       for (query <- queries) {
         numQueries += 1
         val queryExpression = (query \ "queryExpression").extract[String]
+        println(s"Query: $queryExpression")
         val midsInQuery = (query \ "midsInQuery").extract[Seq[String]]
         val midRelationsInQuery = (query \ "midRelationsInQuery").extract[Seq[JValue]]
         val correctIds = (query \ "correctAnswerIds").extract[Seq[String]].toSet
@@ -86,8 +88,10 @@ class Evaluator(
         }
 
         // Now run the expression through the evaluation code and parse the result.
+        println("Evaluating the expression")
         val result = env.evalulateSExpression(expressionToEvaluate).getValue()
         val entityScoreObjects = result.asInstanceOf[Array[Object]]
+        println(s"Done evaluating, ranking ${entityScoreObjects.length} results")
         val entityScores = entityScoreObjects.map(entityScoreObject => {
           val cons = entityScoreObject.asInstanceOf[ConsValue]
           val list = ConsValue.consListToList(cons, classOf[Object])
@@ -103,7 +107,7 @@ class Evaluator(
         writer.write("\n")
         for ((score, entity) <- entityScores) {
           val names = entityNames.getOrElse(entity, "NO ENTITY NAME!")
-          if (score > 0.0) {
+          if (score >= 0.0) {
             if (correctIds.contains(entity)) {
               writer.write("1 ")
             } else if (incorrectIds.contains(entity)) {
@@ -114,7 +118,7 @@ class Evaluator(
             writer.write(s"$score $entity $names\n")
           }
         }
-        val positiveScore = entityScores.filter(_._1 > 0.0)
+        val positiveScore = entityScores.filter(_._1 >= 0.0)
         if (positiveScore.size == 0) writer.write("\n")
         val averagePrecision = Evaluator.computeAveragePrecision(positiveScore.take(runDepth), correctIds)
         averagePrecisionSum += averagePrecision

### 2016-03-03 src/main/scala/org/allenai/semparse/Experiments.scala

@@ -12,7 +12,7 @@ object Experiments {
     val datasets = Seq("large")//, "small")
     val modelTypes = Seq("uschema")//, "ensemble")
     val rankings = Seq("query")//, "predicate")
-    val withGraphOrNot = Seq(true)//, false)
+    val withGraphOrNot = Seq(false)//, true)
     val baselineConfigs = Seq(
       //("small", "baseline", "ignored", false)
       //("large", "baseline", "ignored", false)

### 2016-03-03 src/main/scala/org/allenai/semparse/SfeFunctions.scala

@@ -46,6 +46,7 @@ class FindRelatedEntities extends AmbFunctionValue {
       (word, mid, isSource)
     })
 
+    println("Finding related entities")
     val relatedEntities = parsedMidRelations.flatMap {
       case (word, mid, isSource) => featureComputer.findRelatedEntities(word, mid, isSource)
     }
@@ -56,6 +57,7 @@ class FindRelatedEntities extends AmbFunctionValue {
       println("Found too many related entities, skipping")
       Array.empty
     } else {
+      println(s"Returning ${relatedEntities.size} related entities")
       relatedEntities.toArray
     }
   }

### 2016-03-04 papers/acl2016/paper.tex
Moved the papers a bit
Former-commit-id: 52737d10d068126b1d127ac960df72f8ac9e9a99
A little more work on the paper
Former-commit-id: 2d8759dcdc0d4acf4137449484ca583a350039d4

--- 2016-03-03 paper/paper.tex
@@
 current semantic parsers, we first convert this natural language query into a
-logical form: $\lambda(\entity{x}) \predicate{architect}(\entity{x}) \land
-\predicate{architect\_N/N}(\entity{Italian}, \entity{x})$.  A typical semantic
+logical form: $\lambda x. \predicate{architect}(x) \land
+\predicate{architect\_N/N}(\entity{Italian}, x)$.  A typical semantic
 parser (e.g., that of Kwiatkowski et
@@
 \label{sec:jayant-semparse}
+
+\mattnote{Add a figure here to demonstrate the logical forms.}
 
@@
 work on knowledge base embeddings (RESCAL, TransE, etc.) is at least slightly
-relevant here, as is PRA.  \mattnote{Actually write
-this section}.
+relevant here, as is PRA.  \mattnote{Actually write this section}.
 
@@
 
+In this section we present our models of predicate semantics.  In
+\secref{formal-and-distributional} we describe how we modify Krishnamurthy and
+Mitchell's (K&M's) semantic parser to include features from a formal knowledge base.
+In \secref{computing-pmi} we describe how we select those features for each
+predicate.  The remaining two sections then describe other improvements we made
+to K&M's semantic parsing model: lexicalizing preposition and noun-compound
+predicates, and using the Freebase graph to select candidate entities.
+
 \subsection{Adding SFE features to Jayant's models}
@@
 
-\mattnote{TODO}
+The modification we make to K&M's semantic parser is simple.  For each entity
+and entity pair in the data we compute an SFE feature vector $\psi(e)$ and
+$\psi(e_1, e_2)$.  For each category and relation, we select a subset of the
+features to have associated weights $\omega_c$ and $\omega_r$.  We then add the
+weights $\omega_c$ and $\omega_r$ as parameters to be learned for each
+predicate, and we add the feature vectors $\psi(e)$ and $\psi(e_1, e_2)$ as
+observed features for each entity and entity pair.  The augmented category and
+relation probabilities are as follows:
+
+\begin{align*}
+  P(c(e) & = \true{}) & = & \sigma ( \theta_c^T \phi_e + \omega_c^T \psi_c(e)) \\
+  P(r(e_1, e_2) & = \true{}) & = & \sigma ( \theta_r^T \phi_{(e_1, e_2)} + \omega_r^T \psi_r(e_1, e_2) )
+\end{align*}
+where we have added subscripts on the $\psi$ functions to indicate that each
+predicate selects its own set of features from the SFE feature vector $\psi$.
+
+Note that now there are three sets of parameters to be learned by the semantic
+parser: (1) $\theta$, low-dimensional distributional vectors trained for each
+predicate; (2) $\phi$, low-dimensional distributional vectors trained for each
+entity and entity pair; and (3) $\omega$, weights associated with the selected
+formal SFE features for each predicate.  All of these parameters are optimized
+jointly, using the same ranking objective used by K&M.
 
@@
 
-\mattnote{TODO}
+The feature vectors returned by SFE have dimensionality in the tens of
+millions.  We do not have near enough data to train that many parameters for
+each of our tens of thousands of predicates, nor do we have enough RAM in our
+machines to keep that many parameters in memory.  It is thus necessary to
+select some small number of informative features for each predicate.  We do
+this using pointwise mutual information (PMI).
+
+PMI measures the strength of association between two variables $x$ and $y$; it
+is computed as $\log\frac{p(x,y)}{p(x)p(y)}$.  In our case, we want to
+associate predicates with SFE features.  However, our SFE features are for each
+\emph{entity} and \emph{entity pair}, not each \emph{predicate}.  To associate
+SFE features with predicates, we use the training
 

### 2016-03-07 papers/acl2016/paper.tex
A bunch of work on the paper
Former-commit-id: 3c90e1d56ce2c57dd47a9f0ba5c248f0a283df78

@@
 \secref{formal-and-distributional} we describe how we modify Krishnamurthy and
-Mitchell's (K&M's) semantic parser to include features from a formal knowledge base.
+Mitchell's (K\&M's) semantic parser to include features from a formal knowledge base.
 In \secref{computing-pmi} we describe how we select those features for each
 predicate.  The remaining two sections then describe other improvements we made
-to K&M's semantic parsing model: lexicalizing preposition and noun-compound
+to K\&M's semantic parsing model: lexicalizing preposition and noun-compound
 predicates, and using the Freebase graph to select candidate entities.
@@
 
-The modification we make to K&M's semantic parser is simple.  For each entity
+The modification we make to K\&M's semantic parser is simple.  For each entity
 and entity pair in the data we compute an SFE feature vector $\psi(e)$ and
@@
 formal SFE features for each predicate.  All of these parameters are optimized
-jointly, using the same ranking objective used by K&M.
+jointly, using the same ranking objective used by K\&M.
 
@@
 \emph{entity} and \emph{entity pair}, not each \emph{predicate}.  To associate
-SFE features with predicates, we use the training
+SFE features with predicates, we use the training data to find a mapping from
+entities and entity pairs to predicates that they have been seen with in the
+data.  For example, the phrase ``Italian architect Andrea Palladio'' is
+considered a positive training example for the instantiated predicates
+$\predicate{architect}(\entity{Andrea Palladio})$ and
+$\predicate{architect\_N/N}(\entity{Italy}, \entity{Andrea Palladio})$.  We
+then associate the feature vectors for \entity{Andrea Palladio} and
+(\entity{Italy}, \entity{Andrea Palladio}) with the predicates
+\predicate{architect} and \predicate{architect\_N/N}, respectively.  For each
+predicate $\pi$ and feature $f$, we use these counts to calculate the
+probabilities $p(\pi, f)$, $p(\pi)$ and $p(f)$.  After removing features with
+counts below some threshold, we pick the $k$ features with the highest PMI
+values for each predicate to use in our model.
 
@@
 
-\mattnote{TODO}
+While we largely follow the semantic parsing framework introduced by K\&M, we
+made one important change in how logical forms are generated.  For the running
+example we have been using this paper, ``Italian architect Andrea Palladio'',
+the relation predicate produced by K\&M's system is
+$\predicate{N/N}(\entity{Italy}, \entity{Andrea Palladio})$.  \predicate{N/N}
+does correctly capture the fact that \entity{Italy} is used syntactically as a
+noun modifier of \entity{Andrea Palladio}, but it leaves out the additional
+information contained in the syntax that ``architect'' was mediating that
+noun-noun dependency.  This means that ``U.S. president Barack Obama'' and
+``Italian architect Andrea Palladio'' are both modeled using the same relation
+predicate, which leads to a very generic and largely useless model for the
+predicate \predicate{N/N}.  By splitting \predicate{N/N} into separate
+predicates (\predicate{architect\_N/N} and \predicate{president\_N/N}), we give
+the model the opportunity to learn more fine-grained relation semantics, and we
+allow our feature selection pipeline to find much more useful features for
+relation predicates.  While it would be ideal to use actual dependency
+relations to determine which words to add to the predicate in complex noun
+phrases, most current parsers treat these kinds of noun phrases as flat, with
+all noun modifiers depending directly on the head of the noun phrase.  We
+approximate this ideal by simply taking all words in between the two entities
+in a noun phrase as the predicate (e.g., ``Illinois attorney general Lisa
+Madigan'' would produce the predicate \predicate{attorney\_general\_N/N}).
+
+A similar issue arises with prepositions and possessives.  For a phrase such as
+``Barack Obama, president of the U.S.'', K\&M's system would produce the
+following relation predicate: $\predicate{of}(\entity{Barack Obama},
+\entity{U.S.})$.  Because this same predicate (\predicate{of}) is used for all
+instances of this preposition, the predicate is forced to model too much and
+becomes overly generic.  When there is a common noun mediating a prepositional
+dependency between two entities, as in the phrase above, we add that noun to
+the predicate, giving the instance $\predicate{president\_of}(\entity{Barack
+Obama}, \entity{U.S.})$.  We do the same for possessives in phrases such as
+``Rome, Italy's capital'', producing the predicate \predicate{'s\_capital}.
 
@@
 
-\mattnote{TODO}
+One final way in which we improved K\&M's semantic parser is in how candidate
+entities are generated during inference.  Because the distributional-only
+predicate models used by K\&M's semantic parser need to learn a vector of
+parameters for each entity pair, they cannot give a non-zero score to any
+entity pair not seen during training time.  When given a query such as
+$\lambda(\entity{x}) \predicate{architect\_N/N}(\entity{x}, \entity{Andrea
+Palladio})$, K\&M's system only needs to consider the set of entities
+$\entity{x}$ that have been seen at training time with \entity{Andrea
+Palladio}; all other entities will get a score of 0.
+
+Our predicate models do not have this limitation.  The distributional component
+will still give an unseen entity pair a score of 0, as it is identical to K\&M's
+model, but the formal component of our simples simply computes an observed
+feature vector from Freebase for the entity pair.  As long as both entities
+appear in Freebase, our model can compute a feature vector and give a non-zero
+score.
+
+While this improvement allows us to handle queries over rare entities much
+better than a distributional-only model, it also complicates inference, as we
+cannot just score entity pairs seen at training time.  Optimizing every query's
+score over all of the millions of entities in Freebase is not computationally
+feasible.  To make inference tractable, for a given query we restrict
+candidates to all entities seen with the query entities during training (as
+done by K\&M), as well as all entities directly connected to the query entities
+in Freebase, or connected by a mediator node\footnote{Mediators in Freebase are
+used to capture relations with more than two arguments, such as employment
+tenure, which has an employer, and employee, a start date, and an end date.}.
+
+For some entities, such as the United States, the set of connected entities can
+still be intractably large, so we limit this expansion to only those entities
+with fewer than 100 directly connected entities.  Our motivation for this is
+that this candidate entity generation is most useful for rarely seen entities,
+for which we have few or no related entities seen during training.  These
+entities also tend to have relatively few connected entities in Freebase.
 
@@
 
-\mattnote{TODO}
+\mattnote{I will add more detail to some of these examples; I ran out of
+time...}
+
+Our model does very well on most predicates that have clear Freebase
+correlates: prime ministers, presidents, newspapers, companies, and so on.  The
+query ``French newspaper \blank{}'' gets almost perfect average precision.
+
+It does less well on predicates that do not match as closely with Freebase,
+such as ``Microsoft head honcho \blank{}'', ``Patriots linebacker \blank{}'',
+etc.  The combined model handily beats the distributional-only model in most of
+these cases, but it does not have the nearly-perfect AP seen in the more crisp
+queries above.  The ``head honcho'' example is particularly informative---this
+is a phrase that essentially means ``leader'', and the features learned by the
+formal model get some essential hints from Freebase, even though there is no
+direct correlate.  The features capture the fact that entities that are
+``honchos'' are people, and that they tend to be CEOs and film producers.
+
+For ``Patriots linebacker \blank{}'', the issue is that the features for
+\predicate{linebacker\_N/N} are able to capture which athletes play for which
+teams, but they cannot distinguish well between what positions those athletes
+play, so Patriots quarterbacks, wide receivers, and running backs are scored
+highly for this query.  This could be fixed by using more complex features for
+relation predicates, instead of just edge sequences, but that would explode the
+feature space and make the feature selection process more difficult.  It could
+also be fixed by better negative example selection during training.
+
+There are also cases where a predicate has so many possible entities types in
+Freebase that the it cannot learn models that are useful for all queries.  A
+good example of this is ``\blank{} is a NASA mission''.
+
+The SFE features we used cannot capture time very well.  ``17th century French
+mathematician \blank{}''...
+
+Because of the simple logical forms produced by the semantic parser we used, we
+cannot model some complex phenomena, such as counting and other things.  This
+is an orthogonal issue to the predicate semantics we're concerned with in this
+paper, however.
+
+Vice president Al Gore is modeled as $\predicate{vice}(\entity{Al Gore}) \land
+\predicate{president}(\entity{Al Gore})$.  Clearly there is room for better
+processing of multi-word expressions.
+
+\predicate{head\_honcho\_N/N} was never seen in the training data, so the
+phrase ``Microsoft head honcho \blank{}'' has to rely on knowing whether an
+entity is a ``honcho'' and what entities are related to Microsoft by an unknown
+predicate.  \predicate{honcho\_N/N} \emph{is} seen in the training data,
+however; some kind of backoff to simpler phrases would be useful here.
+
+Using connected entities in Freebase as additional candidates during inference
+is helpful, but it is not very sophisticated.  It over-generates for a lot of
+entities and predicates, and under-generates for others.  A mechanism for
+tailoring a search over Freebase to a particular query would be useful, though
+that would move the model more into the realm of reinforcement learning.
 

### 2016-03-07 papers/acl2016/paper.tex
Minor update
Former-commit-id: 2a9ed3effe7026c77698c8202ddb18f8482ff3ce

--- 2016-03-03 paper/paper.tex
@@
 work on knowledge base embeddings (RESCAL, TransE, etc.) is at least slightly
-relevant here, as is PRA.  \mattnote{Actually write
+relevant here, as is PRA.  And all of the semantic parsing approaches that go from text to a
+pseudo-logical form, then to an actual Freebase query (Kwiatkowski, Reddy's TACL paper, Liang?) \mattnote{Actually write
 this section}.

### 2016-03-07 src/main/scala/org/allenai/semparse/Evaluator.scala
Renamed the models to be more sane
Also re-organized the model and result output locations.


Former-commit-id: e0cb8090a0ffe7b6e3a67ddf47a6ca0ee79f19e4

@@ -254,7 +254,7 @@ object Evaluator {
     data: String,
     modelType: String,
     ranking: String,
-    usingGraphs: Boolean
+    ensembledEvaluation: Boolean
   ): Environment = {
     val dataFiles = data match {
       case "large" => Experiments.COMMON_LARGE_DATA
@@ -264,22 +264,27 @@ object Evaluator {
 
     val modelFiles = modelType match {
       case "baseline" => Seq(Experiments.BASELINE_MODEL_FILE)
-      case "ensemble" => usingGraphs match {
-        case true => Seq(Experiments.BASELINE_MODEL_FILE, Experiments.GRAPH_MODEL_FILE)
-        case false => Seq(Experiments.BASELINE_MODEL_FILE, Experiments.DISTRIBUTIONAL_MODEL_FILE)
+      case "formal" => ensembledEvaluation match {
+        case true => Seq(Experiments.BASELINE_MODEL_FILE, Experiments.FORMAL_MODEL_FILE)
+        case false => Seq(Experiments.FORMAL_MODEL_FILE)
       }
-      case "uschema" => usingGraphs match {
-        case true => Seq(Experiments.GRAPH_MODEL_FILE)
+      case "distributional" => ensembledEvaluation match {
+        case true => Seq(Experiments.BASELINE_MODEL_FILE, Experiments.DISTRIBUTIONAL_MODEL_FILE)
         case false => Seq(Experiments.DISTRIBUTIONAL_MODEL_FILE)
+      }
+      case "combined" => ensembledEvaluation match {
+        case true => Seq(Experiments.BASELINE_MODEL_FILE, Experiments.COMBINED_MODEL_FILE)
+        case false => Seq(Experiments.COMBINED_MODEL_FILE)
       }
       case other => throw new RuntimeException("unrecognized model type")
     }
 
     val evalFile = modelType match {
       case "baseline" => Seq(Experiments.EVAL_BASELINE_FILE)
-      case "uschema" => Seq(Experiments.EVAL_USCHEMA_FILE)
-      case "ensemble" => Seq(Experiments.EVAL_ENSEMBLE_FILE)
-      case other => throw new RuntimeException("unrecognized model type")
+      case other => ensembledEvaluation match {
+        case true => Seq(Experiments.EVAL_ENSEMBLE_FILE)
+        case false => Seq(Experiments.EVAL_USCHEMA_FILE)
+      }
     }
 
     val sfeSpecFile = data match {
[…]

### 2016-03-07 src/main/scala/org/allenai/semparse/Experiments.scala

@@ -5,14 +5,14 @@ package org.allenai.semparse
 // use, and groups some of them together in useful ways.
 object Experiments {
 
-  // Currently, there are four options in the experiments: which dataset do you use, which model
-  // type, what ranking method, and whether to use graph-based features.  If we add very many more
-  // possibilities, this will need some re-thinking to be more sane.
+  // Currently, there are four options in the experiments: which dataset do you use, ensembled with
+  // baseline or not (for evaluation only), what ranking method, and what model type.  If we add
+  // very many more possibilities, this will need some re-thinking to be more sane.
   val experimentConfigs: Seq[(String, String, String, Boolean)] = {
     val datasets = Seq("large")//, "small")
-    val modelTypes = Seq("uschema")//, "ensemble")
+    val modelTypes = Seq("formal")//, "distributional", "combined")
     val rankings = Seq("query")//, "predicate")
-    val withGraphOrNot = Seq(false)//, true)
+    val ensembledEvaluation = Seq(false)//, true)
     val baselineConfigs = Seq(
       //("small", "baseline", "ignored", false)
       //("large", "baseline", "ignored", false)
@@ -22,7 +22,7 @@ object Experiments {
     val configs = for (data <- datasets;
          modelType <- modelTypes;
          ranking <- rankings;
-         usingGraphs <- withGraphOrNot) yield (data, modelType, ranking, usingGraphs)
+         ensembled <- ensembledEvaluation) yield (data, modelType, ranking, ensembled)
 
     (configs ++ baselineConfigs)
   }
@@ -30,9 +30,10 @@ object Experiments {
   val BASE_ENVIRONMENT_FILE = "src/main/lisp/environment.lisp"
   val USCHEMA_ENVIRONMENT_FILE = "src/main/lisp/uschema_environment.lisp"
 
-  val DISTRIBUTIONAL_MODEL_FILE = "src/main/lisp/model.lisp"
-  val GRAPH_MODEL_FILE = "src/main/lisp/model_with_graphs.lisp"
-  val BASELINE_MODEL_FILE = "src/main/lisp/baseline_model.lisp"
+  val DISTRIBUTIONAL_MODEL_FILE = "src/main/lisp/model_distributional.lisp"
+  val COMBINED_MODEL_FILE = "src/main/lisp/model_combined.lisp"
[…]

### 2016-03-07 src/main/scala/org/allenai/semparse/Trainer.scala
Renamed the models to be more sane
Also re-organized the model and result output locations.


Former-commit-id: e0cb8090a0ffe7b6e3a67ddf47a6ca0ee79f19e4
Former-commit-id: 2c5c6efbf29f32177cb8e45b36f36e73268e9566

@@ -6,28 +6,29 @@ import edu.cmu.ml.rtw.users.matt.util.FileUtil
 
 object Trainer {
 
-  def canTrainConfig(data: String, modelType: String, ranking: String, usingGraph: Boolean) = {
-    // At this point, we just need to filter out the ensemble and baseline model types, and we can
-    // train everything else.
+  def canTrainConfig(data: String, modelType: String, ranking: String, ensembledEvaluation: Boolean) = {
+    // At this point, we just need to filter out the baseline model, and we can train everything
+    // else.
     modelType match {
-      case "uschema" => true
-      case _ => false
+      case "baseline" => false
+      case _ => true
     }
   }
 
-  def getModelFile(data: String, ranking: String, usingGraphs: Boolean, baseline: Boolean) = {
-    val graphs = if (usingGraphs) "with_graph_features" else "no_graph_features"
-    baseline match {
-      case true => s"output/${data}/baseline/model.lisp"
-      case false => s"output/${data}/${graphs}/${ranking}/model.ser"
+  def getModelFile(data: String, ranking: String, modelType: String) = {
+    val model = modelType match {
+      case "baseline" => modelType
+      case other => s"${modelType}/${ranking}"
     }
+    val ending = modelType match { case "baseline" => ".lisp"; case other => ".ser" }
+    s"output/${data}/${model}/model${ending}"
   }
 
   def createTrainingEnvironment(
     data: String,
     modelType: String,
     ranking: String,
-    usingGraphs: Boolean
+    ensembledEvaluation: Boolean
   ): Environment = {
     val dataFiles = data match {
       case "large" => ranking match {
@@ -43,11 +44,9 @@ object Trainer {
 
     val modelFile = modelType match {
       case "baseline" => throw new IllegalStateException("we don't handle training the baseline")
-      case "ensemble" => throw new IllegalStateException("you don't train an ensemble...")
-      case "uschema" => usingGraphs match {
-        case true => Experiments.GRAPH_MODEL_FILE
-        case false => Experiments.DISTRIBUTIONAL_MODEL_FILE
-      }
+      case "formal" =>  Experiments.FORMAL_MODEL_FILE
+      case "distributional" => Experiments.DISTRIBUTIONAL_MODEL_FILE
+      case "combined" => Experiments.COMBINED_MODEL_FILE
       case other => throw new RuntimeException("unrecognized model type")
     }
 
[…]

### 2016-03-07 src/main/scala/org/allenai/semparse/Tester.scala
Split Tester out of Evaluator
This should make it so that I don't have to re-run the inference just to update the annotations
and compute new metrics.


Former-commit-id: 1b56fdb0ba4de33831391d4f5eddb20642d06a48

@@ -1,0 +1,252 @@
+package org.allenai.semparse
+
+import java.io.FileWriter
+import java.io.File
+
+import scala.collection.mutable
+
+import com.jayantkrish.jklol.lisp.ConsValue
+
+import edu.cmu.ml.rtw.users.matt.util.FileUtil
+
+import org.json4s._
+import org.json4s.native.JsonMethods.parse
+
+// This class performs inference over a test set for a particular experiment configuration, which
+// is encapsulated in the Environment object given as a parameter.  The query file contains all of
+// the test queries that will be evaluated against the environment, and the entity names is just a
+// map from mids to a human-readable entity name, for easier human scanning of the result file.
+// The file util is my object that abstracts away accessing the file system (and allows for easy
+// faking of the file system, for much easier tests).
+class Tester(
+  env: Environment,
+  queryFile: String,
+  entityNames: => Map[String, String],
+  fileUtil: FileUtil = new FileUtil
+) {
+  implicit val formats = DefaultFormats
+
+  val catQueryFormat = "(expression-eval (quote (get-predicate-marginals %s (find-related-entities (list %s) (list %s)))))"
+
+  // NOTE: the test data currently does not have any relation queries, so this does not get used.
+  val relQueryFormat = "(expression-eval (quote (get-relation-marginals %s entity-tuple-array)))"
+  val poolDepth = 100
+  val runDepth = 200
+
+  def evaluateModel(writer: FileWriter) {
+    // The test file is a JSON object, which is itself a list of objects containing the query
+    // information.
+    val wholeJson = parse(fileUtil.readLinesFromFile(queryFile).mkString("\n"))
+    for (json <- wholeJson.extract[Seq[JValue]]) {
+      val sentence = (json \ "sentence").extract[String]
+      println(s"Scoring queries for sentence: $sentence")
+      val queries = (json \ "queries").extract[Seq[JValue]]
+      for (query <- queries) {
+        val queryExpression = (query \ "queryExpression").extract[String]
+        println(s"Query: $queryExpression")
+        val midsInQuery = (query \ "midsInQuery").extract[Seq[String]]
+        val midRelationsInQuery = (query \ "midRelationsInQuery").extract[Seq[JValue]]
+        val isRelationQuery = (query \ "isRelationQuery") match {
+          case JInt(i) => i == 1
+          case _ => false
+        }
+        val expressionToEvaluate = if (isRelationQuery) {
[…]

### 2016-03-07 src/main/scala/org/allenai/semparse/Evaluator.scala
Split Tester out of Evaluator
This should make it so that I don't have to re-run the inference just to update the annotations
and compute new metrics.


Former-commit-id: 1b56fdb0ba4de33831391d4f5eddb20642d06a48
Former-commit-id: 88ef63bf43e3fe41124032b7b17461ce857ac7ff

@@ -12,132 +12,109 @@ import edu.cmu.ml.rtw.users.matt.util.FileUtil
 import org.json4s._
 import org.json4s.native.JsonMethods.parse
 
-// This class runs an evaluation for a particular experiment configuration, which is encapsulated
-// in the Environment object given as a parameter.  The query file contains all of the test queries
-// that will be evaluated against the environment, and the entity names is just a map from mids to
-// a human-readable entity name, for easier human scanning of the result file.  The file util is my
-// object that abstracts away accessing the file system (and allows for easy faking of the file
-// system, for much easier tests).
+// This class takes the output from Tester (which performs inference over a test set), and a set of
+// annotated results, and performs an evaluation.
 class Evaluator(
-  env: Environment,
+  resultsFile: String,
   queryFile: String,
-  entityNames: => Map[String, String],
   fileUtil: FileUtil = new FileUtil
 ) {
   implicit val formats = DefaultFormats
 
-  val catQueryFormat = "(expression-eval (quote (get-predicate-marginals %s (find-related-entities (list %s) (list %s)))))"
-
-  // NOTE: the test data currently does not have any relation queries, so this does not get used.
-  val relQueryFormat = "(expression-eval (quote (get-relation-marginals %s entity-tuple-array)))"
-  val poolDepth = 100
-  val runDepth = 200
+  def getQueryAnswers(): Map[String, (Set[String], Set[String])] = {
+    val wholeJson = parse(fileUtil.readLinesFromFile(queryFile).mkString("\n"))
+    wholeJson.extract[Seq[JValue]].flatMap(json => {
+      val sentence = (json \ "sentence").extract[String]
+      println(s"Scoring queries for sentence: $sentence")
+      val queries = (json \ "queries").extract[Seq[JValue]]
+      queries.map(query => {
+        val queryExpression = (query \ "queryExpression").extract[String]
+        val correctIds = (query \ "correctAnswerIds").extract[Seq[String]].toSet
+        val incorrectIds = (query \ "incorrectAnswerIds") match {
+          case JArray(values) => values.map(_.extract[String]).toSet
+          case _ => Set[String]()
+        }
+        (queryExpression -> (correctIds.toSet, incorrectIds.toSet))
+      })
+    }).toMap
+  }
 
   def evaluate(writer: FileWriter) {
+    val queryAnswers = getQueryAnswers()
+
[…]

### 2016-03-07 src/main/scala/org/allenai/semparse/Experiments.scala

@@ -11,6 +11,9 @@ object Experiments {
   val experimentConfigs: Seq[(String, String, String, Boolean)] = {
     val datasets = Seq("large")//, "small")
     val modelTypes = Seq("formal")//, "distributional", "combined")
+
+    // I don't actually change these in the experiments for the ACL 2016 paper, but these were
+    // options used for the TACL 2015 paper.
     val rankings = Seq("query")//, "predicate")
     val ensembledEvaluation = Seq(false)//, true)
     val baselineConfigs = Seq(

### 2016-03-07 src/main/scala/org/allenai/semparse/Trainer.scala

@@ -82,9 +82,9 @@ object Trainer {
     // And, for now, we'll do this sequentially, as parallel output in the terminal would be a big
     // mess (not to mention it'd probably take too much memory).
     Experiments.experimentConfigs.foreach(config => {
-      val (data, modelType, ranking, usingGraphs) = config
+      val (data, modelType, ranking, ensembledEvaluation) = config
       val modelFile = getModelFile(data, ranking, modelType)
-      if (!canTrainConfig(data, modelType, ranking, usingGraphs)) {
+      if (!canTrainConfig(data, modelType, ranking, ensembledEvaluation)) {
         println(s"Configuration $config is not trainable.  Skipping...")
       } else if (fileUtil.fileExists(modelFile)) {
         println(s"Model already trained configuration $config (model file: $modelFile).  Skipping...")
@@ -92,7 +92,7 @@ object Trainer {
         println(s"Training model for $config")
         fileUtil.mkdirs(new File(modelFile).getParent())
         println("Creating environment (which trains and outputs the model)")
-        val env = createTrainingEnvironment(data, modelType, ranking, usingGraphs)
+        val env = createTrainingEnvironment(data, modelType, ranking, ensembledEvaluation)
       }
     })
   }

### 2016-03-08 src/main/scala/org/allenai/semparse/Experiments.scala
Fixed a few bugs, added MRR
Former-commit-id: 4c771b7f677f5a34b3a5829c0515d637e3fdaccb
Former-commit-id: df988c1dc701e977838f411f3980b08323b630f9

@@ -10,7 +10,7 @@ object Experiments {
   // very many more possibilities, this will need some re-thinking to be more sane.
   val experimentConfigs: Seq[(String, String, String, Boolean)] = {
     val datasets = Seq("large")//, "small")
-    val modelTypes = Seq("formal")//, "distributional", "combined")
+    val modelTypes = Seq("combined")//, "distributional", "formal")
 
     // I don't actually change these in the experiments for the ACL 2016 paper, but these were
     // options used for the TACL 2015 paper.

### 2016-03-08 src/main/scala/org/allenai/semparse/Evaluator.scala
Fixed a few bugs, added MRR
Former-commit-id: 4c771b7f677f5a34b3a5829c0515d637e3fdaccb

@@ -45,28 +45,29 @@ class Evaluator(
     val queryResponses = new mutable.ListBuffer[(String, String, Seq[String])]()
     var sentence = ""
     var query = ""
-    var predictions: List[String] = Nil
+    var predictions = new mutable.ListBuffer[String]
     for (line <- fileUtil.readLinesFromFile(resultsFile)) {
       if (line.isEmpty()) {
         if (!query.isEmpty()) {
-          queryResponses += Tuple3(sentence, query, predictions)
+          queryResponses += Tuple3(sentence, query, predictions.toSeq)
         }
         sentence = ""
         query = ""
-        predictions = Nil
+        predictions = new mutable.ListBuffer[String]
       }
       if (sentence.isEmpty()) {
         sentence = line
       } else if (query.isEmpty()) {
         query = line
       } else {
-        predictions = line :: predictions
+        predictions += line
       }
     }
 
     val numQueries = queryResponses.size
     var averagePrecisionSum = 0.0
     var weightedAPSum = 0.0
+    var reciprocalRankSum = 0.0
     var numNoAnswerQueries = 0
     var numAnnotatedTrueEntities = 0
     var numAnnotatedFalseEntities = 0
@@ -75,6 +76,9 @@ class Evaluator(
     for ((sentence, query, responses) <- queryResponses) {
       // I think I want this to crash if there's a mismatch, so we'll go with this for now.
       val (correctIds, incorrectIds) = queryAnswers(query)
+      numAnnotatedTrueEntities += correctIds.size
+      numAnnotatedFalseEntities += incorrectIds.size
+      if (correctIds.size == 0) numNoAnswerQueries += 1
 
       writer.write(sentence)
       writer.write("\n")
@@ -104,6 +108,9 @@ class Evaluator(
       val weightedAveragePrecision = averagePrecision * correctIds.size
       weightedAPSum += weightedAveragePrecision
       writer.write(s"WAP: $weightedAveragePrecision\n")
+      val reciprocalRank = Evaluator.computeReciprocalRank(entityScores, correctIds)
+      reciprocalRankSum += reciprocalRank
+      writer.write(s"RR: $reciprocalRank\n")
 
       val pointPrecision = Evaluator.compute11PointPrecision(entityScores, correctIds)
       writer.write("11-point precision/recall: [")
@@ -120,10 +127,10 @@ class Evaluator(
     // Now some global statistics.
[…]

### 2016-03-08 src/main/scala/org/allenai/semparse/Tester.scala

@@ -179,14 +179,16 @@ object Tester {
         val baselineModelFile = Trainer.getModelFile(data, ranking, modelType)
         (baselineModelFile +: baseInputFiles, baseExtraArgs)
       }
-      case "ensemble" => {
-        val serializedModelFile = Trainer.getModelFile(data, ranking, modelType)
-        val baselineModelFile = Trainer.getModelFile(data, ranking, modelType)
-        (baselineModelFile +: baseInputFiles, baseExtraArgs :+ serializedModelFile)
-      }
-      case "uschema" => {
-        val serializedModelFile = Trainer.getModelFile(data, ranking, modelType)
-        (baseInputFiles, baseExtraArgs :+ serializedModelFile)
+      case other => ensembledEvaluation match {
+        case true => {
+          val serializedModelFile = Trainer.getModelFile(data, ranking, modelType)
+          val baselineModelFile = Trainer.getModelFile(data, ranking, modelType)
+          (baselineModelFile +: baseInputFiles, baseExtraArgs :+ serializedModelFile)
+        }
+        case false => {
+          val serializedModelFile = Trainer.getModelFile(data, ranking, modelType)
+          (baseInputFiles, baseExtraArgs :+ serializedModelFile)
+        }
       }
     }
 

### 2016-03-10 src/main/scala/org/allenai/semparse/one_off/copy_annotations.scala
Copied dev set annotations to the old lfs file
Former-commit-id: 01129166f8cf9aeba5e358f7150e7afa90ecec98

@@ -1,0 +1,45 @@
+package org.allenai.semparse.one_off
+
+import edu.cmu.ml.rtw.users.matt.util.FileUtil
+
+import org.json4s._
+import org.json4s.JsonDSL._
+import org.json4s.native.JsonMethods._
+
+object copy_annotations {
+  implicit val formats = DefaultFormats
+  val fileUtil = new FileUtil
+  val copyFrom = "/home/mattg/clone/tacl2015-factorization/src/main/resources/acl2016_dev_set_annotated.json"
+  val copyTo = "/home/mattg/clone/tacl2015-factorization/src/main/resources/acl2016_dev_set_old_lfs_annotated.json"
+
+  def copyQueryAnnotations(json: (JValue, JValue)): JValue = {
+    val (copyFrom, copyTo) = json
+    val correct = copyFrom \ "correctAnswerIds"
+    val incorrect = copyFrom \ "incorrectAnswerIds"
+    val toCopy: JValue = ("correctAnswerIds" -> correct) ~ ("incorrectAnswerIds" -> incorrect)
+    copyTo removeField { _._1 == "incorrectAnswerIds" } removeField { _._1 == "correctAnswerIds" } merge toCopy
+
+  }
+
+  def copySentenceAnnotations(json: (JValue, JValue)): JValue = {
+    val (copyFrom, copyTo) = json
+    val queriesFrom = (copyFrom \ "queries").extract[Seq[JValue]]
+    val queriesTo = (copyTo \ "queries").extract[Seq[JValue]]
+    val copiedJson: JValue = queriesFrom.zip(queriesTo).map(copyQueryAnnotations)
+    val toCopy: JValue = ("queries" -> copiedJson)
+    copyTo removeField { _._1 == "queries" } merge toCopy
+  }
+
+  def main(args: Array[String]) {
+    val jsonToCopyFrom = parse(fileUtil.readLinesFromFile(copyFrom).mkString("\n"))
+    val queriesToCopyFrom = jsonToCopyFrom.extract[Seq[JValue]]
+    val jsonToCopyTo = parse(fileUtil.readLinesFromFile(copyTo).mkString("\n"))
+    val queriesToCopyTo = jsonToCopyTo.extract[Seq[JValue]]
+
+    val copiedJson = queriesToCopyFrom.zip(queriesToCopyTo).map(copySentenceAnnotations)
+
+    val writer = fileUtil.getFileWriter(copyTo)
+    writer.write(pretty(render(copiedJson)))
+    writer.close()
+  }
+}

### 2016-03-10 src/main/scala/org/allenai/semparse/Tester.scala
Fix a typo
Former-commit-id: c9875b2850506b9ed8a861fb8efb6fc4a3338630
Former-commit-id: 7dcdb87922cdd6ae8fc89424fe34477c98105e55

@@ -70,7 +70,7 @@ class Tester(
 
         // Now run the expression through the evaluation code and parse the result.
         println("Evaluating the expression")
-        val result = env.evalulateSExpression(expressionToEvaluate).getValue()
+        val result = env.evaluateSExpression(expressionToEvaluate).getValue()
         val entityScoreObjects = result.asInstanceOf[Array[Object]]
         println(s"Done evaluating, ranking ${entityScoreObjects.length} results")
         val entityScores = entityScoreObjects.map(entityScoreObject => {

### 2016-03-10 src/main/scala/org/allenai/semparse/one_off/dump_feature_weights.scala
Add a script to dump feature weights
Former-commit-id: ca5191c7b43b990f9cefb3d343e694548a54cf72

@@ -1,0 +1,84 @@
+package org.allenai.semparse.one_off
+
+import scala.collection.JavaConverters._
+
+import org.allenai.semparse.Environment
+import org.allenai.semparse.Experiments
+import org.allenai.semparse.Trainer
+
+import com.jayantkrish.jklol.lisp.ListParameterSpec
+import com.jayantkrish.jklol.lisp.SpecAndParameters
+import com.jayantkrish.jklol.models.parametric.TensorSufficientStatistics
+import com.jayantkrish.jklol.models.TableFactor
+import com.jayantkrish.jklol.tensor.SparseTensor
+import com.jayantkrish.jklol.util.IndexedList
+
+import edu.cmu.ml.rtw.users.matt.util.FileUtil
+
+object dump_feature_weights {
+
+  val fileUtil = new FileUtil
+
+  def getCatWordParamIndex(modelType: String): Int = modelType match {
+    case "formal" => 0
+    case "combined" => 1
+    case "distributional" => throw new IllegalStateException("distributional model has no such parameters")
+  }
+
+  def getRelWordParamIndex(modelType: String): Int = modelType match {
+    case "formal" => 1
+    case "combined" => 4
+    case "distributional" => throw new IllegalStateException("distributional model has no such parameters")
+  }
+
+  def getWordParams(params: SpecAndParameters, index: Int): SpecAndParameters = {
+      val paramsList = params.getParameterSpec.asInstanceOf[ListParameterSpec]
+      val childSpec = paramsList.get(index)
+      val childParams = paramsList.getParameter(index, params.getParameters())
+      new SpecAndParameters(childSpec, childParams)
+  }
+
+  def writeParams(filename: String, words: IndexedList[Object], params: SpecAndParameters) {
+    val out = fileUtil.getFileWriter(filename)
+    for ((word, index) <- words.items.asScala.map(_.asInstanceOf[String]).zipWithIndex) {
+      out.write(word)
+      out.write("\n")
+      val wordParams = getWordParams(params, index)
+      val tensor = wordParams.getParameters().asInstanceOf[TensorSufficientStatistics]
+      val summed = tensor.get().elementwiseProduct(SparseTensor.vector(1, 2, Array(1.0, -1.0))).sumOutDimensions(1)
+      val numMap = tensor.getStatisticNames().intersection(0)
+      val factor = new TableFactor(numMap, summed)
+      val assignments = factor.getMostLikelyAssignments(numMap.getDiscreteVariables.get(0).numValues)
[…]

### 2016-03-10 src/scripts/annotation/merge_query_annotations.sh
Done with annotation, I hope...
Former-commit-id: 3a98e474c61389840ec764e1472d45d9fc72c52d

@@ -1,8 +1,8 @@
 
-QUERY_FILE=~/clone/tacl2015-factorization/data/acl2016-test-augmented.txt
+QUERY_FILE=~/clone/tacl2015-factorization/data/tacl2015/tacl2015-test-new-lfs-augmented.txt
 
-ANNOTATION_FILE=~/clone/annotation-framework2/finished_annotations.tsv
+ANNOTATION_FILE=~/clone/annotation-framework/finished_annotations.tsv
 
-ANNOTATED_QUERY_FILE=~/clone/tacl2015-factorization/data/acl2016-test-augmented-annotated.txt
+ANNOTATED_QUERY_FILE=~/clone/tacl2015-factorization/data/tacl2015/tacl2015-test-new-lfs-augmented-annotated.txt
 
 ./src/scripts/annotation/merge_query_annotations2.py $ANNOTATION_FILE $QUERY_FILE > $ANNOTATED_QUERY_FILE

### 2016-03-10 papers/acl2016/paper.tex
Minor update to the paper (probably incorrect, though, as I am rerunning some of those experiments...)
Former-commit-id: 52339c6aaf7c567134a64e5e8ae7785ad23326af

--- 2016-03-07 papers/acl2016/paper.tex
@@
 
-Some related work on including structured information in distributional
-representations: Manaal's retrofitting semantic lexicons, Sebastian Riedel's
-``Injecting Logical Background Knowledge into Embeddings for Relation
-Extraction'', work on PRA and KBC more generally\ldots Also, the whole line of
-work on knowledge base embeddings (RESCAL, TransE, etc.) is at least slightly
-relevant here, as is PRA.  \mattnote{Actually write this section}.
+Some related work on including structured information in distributional representations: Manaal's
+retrofitting semantic lexicons, Sebastian Riedel's ``Injecting Logical Background Knowledge into
+Embeddings for Relation Extraction'', work on PRA and KBC more generally\ldots Also, the whole line
+of work on knowledge base embeddings (RESCAL, TransE, etc.) is at least slightly relevant here, as
+is PRA.  And all of the semantic parsing approaches that go from text to a pseudo-logical form,
+then to an actual Freebase query (Kwiatkowski, Reddy's TACL paper, Liang?) \mattnote{Actually write
+this section}.
 
@@
 \secref{better-lfs}); by being able to better model the relations between
-entities, MAP of all of the models is significantly improved.
+entities, MAP of all of the models is significantly improved.\footnote{Because
+of the large amount of annotation effort involved, we did not include the
+unique results from this run in the evaluation pool.  It is possible that this
+had the effect of lowering the MAP score for these methods.  However, the large
+majority of the predictions made by these methods were already annotated, and
+spot-checking the unannotated ones showed that practically all of the unique
+predictions made in this scenario were incorrect, and thus annotating them
+would not change the score.}
 

### 2016-03-11 papers/acl2016/paper.tex
Minor fixes to paper
Former-commit-id: b8fe45cdc4ed7ae27948c75d0d09d04474e0c829

@@
 will still give an unseen entity pair a score of 0, as it is identical to K\&M's
-model, but the formal component of our simples simply computes an observed
+model, but the formal component of our models simply computes an observed
 feature vector from Freebase for the entity pair.  As long as both entities
@@
 done by K\&M), as well as all entities directly connected to the query entities
-in Freebase, or connected by a mediator node\footnote{Mediators in Freebase are
+in Freebase, or connected by a mediator node.\footnote{Mediators in Freebase are
 used to capture relations with more than two arguments, such as employment
-tenure, which has an employer, and employee, a start date, and an end date.}.
+tenure, which has an employer, and employee, a start date, and an end date.}
 

### 2016-03-11 papers/acl2016/paper.tex
Added a figure to the intro, fixed some other stuff
Former-commit-id: 2a83901ecef50797aac82ce063aaa8e877194740

--- 2016-03-10 papers/acl2016/paper.tex
@@
 \usepackage{color}
+\usepackage{booktabs}
+\usepackage{subfig}
 
@@
 \newcommand{\mattnote}[1]{\textcolor{red}{NOTE: #1}}
-\newcommand{\blank}{\_\_\_}
+\newcommand{\blank}{\underline{\hspace{.5cm}}}
 \newcommand{\predicate}[1]{\ensuremath{\textsc{#1}}}
-\newcommand{\entity}[1]{\ensuremath{\mathrm{#1}}}
+\newcommand{\entity}[1]{\ensuremath{\textsc{#1}}}
 
@@
   are frequently CEOs or film producers.  We use these models in an
-  open-vocabulary semantic parsing task, showing a 63\% relative improvement in
-  mean average precision over a distributional-only model, and a X\%
-  improvement over a formal-only approach.
+  open-vocabulary semantic parsing task, showing a 62\% relative improvement in
+  mean average precision over a distributional-only model.
 
@@
 How should a computer program represent the meaning of a word or a phrase?  The
-answer to this question has a long and rich history.  Motivated by
-Harris's distributional
-hypothesis~\cite{harris-1954-distributional-hypothesis}, much work has been put
-into representing words as collections of the contexts in which they appear.
-Recent work with neural networks and word embeddings have shown that these
-representations can be very useful for a number of natural language processing
-tasks. \mattnote{cite something here}
+answer to this question has a long and rich history.  Motivated by Harris's
+distributional hypothesis~\cite{harris-1954-distributional-hypothesis}, much
+work has been put into representing words as collections of the contexts in
+which they appear.  Recent work with neural networks and word embeddings have
+shown that these representations can be very useful for a number of natural
+language processing tasks (see, e.g., the work Mikolov et
+al.~\shortcite{mikolov-2013-word2vec} and papers that cite them).  This
+approach to modeling semantics is appealing because word embeddings can be
+trained on unlabeled text, allowing for very broad coverage, although shallow,
+semantics.
+
+\begin{figure*}[ht]
+  \small
+  \begin{minipage}{0.28\linewidth}
+    \textbf{Input Text}\\Italian architect Andrea Palladio
+  \end{minipage}
+%
+  ~~ $\rightarrow$ ~~~~~~
+%
+  \begin{minipage}{0.7\linewidth}
+    \textbf{Logical Form}\\
+    $\predicate{architect}(\entity{Palladio})~\land~\predicate{architect\_N/N}(\entity{Italy}, \entity{Palladio})$
+  \end{minipage}
+
+  \vspace{.1in}
+  \begin{minipage}{0.5\linewidth}
+    \textbf{Category models}\\
+    \begin{tabular}{@{}lll}
+      \predicate{architect}: & $\theta$: &[.2, -.6, \ldots] \\
+      & $\omega$: & \textsc{type:architect} $\rightarrow$ .52 \\
+      &           & \textsc{type:designer} $\rightarrow$ .32 \\
+      &           & \textsc{nationality:Italy} $\rightarrow$ .20 \\
+      &           & $\cdots$
+    \end{tabular}
+  \end{minipage}
+  \begin{minipage}{0.5\linewidth}
+    \textbf{Relation models}\\
+    \begin{tabular}{@{}lll}
+      \predicate{architect\_N/N}: & $\theta$: &[-.9, .1, \ldots] \\
+      & $\omega$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ .29 \\
+      &           & \textsc{/structure/architect} $\rightarrow$ .11 \\
+      &           & \textsc{/person/ethnicity\textsuperscript{-1}} $\rightarrow$ .05 \\
+      &           & $\cdots$
+    \end{tabular}
+  \end{minipage}
+
+  \vspace{.1in}
+  \begin{minipage}{0.5\linewidth}
+    \textbf{Entity models}\\
+    \begin{tabular}{@{}lll}
+      \predicate{Palladio}: & $\phi$: &[.15, -.8, \ldots] \\
+      & $\psi$: & \textsc{type:architect} $\rightarrow$ 1 \\
+      &           & \textsc{type:designer} $\rightarrow$ 0 \\
+      &           & \textsc{nationality:Italy} $\rightarrow$ 1 \\
+      &           & $\cdots$
+    \end{tabular}
+  \end{minipage}
+  \begin{minipage}{0.5\linewidth}
+    \textbf{Entity pair models}\\
+    \begin{tabular}{@{}lll}
+      \predicate{(Italy, Palladio)}: & $\phi$: &[-.8, .2, \ldots] \\
+      & $\omega$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ 1 \\
+      &           & \textsc{/structure/architect} $\rightarrow$ 0 \\
+      &           & \textsc{/person/ethnicity\textsuperscript{-1}} $\rightarrow$ 0 \\
+      &           & $\cdots$
+    \end{tabular}
+  \end{minipage}
+
+  \vspace{-.1in}
+  \caption{Overview of the components of our model.  Given an input text, we
+  use a CCG parser and an entity linker to produce a logical form that is a
+  conjunction of predicates involving the entities in the text.  For each
+  predicate (both categories and relations), we learn a distributional vector
+  $\theta$, as well as weights $\omega$ associated with formal features from
+  Freebase (which are shortened to fit in the figure).  For each entity and
+  entity pair, we also learn a distributional vector $\phi$, and we extract a
+  feature vector $\psi$ from Freebase.  These models are combined to assign a
+  probability to the input text, assigning a high probability to the above
+  text, and a low probability to ``Italian architect Barack Obama''.}
+  \label{fig:overview}
+  \vspace{-.1in}
+\end{figure*}
 
@@
 leverage large, curated knowledge sources to perform various natural language
-processing tasks.  \mattnote{cite some semantic parsing papers}
-
-Both of these approaches to modeling predicate semantics have aspects that are
-very appealing.  It is relatively straightforward to learn a distributional
-vector for every word or phrase in a corpus, allowing easy generalization from
-words labeled with part of speech tags or dependency information to other words
-that are distributionally similar.  Yet distributional approaches struggle to
-make good use of the structured information contained in curated knowledge
-sources like Freebase and WordNet~\cite{wordnet-1995}.  On the other hand,
-because formal approaches to semantics typically model word meaning in terms of
-a structured knowledge source, their applicability is limited to the set of
-concepts represented in that knowledge source---a semantic parser trained with
-Freebase cannot even represent words whose meaning has no correlate in the
-Freebase ontology, such as ``front-runner'' and ``honcho''.
+processing
+tasks~\cite{zettlemoyer-2005-ccg,kwiatkowski-2013-ontology-matching,berant-2013-semantic-parsing-qa}.  However,
+semantic parsers are fundamentally limited by the schema of the ontology they
+are trained on---a semantic parser trained with Freebase cannot even represent
+words whose meaning has no correlate in the Freebase ontology, such as
+``front-runner'' and ``honcho''.
 
@@
 logical form: $\lambda x. \predicate{architect}(x) \land
-\predicate{architect\_N/N}(\entity{Italian}, x)$.  A typical semantic
+\predicate{architect\_N/N}(\entity{Italy},
+x)$.\footnote{\predicate{architect\_N/N} represents a noun-compound
+relationship between two entities mediated by the word ``architect'', as in
+``Italian architect Andrea Palladio''.  This is in contrast to, e.g.,
+\predicate{'s\_architect} or \predicate{architect\_of}, both of which also are
+mediated by ``architect'', but through different syntax.  N/N is how
+CCG~\cite{steedman-2006-ccg} represents a noun compound.} A typical semantic
 parser (e.g., that of Kwiatkowski et
 al.~\shortcite{kwiatkowski-2013-ontology-matching}) would then try to map this
-logical form to a Freebase query, matching \entity{Italian} to
-(\predicate{/people/person/nationality}, \entity{Italy}) and
-\predicate{architect} to (\predicate{/type/object/type},
-\entity{/architecture/architect}).  In contrast, we follow Krishnamurthy and
+logical form to a single Freebase query, likely involving
+(\predicate{/people/person/nationality}: \entity{Italy}) and
+(\predicate{/type/object/type}: \entity{/architecture/architect}).  Instead of
+restricting ourselves to modeling only what can be represented as a Freebase
+query, we follow Krishnamurthy and
 Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} in learning a
 model for each predicate that can give a \emph{score} to potential arguments.
-However, while the models of Krishnamurthy and Mitchell are purely
-distributional, using Freebase only as a means of finding entities in text, we
-inject additional information from Freebase into the models for each predicate.
-The model we learn for \predicate{architect} has a \emph{feature} capturing the
-fact that an entity has the type \entity{/architecture/architect} in Freebase,
-and the model for \predicate{architect\_N/N} has a \emph{feature} capturing
-whether the first argument is the country of nationality of the second
-argument.
+The model for \predicate{architect}, e.g., should give high scores to
+\entity{Andrea Palladio} and \entity{Frank Lloyd Wright}, and low scores to
+\entity{Italy}, \entity{BarackObama}, etc.  However, while the models of
+Krishnamurthy and Mitchell are purely distributional, using Freebase only as a
+means of finding entities in text, we inject additional information from
+Freebase into the models for each predicate.  The model we learn for
+\predicate{architect} has a \emph{feature} capturing the fact that an entity
+has the type \entity{/architecture/architect} in Freebase, and the model for
+\predicate{architect\_N/N} has a \emph{feature} capturing whether the first
+argument is the country of nationality of the second argument.  An overview of
+the components of our model is given in \figref{overview}.
 
-This is a fundamentally new kind of predicate semantics.  It is
-distributional---part of the model is still trained in a manner very similar to
-word2vec---yet it is also formal.  However, instead of committing to a single
-Freebase query to represent a phrase, as traditional formal approaches do, our
-models are flexible, encoding many possible Freebase queries as features that
-can give hints to the model.  Thus words that would be impossible to represent
-as a single Freebase query can still benefit from the information contained in
-Freebase---our model for ``front-runner'' learns that acceptable entities are
-politicians, even though there is no exact encoding of ``front-runner'' in
-Freebase.
+This is a new kind of predicate semantics.  It is distributional---part of the
+model is still trained in a manner very similar to word2vec---yet it is also
+formal.  However, instead of committing to a single Freebase query to represent
+a phrase, as traditional formal approaches do, our models are flexible,
+encoding many possible Freebase queries as features that can give hints to the
+model.  Thus words that would be impossible to represent as a single Freebase
+query can still benefit from the information contained in Freebase---our model
+for ``front-runner'' learns that acceptable entities are politicians, even
+though there is no exact encoding of ``front-runner'' in Freebase.
 
@@
 natural language query task.  Using web text linked to Freebase as our training
-and test data, we show a 63\% relative improvement over prior work, giving a
+and test data, we show a 62\% relative improvement over prior work, giving a
 new state-of-the-art result on this dataset.  In \secref{discussion}, we give a
@@
 
-\mattnote{Add a figure here to demonstrate the logical forms.}
-
-This system predicts a denotation $\gamma$, i.e., a set of Freebase
-entities, for a natural language text $s$, using the following
-probabilistic model:
-
-\begin{align*}
-P(\gamma | s) & = \sum_w \sum_\ell P(\gamma | \ell, w) P(w ; \theta, \phi) P(\ell | s)
-\end{align*}
-
-In this equation, $P(\ell | s)$ represents a semantic parser that
-produces a logical form $\ell$ given the text $s$. This logical form
-contains open-vocabulary predicates, as in the ``architect'' example
-above. This factor is deterministic, meaning that it assigns
-probability one to a single logical form. The second factor $P(w)$
-represents a distribution over possible worlds $w$, where a world is
-an assignment of truth values to all possible predicate
-instances. This distribution can be efficiently represented using a
-probabilistic database because each predicate instance is treated as
-an independent random variable. The truth probabilities of these
-variables are predicted using a matrix factorization approach similiar
-to that of Riedel et al., \shortcite{riedel-2013-mf-universal-schema};
-$\theta$ and $\phi$ represent the parameters of the matrix
-factorization. Finally, $P(\gamma | \ell, w)$ represents the
-deterministic evaluation of the logical form $\ell$ on the world $w$
-to produce a denotation $\gamma$. This factor is similar to other
-semantic parsing work, where it represents the deterministic
-evaluation of a query against a given database. Algorithms from the
-probabilistic databases community enable us to efficiently compute the
-marginal probability that an entity $e$ is in the denotation of a
-sentence, $\sum_\gamma P(e \in \gamma | s)$, for a large number of
-queries; we refer the reader to (TODO).
-
-The training problem in this model is to learn the parameters $\theta$
-and $\phi$ of the probabilistic database. The probability of a
-category instance $c(e)$ and relation instance $r(e_1, e_2)$ in the
+Krishnamurthy and
+Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} introduced a
+technique for learning semantic parsers with open predicate vocabularies.
+Instead of mapping text to Freebase queries, they applied the matrix
+factorization semantics used by Riedel et
+al.~\shortcite{riedel-2013-mf-universal-schema} in knowledge base completion to
+the task of learning predicate semantics in a semantic parser.  This method
+assigns truth values to instantiated predicates like
+\predicate{architect}(\entity{AndreaPalladio}) in a probabilistic database.
+The models Krishnamurthy and Mitchell use for the predicates and entities are
+essentially equivalent to modern techniques for constructing word embeddings,
+implicitly factorizing a cooccurrence matrix between categories and entities,
+and relations and entity pairs~\cite{levy-2014-w2v-as-mf}.  This implicit
+factorization has two sets of parameters: each predicate (category or relation)
+has a learned $k$-dimensional embedding $\theta$, and each entity and entity
+pair has a learned embedding $\phi$.  The probability assigned to a category
+instance $c(e)$ and relation instance $r(e_1, e_2)$ in the probabilistic
 database is given by:
@@
 \begin{align*}
-  P(c(e) & = \true{}) & = & \sigma ( \theta_c^T \phi_e ) \\
-  P(r(e_1, e_2) & = \true{}) & = & \sigma ( \theta_r^T \phi_{(e_1, e_2)} )
+  P(c(e) = \true{}) &= \sigma ( \theta_c^T \phi_e ) \\
+  P(r(e_1, e_2) = \true{}) &= \sigma ( \theta_r^T \phi_{(e_1, e_2)} )
 \end{align*}
 
-The parameters $\theta$ represent $k$-dimensional embeddings of each
-category and relation predicate, and the parameters $\phi$ represent
-$k$-dimensional embeddings of each Freebase entity and entity
-pair. The probability of a predicate instance is the inner product of
-the corresponding predicate and entity embeddings. Thus, predicates
-with nearby embeddings will have similar distributions over the
-entities in their denotation.
+The probability of a predicate instance is the (sigmoided) inner product of the
+corresponding predicate and entity embeddings. Thus, predicates with nearby
+embeddings will have similar distributions over the entities in their
+denotation.  The model is trained using a ranking objective that learns to rank
+the observed entities for each query above unobserved entities.  The
+probabilistic database produced by these predicate models is then input to a
+reasoning system that can handle a subset of first-order logic.
 
-The parameters $\theta$ and $\phi$ are learned from predicate/entity
-co-occurrence counts collected from a large corpus. The training data
-consists of query/entity pairs, $\{(\ell^i, e^i)\}$, where the entity
-$e^i$ is observed to be an element of $\ell^i$'s denotation. These
-pairs are collected by semantically parsing entity-linked sentences
-and simplifying the resulting logical forms to identify conjunctions
-of predicates where all arguments are bound to specific
-entities. Extracting an entity from this conjunction results in a
-query/entity pair. The model is trained using a ranking objective that
-learns to rank the observed entities for each query above unobserved
-entities.
+In this paper, we use the system produced by Krishnamurthy and Mitchell,
+changing only the models of predicate semantics, as described in
+\secref{method}.
 
@@
 described in \secref{jayant-semparse}.  The combined model is the model
-described in \secref{sec:formal-and-distributional}, while the formal-only
+described in \secref{formal-and-distributional}, while the formal-only
 model removes the distributional component from the combined model (i.e., all
@@
   \centering
-  \begin{tabular}{|l|r|r|}
-    \hline
-    Method & MAP & MRR \\
-    \hline
-    Distributional-only & .239 & ?? \\
-    Distributional-only (old lfs) & ?? & ?? \\
-    \hline
-    Formal-only & ?? & ?? \\
-    Formal-only (old lfs) & ?? & ?? \\
-    \hline
-    Combined model & \textbf{.340} & ?? \\
-    Combined model (old lfs) & ?? & ?? \\
-    \hline
+  {\small
+    \begin{tabular}{lccc}
+      \toprule
+      Method & MAP & Weighted MAP & MRR \\
+      \midrule
+      Distributional-only & .284 & .371 & .379 \\
+      \ \ \ (old lfs) & ?? & ?? & ?? \\
+      \midrule
+      Formal-only & .276 & .469 & .334 \\
+      \ \ \ (old lfs) & ?? & ?? & ?? \\
+      \midrule
+      Combined model & \textbf{.335} & \textbf{.477} & \textbf{.429} \\
+      \ \ \ (old lfs) & ?? & ?? & ?? \\
+      \bottomrule
     \end{tabular}
+  }
   \caption{Results on the development set for our fill-in-the-blank task.  The
@@
   \centering
-  \begin{tabular}{|l|r|r|}
-    \hline
-    Method & MAP & MRR \\
-    \hline
-    Distributional-only & .231 & ?? \\
-    \ \ \ -related entities & .170 & ?? \\
-    \hline
-    Formal-only & ?? & ?? \\
-    \hline
-    Combined model & \textbf{.376} & ?? \\
-    \hline
+  {\small
+    \begin{tabular}{lccc}
+      \toprule
+      Method & MAP & Weighted MAP & MRR \\
+      \midrule
+      Distributional-only & .229 & .275 & .312 \\
+      \ \ \ -related entities & .163 & .163 & .288 \\
+      \midrule
+      Formal-only & .355 & .495 & .419 \\
+      \midrule
+      Combined model & \textbf{.370} & \textbf{.513} & \textbf{.469} \\
+      \bottomrule
     \end{tabular}
+  }
   \caption{Results on the final test set for our fill-in-the-blank task.  The
-  combined model improves MAP by 63\% relative to the distributional-only
+  combined model improves MAP by 62\% relative to the distributional-only
   baseline.  Additionally, allowing the distributional-only model to use
-  Freebase to propose candidates improves MAP by 6 points absolute due to
+  Freebase to propose candidates improves MAP by 6.6 points absolute due to
   improved recall.}
@@
 final test set, as well.  The performance improvement seen by the combined
-model is actually larger on this set, going from a MAP of .231 to .376, a 63\%
+model is actually larger on this set, going from a MAP of .229 to .370, a 62\%
 relative improvement.  In this table, we also show the improvement gained by
@@
 score of 0), the additional recall provided by being able to propose more
-entities raises MAP of the distributional-only model from .170 to .231.
+entities raises MAP of the distributional-only model from .163 to .229.
 

### 2016-03-11 papers/acl2016/paper.tex
Shorten some references to K&M, add a couple more results
Former-commit-id: bfe39fdd2351aa7c7d3f5eea8e44eca29266fb29

@@
 
-  \vspace{.1in}
+  \vspace{.2in}
   \begin{minipage}{0.5\linewidth}
@@
 processing
-tasks~\cite{zettlemoyer-2005-ccg,kwiatkowski-2013-ontology-matching,berant-2013-semantic-parsing-qa}.  However,
-semantic parsers are fundamentally limited by the schema of the ontology they
-are trained on---a semantic parser trained with Freebase cannot even represent
-words whose meaning has no correlate in the Freebase ontology, such as
-``front-runner'' and ``honcho''.
+tasks~\cite{zettlemoyer-2005-ccg,kwiatkowski-2013-ontology-matching,berant-2013-semantic-parsing-qa}.
+However, semantic parsers are fundamentally limited by the schema of the
+ontology they are trained on---a semantic parser trained with Freebase cannot
+even represent words whose meaning has no correlate in the Freebase ontology,
+such as ``front-runner'' and ``honcho''.
 
@@
 Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} introduced a
-technique for learning semantic parsers with open predicate vocabularies.
-Instead of mapping text to Freebase queries, they applied the matrix
-factorization semantics used by Riedel et
+technique for learning semantic parsers with open predicate vocabularies
+(hereafter referred to as K\&M).  Instead of mapping text to Freebase queries,
+they applied the matrix factorization semantics used by Riedel et
 al.~\shortcite{riedel-2013-mf-universal-schema} in knowledge base completion to
@@
 \predicate{architect}(\entity{AndreaPalladio}) in a probabilistic database.
-The models Krishnamurthy and Mitchell use for the predicates and entities are
-essentially equivalent to modern techniques for constructing word embeddings,
-implicitly factorizing a cooccurrence matrix between categories and entities,
-and relations and entity pairs~\cite{levy-2014-w2v-as-mf}.  This implicit
-factorization has two sets of parameters: each predicate (category or relation)
-has a learned $k$-dimensional embedding $\theta$, and each entity and entity
-pair has a learned embedding $\phi$.  The probability assigned to a category
-instance $c(e)$ and relation instance $r(e_1, e_2)$ in the probabilistic
-database is given by:
+The models K\&M use for the predicates and entities are essentially equivalent
+to modern techniques for constructing word embeddings, implicitly factorizing a
+cooccurrence matrix between categories and entities, and relations and entity
+pairs~\cite{levy-2014-w2v-as-mf}.  This implicit factorization has two sets of
+parameters: each predicate (category or relation) has a learned $k$-dimensional
+embedding $\theta$, and each entity and entity pair has a learned embedding
+$\phi$.  The probability assigned to a category instance $c(e)$ and relation
+instance $r(e_1, e_2)$ in the probabilistic database is given by:
 
@@
 
-In this paper, we use the system produced by Krishnamurthy and Mitchell,
-changing only the models of predicate semantics, as described in
-\secref{method}.
+In this paper, we use the system produced by K\&M, changing only the models of
+predicate semantics, as described in \secref{method}.
 
@@
 \secref{formal-and-distributional} we describe how we modify Krishnamurthy and
-Mitchell's (K\&M's) semantic parser to include features from a formal knowledge base.
-In \secref{computing-pmi} we describe how we select those features for each
-predicate.  The remaining two sections then describe other improvements we made
-to K\&M's semantic parsing model: lexicalizing preposition and noun-compound
-predicates, and using the Freebase graph to select candidate entities.
+Mitchell's (K\&M's) semantic parser to include features from a formal knowledge
+base.  In \secref{computing-pmi} we describe how we select those features for
+each predicate.  The remaining two sections then describe other improvements we
+made to K\&M's semantic parsing model: lexicalizing preposition and
+noun-compound predicates, and using the Freebase graph to select candidate
+entities.
 
@@
 
-We also used the test set created by Krishnamurthy and Mitchell, which contains
+We also used the test set created by K\&M, which contains
 220 queries generated in the same fashion as the training data from a separate
@@
       Distributional-only & .284 & .371 & .379 \\
-      \ \ \ (old lfs) & ?? & ?? & ?? \\
+      \ \ \ (old lfs) & .269 & .330 & .380 \\
       \midrule
       Formal-only & .276 & .469 & .334 \\
-      \ \ \ (old lfs) & ?? & ?? & ?? \\
+      \ \ \ (old lfs) & .231 & .358 & .216 \\
       \midrule
       Combined model & \textbf{.335} & \textbf{.477} & \textbf{.429} \\
-      \ \ \ (old lfs) & ?? & ?? & ?? \\
+      \ \ \ (old lfs) & .313 & .396 & .413 \\
       \bottomrule
@@
 \secref{better-lfs}); by being able to better model the relations between
-entities, MAP of all of the models is significantly improved.\footnote{Because
-of the large amount of annotation effort involved, we did not include the
-unique results from this run in the evaluation pool.  It is possible that this
-had the effect of lowering the MAP score for these methods.  However, the large
-majority of the predictions made by these methods were already annotated, and
-spot-checking the unannotated ones showed that practically all of the unique
-predictions made in this scenario were incorrect, and thus annotating them
-would not change the score.}
+entities, MAP of all of the models is improved.  Not surprisingly, the
+improvement is more pronounced for the models that have formal features, which
+can make better use of rich information from Freebase with our improved logical
+forms.\footnote{Because of the large amount of annotation effort involved, we
+did not include the unique results from this run in the evaluation pool.  This
+has the effect of slightly lowering the MAP score for these methods.  However,
+the large majority of the predictions made by these methods were already
+annotated, and spot-checking the unannotated predictions seemed to indicate
+that annotating them would not substantially change the result shown.}
 

### 2016-03-11 src/main/scala/org/allenai/semparse/one_off/test_significance.scala
Added a script to test for statistical significance
Former-commit-id: ff682dfb2f0dac0fbe4ab72e2f41a45331a18366

@@ -1,0 +1,25 @@
+package org.allenai.semparse.one_off
+
+import edu.cmu.ml.rtw.pra.experiments.ExperimentScorer
+import edu.cmu.ml.rtw.users.matt.util.FileUtil
+
+// TODO(matt): This should be put into a common space, not a one_off script.
+object test_significance {
+  val combined_ap_file = "/home/mattg/clone/tacl2015-factorization/results/large/combined_ap.txt"
+  val distributional_ap_file = "/home/mattg/clone/tacl2015-factorization/results/large/distributional_ap.txt"
+  val formal_ap_file = "/home/mattg/clone/tacl2015-factorization/results/large/formal_ap.txt"
+
+  val fileUtil = new FileUtil
+
+  def main(args: Array[String]) {
+    val combined_ap = fileUtil.getLineIterator(combined_ap_file).map(_.split(": ")(1).toDouble).toSeq
+    val distributional_ap = fileUtil.getLineIterator(distributional_ap_file).map(_.split(": ")(1).toDouble).toSeq
+    val formal_ap = fileUtil.getLineIterator(formal_ap_file).map(_.split(": ")(1).toDouble).toSeq
+    println("Combined MAP: " + (combined_ap.sum / combined_ap.size))
+    println("Distributional MAP: " + (distributional_ap.sum / distributional_ap.size))
+    println("Formal MAP: " + (formal_ap.sum / formal_ap.size))
+    println("Combined vs. distributional: " + ExperimentScorer.getPValue(combined_ap.zip(distributional_ap)))
+    println("Combined vs. formal: " + ExperimentScorer.getPValue(combined_ap.zip(formal_ap)))
+    println("Distributional vs. formal: " + ExperimentScorer.getPValue(distributional_ap.zip(formal_ap)))
+  }
+}

### 2016-03-11 src/main/scala/org/allenai/semparse/Experiments.scala
Minor bug fix
Former-commit-id: d5a88a1a43c33c2cde7a9884745e96368a56cad5
Former-commit-id: f3b776ba603bfbd76db7416d22e186969fce1542

@@ -46,7 +46,7 @@ object Experiments {
   val EVAL_USCHEMA_FILE = "src/main/lisp/eval_uschema.lisp"
   val EVAL_ENSEMBLE_FILE = "src/main/lisp/eval_ensemble.lisp"
 
-  val SMALL_BASE_DATA_FILE = "data/tacl2015-training-sample.txt"
+  val SMALL_BASE_DATA_FILE = "data/tacl2015/tacl2015-training-sample.txt"
   val SMALL_WORD_FILE = "data/small/words.lisp"
   val SMALL_ENTITY_FILE = "data/small/entities.lisp"
   val SMALL_JOINT_ENTITY_FILE = "data/small/joint_entities.lisp"

### 2016-03-14 papers/acl2016/paper.tex
Mostly-finished draft of the ACL 2016 paper
Former-commit-id: 5826274506c82738642a90457ebb0a27b8b24617

@@
 \usepackage{subfig}
+\usepackage{tikz}
+\usetikzlibrary{bayesnet}
 
@@
 \begin{align*}
-  P(c(e) = \true{}) &= \sigma ( \theta_c^T \phi_e ) \\
-  P(r(e_1, e_2) = \true{}) &= \sigma ( \theta_r^T \phi_{(e_1, e_2)} )
+  P(c(e)) &= \sigma ( \theta_c^T \phi_e ) \\
+  P(r(e_1, e_2)) &= \sigma ( \theta_r^T \phi_{(e_1, e_2)} )
 \end{align*}
@@
 In this paper, we use the system produced by K\&M, changing only the models of
-predicate semantics, as described in \secref{method}.
+predicate semantics, as described in \secref{method}.  K\&M introduced several
+variations of their parser; in this work, we use their query ranking objective,
+as it had the best performance, and we evaluate the model they called
+``Factorization'', without ensembling it with a clustering baseline.
 
 \subsection{Subgraph feature extraction}
+
+\begin{figure}
+  {\center
+  \begin{tikzpicture}[
+    ->,
+    shorten >=1pt,
+    auto,
+    node distance=3cm,
+    thick,
+    main node/.style={draw=none,fill=none}
+    ]
+
+    \node[main node] (1) {\entity{Palladio}};
+    \node[main node] (2) [right=4cm of 1] {\entity{Italy}};
+    \node[main node] (3) [below=1.7cm of 1] {\entity{architect}};
+    \node[main node] (4) [below=1.7cm of 2] {\entity{country}};
+    \node[main node] (5) [below right=.1cm and .5cm of 3] {\entity{Villa Capra}};
+
+    \path[]
+      (1) edge node [sloped, anchor=center, above] {\predicate{nationality}} (2)
+      (1) edge node [sloped, anchor=center, above] {\predicate{type}} (3)
+      (1) edge node [sloped, anchor=center, above] {\predicate{designed}} (5)
+      (2) edge node [sloped, anchor=center, above] {\predicate{type}} (4)
+      (5) edge node [sloped, anchor=center, above] {\predicate{located\_in}} (2);
+  \end{tikzpicture}
+  }
+  \textbf{Features between \entity{Palladio} and \entity{Italy}}:\\
+  \textless\predicate{nationality}\textgreater\\
+  \textless\predicate{designed}, \predicate{located\_in}\textgreater
+  \caption{A subset of the Freebase graph, and some example extracted features
+  between \entity{Palladio} and \entity{Italy}.  The actual Freebase relations
+  and entity identifiers used are modified here to aid readability.}
+  \label{fig:sfe}
+\end{figure}
 
@@
 extracts various kinds of features from that subgraph, such as the set of edge
-sequences that connect the two nodes.  \mattnote{Give an example graph with
-features.}  Gardner and Mitchell used these features to perform link
-prediction in the graph, using characteristics of the subgraph around two nodes
-to determine if an edge of a particular type should exist between those nodes
-(when the graph corresponds to a knowledge base like Freebase, this task is
-also known as knowledge base completion). Gardner and Mitchell only used these
-features to model formal KB relations, however.
+sequences that connect the two nodes.  \figref{sfe} shows an example subgraph,
+centered around \entity{Andrea Pallado} and \entity{Italy}, and features that
+would be extracted for that entity pair.  Gardner and Mitchell used these
+features to perform link prediction in the graph, using characteristics of the
+subgraph around two nodes to determine if an edge of a particular type should
+exist between those nodes.\footnote{When the graph corresponds to a knowledge
+base like Freebase, this task is also known as knowledge base completion.}
+Gardner and Mitchell only used these features to model formal KB relations,
+however.
 
@@
 
-Some related work on including structured information in distributional representations: Manaal's
-retrofitting semantic lexicons, Sebastian Riedel's ``Injecting Logical Background Knowledge into
-Embeddings for Relation Extraction'', work on PRA and KBC more generally\ldots Also, the whole line
-of work on knowledge base embeddings (RESCAL, TransE, etc.) is at least slightly relevant here, as
-is PRA.  And all of the semantic parsing approaches that go from text to a pseudo-logical form,
-then to an actual Freebase query (Kwiatkowski, Reddy's TACL paper, Liang?) \mattnote{Actually write
-this section}.
+There is a large body of other work that is closely related to what is
+presented in this paper.  Two recent papers that also attempt to include some
+form of structured knowledge into distributional representations are those by
+Faruqui et al.~\shortcite{faruqui-2015-retrofitting-word-vectors}, and by
+Rockt\"{a}schel et al.~\shortcite{rocktaschel-2015-logical-embeddings}.  A key
+difference between their approaches and ours is that they use the structured
+information only to modify distributional representations, while we include the
+structured information directly in our models, training weights for structured
+information jointly with distributional representations.  Also conceptually
+similar is the Additive Relational Effects model for knowledge base completion
+by Nickel et al.~\shortcite{nickel-2014-are}, which tries to factorize the
+residual of a KB tensor that cannot be explained by observable features that
+are somewhat similar to the formal features we use in this model.  But while
+this model is conceptually similar, it is computationally quite different, and
+would be rather difficult to use in the setting we explore in this work.
+
+Our work draws a lot of inspiration from recent work on knowledge base
+completion.  We are building on top of work in embedding the entities and
+relations in a knowledge
+base~\cite{riedel-2013-mf-universal-schema,nickel-2011-rescal,bordes-2013-transe},
+as well as work on graph-based methods for reasoning with knowledge
+bases~\cite{lao-2010-original-pra,gardner-2014-vector-space-pra,neelakantan-2015-rnn-kbc}.
+
+Lastly, there is an extensive literature on building semantic parsers to answer
+questions against a structured knowledge
+base~\cite{zettlemoyer-2005-ccg,berant-2013-semantic-parsing-qa,%
+kwiatkowski-2013-ontology-matching,krishnamurthy-2012-semantic-parsing}.  The
+vast majority of this work is focused on matching natural language text to
+statements in a specific ontology, with no hope of assigning meaning to
+language that falls outside of that ontology.  Only very recently has there
+been work attempting to learn broad coverage meaning representations in
+semantic parsers.  In addition to the work by Krishnamurthy and Mitchell which
+we extend in this paper, there was recently a nice piece of work by Choi et
+al.~\shortcite{choi-2015-semantic-parsing-partial-ontologies}.  The aim of
+their work is, like typical semantic parsers, to map text onto a single formal
+statement, but they allow some of the predicates to be ``open'' predicates not
+contained in the Freebase ontology.  A key difference between their work and
+ours is that we score surface logical forms directly, using a weighted
+combination of many Freebase queries, instead of trying to map them to a single
+Freebase logical form.  Additionally, while their system might learn that
+``front-runner'' should be modeled as an open predicate that has no
+representation in Freebase, they have no method to assign any further meaning
+to that predicate, while our models learn both distributional and formal
+information about the meaning of ``front-runner''.
 
@@
 
-\subsection{Adding SFE features to Jayant's models}
+\subsection{Formal features for predicate semantics}
 \label{sec:formal-and-distributional}
 
-The modification we make to K\&M's semantic parser is simple.  For each entity
-and entity pair in the data we compute an SFE feature vector $\psi(e)$ and
-$\psi(e_1, e_2)$.  For each category and relation, we select a subset of the
-features to have associated weights $\omega_c$ and $\omega_r$.  We then add the
-weights $\omega_c$ and $\omega_r$ as parameters to be learned for each
+We inject information from a formal knowledge base into our models of predicate
+semantics simply by augmenting the learned distributional feature vectors with
+formal features.
+
+For each entity and entity pair in the data we compute an SFE feature vector
+$\psi(e)$ and $\psi(e_1, e_2)$.  For entity pairs, the vector $\psi(e_1, e_2)$
+is a sparse binary vector containing indicator features for all edge sequences
+that connect nodes $e_1$ and $e_2$ in the Freebase graph, up to length 4.
+These features are shown for the entity pair (\entity{Palladio},
+\entity{Italy}) in the example graph in \figref{sfe}.  For entities, we extract
+similar features to form the sparse binary vector $\psi(e)$.  These features
+are of two types: (1) edge sequences that begin at node $e$ (up to length two),
+and (2) edge sequences that begin at node $e$ along with the node at the end of
+the sequence.  For example, all of the features listed in \figref{sfe} for the
+entity pair (\entity{Palladio}, \entity{Italy}) are also valid features of type
+(1) for the entity \entity{Palladio}, as well as the features
+\textless\predicate{type}\textgreater and
+\textless\predicate{designed}\textgreater.  Examples of of type (2) features
+are \textless\predicate{type}\textgreater:\entity{architect}, and
+\textless\predicate{nationality}\textgreater:\entity{Italy}.  Intuitively,
+features of type (1) capture the fact that an entity participates in particular
+kinds of relations, such as designing architectural structures, while features
+of type (2) capture the way an entity is related to particular other entities.
+Features of type (2) are very specific, and are most useful in practice when
+the entity in the feature is a type node, such as with
+\textless\predicate{type}\textgreater:\entity{architect}, though occasionally
+features of this type involving other entities are also selected in our feature
+selection process.
+
+For each category and relation, we select a subset of the SFE features in the
+vectors $\psi$ to have associated weights $\omega_c$ and $\omega_r$.  We then
+add the weights $\omega_c$ and $\omega_r$ as parameters to be learned for each
 predicate, and we add the feature vectors $\psi(e)$ and $\psi(e_1, e_2)$ as
@@
 \begin{align*}
-  P(c(e) & = \true{}) & = & \sigma ( \theta_c^T \phi_e + \omega_c^T \psi_c(e)) \\
-  P(r(e_1, e_2) & = \true{}) & = & \sigma ( \theta_r^T \phi_{(e_1, e_2)} + \omega_r^T \psi_r(e_1, e_2) )
+  P(c(e)) &= \sigma ( \theta_c^T \phi_e + \omega_c^T \psi_c(e)) \\
+  P(r(e_1, e_2)) &= \sigma ( \theta_r^T \phi_{(e_1, e_2)} + \omega_r^T \psi_r(e_1, e_2) )
 \end{align*}
@@
 
-Note that now there are three sets of parameters to be learned by the semantic
-parser: (1) $\theta$, low-dimensional distributional vectors trained for each
-predicate; (2) $\phi$, low-dimensional distributional vectors trained for each
-entity and entity pair; and (3) $\omega$, weights associated with the selected
-formal SFE features for each predicate.  All of these parameters are optimized
-jointly, using the same ranking objective used by K\&M.
+We pause here to note that these features obtained from SFE correspond exactly
+to a limited set of horn clauses using the Freebase vocabulary, which in turn
+can be seen as Freebase queries that define sets of entities or entity pairs.
+By associating a number of these features with each predicate and assigning
+them weights, what we are effectively doing is mapping language onto a weighted
+combination of possible Freebase statements, instead of onto a single Freebase
+query, as is typically done in the semantic parsing literature.  This is a
+fundamentally new kind of predicate semantics that has not been used previously
+in semantic parsers.
+
+Note also that in our combined model there are now three sets of parameters to
+be learned by the semantic parser: (1) $\theta$, low-dimensional distributional
+vectors trained for each predicate; (2) $\phi$, low-dimensional distributional
+vectors trained for each entity and entity pair; and (3) $\omega$, weights
+associated with the selected formal SFE features for each predicate.  All of
+these parameters are optimized jointly, using the same ranking objective used
+by K\&M.
 
@@
 counts below some threshold, we pick the $k$ features with the highest PMI
-values for each predicate to use in our model.
+values for each predicate to use in our model.\footnote{We used $k=100$ in this
+paper.}
 
@@
 
+On both of these datasets, the difference between the combined model and the
+distributional model is statistically significant (by a paired permutation
+test, $p < 0.05$).  The difference between the combined model and the formal
+model, and between the formal model and the distributional model, are not
+statistically significant, as each method has certain kinds of queries that it
+performs well on.  Only the combined model is able to consistently outperform
+the distributional model on all kinds of queries.
+
 \section{Discussion}
@@
 
-\mattnote{I will add more detail to some of these examples; I ran out of
-time...}
+Here we discuss some of the successes and failures of our model.
 
-Our model does very well on most predicates that have clear Freebase
-correlates: prime ministers, presidents, newspapers, companies, and so on.  The
-query ``French newspaper \blank{}'' gets almost perfect average precision.
+When a predicate has a clear Freebase correlate (such a
+\predicate{prime\_minister\_N/N}, \predicate{president\_of},
+\predicate{newspaper}, \predicate{company}, etc.), our formal model is able to
+capture the meaning very well.  The query ``French newspaper \blank{}'' has
+nearly perfect average precision, for instance, as does ``Israeli prime
+minister \blank{}''.  The distributional model does much less well here, and in
+combination, the distributional component of the model occasionally lowers its
+performance relative to the formal model.\footnote{This is why the difference
+between the formal model and the combined model is not statistically
+significant.}
 
-It does less well on predicates that do not match as closely with Freebase,
-such as ``Microsoft head honcho \blank{}'', ``Patriots linebacker \blank{}'',
-etc.  The combined model handily beats the distributional-only model in most of
-these cases, but it does not have the nearly-perfect AP seen in the more crisp
-queries above.  The ``head honcho'' example is particularly informative---this
+The formal models also perform well on predicates that can be partially
+expressed by Freebase, such as ``Microsoft head honcho \blank{}'', ``The United
+States, \blank{}'s closest ally'', and ``Patriots linebacker \blank{}'', though
+the models do not have the nearly-perfect AP that they do for the more crisp
+queries above.  The ``head honcho'' example is particularly instructive---this
 is a phrase that essentially means ``leader'', and the features learned by the
@@
 
-For ``Patriots linebacker \blank{}'', the issue is that the features for
+For ``Patriots linebacker \blank{}'', the reason that this can only be
+partially expressed in terms of Freebase queries is that the features for
 \predicate{linebacker\_N/N} are able to capture which athletes play for which
 teams, but they cannot distinguish well between what positions those athletes
-play, so Patriots quarterbacks, wide receivers, and running backs are scored
-highly for this query.  This could be fixed by using more complex features for
-relation predicates, instead of just edge sequences, but that would explode the
-feature space and make the feature selection process more difficult.  It could
-also be fixed by better negative example selection during training.
+play.  This leads to Patriots quarterbacks, wide receivers, and running backs
+being scored highly for this query.  This issue could be fixed by using more
+complex features for relation predicates, instead of just edge sequences,
+though that would drammatically increase the size of the feature space and make
+the feature selection process much more difficult.  It could also potentially
+be mitigated by better negative example selection during training.
 
-There are also cases where a predicate has so many possible entities types in
-Freebase that the it cannot learn models that are useful for all queries.  A
-good example of this is ``\blank{} is a NASA mission''.
+There are also cases where a predicate has so many possible entity types in
+Freebase (or no close correlate at all) that the PMI feature selection process
+does not find features that are useful for all queries.  A good example of this
+is ``\blank{} is a NASA mission''; in this case, the distributional model
+outperforms the formal model, because it has learned associations between
+particular NASA missions and NASA.
 
-The SFE features we used cannot capture time very well.  ``17th century French
-mathematician \blank{}''...
+While the new logical forms we introduced in \secref{better-lfs} improved the
+performance of the models, there is still a lot of room for further
+improvement.  For instance, ``Vice president Al Gore'' is modeled as
+$\predicate{vice}(\entity{Al Gore}) \land \predicate{president}(\entity{Al
+Gore})$.  Better processing of multi-word expressions would allow for more
+crisp models of the predicates, so the model for \predicate{president} could
+have more specific features.  Also, the predicate \predicate{head\_honcho\_N/N}
+was never seen in the training data, so an \predicate{unknown} predicate was
+used to score the relation in the phrase ``Microsoft head honcho \blank{}''.
+This means the model had to rely solely on knowing which entities are
+``honchos'' and which entities are related to Microsoft in some unknown manner.
+The predicate \predicate{honcho\_N/N} \emph{is} seen in the training data,
+however; some kind of backoff to simpler phrases for unseen predicates would be
+useful here.
 
-Because of the simple logical forms produced by the semantic parser we used, we
-cannot model some complex phenomena, such as counting and other things.  This
-is an orthogonal issue to the predicate semantics we're concerned with in this
-paper, however.
-
-Vice president Al Gore is modeled as $\predicate{vice}(\entity{Al Gore}) \land
-\predicate{president}(\entity{Al Gore})$.  Clearly there is room for better
-processing of multi-word expressions.
-
-\predicate{head\_honcho\_N/N} was never seen in the training data, so the
-phrase ``Microsoft head honcho \blank{}'' has to rely on knowing whether an
-entity is a ``honcho'' and what entities are related to Microsoft by an unknown
-predicate.  \predicate{honcho\_N/N} \emph{is} seen in the training data,
-however; some kind of backoff to simpler phrases would be useful here.
-
-Using connected entities in Freebase as additional candidates during inference
-is helpful, but it is not very sophisticated.  It over-generates for a lot of
-entities and predicates, and under-generates for others.  A mechanism for
-tailoring a search over Freebase to a particular query would be useful, though
-that would move the model more into the realm of reinforcement learning.
+Finally, using connected entities in Freebase as additional candidates during
+inference is helpful, but it is not very sophisticated.  It over-generates for
+a lot of entities and predicates, and under-generates for others.  A mechanism
+for tailoring a search over Freebase to a particular query would be useful,
+though it would add a lot of additional complexity, possibly requiring methods
+from reinforcement learning to resolve.
 
@@
 
-\mattnote{TODO}
+In this paper, we have considered the problem of assigning meaning to
+predicates (both categories and relations) in natural language, using both
+distributional information and information from a formal knowledge base.  To do
+this, we developed a model that can represent words as a weighted combination
+of formal statements, and trained that model jointly with a distributional
+model of word meaning.  This joint model achieved a relative gain of 62\% in
+mean average precision over the distributional model alone.  We also introduced
+a better mapping from surface text to logical forms, and a simple method for
+using Freebase to find candidate entities during inference.  Taken together,
+the methods introduced in this paper improved mean average precision on a
+fill-in-the-blank natural language query task from .163 to .370, a 127\%
+relative improvement.
 

### 2016-03-14 src/main/scala/org/allenai/semparse/one_off/add_rel_variables_to_test_file.scala
Updated some dependencies
Former-commit-id: 66ba1bfba0609f661f85557799693199a9738ec9

@@ -6,7 +6,7 @@ import org.json4s.native.JsonMethods._
 
 import scala.collection.mutable
 
-import edu.cmu.ml.rtw.users.matt.util.FileUtil
+import com.mattg.util.FileUtil
 
 class TestJsonAugmenter {
   implicit val formats = DefaultFormats

### 2016-03-14 src/main/scala/org/allenai/semparse/one_off/copy_annotations.scala

@@ -1,6 +1,6 @@
 package org.allenai.semparse.one_off
 
-import edu.cmu.ml.rtw.users.matt.util.FileUtil
+import com.mattg.util.FileUtil
 
 import org.json4s._
 import org.json4s.JsonDSL._

### 2016-03-14 src/main/scala/org/allenai/semparse/one_off/dump_feature_weights.scala

@@ -13,7 +13,7 @@ import com.jayantkrish.jklol.models.TableFactor
 import com.jayantkrish.jklol.tensor.SparseTensor
 import com.jayantkrish.jklol.util.IndexedList
 
-import edu.cmu.ml.rtw.users.matt.util.FileUtil
+import com.mattg.util.FileUtil
 
 object dump_feature_weights {
 

### 2016-03-14 src/main/scala/org/allenai/semparse/one_off/test_significance.scala

@@ -1,7 +1,7 @@
 package org.allenai.semparse.one_off
 
 import edu.cmu.ml.rtw.pra.experiments.ExperimentScorer
-import edu.cmu.ml.rtw.users.matt.util.FileUtil
+import com.mattg.util.FileUtil
 
 // TODO(matt): This should be put into a common space, not a one_off script.
 object test_significance {

### 2016-03-14 src/main/scala/org/allenai/semparse/PreFilteredFeatureComputer.scala
Updated some dependencies
Former-commit-id: 66ba1bfba0609f661f85557799693199a9738ec9
Former-commit-id: 1db32034448ebed5bbccab0ef2341696d61d6051

@@ -8,8 +8,8 @@ import edu.cmu.ml.rtw.pra.features.NodePairSubgraphFeatureGenerator
 import edu.cmu.ml.rtw.pra.features.NodeSubgraphFeatureGenerator
 import edu.cmu.ml.rtw.pra.graphs.Graph
 import edu.cmu.ml.rtw.pra.graphs.Graph
-import edu.cmu.ml.rtw.users.matt.util.FileUtil
-import edu.cmu.ml.rtw.users.matt.util.SpecFileReader
+import com.mattg.util.FileUtil
+import com.mattg.util.SpecFileReader
 
 import org.json4s._
 

### 2016-03-14 src/main/scala/org/allenai/semparse/SfeFeatureComputer.scala

@@ -10,8 +10,8 @@ import edu.cmu.ml.rtw.pra.features.NodePairSubgraphFeatureGenerator
 import edu.cmu.ml.rtw.pra.features.NodeSubgraphFeatureGenerator
 import edu.cmu.ml.rtw.pra.graphs.Graph
 import edu.cmu.ml.rtw.pra.graphs.Graph
-import edu.cmu.ml.rtw.users.matt.util.FileUtil
-import edu.cmu.ml.rtw.users.matt.util.SpecFileReader
+import com.mattg.util.FileUtil
+import com.mattg.util.SpecFileReader
 
 import org.json4s._
 

### 2016-03-14 src/main/scala/org/allenai/semparse/SfeFunctions.scala

@@ -10,12 +10,13 @@ import com.jayantkrish.jklol.lisp.AmbEval.AmbFunctionValue
 import com.jayantkrish.jklol.lisp.ConstantValue
 import com.jayantkrish.jklol.lisp.ConsValue
 import com.jayantkrish.jklol.lisp.{Environment => JEnv}
+import com.jayantkrish.jklol.lisp.EvalContext
 import com.jayantkrish.jklol.lisp.LispUtil
 import com.jayantkrish.jklol.lisp.ParametricBfgBuilder
 import com.jayantkrish.jklol.lisp.SpecAndParameters
 
 class CreateSfeFeatureComputer extends AmbFunctionValue {
-  override def apply(argumentValues: JList[Object], env: JEnv, b: ParametricBfgBuilder) = {
+  override def apply(argumentValues: JList[Object], c: EvalContext, b: ParametricBfgBuilder) = {
     Preconditions.checkArgument(argumentValues.size() == 1)
     val specFile = argumentValues.get(0).asInstanceOf[String]
     new SfeFeatureComputer(specFile)
@@ -23,7 +24,7 @@ class CreateSfeFeatureComputer extends AmbFunctionValue {
 }
 
 class DisplayParameters extends AmbFunctionValue {
-  override def apply(argumentValues: JList[Object], env: JEnv, b: ParametricBfgBuilder) = {
+  override def apply(argumentValues: JList[Object], c: EvalContext, b: ParametricBfgBuilder) = {
     Preconditions.checkArgument(argumentValues.size() == 1)
     val params = argumentValues.get(0).asInstanceOf[SpecAndParameters]
     val stats = params.getParameters()
@@ -33,7 +34,7 @@ class DisplayParameters extends AmbFunctionValue {
 }
 
 class FindRelatedEntities extends AmbFunctionValue {
-  override def apply(argumentValues: JList[Object], env: JEnv, b: ParametricBfgBuilder) = {
+  override def apply(argumentValues: JList[Object], c: EvalContext, b: ParametricBfgBuilder) = {
     Preconditions.checkArgument(argumentValues.size() == 2)
     val midRelations = ConsValue.consListToList(argumentValues.get(0))
     val featureComputer = argumentValues.get(1).asInstanceOf[SfeFeatureComputer]
@@ -64,7 +65,7 @@ class FindRelatedEntities extends AmbFunctionValue {
 }
 
 class GetCatWordFeatureList extends AmbFunctionValue {
[…]

### 2016-03-14 src/main/scala/org/allenai/semparse/Tester.scala

@@ -7,7 +7,7 @@ import scala.collection.mutable
 
 import com.jayantkrish.jklol.lisp.ConsValue
 
-import edu.cmu.ml.rtw.users.matt.util.FileUtil
+import com.mattg.util.FileUtil
 
 import org.json4s._
 import org.json4s.native.JsonMethods.parse

### 2016-03-14 src/main/scala/org/allenai/semparse/Trainer.scala

@@ -2,7 +2,7 @@ package org.allenai.semparse
 
 import java.io.File
 
-import edu.cmu.ml.rtw.users.matt.util.FileUtil
+import com.mattg.util.FileUtil
 
 object Trainer {
 

### 2016-03-14 src/main/scala/org/allenai/semparse/TrainingDataProcessor.scala

@@ -2,7 +2,7 @@ package org.allenai.semparse
 
 import collection.mutable
 
-import edu.cmu.ml.rtw.users.matt.util.FileUtil
+import com.mattg.util.FileUtil
 
 import org.json4s.DefaultFormats
 import org.json4s.JValue

### 2016-03-14 src/test/scala/org/allenai/semparse/CachedFeatureDictionarySpec.scala

@@ -4,7 +4,7 @@ import org.scalatest._
 
 import com.jayantkrish.jklol.tensor.SparseTensor
 
-import edu.cmu.ml.rtw.users.matt.util.FakeFileUtil
+import com.mattg.util.FakeFileUtil
 
 class CachedFeatureDictionarySpec extends FlatSpecLike with Matchers {
 

### 2016-03-14 src/main/scala/org/allenai/semparse/one_off/add_rel_variables_to_test_file.scala
Made a pipeline/ directory, which has all of the main methods (that will soon go away, mostly)
Former-commit-id: 0168254f5360f6e6aa782d9cb0c03ac13068390e

@@ -73,7 +73,9 @@ object add_rel_variables_to_test_file {
   val prettyTestFile = "/home/mattg/clone/tacl2015-factorization/data/acl2016-test-augmented-pretty.json"
   val fileUtil = new FileUtil
 
-  def main(args: Array[String]) {
+  // The test files are now checked into the repo, and they have the stuff this script was meant to
+  // add.
+  def NOT_main(args: Array[String]) {
     val augmenter = new TestJsonAugmenter
     //val newLines = fileUtil.getLineIterator(testFile).map(augmenter.augmentLine).toSeq
     val json = parse(fileUtil.readLinesFromFile(testFile).mkString("\n"))

### 2016-03-14 src/main/scala/org/allenai/semparse/one_off/copy_annotations.scala

@@ -30,7 +30,9 @@ object copy_annotations {
     copyTo removeField { _._1 == "queries" } merge toCopy
   }
 
-  def main(args: Array[String]) {
+  // This script is useful for copying annotations over from the new logical form file to the old
+  // logical form file.  Hopefully I won't need to use it again...
+  def NOT_main(args: Array[String]) {
     val jsonToCopyFrom = parse(fileUtil.readLinesFromFile(copyFrom).mkString("\n"))
     val queriesToCopyFrom = jsonToCopyFrom.extract[Seq[JValue]]
     val jsonToCopyTo = parse(fileUtil.readLinesFromFile(copyTo).mkString("\n"))

### 2016-03-14 src/main/scala/org/allenai/semparse/one_off/dump_feature_weights.scala

@@ -55,6 +55,7 @@ object dump_feature_weights {
     out.close()
   }
 
+  // TODO(matt): make this a Step, not a one_off script.
   def main(args: Array[String]) {
     Experiments.experimentConfigs.foreach(config => {
       val (data, modelType, ranking, ensembledEvaluation) = config

### 2016-03-14 src/main/scala/org/allenai/semparse/one_off/test_significance.scala

@@ -3,7 +3,8 @@ package org.allenai.semparse.one_off
 import edu.cmu.ml.rtw.pra.experiments.ExperimentScorer
 import com.mattg.util.FileUtil
 
-// TODO(matt): This should be put into a common space, not a one_off script.
+// TODO(matt): This should be put into a common space, not a one_off script.  And, actually, it
+// should be a Step, probably the one that actually gets called.
 object test_significance {
   val combined_ap_file = "/home/mattg/clone/tacl2015-factorization/results/large/combined_ap.txt"
   val distributional_ap_file = "/home/mattg/clone/tacl2015-factorization/results/large/distributional_ap.txt"

### 2016-03-15 papers/acl2016/paper.tex
working on background
Former-commit-id: bb38d049dc5d8f97bde0d9c0e66ebe0e9a51cca9

@@
 Krishnamurthy and
-Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} introduced a
-technique for learning semantic parsers with open predicate vocabularies
-(hereafter referred to as K\&M).  Instead of mapping text to Freebase queries,
-they applied the matrix factorization semantics used by Riedel et
-al.~\shortcite{riedel-2013-mf-universal-schema} in knowledge base completion to
-the task of learning predicate semantics in a semantic parser.  This method
-assigns truth values to instantiated predicates like
-\predicate{architect}(\entity{AndreaPalladio}) in a probabilistic database.
-The models K\&M use for the predicates and entities are essentially equivalent
-to modern techniques for constructing word embeddings, implicitly factorizing a
-cooccurrence matrix between categories and entities, and relations and entity
-pairs~\cite{levy-2014-w2v-as-mf}.  This implicit factorization has two sets of
-parameters: each predicate (category or relation) has a learned $k$-dimensional
-embedding $\theta$, and each entity and entity pair has a learned embedding
-$\phi$.  The probability assigned to a category instance $c(e)$ and relation
-instance $r(e_1, e_2)$ in the probabilistic database is given by:
+Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}
+introduced a technique for learning semantic parsers with open
+predicate vocabularies (hereafter referred to as K\&M). Instead of
+mapping text directly to Freebase queries, this method parses text to
+a surface logical form whose predicates are derived directly from the
+words in the text. Next, a distribution over denotations for each
+predicate is learned using a matrix factorization approach similar to
+that of Riedel et
+al.~\shortcite{riedel-2013-mf-universal-schema}. This distribution is
+concisely represented using a probabilistic database, which also
+enables efficient probabilistic execution of logical form queries.
+
+This method assigns a truth probability to a predicate instance such
+as \predicate{architect}(\entity{AndreaPalladio}) using probabilistic
+matrix factorization. This factorization has two sets of parameters:
+each category or relation has a learned $k$-dimensional embedding
+$\theta$, and each entity or entity pair has a learned embedding
+$\phi$. The probability assigned to a category instance $c(e)$ or
+relation instance $r(e_1, e_2)$ is given by:
 
@@
 
-The probability of a predicate instance is the (sigmoided) inner product of the
-corresponding predicate and entity embeddings. Thus, predicates with nearby
-embeddings will have similar distributions over the entities in their
-denotation.  The model is trained using a ranking objective that learns to rank
-the observed entities for each query above unobserved entities.  The
-probabilistic database produced by these predicate models is then input to a
-reasoning system that can handle a subset of first-order logic.
+The probability of a predicate instance is the (sigmoided) inner
+product of the corresponding predicate and entity embeddings. Thus,
+predicates with nearby embeddings will have similar distributions over
+the entities in their denotation.
 
-In this paper, we use the system produced by K\&M, changing only the models of
-predicate semantics, as described in \secref{method}.  K\&M introduced several
-variations of their parser; in this work, we use their query ranking objective,
-as it had the best performance, and we evaluate the model they called
-``Factorization'', without ensembling it with a clustering baseline.
+The model is trained using a query ranking objective that learns to
+rank entities observed in the denotation of a logical form above
+unobserved entities. The training data consists of logical form /
+entity pairs $\{(\ell^i, e_^i)\}_{i=1}^n$ that are automatically
+derived from an entity-linked web corpus. Training optimizes the
+ranking objective function using AdaGrad, and produces the parameters
+$\theta$ and $\phi$ as output. Note that this approach is similar to
+modern techniques for constructing word embeddings in that it factors
+a cooccurrence matrix between predicates and
+entities~\cite{levy-2014-w2v-as-mf}. Given the trained predicate and
+entity parameters, the system is capable of efficiently computing the
+marginal probability that an entity is an element of a logical form's
+denotation using approximate inference algorithms for probabilistic
+databases.
+
+This paper extends K\&M by modifying the models of predicate semantics
+as described in \secref{method}. K\&M introduced several variations of
+their parser; in this work, we use their query ranking objective, as
+it had the best performance, and we compare against the model they
+called ``Factorization,'' without ensembling it with a corpus lookup
+baseline.
 

### 2016-03-15 papers/acl2016/paper.tex
introduction edits
Former-commit-id: af0c43a215d6663811c735112db67026c34d5be9

@@
 
-How should a computer program represent the meaning of a word or a phrase?  The
-answer to this question has a long and rich history.  Motivated by Harris's
-distributional hypothesis~\cite{harris-1954-distributional-hypothesis}, much
-work has been put into representing words as collections of the contexts in
-which they appear.  Recent work with neural networks and word embeddings have
-shown that these representations can be very useful for a number of natural
-language processing tasks (see, e.g., the work Mikolov et
-al.~\shortcite{mikolov-2013-word2vec} and papers that cite them).  This
-approach to modeling semantics is appealing because word embeddings can be
-trained on unlabeled text, allowing for very broad coverage, although shallow,
-semantics.
+How should a computer program represent the meaning of a word or a
+phrase? Recent work has suggested two vastly different approaches --
+distributional vector space models and semantic parsing -- each with
+its own advantages and disadvantages. On one hand, distributional
+models produce a vector representation of the meaning of each word
+from a large unlabeled text corpus. These models have broad coverage,
+but a shallow semantics centered around word similarity. On the other
+hand, semantic parsing translates natural language into logical
+queries against a formal knowledge base, such as Freebase. This
+approach produces a rich compositional semantics and furthermore can
+leverage structured information from the knowledge base, e.g., to
+answer natural language questions. However, semantic parsers have
+limited coverage as they can only represent the meanings of words that
+can be mapped to knowledge base predicates. A critical question is
+\emph{how do we obtain the benefits of both approaches?}
+
+% The answer to this question has a long and rich history.  Motivated by
+% , much work has been put into representing words as collections of the
+% contexts in which they appear.  Recent work with neural networks and
+% word embeddings have shown that these representations can be very
+% useful for a number of natural language processing tasks (see, e.g.,
+% the work Mikolov et al.~\shortcite{mikolov-2013-word2vec} and papers
+% that cite them).  This approach to modeling semantics is appealing
+% because word embeddings can be trained on unlabeled text, allowing for
+% very broad coverage, although shallow, semantics.
 
@@
 
-At the same time, other researchers have found Montague's ideas about English
-as a formal language to be useful~\cite{montague-1974-english-formal-language}.
-Modern semantic parsers make use of a model-theoretic semantics that represents
-words and phrases as formal predicates.  These predicates are then typically
-mapped onto a query over a structured knowledge base, such as
-Freebase~\cite{freebase-2008-bollacker}.  This kind of modeling allows semantic
-parsers to handle the compositional structure of natural language and to
-leverage large, curated knowledge sources to perform various natural language
-processing
-tasks~\cite{zettlemoyer-2005-ccg,kwiatkowski-2013-ontology-matching,berant-2013-semantic-parsing-qa}.
-However, semantic parsers are fundamentally limited by the schema of the
-ontology they are trained on---a semantic parser trained with Freebase cannot
-even represent words whose meaning has no correlate in the Freebase ontology,
-such as ``front-runner'' and ``honcho''.
+% At the same time, other researchers have found Montague's ideas about English
+% as a formal language to be useful~\cite{montague-1974-english-formal-language}.
+% Modern semantic parsers make use of a model-theoretic semantics that represents
+% words and phrases as formal predicates.  These predicates are then typically
+% mapped onto a query over a structured knowledge base, such as
+% Freebase~\cite{freebase-2008-bollacker}.  This kind of modeling allows semantic
+% parsers to handle the compositional structure of natural language and to
+% leverage large, curated knowledge sources to perform various natural language
+% processing
+% tasks~\cite{zettlemoyer-2005-ccg,kwiatkowski-2013-ontology-matching,berant-2013-semantic-parsing-qa}.
+% However, semantic parsers are fundamentally limited by the schema of the
+% ontology they are trained on---a semantic parser trained with Freebase cannot
+% even represent words whose meaning has no correlate in the Freebase ontology,
+% such as ``front-runner'' and ``honcho''.
 
-In this work we introduce models of predicate semantics that combine the
-benefits of both distributional and formal approaches.  While there is no
-Freebase predicate that corresponds exactly to the meaning of ``honcho'',
-Freebase \emph{does} contain many predicates that can \emph{partially}
-represent the word.  Our models extract features from Freebase that are
-correlated with words and phrases seen in natural language text, and learns
-weights for those features as additional components of a distributional model
-of the word's meaning.
+Krishnamurthy and
+Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}
+provides a partial answer to this question with their open-vocabulary
+semantic parser. This system answers compositional, fill-in-the-blank
+natural language queries against Freebase, such as ``Hollywood honcho
+\blank{},'' using \emph{distributional} models of predicate
+semantics. The method semantically parses text to a surface logical
+form containing predicates derived from the text itself, such as
+$\lambda x.\predicate{honcho}(x) \land
+\predicate{honcho\_N/N}(\entity{Hollywood}, x)$, then learns the
+denotations of these predicates using distributional information from
+a large, entity-linked corpus. This method combines the broad coverage
+of distributional approaches with the compositionality of semantic
+parsing; however, it does not use structured information from Freebase
+to assist with its predictions.
 
-To demonstrate these models, we focus on the task of fill-in-the-blank natural
-language queries, such as ``Italian architect \blank{}''.  Similar to many
-current semantic parsers, we first convert this natural language query into a
-logical form: $\lambda x. \predicate{architect}(x) \land
-\predicate{architect\_N/N}(\entity{Italy},
-x)$.\footnote{\predicate{architect\_N/N} represents a noun-compound
-relationship between two entities mediated by the word ``architect'', as in
-``Italian architect Andrea Palladio''.  This is in contrast to, e.g.,
-\predicate{'s\_architect} or \predicate{architect\_of}, both of which also are
-mediated by ``architect'', but through different syntax.  N/N is how
-CCG~\cite{steedman-2006-ccg} represents a noun compound.} A typical semantic
-parser (e.g., that of Kwiatkowski et
-al.~\shortcite{kwiatkowski-2013-ontology-matching}) would then try to map this
-logical form to a single Freebase query, likely involving
-(\predicate{/people/person/nationality}: \entity{Italy}) and
-(\predicate{/type/object/type}: \entity{/architecture/architect}).  Instead of
-restricting ourselves to modeling only what can be represented as a Freebase
-query, we follow Krishnamurthy and
-Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} in learning a
-model for each predicate that can give a \emph{score} to potential arguments.
-The model for \predicate{architect}, e.g., should give high scores to
-\entity{Andrea Palladio} and \entity{Frank Lloyd Wright}, and low scores to
-\entity{Italy}, \entity{BarackObama}, etc.  However, while the models of
-Krishnamurthy and Mitchell are purely distributional, using Freebase only as a
-means of finding entities in text, we inject additional information from
-Freebase into the models for each predicate.  The model we learn for
-\predicate{architect} has a \emph{feature} capturing the fact that an entity
-has the type \entity{/architecture/architect} in Freebase, and the model for
-\predicate{architect\_N/N} has a \emph{feature} capturing whether the first
-argument is the country of nationality of the second argument.  An overview of
-the components of our model is given in \figref{overview}.
+In this work, we introduce new models of predicate semantics that
+leverage both structured information from Freebase and distributional
+information. Our key observation is that, while there is no Freebase
+predicate that corresponds exactly to the meaning of ``honcho,''
+Freebase \emph{does} contain predicates that \emph{partially}
+represent its meaning. For example, an entity that can be called
+``honcho'' is likely to have type \predicate{person}. We therefore
+incorporate \emph{features} based on Freebase paths into the predicate
+models of K\&M and learn per-predicate weights for these features
+using distributional information (\figref{overview}). This approach
+effectively learns the meaning of a word as a distributional vector
+plus a \emph{weighted combination of Freebase queries}, a considerably
+more expressive representation than either existing semantic parsers
+or K\&M.
 
-This is a new kind of predicate semantics.  It is distributional---part of the
-model is still trained in a manner very similar to word2vec---yet it is also
-formal.  However, instead of committing to a single Freebase query to represent
-a phrase, as traditional formal approaches do, our models are flexible,
-encoding many possible Freebase queries as features that can give hints to the
-model.  Thus words that would be impossible to represent as a single Freebase
-query can still benefit from the information contained in Freebase---our model
-for ``front-runner'' learns that acceptable entities are politicians, even
-though there is no exact encoding of ``front-runner'' in Freebase.
+We demonstrate our approach on the task of answering fill-in-the-blank
+natural language queries, finding that our approach provides a 62\%
+relative improvement in mean average precision over K\&M. (TODO: other
+empirical findings?)
 
-The rest of this paper is organized as follows.  In \secref{background}, we
-describe the relevant background necessary to understand the models we propose,
-and we situate our model in the context of related work.  In \secref{method},
-we give a formal description of our models of predicate semantics.  In
-\secref{evaluation}, we present experimental results on fill-in-the-blank
-natural language query task.  Using web text linked to Freebase as our training
-and test data, we show a 62\% relative improvement over prior work, giving a
-new state-of-the-art result on this dataset.  In \secref{discussion}, we give a
-detailed discussion of the benefits and drawbacks of the models we have
-proposed.  We then conclude in \secref{conclusion}.
+% Thus, we extend K\&M to incorporate such features from Freebase into
+% its predicate models. Our model automatically generates such features
+% and learns per-predicate weights for them using distributional
+% statistics.
+
+% In this work we introduce models of predicate semantics that combine the
+% benefits of both distributional and formal approaches.  While there is no
+% Freebase predicate that corresponds exactly to the meaning of ``honcho'',
+% Freebase \emph{does} contain many predicates that can \emph{partially}
+% represent the word.  Our models extract features from Freebase that are
+% correlated with words and phrases seen in natural language text, and learns
+% weights for those features as additional components of a distributional model
+% of the word's meaning.
+
+% To demonstrate these models, we focus on the task of fill-in-the-blank natural
+% language queries, such as ``Italian architect \blank{}''.  Similar to many
+% current semantic parsers, we first convert this natural language query into a
+% logical form: $\lambda x. \predicate{architect}(x) \land
+% \predicate{architect\_N/N}(\entity{Italy},
+% x)$.\footnote{\predicate{architect\_N/N} represents a noun-compound
+% relationship between two entities mediated by the word ``architect'', as in
+% ``Italian architect Andrea Palladio''.  This is in contrast to, e.g.,
+% \predicate{'s\_architect} or \predicate{architect\_of}, both of which also are
+% mediated by ``architect'', but through different syntax.  N/N is how
+% CCG~\cite{steedman-2006-ccg} represents a noun compound.} A typical semantic
+% parser (e.g., that of Kwiatkowski et
+% al.~\shortcite{kwiatkowski-2013-ontology-matching}) would then try to map this
+% logical form to a single Freebase query, likely involving
+% (\predicate{/people/person/nationality}: \entity{Italy}) and
+% (\predicate{/type/object/type}: \entity{/architecture/architect}).  Instead of
+% restricting ourselves to modeling only what can be represented as a Freebase
+% query, we follow Krishnamurthy and
+% Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} in learning a
+% model for each predicate that can give a \emph{score} to potential arguments.
+% The model for \predicate{architect}, e.g., should give high scores to
+% \entity{Andrea Palladio} and \entity{Frank Lloyd Wright}, and low scores to
+% \entity{Italy}, \entity{BarackObama}, etc.  However, while the models of
+% Krishnamurthy and Mitchell are purely distributional, using Freebase only as a
+% means of finding entities in text, we inject additional information from
+% Freebase into the models for each predicate.  The model we learn for
+% \predicate{architect} has a \emph{feature} capturing the fact that an entity
+% has the type \entity{/architecture/architect} in Freebase, and the model for
+% \predicate{architect\_N/N} has a \emph{feature} capturing whether the first
+% argument is the country of nationality of the second argument.  An overview of
+% the components of our model is given in \figref{overview}.
+% 
+% This is a new kind of predicate semantics.  It is distributional---part of the
+% model is still trained in a manner very similar to word2vec---yet it is also
+% formal.  However, instead of committing to a single Freebase query to represent
+% a phrase, as traditional formal approaches do, our models are flexible,
+% encoding many possible Freebase queries as features that can give hints to the
+% model.  Thus words that would be impossible to represent as a single Freebase
+% query can still benefit from the information contained in Freebase---our model
+% for ``front-runner'' learns that acceptable entities are politicians, even
+% though there is no exact encoding of ``front-runner'' in Freebase.
+% 
+% The rest of this paper is organized as follows.  In \secref{background}, we
+% describe the relevant background necessary to understand the models we propose,
+% and we situate our model in the context of related work.  In \secref{method},
+% we give a formal description of our models of predicate semantics.  In
+% \secref{evaluation}, we present experimental results on fill-in-the-blank
+% natural language query task.  Using web text linked to Freebase as our training
+% and test data, we show a 62\% relative improvement over prior work, giving a
+% new state-of-the-art result on this dataset.  In \secref{discussion}, we give a
+% detailed discussion of the benefits and drawbacks of the models we have
+% proposed.  We then conclude in \secref{conclusion}.
 
@@
 
-This method assigns a truth probability to a predicate instance such
-as \predicate{architect}(\entity{AndreaPalladio}) using probabilistic
-matrix factorization. This factorization has two sets of parameters:
-each category or relation has a learned $k$-dimensional embedding
-$\theta$, and each entity or entity pair has a learned embedding
-$\phi$. The probability assigned to a category instance $c(e)$ or
-relation instance $r(e_1, e_2)$ is given by:
+The truth probability of a predicate instance such as
+\predicate{architect}(\entity{AndreaPalladio}) is learned using
+probabilistic matrix factorization. This factorization has two sets of
+parameters: each category or relation has a learned $k$-dimensional
+embedding $\theta$, and each entity or entity pair has a learned
+embedding $\phi$. The probability assigned to a category instance
+$c(e)$ or relation instance $r(e_1, e_2)$ is given by:
 
@@
 predicates with nearby embeddings will have similar distributions over
-the entities in their denotation.
-
-The model is trained using a query ranking objective that learns to
+the entities in their denotation. The parameters $\theta$ and $\phi$
+are learned using a query ranking objective that optimizes them to
 rank entities observed in the denotation of a logical form above
-unobserved entities. The training data consists of logical form /
-entity pairs $\{(\ell^i, e_^i)\}_{i=1}^n$ that are automatically
-derived from an entity-linked web corpus. Training optimizes the
-ranking objective function using AdaGrad, and produces the parameters
-$\theta$ and $\phi$ as output. Note that this approach is similar to
-modern techniques for constructing word embeddings in that it factors
-a cooccurrence matrix between predicates and
+unobserved entities. Note that this approach is similar to modern
+techniques for constructing word embeddings in that it factors a
+cooccurrence matrix between predicates and
 entities~\cite{levy-2014-w2v-as-mf}. Given the trained predicate and

### 2016-03-15 papers/acl2016/paper.tex
minor edits
Former-commit-id: b1b122922830ecb6ffff8a0e9acf97291dea192b

@@
 Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}
-provides a partial answer to this question with their open-vocabulary
+provide a partial answer to this question with their open-vocabulary
 semantic parser. This system answers compositional, fill-in-the-blank
@@
 relative improvement in mean average precision over K\&M. (TODO: other
-empirical findings?)
+empirical findings? It would be nice to talk about what features get
+learned for what words, etc.)
 

### 2016-03-17 papers/acl2016/paper.tex
paper edits
Former-commit-id: 2b5783321772f1fe9dd37e49842811b842057b5f

@@
 models produce a vector representation of the meaning of each word
-from a large unlabeled text corpus. These models have broad coverage,
+from a large unlabeled text corpus. These models have broad coverage
 but a shallow semantics centered around word similarity. On the other
@@
 
-\section{Discussion}
-\label{sec:discussion}
+\subsection{Discussion}
 
-Here we discuss some of the successes and failures of our model.
+Our model tends to outperform the distributional model on queries
+containing predicates with exact or partial correlates in
+Freebase. For example, our model obtains nearly perfect average
+precision on the queries ``French newspaper \blank{}'' and ``Israeli
+prime minister \blank{},'' both of which can be exactly expressed in
+Freebase. (TODO: do these relations get high weights in the features?)
+The model also performs well on queries with partial Freebase
+correlates, such as ``Microsoft head honcho \blank{}'', ``The United
+States, \blank{}'s closest ally'', and ``Patriots linebacker
+\blank{},'' although with somewhat lower average precision. The high
+weight features in these cases tend to provide useful hints, even
+though there is no direct correlate; for example, the model learns
+that ``honchos'' are people, and that they tend to be CEOs and film
+producers.
 
-When a predicate has a clear Freebase correlate (such a
-\predicate{prime\_minister\_N/N}, \predicate{president\_of},
-\predicate{newspaper}, \predicate{company}, etc.), our formal model is able to
-capture the meaning very well.  The query ``French newspaper \blank{}'' has
-nearly perfect average precision, for instance, as does ``Israeli prime
-minister \blank{}''.  The distributional model does much less well here, and in
-combination, the distributional component of the model occasionally lowers its
-performance relative to the formal model.\footnote{This is why the difference
-between the formal model and the combined model is not statistically
-significant.}
+There are also some areas where our model can be improved. First, in
+some cases, the edge sequence features used by the model are not
+expressive enough to identify the correct relation in Freebase. An
+example of this problem is the ``linebacker'' example above, where the
+features for \predicate{linebacker\_N/N} can capture which athletes
+play for which teams, but not the \emph{positions} of those
+athletes. Second, our model can underperform on predicates with no
+close mapping to Freebase. An example where this problem occurs is the
+query ``\blank{} is a NASA mission.'' Third, there remains room to
+further improve the logical forms produced by the semantic parser,
+specifically for multi-word expressions. One problem occurs with
+multi-word noun modifiers, e.g., ``Vice president Al Gore'' is mapped
+to $\predicate{vice}(\entity{Al Gore}) \land
+\predicate{president}(\entity{Al Gore})$. Another problem is that
+there is no backoff with multi-word relations. For example, the
+predicate \predicate{head\_honcho\_N/N} was never seen in the training
+data, so it is replaced with \predicate{unknown}; however, it would be
+better to replace it with \predicate{honcho\_N/N}, which \emph{was}
+seen in the training data. Finally, although using connected entities
+in Freebase as additional candidates during inference is helpful, it
+often over- or under-generates candidates. A more tailored, per-query
+search process could improve performance.
 
-The formal models also perform well on predicates that can be partially
-expressed by Freebase, such as ``Microsoft head honcho \blank{}'', ``The United
-States, \blank{}'s closest ally'', and ``Patriots linebacker \blank{}'', though
-the models do not have the nearly-perfect AP that they do for the more crisp
-queries above.  The ``head honcho'' example is particularly instructive---this
-is a phrase that essentially means ``leader'', and the features learned by the
-formal model get some essential hints from Freebase, even though there is no
-direct correlate.  The features capture the fact that entities that are
-``honchos'' are people, and that they tend to be CEOs and film producers.
+% The ``head honcho'' example is particularly instructive---this is a
+% phrase that essentially means ``leader'', and the features learned by
+% the formal model get some essential hints from Freebase, even though
+% there is no direct correlate.  The features capture the fact that
+% entities that are ``honchos'' are people, and that they tend to be
+% CEOs and film producers.
+% 
+% When a predicate has a clear Freebase correlate (such a
+% \predicate{prime\_minister\_N/N}, \predicate{president\_of},
+% \predicate{newspaper}, \predicate{company}, etc.), our formal model is able to
+% capture the meaning very well.  The   The distributional model does much less well here, and in
+% combination, the distributional component of the model occasionally lowers its
+% performance relative to the formal model.\footnote{This is why the difference
+% between the formal model and the combined model is not statistically
+% significant.}
+% 
+% The formal models also perform well on predicates that can be partially
+% expressed by Freebase, such as , though
+% the models do not have the nearly-perfect AP that they do for the more crisp
+% queries above.  
+% 
+% For ``Patriots linebacker \blank{}'', the reason that this can only be
+% partially expressed in terms of Freebase queries is that the features for
+% \predicate{linebacker\_N/N} are able to capture which athletes play for which
+% teams, but they cannot distinguish well between what positions those athletes
+% play.  This leads to Patriots quarterbacks, wide receivers, and running backs
+% being scored highly for this query.  This issue could be fixed by using more
+% complex features for relation predicates, instead of just edge sequences,
+% though that would drammatically increase the size of the feature space and make
+% the feature selection process much more difficult.  It could also potentially
+% be mitigated by better negative example selection during training.
+% 
+% There are also cases where a predicate has so many possible entity types in
+% Freebase (or no close correlate at all) that the PMI feature selection process
+% does not find features that are useful for all queries.  A good example of this
+% is ``\blank{} is a NASA mission''; in this case, the distributional model
+% outperforms the formal model, because it has learned associations between
+% particular NASA missions and NASA.
+% 
+% While the new logical forms we introduced in \secref{better-lfs} improved the
+% performance of the models, there is still a lot of room for further
+% improvement.  For instance, ``Vice president Al Gore'' is modeled as
+% $\predicate{vice}(\entity{Al Gore}) \land \predicate{president}(\entity{Al
+% Gore})$.  Better processing of multi-word expressions would allow for more
+% crisp models of the predicates, so the model for \predicate{president} could
+% have more specific features.  Also, the predicate \predicate{head\_honcho\_N/N}
+% was never seen in the training data, so an \predicate{unknown} predicate was
+% used to score the relation in the phrase ``Microsoft head honcho \blank{}''.
+% This means the model had to rely solely on knowing which entities are
+% ``honchos'' and which entities are related to Microsoft in some unknown manner.
+% The predicate \predicate{honcho\_N/N} \emph{is} seen in the training data,
+% however; some kind of backoff to simpler phrases for unseen predicates would be
+% useful here.
 
-For ``Patriots linebacker \blank{}'', the reason that this can only be
-partially expressed in terms of Freebase queries is that the features for
-\predicate{linebacker\_N/N} are able to capture which athletes play for which
-teams, but they cannot distinguish well between what positions those athletes
-play.  This leads to Patriots quarterbacks, wide receivers, and running backs
-being scored highly for this query.  This issue could be fixed by using more
-complex features for relation predicates, instead of just edge sequences,
-though that would drammatically increase the size of the feature space and make
-the feature selection process much more difficult.  It could also potentially
-be mitigated by better negative example selection during training.
-
-There are also cases where a predicate has so many possible entity types in
-Freebase (or no close correlate at all) that the PMI feature selection process
-does not find features that are useful for all queries.  A good example of this
-is ``\blank{} is a NASA mission''; in this case, the distributional model
-outperforms the formal model, because it has learned associations between
-particular NASA missions and NASA.
-
-While the new logical forms we introduced in \secref{better-lfs} improved the
-performance of the models, there is still a lot of room for further
-improvement.  For instance, ``Vice president Al Gore'' is modeled as
-$\predicate{vice}(\entity{Al Gore}) \land \predicate{president}(\entity{Al
-Gore})$.  Better processing of multi-word expressions would allow for more
-crisp models of the predicates, so the model for \predicate{president} could
-have more specific features.  Also, the predicate \predicate{head\_honcho\_N/N}
-was never seen in the training data, so an \predicate{unknown} predicate was
-used to score the relation in the phrase ``Microsoft head honcho \blank{}''.
-This means the model had to rely solely on knowing which entities are
-``honchos'' and which entities are related to Microsoft in some unknown manner.
-The predicate \predicate{honcho\_N/N} \emph{is} seen in the training data,
-however; some kind of backoff to simpler phrases for unseen predicates would be
-useful here.
-
-Finally, using connected entities in Freebase as additional candidates during
-inference is helpful, but it is not very sophisticated.  It over-generates for
-a lot of entities and predicates, and under-generates for others.  A mechanism
-for tailoring a search over Freebase to a particular query would be useful,
-though it would add a lot of additional complexity, possibly requiring methods
-from reinforcement learning to resolve.
+% Finally, using connected entities in Freebase as additional candidates during
+% inference is helpful, but it is not very sophisticated.  It over-generates for
+% a lot of entities and predicates, and under-generates for others.  A mechanism
+% for tailoring a search over Freebase to a particular query would be useful,
+% though it would add a lot of additional complexity, possibly requiring methods
+% from reinforcement learning to resolve.
 
@@
 
-In this paper, we have considered the problem of assigning meaning to
-predicates (both categories and relations) in natural language, using both
-distributional information and information from a formal knowledge base.  To do
-this, we developed a model that can represent words as a weighted combination
-of formal statements, and trained that model jointly with a distributional
-model of word meaning.  This joint model achieved a relative gain of 62\% in
-mean average precision over the distributional model alone.  We also introduced
-a better mapping from surface text to logical forms, and a simple method for
-using Freebase to find candidate entities during inference.  Taken together,
-the methods introduced in this paper improved mean average precision on a
-fill-in-the-blank natural language query task from .163 to .370, a 127\%
-relative improvement.
+This paper considers the problem of assigning meaning to predicates
+(both categories and relations) in natural language using both
+distributional information and information from a formal knowledge
+base. Our model represents words as a weighted combination of
+knowledge base queries plus a distributional component. Both of these
+components are jointly trained to correctly predict entity answers to
+fill-in-the-blank natural language queries. This combined model
+achieved a relative gain of 62\% in mean average precision over the
+distributional model alone. We also introduced a better mapping from
+surface text to logical forms, and a simple method for using Freebase
+to find candidate entities during inference.  Taken together, the
+methods introduced in this paper improved mean average precision on a
+fill-in-the-blank natural language query task from .163 to .370, a
+127\% relative improvement.
+
+% There are many directions for future work in this model. One is to
+% address some of the model limitations previously discussed to improve
+% performance. Specifically, feature generation, feature selection and
+% candidate entity generation could be better tailored to each
+% predicate. This problem is challenging because it requires expanding
+% an already very expressive class of features ...  (TODO: reinforcement
+% learning?) Although the features we consider are already more
+% expressive than would be considered by a typical semantic parser, it
+% seems necessary to include even more complex Freebase queries. Another
+% direction (TODO:.... )
+
+A consequence of this work is that it suggests a new direction for
+semantic parsing research. Existing semantic parsers map language to a
+single knowledge base query, an approach that successfully leverages a
+knowledge base's predicate instances, but is fundamentally limited by
+the its schema. In contrast, our approach maps language to a
+\emph{weighted combination of queries} plus a distributional
+component; this approach is capable of representing a much broader
+class of concepts while still using the knowledge base when it is
+helpful. Furthermore, it is capable of using the knowledge base even
+when the meaning of the language cannot be exactly represented by a
+knowledge base predicate, a common occurrence. We believe that this
+kind of approach could significantly expand the applicability of
+semantic parsing techniques to more complex domains where the
+assumptions of traditional techniques are limiting.
+
+TODO: We could say more about what we learned. A big message is that
+we should use the KB as \emph{features}.
 

### 2016-03-17 src/main/scala/org/allenai/semparse/SfeFeatureComputer.scala
Making the pipeline sane
This is a really big code change.  I switched from having a bunch of main
methods you have to run to having a single pipeline, using the pipeline code
in my util library.  I haven't actually tested this yet, though...  Hopefully
it works.


Former-commit-id: 1fb9fd75296405d4221eb66cc21b2172c074c968
Former-commit-id: 8a702f647c163514b4eaaa1ed47a2236251b8344

@@ -17,7 +17,7 @@ import org.json4s._
 
 import scala.collection.mutable
 
-class SfeFeatureComputer(specFile: String, fileUtil: FileUtil = new FileUtil) {
+class SfeFeatureComputer(specFile: String, dataName: String, fileUtil: FileUtil = new FileUtil) {
   implicit val formats = DefaultFormats
   val params = new SpecFileReader("/dev/null").readSpecFile(specFile)
 
@@ -44,10 +44,10 @@ class SfeFeatureComputer(specFile: String, fileUtil: FileUtil = new FileUtil) {
   )
 
   // And here we set up the cached entity feature files and pre-computed word feature dictionaries.
-  val midFeatureFile = (params \ "mid feature file").extract[String]
-  val midPairFeatureFile = (params \ "mid pair feature file").extract[String]
-  val catWordFeatureFile = (params \ "cat word feature file").extract[String]
-  val relWordFeatureFile = (params \ "rel word feature file").extract[String]
+  val midFeatureFile = s"data/$dataName/mid_features.tsv"
+  val midPairFeatureFile = s"data/$dataName/mid_pair_features.tsv"
+  val catWordFeatureFile = s"data/$dataName/cat_word_features.tsv"
+  val relWordFeatureFile = s"data/$dataName/rel_word_features.tsv"
 
   val midFeatures = new CachedFeatureDictionary(midFeatureFile, catWordFeatureFile) {
     override def computeFeaturesForKey(key: String) = computeMidFeatures(key)

### 2016-03-17 src/main/scala/org/allenai/semparse/pipeline/FeatureWeightDumper.scala

@@ -1,0 +1,88 @@
+package org.allenai.semparse.pipeline
+
+import scala.collection.JavaConverters._
+
+import org.allenai.semparse.Environment
+
+import com.jayantkrish.jklol.lisp.ListParameterSpec
+import com.jayantkrish.jklol.lisp.SpecAndParameters
+import com.jayantkrish.jklol.models.parametric.TensorSufficientStatistics
+import com.jayantkrish.jklol.models.TableFactor
+import com.jayantkrish.jklol.tensor.SparseTensor
+import com.jayantkrish.jklol.util.IndexedList
+
+import com.mattg.util.FileUtil
+import com.mattg.pipeline.Step
+
+import org.json4s._
+
+class FeatureWeightDumper(
+  params: JValue,
+  fileUtil: FileUtil = new FileUtil
+) extends Step(None, fileUtil) {
+
+  val trainer = new Trainer(params, fileUtil)
+
+  val modelFile = trainer.serializedModelFile
+
+  val wordFile = s"data/${trainer.dataName}/just_words.lisp"
+  val catWordFile = modelFile.replace("model.ser", "cat_word_feature_weights.txt")
+  val relWordFile = modelFile.replace("model.ser", "rel_word_feature_weights.txt")
+
+  override def inputs = Set((wordFile, None), (modelFile, Some(trainer)))
+  override def outputs = Set(catWordFile, relWordFile)
+
+  val catWordParamIndex = trainer.modelType match {
+    case "formal" => 0
+    case "combined" => 1
+    case "distributional" => throw new IllegalStateException("distributional model has no such parameters")
+  }
+
+  val relWordParamIndex = trainer.modelType match {
+    case "formal" => 1
+    case "combined" => 4
+    case "distributional" => throw new IllegalStateException("distributional model has no such parameters")
+  }
+
+  def getWordParams(params: SpecAndParameters, index: Int): SpecAndParameters = {
+      val paramsList = params.getParameterSpec.asInstanceOf[ListParameterSpec]
+      val childSpec = paramsList.get(index)
+      val childParams = paramsList.getParameter(index, params.getParameters())
+      new SpecAndParameters(childSpec, childParams)
+  }
+
+  def writeParams(filename: String, words: IndexedList[Object], params: SpecAndParameters) {
+    val out = fileUtil.getFileWriter(filename)
+    for ((word, index) <- words.items.asScala.map(_.asInstanceOf[String]).zipWithIndex) {
+      out.write(word)
+      out.write("\n")
[…]

### 2016-03-17 src/main/scala/org/allenai/semparse/pipeline/TrainingDataFeatureComputer.scala

@@ -1,4 +1,4 @@
-package org.allenai.semparse
+package org.allenai.semparse.pipeline
 
 import edu.cmu.ml.rtw.pra.experiments.Outputter
 import edu.cmu.ml.rtw.pra.experiments.RelationMetadata
@@ -8,8 +8,10 @@ import edu.cmu.ml.rtw.pra.features.NodePairSubgraphFeatureGenerator
 import edu.cmu.ml.rtw.pra.features.NodeSubgraphFeatureGenerator
 import edu.cmu.ml.rtw.pra.graphs.Graph
 import edu.cmu.ml.rtw.pra.graphs.Graph
+
 import com.mattg.util.FileUtil
 import com.mattg.util.SpecFileReader
+import com.mattg.pipeline.Step
 
 import org.json4s._
 
@@ -70,21 +72,38 @@ class PreFilteredFeatureComputer(
   }
 }
 
-object compute_full_feature_vectors {
-  val dataSize = "small"
-  val midFile = s"data/${dataSize}/training-mids.tsv"
-  val midPairFile = s"data/${dataSize}/training-mid-pairs.tsv"
-  val midFeatureFile = s"data/${dataSize}/pre-filtered-mid-features.tsv"
-  val midPairFeatureFile = s"data/${dataSize}/pre-filtered-mid-pair-features.tsv"
-  val specFile = s"src/main/resources/sfe_spec_${dataSize}.json"
+class TrainingDataFeatureComputer(
+  params: JValue,
+  fileUtil: FileUtil = new FileUtil
+) extends Step(Some(params), fileUtil) {
+  implicit val formats = DefaultFormats
 
-  def main(args: Array[String]) {
+  val dataName = (params \ "data name").extract[String]
+  val sfeSpecFile = (params \ "sfe spec file").extract[String]
+  val trainingDataParams = (params \ "training data")
+  val trainingDataProcessor = new TrainingDataProcessor(trainingDataParams, fileUtil)
+  val outDir = s"data/$dataName/"
+
+  val midFile = s"${outDir}/training_mids.tsv"
+  val midPairFile = s"${outDir}/training_mid_pairs.tsv"
+  val midFeatureFile = s"${outDir}/pre_filtered_mid_features.tsv"
+  val midPairFeatureFile = s"${outDir}/pre_filtered_mid_pair_features.tsv"
+
+  override def paramFile = outDir + "tdfc_params.json"
+  override def name = "Training data feature computer"
[…]

### 2016-03-17 src/main/scala/org/allenai/semparse/pipeline/TrainingDataProcessor.scala

@@ -1,11 +1,14 @@
-package org.allenai.semparse
+package org.allenai.semparse.pipeline
 
 import collection.mutable
 
 import com.mattg.util.FileUtil
+import com.mattg.util.JsonHelper
+import com.mattg.pipeline.Step
 
 import org.json4s.DefaultFormats
-import org.json4s.JValue
+import org.json4s._
+import org.json4s.JsonDSL._
 import org.json4s.native.JsonMethods.parse
 
 // I was was tired of having such a nasty pipeline of so many different scripts to run to get this
@@ -128,20 +131,42 @@ class TrainingData(
 }
 
 class TrainingDataProcessor(
-  trainingFile: String,
-  outDir: String,
-  wordCountThreshold: Int,
-  linesToUse: Option[Int],
+  params: JValue,
   fileUtil: FileUtil = new FileUtil
-) {
+) extends Step(Some(params), fileUtil) {
   implicit val formats = DefaultFormats
+
+  val trainingDataFile = (params \ "training data file").extract[String]
+  val dataName = (params \ "data name").extract[String]
+  val wordCountThreshold = (params \ "word count threshold").extract[Int]
+  val linesToUse: Option[Int] = (params \ "lines to use") match {
+    case JNothing => None
+    case jval => Some(jval.extract[Int])
+  }
+
+  val outDir = s"data/$dataName/"
+
+  override def paramFile = outDir + "tdp_params.json"
+  override def name = "Training data processor"
+  override def inputs = Set((trainingDataFile, None))
+  override def outputs = Set(
+    s"$outDir/words.lisp",
+    s"$outDir/entities.lisp",
+    s"$outDir/joint_entities.lisp",
+    s"$outDir/predicate_ranking_lf.lisp",
+    s"$outDir/query_ranking_lf.lisp",
+    s"$outDir/training_mids.tsv",
+    s"$outDir/training_mid_pairs.tsv",
+    s"$outDir/training_mid_words.tsv",
+    s"$outDir/training_mid_pair_words.tsv"
+  )
 
   val midRegex = "\"/m/[^\"]*\"".r
   val catWordRegex = "word-cat \"([^\"]*)\"".r
   val relWordRegex = "word-rel \"([^\"]*)\"".r
   fileUtil.mkdirs(outDir)
 
-  def processTrainingFile() {
+  override def _runStep() {
     val wordCounts = getWordCountsFromTrainingFile()
[…]

### 2016-03-17 src/main/scala/org/allenai/semparse/Experiments.scala
Making the pipeline sane
This is a really big code change.  I switched from having a bunch of main
methods you have to run to having a single pipeline, using the pipeline code
in my util library.  I haven't actually tested this yet, though...  Hopefully
it works.


Former-commit-id: 1fb9fd75296405d4221eb66cc21b2172c074c968

@@ -1,34 +1,7 @@
 package org.allenai.semparse
 
-// This defines the experiments that we want to run, which is used by the main methods in Trainer
-// and Evaluator.  It also keeps pointers to all of the lisp input files and data files that we
-// use, and groups some of them together in useful ways.
-object Experiments {
-
-  // Currently, there are four options in the experiments: which dataset do you use, ensembled with
-  // baseline or not (for evaluation only), what ranking method, and what model type.  If we add
-  // very many more possibilities, this will need some re-thinking to be more sane.
-  val experimentConfigs: Seq[(String, String, String, Boolean)] = {
-    val datasets = Seq("large")//, "small")
-    val modelTypes = Seq("combined")//, "distributional", "formal")
-
-    // I don't actually change these in the experiments for the ACL 2016 paper, but these were
-    // options used for the TACL 2015 paper.
-    val rankings = Seq("query")//, "predicate")
-    val ensembledEvaluation = Seq(false)//, true)
-    val baselineConfigs = Seq(
-      //("small", "baseline", "ignored", false)
-      //("large", "baseline", "ignored", false)
-    )
-
-    // Generate all possible combinations
-    val configs = for (data <- datasets;
-         modelType <- modelTypes;
-         ranking <- rankings;
-         ensembled <- ensembledEvaluation) yield (data, modelType, ranking, ensembled)
-
-    (configs ++ baselineConfigs)
-  }
+// This object just keeps track of all of the (hand-written) lisp input files that we use.
+object LispFiles {
 
   val BASE_ENVIRONMENT_FILE = "src/main/lisp/environment.lisp"
   val USCHEMA_ENVIRONMENT_FILE = "src/main/lisp/uschema_environment.lisp"

### 2016-03-17 src/main/scala/org/allenai/semparse/pipeline/SparkPmiComputer.scala

@@ -1,103 +1,102 @@
-package org.allenai.semparse.one_off
+package org.allenai.semparse.pipeline
 
 import org.apache.spark.SparkConf
 import org.apache.spark.SparkContext
 
 import com.mattg.util.FileUtil
+import com.mattg.util.JsonHelper
+import com.mattg.pipeline.Step
 
-object SparkPmiComputer {
+import org.json4s._
 
-  // TODO(matt): these parameters control what files are used as input - just take the files as
-  // as class constructor parameters, and put this control logic in a main method somewhere.
-  val dataSize = "large"  // "small" or "large"
-  val runningLocally = true
-  val midOrPairToRun = "mid"  // "mid" or "mid pair"
+class SparkPmiComputer(
+  params: JValue,
+  fileUtil: FileUtil = new FileUtil
+) extends Step(Some(params), fileUtil) {
+  implicit val formats = DefaultFormats
 
-  val numPartitions = dataSize match {
-    case "large" => 2000
-    case "small" => 1000
-  }
+  val dataName = (params \ "data name").extract[String]
+  val outDir = s"data/${dataName}/"
+  val runningLocally = JsonHelper.extractWithDefault(params, "run locally", true)
+  val midOrPair = JsonHelper.extractOption(params, "mid or pair", Seq("mid", "mid_pair"))
 
   // If we've seen a MID too many times, it blows up the word-feature computation.  The US, God,
   // and TV all show up more than 12k times in the large dataset.  I think we can get a good enough
-  // PMI computation without these really frequent MIDs.
-  // TODO(matt): these values are for "mid", not "mid pair"
-  val MAX_WORD_COUNT = dataSize match {
-    case "large" => 1000
-    case "small" => 500
-  }
-  val MAX_FEATURE_COUNT = dataSize match {
-    case "large" => 50000
-    case "small" => 25000
-  }
+  // PMI computation without these really frequent MIDs.  These parameters throw out a few
+  // very-expensive instances.
+  val maxWordCount = JsonHelper.extractWithDefault(params, "max word count", 1000)
+  val maxFeatureCount = JsonHelper.extractWithDefault(params, "max feature count", 50000)
 
-  val MIN_FEATURE_COUNT = dataSize match {
-    case "large" => Map(("mid" -> 2000), ("mid pair" -> 100))
[…]

### 2016-03-17 src/main/scala/org/allenai/semparse/pipeline/Tester.scala

@@ -1,4 +1,4 @@
-package org.allenai.semparse
+package org.allenai.semparse.pipeline
 
 import java.io.FileWriter
 import java.io.File
@@ -8,32 +8,135 @@ import scala.collection.mutable
 import com.jayantkrish.jklol.lisp.ConsValue
 
 import com.mattg.util.FileUtil
+import com.mattg.util.JsonHelper
+import com.mattg.pipeline.Step
 
 import org.json4s._
 import org.json4s.native.JsonMethods.parse
 
-// This class performs inference over a test set for a particular experiment configuration, which
-// is encapsulated in the Environment object given as a parameter.  The query file contains all of
-// the test queries that will be evaluated against the environment, and the entity names is just a
-// map from mids to a human-readable entity name, for easier human scanning of the result file.
-// The file util is my object that abstracts away accessing the file system (and allows for easy
-// faking of the file system, for much easier tests).
+// This class performs inference over a test set for a particular experiment configuration.
 class Tester(
-  env: Environment,
-  queryFile: String,
-  entityNames: => Map[String, String],
+  params: JValue,
   fileUtil: FileUtil = new FileUtil
-) {
+) extends Step(Some(params), fileUtil) {
   implicit val formats = DefaultFormats
 
+  // Parameters we take.
+  val poolDepth = JsonHelper.extractWithDefault(params, "pool depth", 100)
+  val queryFile = (params \ "test query file").extract[String]
+  val dataName = (params \ "data name").extract[String]
+  val ranking = JsonHelper.extractOptionWithDefault(params, "ranking", Seq("query", "predicate"), "query")
+  val modelType = JsonHelper.extractOption(params, "model type", Seq("baseline", "distributional", "formal", "combined"))
+  val ensembledEvaluation = JsonHelper.extractWithDefault(params, "ensembled evaluation", false)
+
+  // Original training data file, which we process to get a set of entity names.
+  val trainingDataFile = (params \ "training data file").extract[String]
+
+  // These are code files that are common to all models, and just specify the base lisp
+  // environment.
+  val baseEnvFile = "src/main/lisp/environment.lisp"
+  val uschemaEnvFile = "src/main/lisp/uschema_environment.lisp"
+
+  // These are code files, specifying the model we're using.
[…]

### 2016-03-17 src/main/scala/org/allenai/semparse/pipeline/Trainer.scala

@@ -1,99 +1,88 @@
-package org.allenai.semparse
+package org.allenai.semparse.pipeline
 
 import java.io.File
 
 import com.mattg.util.FileUtil
+import com.mattg.util.JsonHelper
+import com.mattg.pipeline.Step
 
-object Trainer {
+import org.json4s._
 
-  def canTrainConfig(data: String, modelType: String, ranking: String, ensembledEvaluation: Boolean) = {
-    // At this point, we just need to filter out the baseline model, and we can train everything
-    // else.
-    modelType match {
-      case "baseline" => false
-      case _ => true
-    }
+class Trainer(
+  params: JValue,
+  fileUtil: FileUtil = new FileUtil
+) extends Step(Some(params), fileUtil) {
+  implicit val formats = DefaultFormats
+
+  // The parameters we take.
+  val dataName = (params \ "data name").extract[String]
+  val ranking = JsonHelper.extractOptionWithDefault(params, "ranking", Seq("query", "predicate"), "query")
+  val modelType = JsonHelper.extractOption(params, "model type", Seq("distributional", "formal", "combined"))
+
+  // The output file.
+  val serializedModelFile = s"output/$dataName/$modelType/$ranking/model.ser"
+
+  // These are code files that are common to all models, and just specify the base lisp
+  // environment.
+  val baseEnvFile = "src/main/lisp/environment.lisp"
+  val uschemaEnvFile = "src/main/lisp/uschema_environment.lisp"
+
+  // These are code files, specifying the model we're using.
+  val lispModelFile = s"src/main/lisp/model_${modelType}.lisp"
+  val rankingLispFile = s"src/main/lisp/${ranking}_ranking.lisp"
+  val trainingLispFile = "src/main/lisp/train_model.lisp"
+
+  val handwrittenLispFiles =
+    Seq(baseEnvFile, uschemaEnvFile, rankingLispFile, lispModelFile, trainingLispFile)
+
+  // This one is a (hand-written) parameter file that will be passed to lisp code.
+  val sfeSpecFile = s"src/main/resources/sfe_spec.json"
+
+  // These are data files, produced by TrainingDataProcessor.
+  val entityFile = s"data/${dataName}/entities.lisp"
+  val wordsFile = s"data/${dataName}/words.lisp"
+  val jointEntityFile = s"data/${dataName}/joint_entities.lisp"
+  val logicalFormFile = s"data/${dataName}/${ranking}_ranking_lf.lisp"
+
+  val dataFiles = if (ranking == "query") {
[…]

### 2016-03-17 src/main/scala/org/allenai/semparse/pipeline/SparkPmiComputer.scala
Finally done with this migration.  Now to see if it actually works...
Former-commit-id: ba48c7e107e3537f9b4fc41bb88dfcb721fb8971

@@ -15,11 +15,6 @@ class SparkPmiComputer(
 ) extends Step(Some(params), fileUtil) {
   implicit val formats = DefaultFormats
 
-  val dataName = (params \ "data name").extract[String]
-  val outDir = s"data/${dataName}/"
-  val runningLocally = JsonHelper.extractWithDefault(params, "run locally", true)
-  val midOrPair = JsonHelper.extractOption(params, "mid or pair", Seq("mid", "mid_pair"))
-
   // If we've seen a MID too many times, it blows up the word-feature computation.  The US, God,
   // and TV all show up more than 12k times in the large dataset.  I think we can get a good enough
   // PMI computation without these really frequent MIDs.  These parameters throw out a few
@@ -28,57 +23,92 @@ class SparkPmiComputer(
   val maxFeatureCount = JsonHelper.extractWithDefault(params, "max feature count", 50000)
 
   // This parameter, on the other hand, filters out a large number of infrequently seen features.
-  val minFeatureCountDefault = midOrPair match { case "mid" => 2000; case "mid_pair" => 100 }
-  val minFeatureCount = JsonHelper.extractWithDefault(params, "min feature count", minFeatureCountDefault)
+  val minMidFeatureCount = JsonHelper.extractWithDefault(params, "min mid feature count", 2000)
+  val minMidPairFeatureCount = JsonHelper.extractWithDefault(params, "min mid pair feature count", 100)
 
   // How many features should we keep per word?
   val featuresPerWord = JsonHelper.extractWithDefault(params, "features per word", 100)
 
   val useSquaredPmi = JsonHelper.extractWithDefault(params, "use squared pmi", false)
 
+  // You can run this on a cluster, if you want, but then you have to put all of your data on S3,
+  // and specify in your experiment configuration where those files are, and get your AWS keys into
+  // your shell environment, and so on...
+  val runningLocally = JsonHelper.extractWithDefault(params, "run locally", true)
+
   // TODO(matt): maybe this should be a parameter...?  But this one is purely computational, and
   // changing it does not change the output, so I don't really want it to get saved in the param
   // file...
   val numPartitions = 2000
 
-  val matrixFile = if (runningLocally) {
-    s"$outDir/pre_filtered_${midOrPair}_features.tsv"
[…]

### 2016-03-17 src/main/scala/org/allenai/semparse/pipeline/Tester.scala

@@ -5,6 +5,8 @@ import java.io.File
 
 import scala.collection.mutable
 
+import org.allenai.semparse.Environment
+
 import com.jayantkrish.jklol.lisp.ConsValue
 
 import com.mattg.util.FileUtil
@@ -21,16 +23,18 @@ class Tester(
 ) extends Step(Some(params), fileUtil) {
   implicit val formats = DefaultFormats
 
-  // Parameters we take.
-  val poolDepth = JsonHelper.extractWithDefault(params, "pool depth", 100)
+  // Parameters we take.  Only the query file is required.
   val queryFile = (params \ "test query file").extract[String]
-  val dataName = (params \ "data name").extract[String]
-  val ranking = JsonHelper.extractOptionWithDefault(params, "ranking", Seq("query", "predicate"), "query")
-  val modelType = JsonHelper.extractOption(params, "model type", Seq("baseline", "distributional", "formal", "combined"))
+  val poolDepth = JsonHelper.extractWithDefault(params, "pool depth", 100)
   val ensembledEvaluation = JsonHelper.extractWithDefault(params, "ensembled evaluation", false)
 
-  // Original training data file, which we process to get a set of entity names.
-  val trainingDataFile = (params \ "training data file").extract[String]
+  // Some of the parameters we need we'll grab from steps we depend on.
+  val trainer = new Trainer(params \ "trainer", fileUtil)
+  val processor = trainer.processor
+  val dataName = processor.dataName
+  val ranking = trainer.ranking
+  val modelType = trainer.modelType
+  val trainingDataFile = processor.trainingDataFile
 
   // These are code files that are common to all models, and just specify the base lisp
   // environment.
@@ -88,11 +92,7 @@ class Tester(
     }
   }
 
-  // At this point we're finally ready to override the Step methods.  To do this, we first create
-  // the Step objects we depend on.
-  val processor = new TrainingDataProcessor(params \ "training data", fileUtil)
-  val trainer = new Trainer(params \ "trainer", fileUtil)
-
+  // At this point we're finally ready to override the Step methods.
   override def paramFile = outputFile.replace("output.txt", "params.json")
   override def name = "Model tester"
   override def inputs =

### 2016-03-17 src/main/scala/org/allenai/semparse/pipeline/Trainer.scala

@@ -2,6 +2,8 @@ package org.allenai.semparse.pipeline
 
 import java.io.File
 
+import org.allenai.semparse.Environment
+
 import com.mattg.util.FileUtil
 import com.mattg.util.JsonHelper
 import com.mattg.pipeline.Step
@@ -15,9 +17,13 @@ class Trainer(
   implicit val formats = DefaultFormats
 
   // The parameters we take.
-  val dataName = (params \ "data name").extract[String]
   val ranking = JsonHelper.extractOptionWithDefault(params, "ranking", Seq("query", "predicate"), "query")
   val modelType = JsonHelper.extractOption(params, "model type", Seq("distributional", "formal", "combined"))
+
+  // A few necessary things from previous steps.
+  val pmiComputer = new SparkPmiComputer(params \ "feature computer", fileUtil)
+  val processor = pmiComputer.featureComputer.trainingDataProcessor
+  val dataName = processor.dataName
 
   // The output file.
   val serializedModelFile = s"output/$dataName/$modelType/$ranking/model.ser"
@@ -50,18 +56,12 @@ class Trainer(
     Seq(entityFile, wordsFile, logicalFormFile)
   }
 
-  val midFeatureFiles = Seq(
+  val featureFiles = Seq(
     s"data/${dataName}/mid_features.tsv",
-    s"data/${dataName}/cat_word_features.tsv"
-  )
-  val midPairFeatureFiles = Seq(
     s"data/${dataName}/mid_pair_features.tsv",
+    s"data/${dataName}/cat_word_features.tsv",
     s"data/${dataName}/rel_word_features.tsv"
   )
-
-  val processor = new TrainingDataProcessor(params \ "training data", fileUtil)
-  val midPmiComputer = new SparkPmiComputer(params \ "mid feature computer", fileUtil)
-  val midPairPmiComputer = new SparkPmiComputer(params \ "mid pair feature computer", fileUtil)
 
   // The path to the model file already encodes all of our parameters, really, but this will also
   // check that our data parameters haven't changed (i.e., using a different subset of the data,
@@ -72,8 +72,7 @@ class Trainer(
     handwrittenLispFiles.map((_, None)).toSet ++
     Set((sfeSpecFile, None)) ++
     dataFiles.map((_, Some(processor))).toSet ++
-    midFeatureFiles.map((_, Some(midPmiComputer))).toSet ++
[…]

### 2016-03-17 src/main/scala/org/allenai/semparse/pipeline/TrainingDataProcessor.scala

@@ -496,24 +496,3 @@ class TrainingDataProcessor(
     fileUtil.writeLinesToFile(outDir + "training-mid-pair-words.tsv", midPairWords)
   }
 }
-
-// TODO(matt): remove this once the whole pipeline is converted to the new system.
-object process_training_data {
-  def main(args: Array[String]) {
-    // This is so you can have a small dataset while developing things.
-    println("Processing a sample of the data")
-    val smallParams = ("training data file" -> "data/acl2016-training.txt") ~
-      ("data name" -> "acl2016-sample") ~
-      ("word count threshold" -> 2) ~
-      ("lines to use" -> 100000)
-    val smallProcessor = new TrainingDataProcessor(smallParams)
-    smallProcessor._runStep()
-
-    println("Processing the whole data")
-    val params = ("training data file" -> "data/acl2016-training.txt") ~
-      ("data name" -> "acl2016") ~
-      ("word count threshold" -> 5)
-    val largeProcessor = new TrainingDataProcessor(params)
-    largeProcessor._runStep()
-  }
-}

### 2016-03-17 src/main/scala/org/allenai/semparse/Experiments.scala
Finally done with this migration.  Now to see if it actually works...
Former-commit-id: ba48c7e107e3537f9b4fc41bb88dfcb721fb8971
Former-commit-id: 999709e1d424e81422fc390708612fd75ef91b64

@@ -1,51 +1,0 @@
-package org.allenai.semparse
-
-// This object just keeps track of all of the (hand-written) lisp input files that we use.
-object LispFiles {
-
-  val BASE_ENVIRONMENT_FILE = "src/main/lisp/environment.lisp"
-  val USCHEMA_ENVIRONMENT_FILE = "src/main/lisp/uschema_environment.lisp"
-
-  val DISTRIBUTIONAL_MODEL_FILE = "src/main/lisp/model_distributional.lisp"
-  val COMBINED_MODEL_FILE = "src/main/lisp/model_combined.lisp"
-  val FORMAL_MODEL_FILE = "src/main/lisp/model_formal.lisp"
-  val BASELINE_MODEL_FILE = "src/main/lisp/model_baseline.lisp"
-
-  val PREDICATE_RANKING_FILE = "src/main/lisp/predicate_ranking.lisp"
-  val QUERY_RANKING_FILE = "src/main/lisp/query_ranking.lisp"
-  val TRAIN_FILE = "src/main/lisp/train_model.lisp"
-
-  val EVAL_BASELINE_FILE = "src/main/lisp/eval_baseline.lisp"
-  val EVAL_USCHEMA_FILE = "src/main/lisp/eval_uschema.lisp"
-  val EVAL_ENSEMBLE_FILE = "src/main/lisp/eval_ensemble.lisp"
-
-  val SMALL_BASE_DATA_FILE = "data/tacl2015/tacl2015-training-sample.txt"
-  val SMALL_WORD_FILE = "data/small/words.lisp"
-  val SMALL_ENTITY_FILE = "data/small/entities.lisp"
-  val SMALL_JOINT_ENTITY_FILE = "data/small/joint_entities.lisp"
-  val SMALL_PREDICATE_RANKING_LF_FILE = "data/small/predicate_ranking_lf.lisp"
-  val SMALL_QUERY_RANKING_LF_FILE = "data/small/query_ranking_lf.lisp"
-  val SMALL_SFE_SPEC_FILE = "src/main/resources/sfe_spec_small.json"
-
-  val LARGE_BASE_DATA_FILE = "data/acl2016-training.txt"
-  val LARGE_WORD_FILE = "data/large/words.lisp"
[…]

### 2016-03-17 src/main/scala/org/allenai/semparse/pipeline/Experiments.scala

@@ -1,0 +1,149 @@
+package org.allenai.semparse.pipeline
+
+import org.json4s._
+import org.json4s.JsonDSL._
+
+object Experiments {
+
+  // *********************************
+  // STEP 1: TRAINING DATA PROCESSING
+  // *********************************
+
+  val NEW_LF_TRAINING_DATA_FILE = "data/acl2016-training.txt"
+  val NEW_LF_TRAINING_DATA_NAME = "acl2016"
+  val OLD_LF_TRAINING_DATA_FILE = "data/tacl2015/tacl2015-training.txt"
+  val OLD_LF_TRAINING_DATA_NAME = "tacl2015"
+
+  val newLfTrainingDataParams: JValue =
+    ("training data file" -> NEW_LF_TRAINING_DATA_FILE) ~
+    ("data name" -> NEW_LF_TRAINING_DATA_NAME) ~
+    ("word count threshold" -> 5)
+
+  val newLfTrainingDataSampleParams: JValue =
+    ("training data file" -> NEW_LF_TRAINING_DATA_FILE) ~
+    ("data name" -> (NEW_LF_TRAINING_DATA_NAME + "_sample")) ~
+    ("word count threshold" -> 0) ~
+    ("lines to use" -> 1000)
+
+  val oldLfTrainingDataParams: JValue =
+    ("training data file" -> OLD_LF_TRAINING_DATA_FILE) ~
+    ("data name" -> OLD_LF_TRAINING_DATA_NAME) ~
+    ("word count threshold" -> 5)
+
+  val oldLfTrainingDataSampleParams: JValue =
+    ("training data file" -> OLD_LF_TRAINING_DATA_FILE) ~
+    ("data name" -> (OLD_LF_TRAINING_DATA_NAME + "_sample")) ~
+    ("word count threshold" -> 0) ~
+    ("lines to use" -> 1000)
+
+  // **********************************
+  // STEP 2: FEATURE MATRIX COMPUTATION
+  // **********************************
+
+  val SFE_SPEC_FILE = "src/main/resources/sfe_spec.json"
+
+  val newLfTrainingDataFeatureParams: JValue =
+    ("training data" -> newLfTrainingDataParams) ~
+    ("sfe spec file" -> SFE_SPEC_FILE)
+
+  val newLfTrainingDataSampleFeatureParams: JValue =
+    ("training data" -> newLfTrainingDataSampleParams) ~
[…]

### 2016-03-17 src/main/scala/org/allenai/semparse/pipeline/TrainingDataFeatureComputer.scala

@@ -78,10 +78,10 @@ class TrainingDataFeatureComputer(
 ) extends Step(Some(params), fileUtil) {
   implicit val formats = DefaultFormats
 
-  val dataName = (params \ "data name").extract[String]
-  val sfeSpecFile = (params \ "sfe spec file").extract[String]
   val trainingDataParams = (params \ "training data")
+  val sfeSpecFile = (params \ "sfe spec file").extract[String]
   val trainingDataProcessor = new TrainingDataProcessor(trainingDataParams, fileUtil)
+  val dataName = trainingDataProcessor.dataName
   val outDir = s"data/$dataName/"
 
   val midFile = s"${outDir}/training_mids.tsv"

### 2016-03-17 src/main/scala/org/allenai/semparse/pipeline/SparkPmiComputer.scala
Some bug fixes.  Getting close to having this actually working
Former-commit-id: 8876d003919534260952d545ad702ba51b594fb8
Former-commit-id: a60364969a2aebbe153c0dadb91860a14f1839d2

@@ -15,6 +15,18 @@ class SparkPmiComputer(
 ) extends Step(Some(params), fileUtil) {
   implicit val formats = DefaultFormats
 
+  val validParams = Seq(
+    "max word count",
+    "max feature count",
+    "min mid feature count",
+    "min mid pair feature count",
+    "features per word",
+    "use squared pmi",
+    "run locally",
+    "training data features"
+  )
+  JsonHelper.ensureNoExtras(params, "pmi computer", validParams)
+
   // If we've seen a MID too many times, it blows up the word-feature computation.  The US, God,
   // and TV all show up more than 12k times in the large dataset.  I think we can get a good enough
   // PMI computation without these really frequent MIDs.  These parameters throw out a few
@@ -46,7 +58,7 @@ class SparkPmiComputer(
   val processor = featureComputer.trainingDataProcessor
   val dataName = processor.dataName
 
-  val outDir = s"data/${dataName}/"
+  val outDir = s"data/${dataName}"
 
   val midMatrixFile = if (runningLocally) {
     s"$outDir/pre_filtered_mid_features.tsv"
@@ -73,13 +85,13 @@ class SparkPmiComputer(
   }
 
   val catWordFeatureFile = if (runningLocally) {
-    "$outDir/cat_word_features.tsv"
+    s"$outDir/cat_word_features.tsv"
   } else {
     (params \ "cat word feature file").extract[String]  // some S3 URI
   }
 
   val relWordFeatureFile = if (runningLocally) {
-    "$outDir/rel_word_features.tsv"
+    s"$outDir/rel_word_features.tsv"
   } else {
     (params \ "rel word feature file").extract[String]  // some S3 URI
   }

### 2016-03-17 src/main/scala/org/allenai/semparse/pipeline/Experiments.scala
Some bug fixes.  Getting close to having this actually working
Former-commit-id: 8876d003919534260952d545ad702ba51b594fb8

@@ -115,13 +115,13 @@ object Experiments {
 
   val newLfSampleFormalModelFinalTestParams: JValue =
     ("test query file" -> FINAL_TEST_SET) ~
-    ("model" -> newLfFormalModelParams)
+    ("model" -> newLfSampleFormalModelParams)
   val newLfSampleDistributionalModelFinalTestParams: JValue =
     ("test query file" -> FINAL_TEST_SET) ~
-    ("model" -> newLfDistributionalModelParams)
+    ("model" -> newLfSampleDistributionalModelParams)
   val newLfSampleCombinedModelFinalTestParams: JValue =
     ("test query file" -> FINAL_TEST_SET) ~
-    ("model" -> newLfCombinedModelParams)
+    ("model" -> newLfSampleCombinedModelParams)
 
 
   def main(args: Array[String]) {

### 2016-03-17 src/main/scala/org/allenai/semparse/pipeline/Tester.scala

@@ -23,13 +23,16 @@ class Tester(
 ) extends Step(Some(params), fileUtil) {
   implicit val formats = DefaultFormats
 
+  val validParams = Seq("test query file", "pool depth", "ensembled evaluation", "model")
+  JsonHelper.ensureNoExtras(params, "tester", validParams)
+
   // Parameters we take.  Only the query file is required.
   val queryFile = (params \ "test query file").extract[String]
   val poolDepth = JsonHelper.extractWithDefault(params, "pool depth", 100)
   val ensembledEvaluation = JsonHelper.extractWithDefault(params, "ensembled evaluation", false)
 
   // Some of the parameters we need we'll grab from steps we depend on.
-  val trainer = new Trainer(params \ "trainer", fileUtil)
+  val trainer = new Trainer(params \ "model", fileUtil)
   val processor = trainer.processor
   val dataName = processor.dataName
   val ranking = trainer.ranking
@@ -56,7 +59,7 @@ class Tester(
   val handwrittenLispFiles = Seq(baseEnvFile, uschemaEnvFile) ++ lispModelFiles ++ Seq(evalLispFile)
 
   // This one is a (hand-written) parameter file that will be passed to lisp code.
-  val sfeSpecFile = s"src/main/resources/sfe_spec.json"
+  val sfeSpecFile = trainer.sfeSpecFile
 
   // These are data files, produced by TrainingDataProcessor.
   val entityFile = s"data/${dataName}/entities.lisp"
@@ -64,8 +67,7 @@ class Tester(
 
   val dataFiles = Seq(entityFile, wordsFile)
 
-  // TODO(matt): might make sense to just grab this path directly from Trainer.
-  val serializedModelFile = s"output/$dataName/$modelType/$ranking/model.ser"
+  val serializedModelFile = trainer.serializedModelFile
   val baselineModelFile = s"output/$dataName/baseline/model.lisp"
 
   val baseInputFiles = dataFiles ++ handwrittenLispFiles

### 2016-03-17 src/main/scala/org/allenai/semparse/pipeline/Trainer.scala

@@ -16,6 +16,9 @@ class Trainer(
 ) extends Step(Some(params), fileUtil) {
   implicit val formats = DefaultFormats
 
+  val validParams = Seq("model type", "ranking", "feature computer")
+  JsonHelper.ensureNoExtras(params, "trainer", validParams)
+
   // The parameters we take.
   val ranking = JsonHelper.extractOptionWithDefault(params, "ranking", Seq("query", "predicate"), "query")
   val modelType = JsonHelper.extractOption(params, "model type", Seq("distributional", "formal", "combined"))
@@ -42,7 +45,7 @@ class Trainer(
     Seq(baseEnvFile, uschemaEnvFile, rankingLispFile, lispModelFile, trainingLispFile)
 
   // This one is a (hand-written) parameter file that will be passed to lisp code.
-  val sfeSpecFile = s"src/main/resources/sfe_spec.json"
+  val sfeSpecFile = pmiComputer.featureComputer.sfeSpecFile
 
   // These are data files, produced by TrainingDataProcessor.
   val entityFile = s"data/${dataName}/entities.lisp"

### 2016-03-17 src/main/scala/org/allenai/semparse/pipeline/TrainingDataFeatureComputer.scala

@@ -10,6 +10,7 @@ import edu.cmu.ml.rtw.pra.graphs.Graph
 import edu.cmu.ml.rtw.pra.graphs.Graph
 
 import com.mattg.util.FileUtil
+import com.mattg.util.JsonHelper
 import com.mattg.util.SpecFileReader
 import com.mattg.pipeline.Step
 
@@ -78,11 +79,14 @@ class TrainingDataFeatureComputer(
 ) extends Step(Some(params), fileUtil) {
   implicit val formats = DefaultFormats
 
+  val validParams = Seq("training data", "sfe spec file")
+  JsonHelper.ensureNoExtras(params, "feature matrix computer", validParams)
+
   val trainingDataParams = (params \ "training data")
   val sfeSpecFile = (params \ "sfe spec file").extract[String]
   val trainingDataProcessor = new TrainingDataProcessor(trainingDataParams, fileUtil)
   val dataName = trainingDataProcessor.dataName
-  val outDir = s"data/$dataName/"
+  val outDir = s"data/$dataName"
 
   val midFile = s"${outDir}/training_mids.tsv"
   val midPairFile = s"${outDir}/training_mid_pairs.tsv"
@@ -97,13 +101,14 @@ class TrainingDataFeatureComputer(
   )
   override def outputs = Set(midFeatureFile, midPairFeatureFile)
 
-  override def _runStep(args: Array[String]) {
+  override def _runStep() {
     processInMemory()
   }
 
   def processInMemory() {
     val fileUtil = new FileUtil
     val computer = new PreFilteredFeatureComputer(sfeSpecFile, fileUtil)
+    computer.graph.
 
     {
       // This block is so that midFeatures goes out of scope and can be garbage collected once it's

### 2016-03-17 src/main/scala/org/allenai/semparse/pipeline/TrainingDataProcessor.scala

@@ -136,6 +136,9 @@ class TrainingDataProcessor(
 ) extends Step(Some(params), fileUtil) {
   implicit val formats = DefaultFormats
 
+  val validParams = Seq("training data file", "data name", "word count threshold", "lines to use")
+  JsonHelper.ensureNoExtras(params, "trainer", validParams)
+
   val trainingDataFile = (params \ "training data file").extract[String]
   val dataName = (params \ "data name").extract[String]
   val wordCountThreshold = (params \ "word count threshold").extract[Int]
@@ -144,21 +147,30 @@ class TrainingDataProcessor(
     case jval => Some(jval.extract[Int])
   }
 
-  val outDir = s"data/$dataName/"
+  val outDir = s"data/$dataName"
+  val wordFile = s"$outDir/words.lisp"
+  val entityFile = s"$outDir/entities.lisp"
+  val jointEntityFile = s"$outDir/joint_entities.lisp"
+  val predicateRankingLfFile = s"$outDir/predicate_ranking_lf.lisp"
+  val queryRankingLfFile = s"$outDir/query_ranking_lf.lisp"
+  val midFile = s"$outDir/training_mids.tsv"
+  val midPairFile = s"$outDir/training_mid_pairs.tsv"
+  val midWordFile = s"$outDir/training_mid_words.tsv"
+  val midPairWordFile = s"$outDir/training_mid_pair_words.tsv"
 
   override def paramFile = outDir + "tdp_params.json"
   override def name = "Training data processor"
   override def inputs = Set((trainingDataFile, None))
   override def outputs = Set(
-    s"$outDir/words.lisp",
-    s"$outDir/entities.lisp",
-    s"$outDir/joint_entities.lisp",
-    s"$outDir/predicate_ranking_lf.lisp",
-    s"$outDir/query_ranking_lf.lisp",
-    s"$outDir/training_mids.tsv",
-    s"$outDir/training_mid_pairs.tsv",
-    s"$outDir/training_mid_words.tsv",
-    s"$outDir/training_mid_pair_words.tsv"
+    wordFile,
+    entityFile,
+    jointEntityFile,
+    predicateRankingLfFile,
+    queryRankingLfFile,
+    midFile,
+    midPairFile,
+    midWordFile,
+    midPairWordFile
   )
 
   val midRegex = "\"/m/[^\"]*\"".r
@@ -280,68 +292,68 @@ class TrainingDataProcessor(
   }
 
[…]

### 2016-03-17 src/main/scala/org/allenai/semparse/pipeline/TrainingDataFeatureComputer.scala
Somehow the last commit had a temporary eclim version of a file...
Former-commit-id: b5db45d95b59f958109f55d07829252b069c7c68

@@ -108,7 +108,6 @@ class TrainingDataFeatureComputer(
   def processInMemory() {
     val fileUtil = new FileUtil
     val computer = new PreFilteredFeatureComputer(sfeSpecFile, fileUtil)
-    computer.graph.
 
     {
       // This block is so that midFeatures goes out of scope and can be garbage collected once it's

### 2016-03-18 papers/acl2016/paper.tex

@@
 \newcommand{\blank}{\underline{\hspace{.5cm}}}
-\newcommand{\predicate}[1]{\ensuremath{\textsc{#1}}}
+\newcommand{\lexicalpredicate}[1]{\ensuremath{\textit{#1}}}
+\newcommand{\formalpredicate}[1]{\ensuremath{\textsc{#1}}}
 \newcommand{\entity}[1]{\ensuremath{\textsc{#1}}}
 
-\newcommand{\true}[0]{\predicate{true}}
-\newcommand{\false}[0]{\predicate{false}}
+\newcommand{\true}[0]{\formalpredicate{true}}
+\newcommand{\false}[0]{\formalpredicate{false}}
 
@@
 
-\title{Combining formal and distributional models of predicate semantics}
+\title{Combining Formal and Distributional Models of Predicate Semantics}
 
@@
 How should a computer program represent the meaning of a word or a
-phrase? Recent work has suggested two vastly different approaches --
-distributional vector space models and semantic parsing -- each with
-its own advantages and disadvantages. On one hand, distributional
-models produce a vector representation of the meaning of each word
-from a large unlabeled text corpus. These models have broad coverage
-but a shallow semantics centered around word similarity. On the other
-hand, semantic parsing translates natural language into logical
-queries against a formal knowledge base, such as Freebase. This
-approach produces a rich compositional semantics and furthermore can
-leverage structured information from the knowledge base, e.g., to
-answer natural language questions. However, semantic parsers have
-limited coverage as they can only represent the meanings of words that
-can be mapped to knowledge base predicates. A critical question is
-\emph{how do we obtain the benefits of both approaches?}
-
-% The answer to this question has a long and rich history.  Motivated by
-% , much work has been put into representing words as collections of the
-% contexts in which they appear.  Recent work with neural networks and
-% word embeddings have shown that these representations can be very
-% useful for a number of natural language processing tasks (see, e.g.,
-% the work Mikolov et al.~\shortcite{mikolov-2013-word2vec} and papers
-% that cite them).  This approach to modeling semantics is appealing
-% because word embeddings can be trained on unlabeled text, allowing for
-% very broad coverage, although shallow, semantics.
+phrase? Recent work has suggested two vastly different
+approaches---distributional vector space models and semantic
+parsing---each with its own advantages and disadvantages. On one hand,
+distributional models produce a vector representation of the meaning
+of each word from a large unlabeled text corpus. These models have
+broad coverage but a shallow semantics centered around word
+similarity. On the other hand, semantic parsing translates natural
+language into logical queries against a formal knowledge base, such as
+Freebase. This approach produces a rich compositional semantics and
+furthermore can leverage structured information from the knowledge
+base, e.g., to answer natural language questions. However, semantic
+parsers have limited coverage as they can only represent the meanings
+of words that can be mapped to knowledge base predicates. A critical
+question is \emph{how do we obtain the benefits of both approaches?}
 
@@
   \begin{minipage}{0.28\linewidth}
-    \textbf{Input Text}\\Italian architect Andrea Palladio
+    \textbf{Input Text}\\Italian architect \blank{}
   \end{minipage}
@@
     \textbf{Logical Form}\\
-    $\predicate{architect}(\entity{Palladio})~\land~\predicate{architect\_N/N}(\entity{Italy}, \entity{Palladio})$
+    $\lexicalpredicate{architect}(x)~\land~\lexicalpredicate{architect\_N/N}(\entity{Italy}, x)$
   \end{minipage}
@@
     \begin{tabular}{@{}lll}
-      \predicate{architect}: & $\theta$: &[.2, -.6, \ldots] \\
+      \lexicalpredicate{architect}: & $\theta$: &[.2, -.6, \ldots] \\
       & $\omega$: & \textsc{type:architect} $\rightarrow$ .52 \\
@@
     \begin{tabular}{@{}lll}
-      \predicate{architect\_N/N}: & $\theta$: &[-.9, .1, \ldots] \\
+      \lexicalpredicate{architect\_N/N}: & $\theta$: &[-.9, .1, \ldots] \\
       & $\omega$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ .29 \\
@@
 
-  \vspace{.1in}
   \begin{minipage}{0.5\linewidth}
@@
     \begin{tabular}{@{}lll}
-      \predicate{Palladio}: & $\phi$: &[.15, -.8, \ldots] \\
+      \entity{Palladio}: & $\phi$: &[.15, -.8, \ldots] \\
       & $\psi$: & \textsc{type:architect} $\rightarrow$ 1 \\
-      &           & \textsc{type:designer} $\rightarrow$ 0 \\
       &           & \textsc{nationality:Italy} $\rightarrow$ 1 \\
+      &           & $\cdots$ \\
+      \entity{Obama}: & $\phi$: &[.85, .1, \ldots] \\
+      & $\psi$: & \textsc{type:politician} $\rightarrow$ 1 \\
+      &           & \textsc{nationality:Italy} $\rightarrow$ 0 \\
       &           & $\cdots$
@@
     \begin{tabular}{@{}lll}
-      \predicate{(Italy, Palladio)}: & $\phi$: &[-.8, .2, \ldots] \\
+      \entity{(Italy, Palladio)}: & $\phi$: &[-.8, .2, \ldots] \\
       & $\omega$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ 1 \\
       &           & \textsc{/structure/architect} $\rightarrow$ 0 \\
-      &           & \textsc{/person/ethnicity\textsuperscript{-1}} $\rightarrow$ 0 \\
+      &           & $\cdots$ \\
+      \entity{(Italy, Obama)}: & $\phi$: &[-.2, -.2, \ldots] \\
+      & $\omega$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ 0 \\
+      &           & \textsc{/structure/architect} $\rightarrow$ 0 \\
       &           & $\cdots$
@@
 
+  \begin{minipage}{0.5\linewidth}
+    \textbf{Output}\\
+    \begin{tabular}{@{}ll}
+      $\mathrm{prob}(\entity{Palladio})$: & 0.79 \\
+      $\mathrm{prob}(\entity{Obama})$: & 0.01 \\
+      $\cdots$ \\
+    \end{tabular}
+  \end{minipage}
+
   \vspace{-.1in}
-  \caption{Overview of the components of our model.  Given an input text, we
-  use a CCG parser and an entity linker to produce a logical form that is a
-  conjunction of predicates involving the entities in the text.  For each
-  predicate (both categories and relations), we learn a distributional vector
-  $\theta$, as well as weights $\omega$ associated with formal features from
-  Freebase (which are shortened to fit in the figure).  For each entity and
-  entity pair, we also learn a distributional vector $\phi$, and we extract a
-  feature vector $\psi$ from Freebase.  These models are combined to assign a
-  probability to the input text, assigning a high probability to the above
-  text, and a low probability to ``Italian architect Barack Obama''.}
+  \caption{Overview of the components of our model.  Given an input
+  text, we use a CCG parser and an entity linker to produce a logical
+  form that is a conjunction of predicates involving the entities in
+  the text.  For each predicate (both categories and relations), we
+  learn a distributional vector $\theta$, as well as weights $\omega$
+  associated with formal features from Freebase (which are shortened
+  to fit in the figure).  For each entity and entity pair, we also
+  learn a distributional vector $\phi$, and we extract a feature
+  vector $\psi$ from Freebase.  These models are combined to assign a
+  probability to candidate entities, assigning a high probability to
+  \entity{Andrea Palladio} and a low probability to \entity{Barack
+  Obama}.}
   \label{fig:overview}
@@
 \end{figure*}
-
-% At the same time, other researchers have found Montague's ideas about English
-% as a formal language to be useful~\cite{montague-1974-english-formal-language}.
-% Modern semantic parsers make use of a model-theoretic semantics that represents
-% words and phrases as formal predicates.  These predicates are then typically
-% mapped onto a query over a structured knowledge base, such as
-% Freebase~\cite{freebase-2008-bollacker}.  This kind of modeling allows semantic
-% parsers to handle the compositional structure of natural language and to
-% leverage large, curated knowledge sources to perform various natural language
-% processing
-% tasks~\cite{zettlemoyer-2005-ccg,kwiatkowski-2013-ontology-matching,berant-2013-semantic-parsing-qa}.
-% However, semantic parsers are fundamentally limited by the schema of the
-% ontology they are trained on---a semantic parser trained with Freebase cannot
-% even represent words whose meaning has no correlate in the Freebase ontology,
-% such as ``front-runner'' and ``honcho''.
 
@@
 form containing predicates derived from the text itself, such as
-$\lambda x.\predicate{honcho}(x) \land
-\predicate{honcho\_N/N}(\entity{Hollywood}, x)$, then learns the
+$\lambda x.\lexicalpredicate{honcho}(x) \land
+\lexicalpredicate{honcho\_N/N}(\entity{Hollywood}, x)$, then learns the
 denotations of these predicates using distributional information from
@@
 represent its meaning. For example, an entity that can be called
-``honcho'' is likely to have type \predicate{person}. We therefore
+``honcho'' is likely to have type \formalpredicate{person}. We therefore
 incorporate \emph{features} based on Freebase paths into the predicate
@@
 
-% Thus, we extend K\&M to incorporate such features from Freebase into
-% its predicate models. Our model automatically generates such features
-% and learns per-predicate weights for them using distributional
-% statistics.
-
-% In this work we introduce models of predicate semantics that combine the
-% benefits of both distributional and formal approaches.  While there is no
-% Freebase predicate that corresponds exactly to the meaning of ``honcho'',
-% Freebase \emph{does} contain many predicates that can \emph{partially}
-% represent the word.  Our models extract features from Freebase that are
-% correlated with words and phrases seen in natural language text, and learns
-% weights for those features as additional components of a distributional model
-% of the word's meaning.
-
-% To demonstrate these models, we focus on the task of fill-in-the-blank natural
-% language queries, such as ``Italian architect \blank{}''.  Similar to many
-% current semantic parsers, we first convert this natural language query into a
-% logical form: $\lambda x. \predicate{architect}(x) \land
-% \predicate{architect\_N/N}(\entity{Italy},
-% x)$.\footnote{\predicate{architect\_N/N} represents a noun-compound
-% relationship between two entities mediated by the word ``architect'', as in
-% ``Italian architect Andrea Palladio''.  This is in contrast to, e.g.,
-% \predicate{'s\_architect} or \predicate{architect\_of}, both of which also are
-% mediated by ``architect'', but through different syntax.  N/N is how
-% CCG~\cite{steedman-2006-ccg} represents a noun compound.} A typical semantic
-% parser (e.g., that of Kwiatkowski et
-% al.~\shortcite{kwiatkowski-2013-ontology-matching}) would then try to map this
-% logical form to a single Freebase query, likely involving
-% (\predicate{/people/person/nationality}: \entity{Italy}) and
-% (\predicate{/type/object/type}: \entity{/architecture/architect}).  Instead of
-% restricting ourselves to modeling only what can be represented as a Freebase
-% query, we follow Krishnamurthy and
-% Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} in learning a
-% model for each predicate that can give a \emph{score} to potential arguments.
-% The model for \predicate{architect}, e.g., should give high scores to
-% \entity{Andrea Palladio} and \entity{Frank Lloyd Wright}, and low scores to
-% \entity{Italy}, \entity{BarackObama}, etc.  However, while the models of
-% Krishnamurthy and Mitchell are purely distributional, using Freebase only as a
-% means of finding entities in text, we inject additional information from
-% Freebase into the models for each predicate.  The model we learn for
-% \predicate{architect} has a \emph{feature} capturing the fact that an entity
-% has the type \entity{/architecture/architect} in Freebase, and the model for
-% \predicate{architect\_N/N} has a \emph{feature} capturing whether the first
-% argument is the country of nationality of the second argument.  An overview of
-% the components of our model is given in \figref{overview}.
-% 
-% This is a new kind of predicate semantics.  It is distributional---part of the
-% model is still trained in a manner very similar to word2vec---yet it is also
-% formal.  However, instead of committing to a single Freebase query to represent
-% a phrase, as traditional formal approaches do, our models are flexible,
-% encoding many possible Freebase queries as features that can give hints to the
-% model.  Thus words that would be impossible to represent as a single Freebase
-% query can still benefit from the information contained in Freebase---our model
-% for ``front-runner'' learns that acceptable entities are politicians, even
-% though there is no exact encoding of ``front-runner'' in Freebase.
-% 
-% The rest of this paper is organized as follows.  In \secref{background}, we
-% describe the relevant background necessary to understand the models we propose,
-% and we situate our model in the context of related work.  In \secref{method},
-% we give a formal description of our models of predicate semantics.  In
-% \secref{evaluation}, we present experimental results on fill-in-the-blank
-% natural language query task.  Using web text linked to Freebase as our training
-% and test data, we show a 62\% relative improvement over prior work, giving a
-% new state-of-the-art result on this dataset.  In \secref{discussion}, we give a
-% detailed discussion of the benefits and drawbacks of the models we have
-% proposed.  We then conclude in \secref{conclusion}.
-
 \section{Background}
@@
 
-Our proposed method is best viewed as the addition of SFE
-features~\cite{gardner-2015-sfe} to Krishnamurthy and
-Mitchell's~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}
-open-vocabulary semantic parser.  Accordingly, in this section we briefly
-describe both of these techniques, as well as give a short overview of other
-closely related work.
+In this work, we make heavy use of the open-vocabulary semantic parser
+of Krishnamurthy and
+Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}, as
+well as features derived from a knowledge base using a technique
+called subgraph feature extraction~\cite[SFE]{gardner-2015-sfe}.
+Accordingly, in this section we briefly describe both of these
+techniques.
 
@@
 The truth probability of a predicate instance such as
-\predicate{architect}(\entity{AndreaPalladio}) is learned using
+\lexicalpredicate{architect}(\entity{AndreaPalladio}) is learned using
 probabilistic matrix factorization. This factorization has two sets of
@@
     \path[]
-      (1) edge node [sloped, anchor=center, above] {\predicate{nationality}} (2)
-      (1) edge node [sloped, anchor=center, above] {\predicate{type}} (3)
-      (1) edge node [sloped, anchor=center, above] {\predicate{designed}} (5)
-      (2) edge node [sloped, anchor=center, above] {\predicate{type}} (4)
-      (5) edge node [sloped, anchor=center, above] {\predicate{located\_in}} (2);
+      (1) edge node [sloped, anchor=center, above] {\formalpredicate{nationality}} (2)
+      (1) edge node [sloped, anchor=center, above] {\formalpredicate{type}} (3)
+      (1) edge node [sloped, anchor=center, above] {\formalpredicate{designed}} (5)
+      (2) edge node [sloped, anchor=center, above] {\formalpredicate{type}} (4)
+      (5) edge node [sloped, anchor=center, above] {\formalpredicate{located\_in}} (2);
   \end{tikzpicture}
@@
   \textbf{Features between \entity{Palladio} and \entity{Italy}}:\\
-  \textless\predicate{nationality}\textgreater\\
-  \textless\predicate{designed}, \predicate{located\_in}\textgreater
+  \textless\formalpredicate{nationality}\textgreater\\
+  \textless\formalpredicate{designed}, \formalpredicate{located\_in}\textgreater
   \caption{A subset of the Freebase graph, and some example extracted features
@@
 
-\subsection{Other related work}
-
-There is a large body of other work that is closely related to what is
-presented in this paper.  Two recent papers that also attempt to include some
-form of structured knowledge into distributional representations are those by
-Faruqui et al.~\shortcite{faruqui-2015-retrofitting-word-vectors}, and by
-Rockt\"{a}schel et al.~\shortcite{rocktaschel-2015-logical-embeddings}.  A key
-difference between their approaches and ours is that they use the structured
-information only to modify distributional representations, while we include the
-structured information directly in our models, training weights for structured
-information jointly with distributional representations.  Also conceptually
-similar is the Additive Relational Effects model for knowledge base completion
-by Nickel et al.~\shortcite{nickel-2014-are}, which tries to factorize the
-residual of a KB tensor that cannot be explained by observable features that
-are somewhat similar to the formal features we use in this model.  But while
-this model is conceptually similar, it is computationally quite different, and
-would be rather difficult to use in the setting we explore in this work.
-
-Our work draws a lot of inspiration from recent work on knowledge base
-completion.  We are building on top of work in embedding the entities and
-relations in a knowledge
-base~\cite{riedel-2013-mf-universal-schema,nickel-2011-rescal,bordes-2013-transe},
-as well as work on graph-based methods for reasoning with knowledge
-bases~\cite{lao-2010-original-pra,gardner-2014-vector-space-pra,neelakantan-2015-rnn-kbc}.
-
-Lastly, there is an extensive literature on building semantic parsers to answer
-questions against a structured knowledge
-base~\cite{zettlemoyer-2005-ccg,berant-2013-semantic-parsing-qa,%
-kwiatkowski-2013-ontology-matching,krishnamurthy-2012-semantic-parsing}.  The
-vast majority of this work is focused on matching natural language text to
-statements in a specific ontology, with no hope of assigning meaning to
-language that falls outside of that ontology.  Only very recently has there
-been work attempting to learn broad coverage meaning representations in
-semantic parsers.  In addition to the work by Krishnamurthy and Mitchell which
-we extend in this paper, there was recently a nice piece of work by Choi et
-al.~\shortcite{choi-2015-semantic-parsing-partial-ontologies}.  The aim of
-their work is, like typical semantic parsers, to map text onto a single formal
-statement, but they allow some of the predicates to be ``open'' predicates not
-contained in the Freebase ontology.  A key difference between their work and
-ours is that we score surface logical forms directly, using a weighted
-combination of many Freebase queries, instead of trying to map them to a single
-Freebase logical form.  Additionally, while their system might learn that
-``front-runner'' should be modeled as an open predicate that has no
-representation in Freebase, they have no method to assign any further meaning
-to that predicate, while our models learn both distributional and formal
-information about the meaning of ``front-runner''.
-
 \section{Method}
@@
 (1) for the entity \entity{Palladio}, as well as the features
-\textless\predicate{type}\textgreater and
-\textless\predicate{designed}\textgreater.  Examples of of type (2) features
-are \textless\predicate{type}\textgreater:\entity{architect}, and
-\textless\predicate{nationality}\textgreater:\entity{Italy}.  Intuitively,
+\textless\formalpredicate{type}\textgreater and
+\textless\formalpredicate{designed}\textgreater.  Examples of of type (2) features
+are \textless\formalpredicate{type}\textgreater:\entity{architect}, and
+\textless\formalpredicate{nationality}\textgreater:\entity{Italy}.  Intuitively,
 features of type (1) capture the fact that an entity participates in particular
@@
 the entity in the feature is a type node, such as with
-\textless\predicate{type}\textgreater:\entity{architect}, though occasionally
+\textless\formalpredicate{type}\textgreater:\entity{architect}, though occasionally
 features of this type involving other entities are also selected in our feature
@@
 considered a positive training example for the instantiated predicates
-$\predicate{architect}(\entity{Andrea Palladio})$ and
-$\predicate{architect\_N/N}(\entity{Italy}, \entity{Andrea Palladio})$.  We
+$\lexicalpredicate{architect}(\entity{Andrea Palladio})$ and
+$\lexicalpredicate{architect\_N/N}(\entity{Italy}, \entity{Andrea Palladio})$.  We
 then associate the feature vectors for \entity{Andrea Palladio} and
 (\entity{Italy}, \entity{Andrea Palladio}) with the predicates
-\predicate{architect} and \predicate{architect\_N/N}, respectively.  For each
+\lexicalpredicate{architect} and \lexicalpredicate{architect\_N/N}, respectively.  For each
 predicate $\pi$ and feature $f$, we use these counts to calculate the
@@
 the relation predicate produced by K\&M's system is
-$\predicate{N/N}(\entity{Italy}, \entity{Andrea Palladio})$.  \predicate{N/N}
+$\lexicalpredicate{N/N}(\entity{Italy}, \entity{Andrea Palladio})$.
+\lexicalpredicate{N/N}
 does correctly capture the fact that \entity{Italy} is used syntactically as a
@@
 predicate, which leads to a very generic and largely useless model for the
-predicate \predicate{N/N}.  By splitting \predicate{N/N} into separate
-predicates (\predicate{architect\_N/N} and \predicate{president\_N/N}), we give
+predicate \lexicalpredicate{N/N}.  By splitting \lexicalpredicate{N/N} into separate
+predicates (\lexicalpredicate{architect\_N/N} and \lexicalpredicate{president\_N/N}), we give
 the model the opportunity to learn more fine-grained relation semantics, and we
@@
 in a noun phrase as the predicate (e.g., ``Illinois attorney general Lisa
-Madigan'' would produce the predicate \predicate{attorney\_general\_N/N}).
+Madigan'' would produce the predicate \lexicalpredicate{attorney\_general\_N/N}).
 
@@
 ``Barack Obama, president of the U.S.'', K\&M's system would produce the
-following relation predicate: $\predicate{of}(\entity{Barack Obama},
-\entity{U.S.})$.  Because this same predicate (\predicate{of}) is used for all
+following relation predicate: $\lexicalpredicate{of}(\entity{Barack Obama},
+\entity{U.S.})$.  Because this same predicate (\lexicalpredicate{of}) is used for all
 instances of this preposition, the predicate is forced to model too much and
@@
 dependency between two entities, as in the phrase above, we add that noun to
-the predicate, giving the instance $\predicate{president\_of}(\entity{Barack
+the predicate, giving the instance $\lexicalpredicate{president\_of}(\entity{Barack
 Obama}, \entity{U.S.})$.  We do the same for possessives in phrases such as
-``Rome, Italy's capital'', producing the predicate \predicate{'s\_capital}.
+``Rome, Italy's capital'', producing the predicate \lexicalpredicate{'s\_capital}.
 
@@
 entity pair not seen during training time.  When given a query such as
-$\lambda(\entity{x}) \predicate{architect\_N/N}(\entity{x}, \entity{Andrea
+$\lambda(\entity{x}) \lexicalpredicate{architect\_N/N}(\entity{x}, \entity{Andrea
 Palladio})$, K\&M's system only needs to consider the set of entities
@@
 
-We evaluate our models of predicate semantics on a fill-in-the-blank natural
-language query task.  Each test example is a natural language phrase containing
-at least two Freebase entities, one of which is held out.  The system must
-propose Freebase entities to fill in the blank left by the held out entity, and
-the predicted entities are then judged manually for correctness.  We compare
-our proposed models, which combine distributional and formal elements, with
-distributional-only and formal-only baselines.
+We evaluate our models of predicate semantics on a fill-in-the-blank
+natural language query task.  Each test example is a natural language
+phrase containing at least two Freebase entities, one of which is held
+out.  The system must propose Freebase entities to fill in the blank
+left by the held out entity, and the predicted entities are then
+judged manually for correctness.  We compare our proposed models,
+which combine distributional and formal elements, with a
+distributional-only baseline from prior work.  All of the data and
+code used in these experiments is available at [url withheld for
+review].
 
@@
 We use the dataset introduced by Krishnamurthy and
-Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}, which
-consists of the ClueWeb09 web
-corpus\footnote{http://www.lemuproject.org/clueweb09.php} along with Google's
-FACC entity linking of that corpus to
-Freebase~\cite{gabrilovich-2013-clueweb-entity-linking}.  For training data, 3
-million webpages from this corpus were processed with a CCG parser to produce
-logical forms, as described in \secref{jayant-semparse}.  This produced 2.1m
-predicate instances involving 142k entity pairs and 184k entities.  After
-removing infrequently-seen predicates (seen fewer than 6 times), there were 25k
-categories and 4.2k relations.\footnote{The differences in numbers reported
-here versus those reported by Krishnamurthy and
-Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} are due to the
-improved logical form generation, discussed in \secref{better-lfs}.}
+Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary},
+which consists of the ClueWeb09 web
+corpus\footnote{http://www.lemuproject.org/clueweb09.php} along with
+Google's FACC entity linking of that corpus to
+Freebase~\cite{gabrilovich-2013-clueweb-entity-linking}.  For training
+data, 3 million webpages from this corpus were processed with a CCG
+parser to produce logical forms.  This produced 2.1m predicate
+instances involving 142k entity pairs and 184k entities.  After
+removing infrequently-seen predicates (seen fewer than 6 times), there
+were 25k categories and 4.2k relations.  The differences in numbers
+reported here versus those reported by Krishnamurthy and
+Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} are
+due to our improved logical form generation, discussed in
+\secref{better-lfs}.
 
-We also used the test set created by K\&M, which contains
-220 queries generated in the same fashion as the training data from a separate
-section of ClueWeb.  However, we used this set for intermediate evaluations
-while developing our models, and so we also generated another, similar test set
-from a different held out section of ClueWeb.  This final test set contains 307
-queries.  We report results on both of these test sets below.  All of the data
-used in these experiments is available at [url withheld for review].
+We also used the test set created by Krishnamurthy and Mitchell, which
+contains 220 queries generated in the same fashion as the training
+data from a separate section of ClueWeb.  However, as they did not
+release a development set in with their data, we used this set as a
+development set.  For a final evaluation, we generated another,
+similar test set from a different held out section of ClueWeb, in the
+same fashion as done by Krishnamurthy and Mitchell.  This final test
+set contains 307 queries.  We report results on both of these test
+sets below.
 
-\subsection{Experiments}
+\subsection{Models}
 
-We compare three models in our experiments: a distributional-only model, a
-formal-only model, and our proposed model, which is both distributional and
-formal.  The distributional-only model is the model proposed by Krishnamurthy
-and Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} and
-described in \secref{jayant-semparse}.  The combined model is the model
-described in \secref{formal-and-distributional}, while the formal-only
-model removes the distributional component from the combined model (i.e., all
-parameters $\theta$ and $\phi$ from the distributional portion of the model are
-fixed at zero during training and test).  Note that this formal-only baseline
-is also new to this work---we are not aware of any other work that models
-language in terms of features derived from a formal knowledge base.
-
-In addition to running experiments comparing these three models on the two test
-sets described above, we also evaluated the improvement gained by using our
-modified logical forms (\secref{better-lfs}), and our entity proposal mechanism
+We compare three models in our experiments: (1) a distributional-only
+model (the prior work of Krishnamurthy and
+Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}); (2)
+a formal-only model (new to this work), where the distributional
+parameters $\theta$ and $\phi$ in \secref{formal-and-distributional}
+are fixed at zero; and (3) the combined model described in
+\secref{formal-and-distributional} (also new to this work).  Except
+where noted, all experiments use our modified logical forms
+(\secref{better-lfs}) and our entity proposal mechanism
 (\secref{better-candidates}).
@@
 
-Given a fill-in-the-blank query such as ``Italian architect \blank{}'', each
-system produces a ranked list of 100 candidate entities.  To compare the output
-of the systems, we follow a pooled evaluation protocol commonly used in
-relation extraction and information
-retrieval~\cite{west-2014-kbc-via-qa,riedel-2013-mf-universal-schema}.  We take
-the top 30 predictions from each system and manually annotate whether they are
-correct, and use those annotations to compute the average precision (AP) and
-reciprocal rank (RR) of each system on the query.  Average precision is defined
-as $\frac{1}{m}\sum^m_{k=1} \mathrm{Prec}(k) \times \mathrm{Correct}(k)$, where
-$\mathrm{Prec}(k)$ is the recision at rank $k$, $\mathrm{Correct}(k)$ is an
-indicator function for whether the $k$th answer is correct, and $m$ is number
-of returned answers (up to 100, in this evaluation).  Reciprocal rank is
-computed by first finding the rank $r$ of the first correct prediction made by a
-system.  Reciprocal rank is then $\frac{1}{r}$, ranging from 1 (if the first
-prediction is correct) to 0 (if there is no correct answer returned).  In the
-tables below we report \emph{mean} average precision (MAP) and reciprocal rank
-(MRR), averaged over all of the queries in the test set.  We also report a
-weighted version of MAP, where the AP of each query is scaled by the number of
-annotated correct answers to the query.
+Given a fill-in-the-blank query such as ``Italian architect
+\blank{}'', each system produces a ranked list of 100 candidate
+entities.  To compare the output of the systems, we follow a pooled
+evaluation protocol commonly used in relation extraction and
+information
+retrieval~\cite{west-2014-kbc-via-qa,riedel-2013-mf-universal-schema}.
+We take the top 30 predictions from each system and manually annotate
+whether they are correct, and use those annotations to compute the
+average precision (AP) and reciprocal rank (RR) of each system on the
+query.  Average precision is defined as $\frac{1}{m}\sum^m_{k=1}
+\mathrm{Prec}(k) \times \mathrm{Correct}(k)$, where $\mathrm{Prec}(k)$
+is the recision at rank $k$, $\mathrm{Correct}(k)$ is an indicator
+function for whether the $k$th answer is correct, and $m$ is number of
+returned answers (up to 100, in this evaluation).  Reciprocal rank is
+computed by first finding the rank $r$ of the first correct prediction
+made by a system.  Reciprocal rank is then $\frac{1}{r}$, ranging from
+1 (if the first prediction is correct) to 0 (if there is no correct
+answer returned).  In the tables below we report \emph{mean} average
+precision (MAP) and reciprocal rank (MRR), averaged over all of the
+queries in the test set.  We also report a weighted version of MAP,
+where the AP of each query is scaled by the number of annotated
+correct answers to the query (shown as W-MAP in the tables for space
+considerations).
 
@@
   {\small
-    \begin{tabular}{lccc}
+    \begin{tabular}{lcc}
       \toprule
-      Method & MAP & Weighted MAP & MRR \\
+      Method & K\&M's LFs & Our LFs \\
       \midrule
-      Distributional-only & .284 & .371 & .379 \\
-      \ \ \ (old lfs) & .269 & .330 & .380 \\
+      Distributional-only & .269 & \textbf{.284} \\
       \midrule
-      Formal-only & .276 & .469 & .334 \\
-      \ \ \ (old lfs) & .231 & .358 & .216 \\
+      Formal-only & .231 & \textbf{.276} \\
       \midrule
-      Combined model & \textbf{.335} & \textbf{.477} & \textbf{.429} \\
-      \ \ \ (old lfs) & .313 & .396 & .413 \\
+      Combined model & .313 & \textbf{.335} \\
       \bottomrule
@@
   }
-  \caption{Results on the development set for our fill-in-the-blank task.  The
-  combined model improves MAP by 42\% compared to the distributional-only
-  baseline.  Additionally, the improved logical forms presented in
-  \secref{better-lfs} significantly improve all models.}
-  \label{tab:dev-results}
+  \caption{Comparison of models using logical forms from prior work
+  versus those introduced in this paper.  The metric shown is mean
+  average precision on the dev set.  With our logical forms,
+  performance of all models improves, quite substantially in the case
+  of the formal model.}
+  \label{tab:better-lfs}
 \end{table}
 
-\tabref{dev-results} shows the results of our experiments on the development
-set (the same as the test set used by Krishnamurthy and
-Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}).  As can be
-seen, the combined model significantly improves performance, giving a 42\%
-relative increase in MAP over the distributional-only baseline.  This table
-also shows the benefit of using our modified logical forms (see
-\secref{better-lfs}); by being able to better model the relations between
-entities, MAP of all of the models is improved.  Not surprisingly, the
-improvement is more pronounced for the models that have formal features, which
-can make better use of rich information from Freebase with our improved logical
-forms.\footnote{Because of the large amount of annotation effort involved, we
-did not include the unique results from this run in the evaluation pool.  This
-has the effect of slightly lowering the MAP score for these methods.  However,
-the large majority of the predictions made by these methods were already
-annotated, and spot-checking the unannotated predictions seemed to indicate
-that annotating them would not substantially change the result shown.}
+We first show the effect of using the new logical forms introduced in
+\secref{better-lfs}.  As can be seen in \tabref{better-lfs}, with
+improved logical forms, all models are better able to capture the
+semantics of language.  This improvement is more pronounced in the
+formal models, which have more capacity to get specific features from
+Freebase with the new logical forms.  As our logical forms are able to
+give all models better performance, the remaining experiments we
+present all use these logical forms.
 
@@
       \toprule
-      Method & MAP & Weighted MAP & MRR \\
+      Method & MAP & W-MAP & MRR \\
       \midrule
-      Distributional-only & .229 & .275 & .312 \\
-      \ \ \ -related entities & .163 & .163 & .288 \\
+      Distributional model & .163 & .163 & .288 \\
       \midrule
-      Formal-only & .355 & .495 & .419 \\
-      \midrule
-      Combined model & \textbf{.370} & \textbf{.513} & \textbf{.469} \\
+      With freebase entities & .\textbf{229} & \textbf{.275} & \textbf{.312} \\
+      \bottomrule
+      Relative improvement & 40\% & 69\% & 8\% \\
       \bottomrule
@@
   }
-  \caption{Results on the final test set for our fill-in-the-blank task.  The
-  combined model improves MAP by 62\% relative to the distributional-only
-  baseline.  Additionally, allowing the distributional-only model to use
-  Freebase to propose candidates improves MAP by 6.6 points absolute due to
-  improved recall.}
+  \caption{Allowing Krishnamurthy and Mitchell's model to propose
+  candidate entities from Freebase improves mean average precision
+  substantially, by allowing the model to have higher recall.}
+  \label{tab:better-candidates}
+\end{table}
+
+We next show the improvement gained by using the simple candidate
+entity generation outlined in \secref{better-candidates}.  By simply
+appending the list of connected entities to the end of the rankings
+returned by the distributional model, MAP improves by 40\% (see
+\tabref{better-candidates}).  The connectedness of an entity pair in
+Freebase is very informative, especially for rare entities that are
+not seen together during training.
+
+\begin{table}
+  \centering
+  {\small
+    \begin{tabular}{lccc}
+      \toprule
+      Method & MAP & W-MAP & MRR \\
+      \midrule
+      Prior work (distributional) & .284 & .371 & .379 \\
+      \midrule
+      Our formal model & .276 & .469 & .334 \\
+      \midrule
+      Our combined model & \textbf{.335} & \textbf{.477} & \textbf{.429} \\
+      \bottomrule
+      Relative improvement & 18\% & 29\% & 13\% \\
+      \bottomrule
+    \end{tabular}
+  }
+  \caption{Results on the development set for our fill-in-the-blank task.  The
+  combined model significantly improves MAP over prior work.}
+  \label{tab:dev-results}
+\end{table}
+
+\tabref{dev-results} shows the results of our experiments on the
+development set (the same as the test set used by Krishnamurthy and
+Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}).  As
+can be seen, the combined model significantly improves performance,
+giving a relative gain in weighted MAP of 29\%.
+
+\begin{table}
+  \centering
+  {\small
+    \begin{tabular}{lccc}
+      \toprule
+      Method & MAP & W-MAP & MRR \\
+      \midrule
+      Prior work (distributional) & .229 & .275 & .312 \\
+      \midrule
+      Our formal model & .355 & .495 & .419 \\
+      \midrule
+      Our combined model & \textbf{.370} & \textbf{.513} & \textbf{.469} \\
+      \bottomrule
+      Relative improvement & 62\% & 87\% & 50\% \\
+      \bottomrule
+    \end{tabular}
+  }
+  \caption{Results on the final test set for our fill-in-the-blank
+  task.  The combined model improves over prior work by 50--87\% on
+  our metrics.  Note that these improvements over the baseline are
+  \emph{after} the baseline has been improved by the methods developed
+  in this paper, shown in \tabref{better-lfs} and
+  \tabref{better-candidates}.  The cumulative effect of the methods
+  presented in this work is an improvement of over 120\% in MAP.}
   \label{tab:final-results}
@@
 
-\tabref{final-results} shows that these improvements are consistent on the
-final test set, as well.  The performance improvement seen by the combined
-model is actually larger on this set, going from a MAP of .229 to .370, a 62\%
-relative improvement.  In this table, we also show the improvement gained by
-allowing the distributional-only model to propose candidate entities that are
-related in Freebase (see \secref{better-candidates}).  Even though these
-candidates are always ranked at the bottom of the list of predictions (with a
-score of 0), the additional recall provided by being able to propose more
-entities raises MAP of the distributional-only model from .163 to .229.
+\tabref{final-results} shows that these improvements are consistent on
+the final test set, as well.  The performance improvement seen by the
+combined model is actually larger on this set, with gains on our
+metrics ranging from 50\% to 97\%.
 
-On both of these datasets, the difference between the combined model and the
-distributional model is statistically significant (by a paired permutation
-test, $p < 0.05$).  The difference between the combined model and the formal
-model, and between the formal model and the distributional model, are not
-statistically significant, as each method has certain kinds of queries that it
-performs well on.  Only the combined model is able to consistently outperform
-the distributional model on all kinds of queries.
+On both of these datasets, the difference in MAP between the combined
+model and the distributional model is statistically significant (by a
+paired permutation test, $p < 0.05$).  The difference between the
+combined model and the formal model, and between the formal model and
+the distributional model, are not statistically significant, as each
+method has certain kinds of queries that it performs well on.  Only
+the combined model is able to consistently outperform the
+distributional model on all kinds of queries.
 
@@
 example of this problem is the ``linebacker'' example above, where the
-features for \predicate{linebacker\_N/N} can capture which athletes
+features for \lexicalpredicate{linebacker\_N/N} can capture which athletes
 play for which teams, but not the \emph{positions} of those
@@
 multi-word noun modifiers, e.g., ``Vice president Al Gore'' is mapped
-to $\predicate{vice}(\entity{Al Gore}) \land
-\predicate{president}(\entity{Al Gore})$. Another problem is that
+to $\lexicalpredicate{vice}(\entity{Al Gore}) \land
+\lexicalpredicate{president}(\entity{Al Gore})$. Another problem is that
 there is no backoff with multi-word relations. For example, the
-predicate \predicate{head\_honcho\_N/N} was never seen in the training
-data, so it is replaced with \predicate{unknown}; however, it would be
-better to replace it with \predicate{honcho\_N/N}, which \emph{was}
+predicate \lexicalpredicate{head\_honcho\_N/N} was never seen in the training
+data, so it is replaced with \lexicalpredicate{unknown}; however, it would be
+better to replace it with \lexicalpredicate{honcho\_N/N}, which \emph{was}
 seen in the training data. Finally, although using connected entities
@@
 
-% The ``head honcho'' example is particularly instructive---this is a
-% phrase that essentially means ``leader'', and the features learned by
-% the formal model get some essential hints from Freebase, even though
-% there is no direct correlate.  The features capture the fact that
-% entities that are ``honchos'' are people, and that they tend to be
-% CEOs and film producers.
-% 
-% When a predicate has a clear Freebase correlate (such a
-% \predicate{prime\_minister\_N/N}, \predicate{president\_of},
-% \predicate{newspaper}, \predicate{company}, etc.), our formal model is able to
-% capture the meaning very well.  The   The distributional model does much less well here, and in
-% combination, the distributional component of the model occasionally lowers its
-% performance relative to the formal model.\footnote{This is why the difference
-% between the formal model and the combined model is not statistically
-% significant.}
-% 
-% The formal models also perform well on predicates that can be partially
-% expressed by Freebase, such as , though
-% the models do not have the nearly-perfect AP that they do for the more crisp
-% queries above.  
-% 
-% For ``Patriots linebacker \blank{}'', the reason that this can only be
-% partially expressed in terms of Freebase queries is that the features for
-% \predicate{linebacker\_N/N} are able to capture which athletes play for which
-% teams, but they cannot distinguish well between what positions those athletes
-% play.  This leads to Patriots quarterbacks, wide receivers, and running backs
-% being scored highly for this query.  This issue could be fixed by using more
-% complex features for relation predicates, instead of just edge sequences,
-% though that would drammatically increase the size of the feature space and make
-% the feature selection process much more difficult.  It could also potentially
-% be mitigated by better negative example selection during training.
-% 
-% There are also cases where a predicate has so many possible entity types in
-% Freebase (or no close correlate at all) that the PMI feature selection process
-% does not find features that are useful for all queries.  A good example of this
-% is ``\blank{} is a NASA mission''; in this case, the distributional model
-% outperforms the formal model, because it has learned associations between
-% particular NASA missions and NASA.
-% 
-% While the new logical forms we introduced in \secref{better-lfs} improved the
-% performance of the models, there is still a lot of room for further
-% improvement.  For instance, ``Vice president Al Gore'' is modeled as
-% $\predicate{vice}(\entity{Al Gore}) \land \predicate{president}(\entity{Al
-% Gore})$.  Better processing of multi-word expressions would allow for more
-% crisp models of the predicates, so the model for \predicate{president} could
-% have more specific features.  Also, the predicate \predicate{head\_honcho\_N/N}
-% was never seen in the training data, so an \predicate{unknown} predicate was
-% used to score the relation in the phrase ``Microsoft head honcho \blank{}''.
-% This means the model had to rely solely on knowing which entities are
-% ``honchos'' and which entities are related to Microsoft in some unknown manner.
-% The predicate \predicate{honcho\_N/N} \emph{is} seen in the training data,
-% however; some kind of backoff to simpler phrases for unseen predicates would be
-% useful here.
+\section{Related work}
 
-% Finally, using connected entities in Freebase as additional candidates during
-% inference is helpful, but it is not very sophisticated.  It over-generates for
-% a lot of entities and predicates, and under-generates for others.  A mechanism
-% for tailoring a search over Freebase to a particular query would be useful,
-% though it would add a lot of additional complexity, possibly requiring methods
-% from reinforcement learning to resolve.
+There is a large body of other work that is closely related to what is
+presented in this paper.  Two recent papers that also attempt to
+include some form of structured knowledge into distributional
+representations are those by Faruqui et
+al.~\shortcite{faruqui-2015-retrofitting-word-vectors}, and by
+Rockt\"{a}schel et
+al.~\shortcite{rocktaschel-2015-logical-embeddings}.  A key difference
+between their approaches and ours is that they use the structured
+information only to modify distributional representations, while we
+include the structured information directly in our models, training
+weights for structured information jointly with distributional
+representations.  Also conceptually similar is the Additive Relational
+Effects model for knowledge base completion by Nickel et
+al.~\shortcite{nickel-2014-are}, which tries to factorize the residual
+of a KB tensor that cannot be explained by observable features that
+are somewhat similar to the formal features we use in this model.  But
+while this model is conceptually similar, it is computationally quite
+different, and would be rather difficult to use in the setting we
+explore in this work.
+
+Our work draws a lot of inspiration from recent work on knowledge base
+completion.  We are building on top of work in embedding the entities
+and relations in a knowledge
+base~\cite{riedel-2013-mf-universal-schema,nickel-2011-rescal,bordes-2013-transe},
+as well as work on graph-based methods for reasoning with knowledge
+bases~\cite{lao-2010-original-pra,gardner-2014-vector-space-pra,neelakantan-2015-rnn-kbc}.
+
+Lastly, there is an extensive literature on building semantic parsers
+to answer questions against a structured knowledge
+base~\cite{zettlemoyer-2005-ccg,berant-2013-semantic-parsing-qa,%
+kwiatkowski-2013-ontology-matching,krishnamurthy-2012-semantic-parsing}.
+The vast majority of this work is focused on matching natural language
+text to statements in a specific ontology, with no hope of assigning
+meaning to language that falls outside of that ontology.  Only very
+recently has there been work attempting to learn broad coverage
+meaning representations in semantic parsers.  In addition to the work
+by Krishnamurthy and Mitchell which we extend in this paper, there was
+recently a nice piece of work by Choi et
+al.~\shortcite{choi-2015-semantic-parsing-partial-ontologies}.  The
+aim of their work is, like typical semantic parsers, to map text onto
+a single formal statement, but they allow some of the predicates to be
+``open'' predicates not contained in the Freebase ontology.  A key
+difference between their work and ours is that we score surface
+logical forms directly, using a weighted combination of many Freebase
+queries, instead of trying to map them to a single Freebase logical
+form.  Additionally, while their system might learn that
+``front-runner'' should be modeled as an open predicate that has no
+representation in Freebase, they have no method to assign any further
+meaning to that predicate, while our models learn both distributional
+and formal information about the meaning of ``front-runner''.
 
@@
 fill-in-the-blank natural language queries. This combined model
-achieved a relative gain of 62\% in mean average precision over the
-distributional model alone. We also introduced a better mapping from
-surface text to logical forms, and a simple method for using Freebase
-to find candidate entities during inference.  Taken together, the
-methods introduced in this paper improved mean average precision on a
-fill-in-the-blank natural language query task from .163 to .370, a
-127\% relative improvement.
-
-% There are many directions for future work in this model. One is to
-% address some of the model limitations previously discussed to improve
-% performance. Specifically, feature generation, feature selection and
-% candidate entity generation could be better tailored to each
-% predicate. This problem is challenging because it requires expanding
-% an already very expressive class of features ...  (TODO: reinforcement
-% learning?) Although the features we consider are already more
-% expressive than would be considered by a typical semantic parser, it
-% seems necessary to include even more complex Freebase queries. Another
-% direction (TODO:.... )
+achieved relative gains of over 50\% in mean average precision and
+mean reciprocal rank versus prior work.  We also introduced a better
+mapping from surface text to logical forms, and a simple method for
+using Freebase to find candidate entities during inference.  Taken
+together, the methods introduced in this paper improved mean average
+precision on our task from .163 to .370, a 127\% relative improvement.
 
@@
 knowledge base's predicate instances, but is fundamentally limited by
-the its schema. In contrast, our approach maps language to a
+its schema. In contrast, our approach maps language to a
 \emph{weighted combination of queries} plus a distributional
@@
 when the meaning of the language cannot be exactly represented by a
-knowledge base predicate, a common occurrence. We believe that this
-kind of approach could significantly expand the applicability of
-semantic parsing techniques to more complex domains where the
-assumptions of traditional techniques are limiting.
-
-TODO: We could say more about what we learned. A big message is that
-we should use the KB as \emph{features}.
+knowledge base predicate, which is a common occurrence. We believe
+that this kind of approach could significantly expand the
+applicability of semantic parsing techniques to more complex domains
+where the assumptions of traditional techniques are too limiting.
 

### 2016-03-18 papers/acl2016/paper.tex
working on method
Former-commit-id: 76c883465605e8ee391de66afe27541fff462669

--- 2016-03-17 papers/acl2016/paper.tex
@@
   \textless\predicate{designed}, \predicate{located\_in}\textgreater
+
+  \textbf{Features for \entity{Palladio}}:\\
+  \textless\predicate{nationality}\textgreater\\
+  \textless\predicate{nationality}\textgreater:\entity{Italy}\\
+  \textless\predicate{type}\textgreater:\entity{Architect}\\
+  \textless\predicate{designed}, \predicate{located\_in}\textgreater \\
+  \textless\predicate{designed}, \predicate{located\_in}\textgreater:\entity{Italy}
+
   \caption{A subset of the Freebase graph, and some example extracted features
@@
 
-In this section we present our models of predicate semantics.  In
-\secref{formal-and-distributional} we describe how we modify Krishnamurthy and
-Mitchell's (K\&M's) semantic parser to include features from a formal knowledge
-base.  In \secref{computing-pmi} we describe how we select those features for
-each predicate.  The remaining two sections then describe other improvements we
-made to K\&M's semantic parsing model: lexicalizing preposition and
-noun-compound predicates, and using the Freebase graph to select candidate
-entities.
+This section presents our approach to open vocabulary semantic
+parsing. Our approach follows the same structure as described in
+Section \ref{sec:jayant-semparse}: we generate a surface logical form
+from a query, then evaluate it against a probabilistic database with
+learned predicate instance probabilities.  Section
+\ref{sec:better-lfs} describes logical form generation, which improves
+on prior work by lexicalizing additional predicates. Section
 
-\subsection{Formal features for predicate semantics}
+However, we improve both
+logical form generation and the predicate models.
+
+In
+\secref{formal-and-distributional} we describe how we modify
+Krishnamurthy and Mitchell's (K\&M's) semantic parser to include
+features from a formal knowledge base.  In \secref{computing-pmi} we
+describe how we select those features for each predicate.  The
+remaining two sections then describe other improvements we made to
+K\&M's semantic parsing model: lexicalizing preposition and
+noun-compound predicates, and using the Freebase graph to select
+candidate entities.
+
+\subsection{Overview}
 \label{sec:formal-and-distributional}
 
-We inject information from a formal knowledge base into our models of predicate
-semantics simply by augmenting the learned distributional feature vectors with
-formal features.
+% TODO: ``query'' features?
 
-For each entity and entity pair in the data we compute an SFE feature vector
-$\psi(e)$ and $\psi(e_1, e_2)$.  For entity pairs, the vector $\psi(e_1, e_2)$
-is a sparse binary vector containing indicator features for all edge sequences
-that connect nodes $e_1$ and $e_2$ in the Freebase graph, up to length 4.
-These features are shown for the entity pair (\entity{Palladio},
-\entity{Italy}) in the example graph in \figref{sfe}.  For entities, we extract
-similar features to form the sparse binary vector $\psi(e)$.  These features
-are of two types: (1) edge sequences that begin at node $e$ (up to length two),
-and (2) edge sequences that begin at node $e$ along with the node at the end of
-the sequence.  For example, all of the features listed in \figref{sfe} for the
-entity pair (\entity{Palladio}, \entity{Italy}) are also valid features of type
-(1) for the entity \entity{Palladio}, as well as the features
-\textless\predicate{type}\textgreater and
-\textless\predicate{designed}\textgreater.  Examples of of type (2) features
-are \textless\predicate{type}\textgreater:\entity{architect}, and
-\textless\predicate{nationality}\textgreater:\entity{Italy}.  Intuitively,
-features of type (1) capture the fact that an entity participates in particular
-kinds of relations, such as designing architectural structures, while features
-of type (2) capture the way an entity is related to particular other entities.
-Features of type (2) are very specific, and are most useful in practice when
-the entity in the feature is a type node, such as with
-\textless\predicate{type}\textgreater:\entity{architect}, though occasionally
-features of this type involving other entities are also selected in our feature
-selection process.
-
-For each category and relation, we select a subset of the SFE features in the
-vectors $\psi$ to have associated weights $\omega_c$ and $\omega_r$.  We then
-add the weights $\omega_c$ and $\omega_r$ as parameters to be learned for each
-predicate, and we add the feature vectors $\psi(e)$ and $\psi(e_1, e_2)$ as
-observed features for each entity and entity pair.  The augmented category and
-relation probabilities are as follows:
+We inject information from a knowledge base into our predicate models
+by augmenting the learned embeddings with features. The truth
+probability of a category instance $c(e)$ or relation instance $r(e_1,
+e_2)$ in our model is given by:
 
@@
 \end{align*}
-where we have added subscripts on the $\psi$ functions to indicate that each
-predicate selects its own set of features from the SFE feature vector $\psi$.
 
-We pause here to note that these features obtained from SFE correspond exactly
-to a limited set of horn clauses using the Freebase vocabulary, which in turn
-can be seen as Freebase queries that define sets of entities or entity pairs.
-By associating a number of these features with each predicate and assigning
-them weights, what we are effectively doing is mapping language onto a weighted
-combination of possible Freebase statements, instead of onto a single Freebase
-query, as is typically done in the semantic parsing literature.  This is a
-fundamentally new kind of predicate semantics that has not been used previously
-in semantic parsers.
+In the above equation, the $\theta$ and $\phi$ terms are learned
+predicate and entity embeddings, as described in Section
+\ref{sec:jayant-semparse}. The second term in the sum represents our
+new features and their learned weights. $\psi_c(e)$ and $\psi_r(e_1,
+e_2)$ are SFE feature vectors for each entity and entity pair; a
+different set of features is chosen for each predicate in order to
+maximize their usefulness. The terms $\omega_c$ and $\omega_r$
+represent learned weights for these features.
 
-Note also that in our combined model there are now three sets of parameters to
-be learned by the semantic parser: (1) $\theta$, low-dimensional distributional
-vectors trained for each predicate; (2) $\phi$, low-dimensional distributional
-vectors trained for each entity and entity pair; and (3) $\omega$, weights
-associated with the selected formal SFE features for each predicate.  All of
-these parameters are optimized jointly, using the same ranking objective used
-by K\&M.
+Each SFE feature can be viewed as either a Freebase query or a horn
+clause implication rule using the Freebase schema. In both cases, the
+feature defines a set of entities (or entity pairs), and the
+associated feature weight measures the likelihood that an entity in
+this set is also in the denotation of the surface predicate. Our
+models include \emph{many} such features for each surface predicate,
+effectively mapping each surface predicate onto a \emph{weighted
+  combination of Freebase queries}. This approach is fundamentally
+different from typical semantic parsers that map language to a single
+Freebase query.
 
-\subsection{Finding relevant features for each predicate}
-\label{sec:computing-pmi}
+In our model, there are now three sets of parameters to be learned:
+(1) $\theta$, low-dimensional distributional vectors trained for each
+predicate; (2) $\phi$, low-dimensional distributional vectors trained
+for each entity and entity pair; and (3) $\omega$, weights associated
+with the selected formal SFE features for each predicate.  All of
+these parameters are optimized jointly, using the same ranking
+objective used by K\&M (TODO: not sure how to eliminate this backref).
 
-The feature vectors returned by SFE have dimensionality in the tens of
-millions.  We do not have near enough data to train that many parameters for
-each of our tens of thousands of predicates, nor do we have enough RAM in our
-machines to keep that many parameters in memory.  It is thus necessary to
-select some small number of informative features for each predicate.  We do
-this using pointwise mutual information (PMI).
+% For each category and relation, we select a subset of the SFE features in the
+% vectors $\psi$ to have associated weights $\omega_c$ and $\omega_r$.  We then
+% add the weights $\omega_c$ and $\omega_r$ as parameters to be learned for each
+% predicate, and we add the feature vectors $\psi(e)$ and $\psi(e_1, e_2)$ as
+% observed features for each entity and entity pair.  The augmented category and
+% relation probabilities are as follows:
 
-PMI measures the strength of association between two variables $x$ and $y$; it
-is computed as $\log\frac{p(x,y)}{p(x)p(y)}$.  In our case, we want to
-associate predicates with SFE features.  However, our SFE features are for each
-\emph{entity} and \emph{entity pair}, not each \emph{predicate}.  To associate
-SFE features with predicates, we use the training data to find a mapping from
-entities and entity pairs to predicates that they have been seen with in the
-data.  For example, the phrase ``Italian architect Andrea Palladio'' is
-considered a positive training example for the instantiated predicates
+\subsection{Generating predicate features}
+
+The feature vectors $\psi_c(e)$ and $\psi_r(e_1, e_2)$ are constructed
+using a two-stage process. First, we generate a predicate-independent
+feature vector $\psi(e)$ for each entity $e$ and $\psi(e_1, e_2)$ for
+each entity pair $(e_1, e_2)$ using SFE. This step generates very
+high-dimensional feature vectors, where most of the
+features are not relevant for any given predicate. Next, we perform
+per-predicate feature selection to identify a subset of these features
+that are relevant for each category and relation predicate.
+
+The predicate-independent feature extraction stage computes the
+following feature vectors. For entity pairs, the vector $\psi(e_1,
+e_2)$ is a sparse binary vector containing indicator features for all
+edge sequences that connect nodes $e_1$ and $e_2$ in the Freebase
+graph, up to length 4.  For an entity $e$, we extract two kinds of
+features: (1) all edge sequences up to length two that begin at $e$,
+and (2) the same sequences paired with the entity at their
+endpoint. Features of type (1) capture the kinds of relations that an
+entity participates in, e.g., designing architectural structures,
+while features of type (2) capture relations to other particular
+entities. This second kind of feature is most helpful when the
+endpoint entity is a type, such as \entity{architect}, although there
+are some other valuable features of this kind. \figref{sfe} shows some
+example entity and entity pair features extracted from a subset of the
+Freebase graph.
+
+% For each category and relation, we select a subset of the SFE features in the
+% vectors $\psi$ to have associated weights $\omega_c$ and $\omega_r$.  We then
+% add the weights $\omega_c$ and $\omega_r$ as parameters to be learned for each
+% predicate, and we add the feature vectors $\psi(e)$ and $\psi(e_1, e_2)$ as
+% observed features for each entity and entity pair.  The augmented category and
+% relation probabilities are as follows:
+% 
+% \begin{align*}
+%   P(c(e)) &= \sigma ( \theta_c^T \phi_e + \omega_c^T \psi_c(e)) \\
+%   P(r(e_1, e_2)) &= \sigma ( \theta_r^T \phi_{(e_1, e_2)} + \omega_r^T \psi_r(e_1, e_2) )
+% \end{align*}
+% where we have added subscripts on the $\psi$ functions to indicate that each
+% predicate selects its own set of features from the SFE feature vector $\psi$.
+
+% The feature vectors returned by SFE have dimensionality in the tens of
+% millions.  We do not have near enough data to train that many parameters for
+% each of our tens of thousands of predicates, nor do we have enough RAM in our
+% machines to keep that many parameters in memory.  It is thus necessary to
+% select some small number of informative features for each predicate.  We do
+% this using pointwise mutual information (PMI).
+
+The feature selection step uses pointwise mutual information (PMI) to
+reduce the number of features considered by the model for each
+predicate. The feature vectors generated above have tens of millions
+of dimensions, but, for any given surface predicate, only a handful of
+these dimensions represent relevant Freebase queries. We select
+features by first summing the entity and entity pair feature vectors
+seen with each predicate in the training data. For example, the phrase
+``Italian architect Andrea Palladio'' is considered a positive
+training example for the instantiated predicates
 $\predicate{architect}(\entity{Andrea Palladio})$ and
-$\predicate{architect\_N/N}(\entity{Italy}, \entity{Andrea Palladio})$.  We
-then associate the feature vectors for \entity{Andrea Palladio} and
-(\entity{Italy}, \entity{Andrea Palladio}) with the predicates
-\predicate{architect} and \predicate{architect\_N/N}, respectively.  For each
-predicate $\pi$ and feature $f$, we use these counts to calculate the
-probabilities $p(\pi, f)$, $p(\pi)$ and $p(f)$.  After removing features with
-counts below some threshold, we pick the $k$ features with the highest PMI
-values for each predicate to use in our model.\footnote{We used $k=100$ in this
-paper.}
+$\predicate{architect\_N/N}(\entity{Italy}, \entity{Andrea
+  Palladio})$. We then add the feature vectors for \entity{Andrea
+  Palladio} and (\entity{Italy}, \entity{Andrea Palladio}) to the
+feature counts for the predicates \predicate{architect} and
+\predicate{architect\_N/N}, respectively. Next, for each predicate
+$\pi$ and feature $f$, we use these counts to calculate three
+probabilities: $p(\pi, f)$, $p(\pi)$ and $p(f)$. (TODO: how did you
+calculate these?). The PMI of a predicate/feature pair is then $\log
+\frac{p(\pi, f)}{p(\pi)p(f)}$. After removing features with counts
+below a threshold, we pick the $k=100$ features with the highest PMI
+values for each predicate to use in our model.
+
+% PMI measures the strength of association between two variables $x$ and $y$; it
+% is computed as $\log\frac{p(x,y)}{p(x)p(y)}$.  In our case, we want to
+% associate predicates with SFE features.  However, our SFE features are for each
+% \emph{entity} and \emph{entity pair}, not each \emph{predicate}.  To associate
+% SFE features with predicates, we  For each
+% predicate $\pi$ and feature $f$, we use these counts to calculate the
+% probabilities $p(\pi, f)$, $p(\pi)$ and $p(f)$.
 

### 2016-03-18 papers/acl2016/paper.tex
Getting close...
Former-commit-id: c27e7319ef51ed8cff9c6d7725164f8ac171482d

--- 2016-03-18 papers/acl2016/paper.tex
@@
 
-\title{Combining Formal and Distributional Models of Predicate Semantics}
+\title{Open-Vocabulary Semantic Parsing\\with both Distributional
+Statistics and Formal Knowledge}
 
@@
 
-  We consider the problem of learning models of predicate (category and
-  relation) semantics using both distributional information and structured
-  information contained in a formal knowledge base.  Most previous approaches
-  to modeling predicate semantics have either been purely distributional (such
-  as word2vec and knowledge base embedding methods) or purely formal (such as
-  most semantic parsers).  Distributional approaches have very broad coverage,
-  but lack the compositional, logical semantics used by semantic parsers, and
-  it has so far been difficult to combine the benefits of both of these
-  techniques.
-
-  In this paper, we present a method that incorporates logical statements
-  derived from a knowledge base into distributional models of categories and
-  relations.  Instead of mapping a phrase to a single logical statement, as
-  done by semantic parsers, our method uses logical statements as features
-  added to distributional models of words, allowing the model to learn that
-  Freebase entities that are "honchos" are people, not buildings, and that they
-  are frequently CEOs or film producers.  We use these models in an
-  open-vocabulary semantic parsing task, showing a 62\% relative improvement in
-  mean average precision over a distributional-only model.
+  We consider the problem of mapping language onto meaning
+  representations that are executable, returning truth values for
+  complete statements and distributions over entities for queries.
+  The typical approach to solve this problem is semantic parsing;
+  however, this approach fails when the language cannot be represented
+  by a single query over the Freebase schema.  Instead, our approach
+  represents language as a \emph{weighted combination} of queries over
+  the formal schema, along with a distributional component similar to
+  a word embedding.  This technique combines the advantages of
+  traditional semantic parsing (compositionality and the ability to
+  leverage a structured knowledge base) with the broad coverage
+  obtained by distributional methods.  We present relative gains of
+  over 120\% in mean average precision versus prior work on an
+  open-vocabulary fill-in-the-blank question answering task.
 
@@
 of each word from a large unlabeled text corpus. These models have
-broad coverage but a shallow semantics centered around word
-similarity. On the other hand, semantic parsing translates natural
-language into logical queries against a formal knowledge base, such as
-Freebase. This approach produces a rich compositional semantics and
-furthermore can leverage structured information from the knowledge
-base, e.g., to answer natural language questions. However, semantic
-parsers have limited coverage as they can only represent the meanings
-of words that can be mapped to knowledge base predicates. A critical
-question is \emph{how do we obtain the benefits of both approaches?}
+broad coverage, but they also have a shallow semantics centered around
+word similarity. On the other hand, semantic parsing translates
+natural language into logical queries against a formal knowledge base,
+such as Freebase. This approach produces a rich compositional
+semantics and furthermore can leverage structured information from the
+knowledge base. However, semantic parsers have limited coverage as
+they can only represent the meanings of words that can be mapped to
+knowledge base predicates. A critical question is \emph{how do we
+obtain the benefits of both of these approaches?}
 
@@
   \small
-  \begin{minipage}{0.28\linewidth}
+  \begin{minipage}{0.18\linewidth}
     \textbf{Input Text}\\Italian architect \blank{}
@@
 %
-  ~~ $\rightarrow$ ~~~~~~
+  ~~ $\longrightarrow$ ~~~~~~
 %
@@
 leverage both structured information from Freebase and distributional
-information. Our key observation is that, while there is no Freebase
-predicate that corresponds exactly to the meaning of ``honcho,''
-Freebase \emph{does} contain predicates that \emph{partially}
-represent its meaning. For example, an entity that can be called
-``honcho'' is likely to have type \formalpredicate{person}. We therefore
-incorporate \emph{features} based on Freebase paths into the predicate
-models of K\&M and learn per-predicate weights for these features
-using distributional information (\figref{overview}). This approach
+information from a corpus. Our key observation is that, while there is
+no Freebase predicate that corresponds exactly to the meaning of
+``honcho,'' Freebase \emph{does} contain predicates that
+\emph{partially} represent its meaning. For example, an entity that
+can be called ``honcho'' is likely to have type
+\formalpredicate{person}. We therefore incorporate \emph{features}
+based on Freebase paths into the predicate models of Krishnamurthy and
+Mitchell and learn per-predicate weights for these features using
+distributional information (\figref{overview}). This approach
 effectively learns the meaning of a word as a distributional vector
 plus a \emph{weighted combination of Freebase queries}, a considerably
-more expressive representation than either existing semantic parsers
-or K\&M.
+more expressive representation than either traditional semantic parsers
+or the work by Krishnamurthy and Mitchell.
 
 We demonstrate our approach on the task of answering fill-in-the-blank
-natural language queries, finding that our approach provides a 62\%
-relative improvement in mean average precision over K\&M. (TODO: other
-empirical findings? It would be nice to talk about what features get
-learned for what words, etc.)
+natural language queries.  We first present two simple improvements to
+the distributional models of Krishnamurthy and Mitchell (an improved
+surface logical form representation, and better candidate generation
+during inference), improving the performance of that system by over
+40\%.  We then show that our approach improves mean average precision
+by 62\% over this improved baseline.  Taken together, the methods
+presented in this paper give a relative gain over prior work of more
+than 120\%.
 
@@
 well as features derived from a knowledge base using a technique
-called subgraph feature extraction~\cite[SFE]{gardner-2015-sfe}.
-Accordingly, in this section we briefly describe both of these
-techniques.
+called subgraph feature extraction~\cite{gardner-2015-sfe}.  We
+briefly describe both of these techniques.
 
@@
 introduced a technique for learning semantic parsers with open
-predicate vocabularies (hereafter referred to as K\&M). Instead of
-mapping text directly to Freebase queries, this method parses text to
-a surface logical form whose predicates are derived directly from the
-words in the text. Next, a distribution over denotations for each
-predicate is learned using a matrix factorization approach similar to
-that of Riedel et
+predicate vocabularies. Instead of mapping text directly to Freebase
+queries, this method parses text to a surface logical form whose
+predicates are derived directly from the words in the text (an example
+of these logical forms is shown in \figref{overview}). Next, a
+distribution over denotations for each predicate is learned using a
+matrix factorization approach similar to that of Riedel et
 al.~\shortcite{riedel-2013-mf-universal-schema}. This distribution is
@@
 embedding $\theta$, and each entity or entity pair has a learned
-embedding $\phi$. The probability assigned to a category instance
-$c(e)$ or relation instance $r(e_1, e_2)$ is given by:
+$k$-dimensional embedding $\phi$. The probability assigned to a
+category instance $c(e)$ or relation instance $r(e_1, e_2)$ is given
+by:
 
@@
 
-This paper extends K\&M by modifying the models of predicate semantics
-as described in \secref{method}. K\&M introduced several variations of
-their parser; in this work, we use their query ranking objective, as
-it had the best performance, and we compare against the model they
-called ``Factorization,'' without ensembling it with a corpus lookup
-baseline.
+In this paper, we use the open-vocabulary semantic parsing framework
+outlined in this section.  However, where Krishnamurthy and Mitchell
+used only distributional methods to compute $P(c(e))$ and $P(r(e_1,
+e_2))$, we augment these models with features derived from a formal
+knowledge base, as described in \secref{method}.
 
@@
   \textless\formalpredicate{nationality}\textgreater\\
-  \textless\formalpredicate{designed}, \formalpredicate{located\_in}\textgreater
-  \caption{A subset of the Freebase graph, and some example extracted features
-  between \entity{Palladio} and \entity{Italy}.  The actual Freebase relations
-  and entity identifiers used are modified here to aid readability.}
+  \textless\formalpredicate{designed}$\rightarrow$\formalpredicate{located\_in}\textgreater
+  \caption{A subset of the Freebase graph, and some example extracted
+  features between \entity{Palladio} and \entity{Italy}.  The actual
+  Freebase relations and entity identifiers used are modified here to
+  aid readability.}
   \label{fig:sfe}
@@
 
-Subgraph feature extraction (SFE) is a technique introduced by Gardner and
-Mitchell~\shortcite{gardner-2015-sfe} for generating feature matrices over node
-pairs in a graph with labeled edges.  Given a pair of nodes in a graph, SFE
-performs a search to characterize a subgraph around those two nodes, then
-extracts various kinds of features from that subgraph, such as the set of edge
-sequences that connect the two nodes.  \figref{sfe} shows an example subgraph,
-centered around \entity{Andrea Pallado} and \entity{Italy}, and features that
-would be extracted for that entity pair.  Gardner and Mitchell used these
-features to perform link prediction in the graph, using characteristics of the
-subgraph around two nodes to determine if an edge of a particular type should
-exist between those nodes.\footnote{When the graph corresponds to a knowledge
-base like Freebase, this task is also known as knowledge base completion.}
-Gardner and Mitchell only used these features to model formal KB relations,
-however.
+Subgraph feature extraction (SFE) is a technique introduced by Gardner
+and Mitchell~\shortcite{gardner-2015-sfe} for generating feature
+matrices over node pairs in a graph with labeled edges.  Given a pair
+of nodes in a graph, SFE performs a search to characterize and extract
+features from a subgraph around those two nodes.  Example features
+include the set of edge sequences that connect the two nodes.
+\figref{sfe} shows an example subgraph for the pair \entity{Andrea
+Pallado} and \entity{Italy}, and features that would be extracted for
+that entity pair.  Gardner and Mitchell used these features to perform
+link prediction in the graph, using characteristics of the subgraph
+around two nodes to determine if an edge of a particular type should
+exist between those nodes.\footnote{When the graph corresponds to a
+knowledge base like Freebase, this task is also known as knowledge
+base completion.}
 
-We differ from the work done by Gardner and Mitchell in two ways.  First, we
-apply these features to models of natural language, instead of formal KB
-relations.  There are some non-trivial problems that need to be solved in order
-to make this work, which will be discussed in \secref{method}.  Second, Gardner
-and Mitchell only considered generating feature matrices over node \emph{pairs}
-in a graph, with which one can model binary relations.  The natural language
-queries we wish to answer also involve unary predicates, or categories.  We
-thus extend SFE to also generate feature matrices over \emph{nodes} in a graph,
-an extension that is straightforward and is also discussed in more detail in
+We differ from the work done by Gardner and Mitchell in two ways.
+First, we apply these features to models of natural language, instead
+of to the link prediction task.  Second, Gardner and Mitchell only
+considered generating feature matrices over node \emph{pairs} in a
+graph, with which one can model binary relations.  The natural
+language queries we wish to answer also involve unary predicates.  We
+thus extend SFE to also generate feature matrices over \emph{nodes} in
+a graph, a straightforward extension that is described in
 \secref{method}.
@@
 phrase containing at least two Freebase entities, one of which is held
-out.  The system must propose Freebase entities to fill in the blank
-left by the held out entity, and the predicted entities are then
-judged manually for correctness.  We compare our proposed models,
-which combine distributional and formal elements, with a
-distributional-only baseline from prior work.  All of the data and
-code used in these experiments is available at [url withheld for
-review].
+out.  The system must propose a ranked list of Freebase entities to
+fill in the blank left by the held out entity, and the predicted
+entities are then judged manually for correctness.  We compare our
+proposed models, which combine distributional and formal elements,
+with a purely distributional baseline from prior work.  All of the
+data and code used in these experiments is available at [url withheld
+for review].
 
@@
 same fashion as done by Krishnamurthy and Mitchell.  This final test
-set contains 307 queries.  We report results on both of these test
-sets below.
+set contains 307 queries.  We report results on both of these sets
+below.
 
@@
 
-We compare three models in our experiments: (1) a distributional-only
-model (the prior work of Krishnamurthy and
+We compare three models in our experiments: (1) a distributional model
+(the prior work of Krishnamurthy and
 Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}); (2)
-a formal-only model (new to this work), where the distributional
-parameters $\theta$ and $\phi$ in \secref{formal-and-distributional}
-are fixed at zero; and (3) the combined model described in
+a formal model (new to this work), where the distributional parameters
+$\theta$ and $\phi$ in \secref{formal-and-distributional} are fixed at
+zero; and (3) the combined model described in
 \secref{formal-and-distributional} (also new to this work).  Except
@@
 \mathrm{Prec}(k) \times \mathrm{Correct}(k)$, where $\mathrm{Prec}(k)$
-is the recision at rank $k$, $\mathrm{Correct}(k)$ is an indicator
+is the precision at rank $k$, $\mathrm{Correct}(k)$ is an indicator
 function for whether the $k$th answer is correct, and $m$ is number of
-returned answers (up to 100, in this evaluation).  Reciprocal rank is
+returned answers (up to 100 in this evaluation).  Reciprocal rank is
 computed by first finding the rank $r$ of the first correct prediction
@@
       \midrule
-      Distributional-only & .269 & \textbf{.284} \\
+      Distributional model & .269 & \textbf{.284} \\
       \midrule
-      Formal-only & .231 & \textbf{.276} \\
+      Formal model & .231 & \textbf{.276} \\
       \midrule
@@
       With freebase entities & .\textbf{229} & \textbf{.275} & \textbf{.312} \\
-      \bottomrule
+      \midrule
+      \midrule
       Relative improvement & 40\% & 69\% & 8\% \\
@@
       Our combined model & \textbf{.335} & \textbf{.477} & \textbf{.429} \\
-      \bottomrule
+      \midrule
+      \midrule
       Relative improvement & 18\% & 29\% & 13\% \\
@@
 \tabref{dev-results} shows the results of our experiments on the
-development set (the same as the test set used by Krishnamurthy and
-Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}).  As
-can be seen, the combined model significantly improves performance,
-giving a relative gain in weighted MAP of 29\%.
+development set.  As can be seen, the combined model significantly
+improves performance over prior work, giving a relative gain in
+weighted MAP of 29\%.
 
@@
       Our combined model & \textbf{.370} & \textbf{.513} & \textbf{.469} \\
-      \bottomrule
+      \midrule
+      \midrule
       Relative improvement & 62\% & 87\% & 50\% \\
@@
 model and the distributional model is statistically significant (by a
-paired permutation test, $p < 0.05$).  The difference between the
+paired permutation test, $p < 0.05$).  The differences between the
 combined model and the formal model, and between the formal model and

### 2016-03-18 papers/acl2016/paper.tex

--- 2016-03-18 papers/acl2016/paper.tex
@@
   \textless\formalpredicate{designed}, \formalpredicate{located\_in}\textgreater
+
+  \textbf{Features for \entity{Palladio}}:\\
+  \textless\formalpredicate{nationality}\textgreater\\
+  \textless\formalpredicate{nationality}\textgreater:\entity{Italy}\\
+  \textless\formalpredicate{type}\textgreater:\entity{Architect}\\
+  \textless\formalpredicate{designed}, \formalpredicate{located\_in}\textgreater \\
+  \textless\formalpredicate{designed}, \formalpredicate{located\_in}\textgreater:\entity{Italy}
+
   \caption{A subset of the Freebase graph, and some example extracted features
@@
 
-In this section we present our models of predicate semantics.  In
-\secref{formal-and-distributional} we describe how we modify Krishnamurthy and
-Mitchell's (K\&M's) semantic parser to include features from a formal knowledge
-base.  In \secref{computing-pmi} we describe how we select those features for
-each predicate.  The remaining two sections then describe other improvements we
-made to K\&M's semantic parsing model: lexicalizing preposition and
-noun-compound predicates, and using the Freebase graph to select candidate
-entities.
+This section presents our approach to open vocabulary semantic
+parsing. Our approach follows the same structure as described in
+Section \ref{sec:jayant-semparse}: we generate a surface logical form
+from a query, then evaluate it against a probabilistic database with
+learned predicate instance probabilities. Section \ref{sec:better-lfs}
+describes our logical form generation, which improves the analyses of
+noun-mediated relations relative to prior work. Sections
+\ref{sec:formal-and-distributional} and \ref{sec:feature-generation}
+describe our improved predicate models and the corresponding feature
+generation process. Finally, Section \ref{sec:better-candidates}
+describes an improvement on candidate entity generation for question
+answering.
 
-\subsection{Formal features for predicate semantics}
+% In \secref{formal-and-distributional} we describe how we modify
+% Krishnamurthy and Mitchell's (K\&M's) semantic parser to include
+% features from a formal knowledge base.  In \secref{computing-pmi} we
+% describe how we select those features for each predicate.  The
+% remaining two sections then describe other improvements we made to
+% K\&M's semantic parsing model: lexicalizing preposition and
+% noun-compound predicates, and using the Freebase graph to select
+% candidate entities.
+
+\subsection{Logical form generation}
+\label{sec:better-lfs}
+
+As in K\&M, we generate logical forms from natural language statements
+by computing a syntactic CCG parse, then applying a collection of
+rules to produce logical forms. However, their logical form analyses
+do not model noun-mediated relations well. For example, given the
+phrase ``Italian architect Andrea Palladio,'' their system's logical
+form would include the relation
+$\lexicalpredicate{N/N}(\entity{Italy}, \entity{Andrea
+  Palladio})$. Here, the \lexicalpredicate{N/N} predicate represents a
+generic noun modifier relation; however, this relation is too vague
+for the predicate model to accurately learn its denotation. A similar
+problem occurs with prepositions and possessives, e.g., it is
+similarly hard to learn the denotation of the predicate
+\lexicalpredicate{of}.
+
+Our system improves the analysis of noun-mediated relations by simply
+including the noun in the predicate name. In the architect example
+above, our system produces the relation
+\lexicalpredicate{architect\_N/N}. It does this by simply
+concatenating all intervening noun modifiers between two entity
+mentions and including them in the predicate name; for example,
+``Illinois attorney general Lisa Madigan'' produces the predicate
+\lexicalpredicate{attorney\_general\_N/N}). (While it would be
+preferable to use actual dependency relations to determine which words
+to add to the predicate, this is not possible because our parser
+produces flat analyses of noun phrases where all noun modifiers depend
+directly on the head of the noun phrase.) We similarly improve the
+analyses of prepositions and possessives to include the head noun. For
+example, ``Barack Obama, president of the U.S.'' produces the
+predicate instance $\lexicalpredicate{president\_of}(\entity{Barack
+  Obama}, \entity{U.S.})$, and ``Rome, Italy's capital'' produces the
+predicate \lexicalpredicate{'s\_capital}. This process generates more
+specific predicates that we empirically found were easier for the
+predicate models to learn.
+
+% While we largely follow the semantic parsing framework introduced by K\&M, we
+% made one important change in how logical forms are generated.  For the running
+% example we have been using this paper, ``Italian architect Andrea Palladio'',
+% the relation predicate produced by K\&M's system is
+% $\lexicalpredicate{N/N}(\entity{Italy}, \entity{Andrea Palladio})$.
+% \lexicalpredicate{N/N}
+% does correctly capture the fact that \entity{Italy} is used syntactically as a
+% noun modifier of \entity{Andrea Palladio}, but it leaves out the additional
+% information contained in the syntax that ``architect'' was mediating that
+% noun-noun dependency.  This means that ``U.S. president Barack Obama'' and
+% ``Italian architect Andrea Palladio'' are both modeled using the same relation
+% predicate, which leads to a very generic and largely useless model for the
+% predicate \lexicalpredicate{N/N}.  By splitting \lexicalpredicate{N/N} into separate
+% predicates (\lexicalpredicate{architect\_N/N} and \lexicalpredicate{president\_N/N}), we give
+% the model the opportunity to learn more fine-grained relation semantics, and we
+% allow our feature selection pipeline to find much more useful features for
+% relation predicates.  While it would be ideal to use actual dependency
+% relations to determine which words to add to the predicate in complex noun
+% phrases, most current parsers treat these kinds of noun phrases as flat, with
+% all noun modifiers depending directly on the head of the noun phrase.  We
+% approximate this ideal by simply taking all words in between the two entities
+% in a noun phrase as the predicate (e.g., ``Illinois attorney general Lisa
+% Madigan'' would produce the predicate \lexicalpredicate{attorney\_general\_N/N}).
+
+% A similar issue arises with prepositions and possessives.  For a phrase such as
+% ``Barack Obama, president of the U.S.'', K\&M's system would produce the
+% following relation predicate: $\lexicalpredicate{of}(\entity{Barack Obama},
+% \entity{U.S.})$.  Because this same predicate (\lexicalpredicate{of}) is used for all
+% instances of this preposition, the predicate is forced to model too much and
+% becomes overly generic.  When there is a common noun mediating a prepositional
+% dependency between two entities, as in the phrase above, we add that noun to
+% the predicate, giving the instance $\lexicalpredicate{president\_of}(\entity{Barack
+% Obama}, \entity{U.S.})$.  We do the same for possessives in phrases such as
+% ``Rome, Italy's capital'', producing the predicate \lexicalpredicate{'s\_capital}.
+
+\subsection{Predicate models}
 \label{sec:formal-and-distributional}
 
-We inject information from a formal knowledge base into our models of predicate
-semantics simply by augmenting the learned distributional feature vectors with
-formal features.
+% TODO: ``query'' features?
 
-For each entity and entity pair in the data we compute an SFE feature vector
-$\psi(e)$ and $\psi(e_1, e_2)$.  For entity pairs, the vector $\psi(e_1, e_2)$
-is a sparse binary vector containing indicator features for all edge sequences
-that connect nodes $e_1$ and $e_2$ in the Freebase graph, up to length 4.
-These features are shown for the entity pair (\entity{Palladio},
-\entity{Italy}) in the example graph in \figref{sfe}.  For entities, we extract
-similar features to form the sparse binary vector $\psi(e)$.  These features
-are of two types: (1) edge sequences that begin at node $e$ (up to length two),
-and (2) edge sequences that begin at node $e$ along with the node at the end of
-the sequence.  For example, all of the features listed in \figref{sfe} for the
-entity pair (\entity{Palladio}, \entity{Italy}) are also valid features of type
-(1) for the entity \entity{Palladio}, as well as the features
-\textless\formalpredicate{type}\textgreater and
-\textless\formalpredicate{designed}\textgreater.  Examples of of type (2) features
-are \textless\formalpredicate{type}\textgreater:\entity{architect}, and
-\textless\formalpredicate{nationality}\textgreater:\entity{Italy}.  Intuitively,
-features of type (1) capture the fact that an entity participates in particular
-kinds of relations, such as designing architectural structures, while features
-of type (2) capture the way an entity is related to particular other entities.
-Features of type (2) are very specific, and are most useful in practice when
-the entity in the feature is a type node, such as with
-\textless\formalpredicate{type}\textgreater:\entity{architect}, though occasionally
-features of this type involving other entities are also selected in our feature
-selection process.
-
-For each category and relation, we select a subset of the SFE features in the
-vectors $\psi$ to have associated weights $\omega_c$ and $\omega_r$.  We then
-add the weights $\omega_c$ and $\omega_r$ as parameters to be learned for each
-predicate, and we add the feature vectors $\psi(e)$ and $\psi(e_1, e_2)$ as
-observed features for each entity and entity pair.  The augmented category and
-relation probabilities are as follows:
+We inject information from a knowledge base into our predicate models
+by augmenting the learned embeddings with features. The truth
+probability of a category instance $c(e)$ or relation instance $r(e_1,
+e_2)$ in our model is given by:
 
@@
 \end{align*}
-where we have added subscripts on the $\psi$ functions to indicate that each
-predicate selects its own set of features from the SFE feature vector $\psi$.
 
-We pause here to note that these features obtained from SFE correspond exactly
-to a limited set of horn clauses using the Freebase vocabulary, which in turn
-can be seen as Freebase queries that define sets of entities or entity pairs.
-By associating a number of these features with each predicate and assigning
-them weights, what we are effectively doing is mapping language onto a weighted
-combination of possible Freebase statements, instead of onto a single Freebase
-query, as is typically done in the semantic parsing literature.  This is a
-fundamentally new kind of predicate semantics that has not been used previously
-in semantic parsers.
+In the above equation, the $\theta$ and $\phi$ terms are learned
+predicate and entity embeddings, as described in Section
+\ref{sec:jayant-semparse}. The second term in the sum represents our
+new features and their learned weights. $\psi_c(e)$ and $\psi_r(e_1,
+e_2)$ are SFE feature vectors for each entity and entity pair; a
+different set of features is chosen for each predicate $c$ and $r$ in
+order to maximize their usefulness. The terms $\omega_c$ and
+$\omega_r$ represent learned weights for these features.
 
-Note also that in our combined model there are now three sets of parameters to
-be learned by the semantic parser: (1) $\theta$, low-dimensional distributional
-vectors trained for each predicate; (2) $\phi$, low-dimensional distributional
-vectors trained for each entity and entity pair; and (3) $\omega$, weights
-associated with the selected formal SFE features for each predicate.  All of
-these parameters are optimized jointly, using the same ranking objective used
-by K\&M.
+Each SFE feature can be viewed as either a Freebase query or a horn
+clause implication rule using the Freebase schema. In both cases, the
+feature defines a set of entities (or entity pairs), and the
+associated feature weight measures the likelihood that an entity in
+this set is also in the denotation of the surface predicate. Our
+models include \emph{many} such features for each surface predicate,
+effectively mapping each surface predicate onto a \emph{weighted
+  combination of Freebase queries}. This approach is fundamentally
+different from typical semantic parsers that map language to a single
+Freebase query.
 
-\subsection{Finding relevant features for each predicate}
-\label{sec:computing-pmi}
+In our model, there are now three sets of parameters to be learned:
+(1) $\theta$, low-dimensional distributional vectors trained for each
+predicate; (2) $\phi$, low-dimensional distributional vectors trained
+for each entity and entity pair; and (3) $\omega$, weights associated
+with the selected formal SFE features for each predicate.  All of
+these parameters are optimized jointly, using the same query ranking
+objective used by K\&M.
 
-The feature vectors returned by SFE have dimensionality in the tens of
-millions.  We do not have near enough data to train that many parameters for
-each of our tens of thousands of predicates, nor do we have enough RAM in our
-machines to keep that many parameters in memory.  It is thus necessary to
-select some small number of informative features for each predicate.  We do
-this using pointwise mutual information (PMI).
+% For each category and relation, we select a subset of the SFE features in the
+% vectors $\psi$ to have associated weights $\omega_c$ and $\omega_r$.  We then
+% add the weights $\omega_c$ and $\omega_r$ as parameters to be learned for each
+% predicate, and we add the feature vectors $\psi(e)$ and $\psi(e_1, e_2)$ as
+% observed features for each entity and entity pair.  The augmented category and
+% relation probabilities are as follows:
 
-PMI measures the strength of association between two variables $x$ and $y$; it
-is computed as $\log\frac{p(x,y)}{p(x)p(y)}$.  In our case, we want to
-associate predicates with SFE features.  However, our SFE features are for each
-\emph{entity} and \emph{entity pair}, not each \emph{predicate}.  To associate
-SFE features with predicates, we use the training data to find a mapping from
-entities and entity pairs to predicates that they have been seen with in the
-data.  For example, the phrase ``Italian architect Andrea Palladio'' is
-considered a positive training example for the instantiated predicates
-$\lexicalpredicate{architect}(\entity{Andrea Palladio})$ and
-$\lexicalpredicate{architect\_N/N}(\entity{Italy}, \entity{Andrea Palladio})$.  We
-then associate the feature vectors for \entity{Andrea Palladio} and
-(\entity{Italy}, \entity{Andrea Palladio}) with the predicates
-\lexicalpredicate{architect} and \lexicalpredicate{architect\_N/N}, respectively.  For each
-predicate $\pi$ and feature $f$, we use these counts to calculate the
-probabilities $p(\pi, f)$, $p(\pi)$ and $p(f)$.  After removing features with
-counts below some threshold, we pick the $k$ features with the highest PMI
-values for each predicate to use in our model.\footnote{We used $k=100$ in this
-paper.}
+\subsection{Generating predicate features}
+\label{sec:feature-generation}
 
-\subsection{Improved logical forms}
-\label{sec:better-lfs}
+The feature vectors $\psi_c(e)$ and $\psi_r(e_1, e_2)$ are constructed
+using a two-stage process. First, we generate a predicate-independent
+feature vector $\psi(e)$ for each entity $e$ and $\psi(e_1, e_2)$ for
+each entity pair $(e_1, e_2)$ using SFE. This step generates very
+high-dimensional feature vectors, where most of the
+features are not relevant for any given predicate. Next, we perform
+per-predicate feature selection to identify a subset of these features
+that are relevant for each category and relation predicate.
 
-While we largely follow the semantic parsing framework introduced by K\&M, we
-made one important change in how logical forms are generated.  For the running
-example we have been using this paper, ``Italian architect Andrea Palladio'',
-the relation predicate produced by K\&M's system is
-$\lexicalpredicate{N/N}(\entity{Italy}, \entity{Andrea Palladio})$.
-\lexicalpredicate{N/N}
-does correctly capture the fact that \entity{Italy} is used syntactically as a
-noun modifier of \entity{Andrea Palladio}, but it leaves out the additional
-information contained in the syntax that ``architect'' was mediating that
-noun-noun dependency.  This means that ``U.S. president Barack Obama'' and
-``Italian architect Andrea Palladio'' are both modeled using the same relation
-predicate, which leads to a very generic and largely useless model for the
-predicate \lexicalpredicate{N/N}.  By splitting \lexicalpredicate{N/N} into separate
-predicates (\lexicalpredicate{architect\_N/N} and \lexicalpredicate{president\_N/N}), we give
-the model the opportunity to learn more fine-grained relation semantics, and we
-allow our feature selection pipeline to find much more useful features for
-relation predicates.  While it would be ideal to use actual dependency
-relations to determine which words to add to the predicate in complex noun
-phrases, most current parsers treat these kinds of noun phrases as flat, with
-all noun modifiers depending directly on the head of the noun phrase.  We
-approximate this ideal by simply taking all words in between the two entities
-in a noun phrase as the predicate (e.g., ``Illinois attorney general Lisa
-Madigan'' would produce the predicate \lexicalpredicate{attorney\_general\_N/N}).
+The predicate-independent feature extraction stage computes the
+following feature vectors. For entity pairs, the vector $\psi(e_1,
+e_2)$ is a sparse binary vector containing indicator features for all
+edge sequences that connect nodes $e_1$ and $e_2$ in the Freebase
+graph, up to length 4.  For an entity $e$, we extract two kinds of
+features: (1) all edge sequences up to length two that begin at $e$,
+and (2) the same sequences paired with the entity at their
+endpoint. Features of type (1) capture the kinds of relations that an
+entity participates in, e.g., designing architectural structures,
+while features of type (2) capture relations to other particular
+entities. This second kind of feature is most helpful when the
+endpoint entity is a type, such as \entity{architect}, although there
+are some other valuable features of this kind. \figref{sfe} shows some
+example entity and entity pair features extracted from a subset of the
+Freebase graph.
 
-A similar issue arises with prepositions and possessives.  For a phrase such as
-``Barack Obama, president of the U.S.'', K\&M's system would produce the
-following relation predicate: $\lexicalpredicate{of}(\entity{Barack Obama},
-\entity{U.S.})$.  Because this same predicate (\lexicalpredicate{of}) is used for all
-instances of this preposition, the predicate is forced to model too much and
-becomes overly generic.  When there is a common noun mediating a prepositional
-dependency between two entities, as in the phrase above, we add that noun to
-the predicate, giving the instance $\lexicalpredicate{president\_of}(\entity{Barack
-Obama}, \entity{U.S.})$.  We do the same for possessives in phrases such as
-``Rome, Italy's capital'', producing the predicate \lexicalpredicate{'s\_capital}.
+% For each category and relation, we select a subset of the SFE features in the
+% vectors $\psi$ to have associated weights $\omega_c$ and $\omega_r$.  We then
+% add the weights $\omega_c$ and $\omega_r$ as parameters to be learned for each
+% predicate, and we add the feature vectors $\psi(e)$ and $\psi(e_1, e_2)$ as
+% observed features for each entity and entity pair.  The augmented category and
+% relation probabilities are as follows:
+% 
+% \begin{align*}
+%   P(c(e)) &= \sigma ( \theta_c^T \phi_e + \omega_c^T \psi_c(e)) \\
+%   P(r(e_1, e_2)) &= \sigma ( \theta_r^T \phi_{(e_1, e_2)} + \omega_r^T \psi_r(e_1, e_2) )
+% \end{align*}
+% where we have added subscripts on the $\psi$ functions to indicate that each
+% predicate selects its own set of features from the SFE feature vector $\psi$.
+
+% The feature vectors returned by SFE have dimensionality in the tens of
+% millions.  We do not have near enough data to train that many parameters for
+% each of our tens of thousands of predicates, nor do we have enough RAM in our
+% machines to keep that many parameters in memory.  It is thus necessary to
+% select some small number of informative features for each predicate.  We do
+% this using pointwise mutual information (PMI).
+
+The feature selection step uses pointwise mutual information (PMI) to
+reduce the number of features considered by the model for each
+predicate. The feature vectors generated above have tens of millions
+of dimensions, but, for any given surface predicate, only a handful of
+these dimensions represent relevant Freebase queries. We select
+features by first summing the entity and entity pair feature vectors
+seen with each predicate in the training data. For example, the phrase
+``Italian architect Andrea Palladio'' is considered a positive
+training example for the instantiated predicates
+$\formalpredicate{architect}(\entity{Andrea Palladio})$ and
+$\formalpredicate{architect\_N/N}(\entity{Italy}, \entity{Andrea
+  Palladio})$. We then add the feature vectors for \entity{Andrea
+  Palladio} and (\entity{Italy}, \entity{Andrea Palladio}) to the
+feature counts for the predicates \formalpredicate{architect} and
+\formalpredicate{architect\_N/N}, respectively. Next, for each predicate
+$\pi$ and feature $f$, we use these counts to calculate three
+probabilities: $p(\pi, f)$, $p(\pi)$ and $p(f)$. (TODO: how did you
+calculate these?). The PMI of a predicate/feature pair is then $\log
+\frac{p(\pi, f)}{p(\pi)p(f)}$. After removing features with counts
+below a threshold, we pick the $k=100$ features with the highest PMI
+values for each predicate to use in our model.
+
+% PMI measures the strength of association between two variables $x$ and $y$; it
+% is computed as $\log\frac{p(x,y)}{p(x)p(y)}$.  In our case, we want to
+% associate predicates with SFE features.  However, our SFE features are for each
+% \emph{entity} and \emph{entity pair}, not each \emph{predicate}.  To associate
+% SFE features with predicates, we  For each
+% predicate $\pi$ and feature $f$, we use these counts to calculate the
+% probabilities $p(\pi, f)$, $p(\pi)$ and $p(f)$.
 
@@
 
-One final way in which we improved K\&M's semantic parser is in how candidate
-entities are generated during inference.  Because the distributional-only
-predicate models used by K\&M's semantic parser need to learn a vector of
-parameters for each entity pair, they cannot give a non-zero score to any
-entity pair not seen during training time.  When given a query such as
-$\lambda(\entity{x}) \lexicalpredicate{architect\_N/N}(\entity{x}, \entity{Andrea
-Palladio})$, K\&M's system only needs to consider the set of entities
-$\entity{x}$ that have been seen at training time with \entity{Andrea
-Palladio}; all other entities will get a score of 0.
+A key benefit of our predicate models is that they are able to assign
+scores to entity pairs that were never seen in the training data. The
+purely-distributional model of K\&M has no basis for assigning these
+scores and therefore assumes $P(r(e_1,e_2)) = 0$ for unseen entity
+pairs $(e_1,e_2)$. This assumption limits the recall of their system
+when it is applied to question answering, as these entity pairs will
+not have been observed for many correct, but rare entity answers. In
+contrast, our predicate models can score any entity pair: the
+distributional component of an unseen pair will be zero, but the SFE
+component is always applicable. This benefit allows our model to
+considerably improve question answering performance on rare entities.
 
-Our predicate models do not have this limitation.  The distributional component
-will still give an unseen entity pair a score of 0, as it is identical to K\&M's
-model, but the formal component of our models simply computes an observed
-feature vector from Freebase for the entity pair.  As long as both entities
-appear in Freebase, our model can compute a feature vector and give a non-zero
-score.
+% One final way in which we improved K\&M's semantic parser is in how candidate
+% entities are generated during inference.  Because the distributional-only
+% predicate models used by K\&M's semantic parser need to learn a vector of
+% parameters for each entity pair, they cannot give a non-zero score to any
+% entity pair not seen during training time.  When given a query such as
+% $\lambda(x).\lexicalpredicate{architect\_N/N}(x, \entity{Andrea
+% Palladio})$, K\&M's system only needs to consider the set of entities
+% $\entity{x}$ that have been seen at training time with \entity{Andrea
+% Palladio}; all other entities will get a score of 0.
+% 
+% Our predicate models do not have this limitation.  The distributional component
+% will still give an unseen entity pair a score of 0, as it is identical to K\&M's
+% model, but the formal component of our models simply computes an observed
+% feature vector from Freebase for the entity pair.  As long as both entities
+% appear in Freebase, our model can compute a feature vector and give a non-zero
+% score.
 
-While this improvement allows us to handle queries over rare entities much
-better than a distributional-only model, it also complicates inference, as we
-cannot just score entity pairs seen at training time.  Optimizing every query's
-score over all of the millions of entities in Freebase is not computationally
-feasible.  To make inference tractable, for a given query we restrict
-candidates to all entities seen with the query entities during training (as
-done by K\&M), as well as all entities directly connected to the query entities
-in Freebase, or connected by a mediator node.\footnote{Mediators in Freebase are
-used to capture relations with more than two arguments, such as employment
-tenure, which has an employer, and employee, a start date, and an end date.}
+However, this benefit has an associated drawback: given a logical form
+query, it is computationally and statistically undesirable to consider
+\emph{all} Freebase entities as answers. Scoring millions of entities
+is slow, and furthermore makes it more difficult to identify correct
+answers (as their frequency in the candidate set
+decreases). Therefore, when answering a query, we compute a set of
+candidate entities and only score these candidates. Our candidate set
+consists of all entities seen with the query entities in the training
+set as well as all entities directly connected to the query entities
+in Freebase, or connected by a mediator node.\footnote{Mediators in
+  Freebase are used to capture relations with more than two arguments,
+  such as employment tenure, which has an employer, and employee, a
+  start date, and an end date.}
 
-For some entities, such as the United States, the set of connected entities can
-still be intractably large, so we limit this expansion to only those entities
-with fewer than 100 directly connected entities.  Our motivation for this is
-that this candidate entity generation is most useful for rarely seen entities,
-for which we have few or no related entities seen during training.  These
-entities also tend to have relatively few connected entities in Freebase.
+% While this improvement allows us to handle queries over rare entities much
+% better than a distributional-only model, it also complicates inference, as we
+% cannot just score entity pairs seen at training time.  Optimizing every query's
+% score over all of the millions of entities in Freebase is not computationally
+% feasible.  To make inference tractable, for a given query we restrict
+% candidates to all entities seen with the query entities during training (as
+% done by K\&M), as well as all entities directly connected to the query entities
+% in Freebase, or connected by a mediator node.\footnote{Mediators in Freebase are
+% used to capture relations with more than two arguments, such as employment
+% tenure, which has an employer, and employee, a start date, and an end date.}
+
+Unfortunately, for some entities, such as the United States, the set
+of connected entities can be intractably large; we therefore limit
+this expansion to only those entities with fewer than 100 directly
+connected entities.  Our motivation for this is that this candidate
+entity generation is most useful for rarely seen entities, for which
+we have few or no related entities seen during training.  These
+entities also tend to have relatively few connected entities in
+Freebase.
 

### 2016-03-18 papers/acl2016/paper.tex

--- 2016-03-18 papers/acl2016/paper.tex
@@
 data, 3 million webpages from this corpus were processed with a CCG
-parser to produce logical forms.  This produced 2.1m predicate
-instances involving 142k entity pairs and 184k entities.  After
-removing infrequently-seen predicates (seen fewer than 6 times), there
-were 25k categories and 4.2k relations.  The differences in numbers
-reported here versus those reported by Krishnamurthy and
+parser to produce logical forms~\cite{krishnamurthy-2014-joint-ccg}.
+This produced 2.1m predicate instances involving 142k entity pairs and
+184k entities.  After removing infrequently-seen predicates (seen
+fewer than 6 times), there were 25k categories and 4.2k relations.
+The differences in numbers reported here versus those reported by
+Krishnamurthy and
 Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} are
@@
 
-There is a large body of other work that is closely related to what is
-presented in this paper.  Two recent papers that also attempt to
-include some form of structured knowledge into distributional
-representations are those by Faruqui et
-al.~\shortcite{faruqui-2015-retrofitting-word-vectors}, and by
-Rockt\"{a}schel et
-al.~\shortcite{rocktaschel-2015-logical-embeddings}.  A key difference
-between their approaches and ours is that they use the structured
-information only to modify distributional representations, while we
-include the structured information directly in our models, training
-weights for structured information jointly with distributional
-representations.  Also conceptually similar is the Additive Relational
-Effects model for knowledge base completion by Nickel et
-al.~\shortcite{nickel-2014-are}, which tries to factorize the residual
-of a KB tensor that cannot be explained by observable features that
-are somewhat similar to the formal features we use in this model.  But
-while this model is conceptually similar, it is computationally quite
-different, and would be rather difficult to use in the setting we
-explore in this work.
+In addition to the work described in \secref{background}, there are
+three broad classes of work that are related to what we have presented
+in this paper.
 
-Our work draws a lot of inspiration from recent work on knowledge base
-completion.  We are building on top of work in embedding the entities
-and relations in a knowledge
-base~\cite{riedel-2013-mf-universal-schema,nickel-2011-rescal,bordes-2013-transe},
-as well as work on graph-based methods for reasoning with knowledge
-bases~\cite{lao-2010-original-pra,gardner-2014-vector-space-pra,neelakantan-2015-rnn-kbc}.
+The first line of research that our work is related to is knowledge
+base completion.  In addition to SFE~\cite{gardner-2015-sfe}, our work
+draws inspiration from work on embedding the entities and relations in
+a knowledge base~\cite{riedel-2013-mf-universal-schema,%
+nickel-2011-rescal,bordes-2013-transe,nickel-2014-are,%
+toutanova-2015-joint-text-kb-embedding}, as well as work on
+graph-based methods for reasoning with knowledge
+bases~\cite{lao-2010-original-pra,gardner-2014-vector-space-pra,%
+neelakantan-2015-rnn-kbc}.
+
+Second, our work is conceptually related to many methods that aim to
+learn word embeddings that are informed by some kind of external
+knowledge~\cite{faruqui-2015-retrofitting-word-vectors,%
+rocktaschel-2015-logical-embeddings,schwartz-2016-symmetric-patterns-w2v,%
+yu-2014-w2v-with-semantic-knowledge}.
+A key difference between these approaches and ours is that they use
+the structured information only to modify distributional
+representations, while we include the structured information directly
+in our models, training weights for structured information jointly
+with distributional representations.
 
@@
 base~\cite{zettlemoyer-2005-ccg,berant-2013-semantic-parsing-qa,%
-kwiatkowski-2013-ontology-matching,krishnamurthy-2012-semantic-parsing}.
-The vast majority of this work is focused on matching natural language
-text to statements in a specific ontology, with no hope of assigning
-meaning to language that falls outside of that ontology.  Only very
-recently has there been work attempting to learn broad coverage
-meaning representations in semantic parsers.  In addition to the work
-by Krishnamurthy and Mitchell which we extend in this paper, there was
-recently a nice piece of work by Choi et
-al.~\shortcite{choi-2015-semantic-parsing-partial-ontologies}.  The
-aim of their work is, like typical semantic parsers, to map text onto
-a single formal statement, but they allow some of the predicates to be
-``open'' predicates not contained in the Freebase ontology.  A key
-difference between their work and ours is that we score surface
-logical forms directly, using a weighted combination of many Freebase
-queries, instead of trying to map them to a single Freebase logical
-form.  Additionally, while their system might learn that
-``front-runner'' should be modeled as an open predicate that has no
-representation in Freebase, they have no method to assign any further
-meaning to that predicate, while our models learn both distributional
-and formal information about the meaning of ``front-runner''.
+kwiatkowski-2013-ontology-matching,krishnamurthy-2012-semantic-parsing,%
+li-2015-semantic-parsing-scfg}.  The vast majority of this work is
+focused on matching natural language text to statements in a specific
+schema, with no hope of assigning meaning to language that falls
+outside of that schema.  Only very recently has there been work
+attempting to learn broad coverage meaning representations in semantic
+parsers.  In addition to the work by Krishnamurthy and Mitchell
+discussed in \secref{background}, and work by Lewis and
+Steedman~\shortcite{lewis-2013-combined-distributional-and-logical-semantics}
+which Krishnamurthy and Mitchell extended, Choi et
+al.~\shortcite{choi-2015-semantic-parsing-partial-ontologies},
+extended a traditional semantic parser with the notion of ``open''
+predicates not contained in the Freebase ontology.  A key difference
+between their work and ours is that, while their system might learn
+that ``front-runner'' should be modeled as an open predicate that has
+no representation in Freebase, they have no method to assign any
+further meaning to that predicate, whereas our models learn both
+distributional and formal information about the meaning of
+``front-runner''.
 

### 2016-03-18 papers/acl2016/paper.tex

--- 2016-03-18 papers/acl2016/paper.tex
@@
   \textless\formalpredicate{nationality}\textgreater\\
-  \textless\formalpredicate{designed}, \formalpredicate{located\_in}\textgreater
+  \textless\formalpredicate{designed}$\rightarrow$\formalpredicate{located\_in}\textgreater
 
@@
   \textless\formalpredicate{type}\textgreater:\entity{Architect}\\
-  \textless\formalpredicate{designed}, \formalpredicate{located\_in}\textgreater \\
-  \textless\formalpredicate{designed}, \formalpredicate{located\_in}\textgreater:\entity{Italy}
+  \textless\formalpredicate{designed}$\rightarrow$\formalpredicate{located\_in}\textgreater \\
+  \textless\formalpredicate{designed}$\rightarrow$\formalpredicate{located\_in}\textgreater:\entity{Italy}
 
-  \caption{A subset of the Freebase graph, and some example extracted features
-  between \entity{Palladio} and \entity{Italy}.  The actual Freebase relations
-  and entity identifiers used are modified here to aid readability.}
+  \caption{A subset of the Freebase graph, and some example extracted
+  features.  The actual Freebase relations and entity identifiers used
+  are modified here to aid readability.}
   \label{fig:sfe}

### 2016-03-21 papers/acl2016/paper.tex
Final version of paper submitted to ACL
Former-commit-id: 1b087d5674865b10a45aef3b9160ff87e1c9985d

@@
 of each word from a large unlabeled text corpus. These models have
-broad coverage, but they also have a shallow semantics centered around
-word similarity. On the other hand, semantic parsing translates
-natural language into logical queries against a formal knowledge base,
-such as Freebase. This approach produces a rich compositional
-semantics and furthermore can leverage structured information from the
-knowledge base. However, semantic parsers have limited coverage as
-they can only represent the meanings of words that can be mapped to
-knowledge base predicates. A critical question is \emph{how do we
-obtain the benefits of both of these approaches?}
+broad coverage, but only a shallow semantics centered around word
+similarity. On the other hand, semantic parsing translates natural
+language into logical queries against a formal knowledge base, such as
+Freebase. This approach produces a rich compositional semantics and
+can leverage structured information from the knowledge base. However,
+semantic parsers have limited coverage as they can only represent the
+meanings of words that can be mapped to knowledge base predicates. A
+critical question is \emph{how do we obtain the benefits of both of
+these approaches?}
 
@@
     \textbf{Logical Form}\\
-    $\lexicalpredicate{architect}(x)~\land~\lexicalpredicate{architect\_N/N}(\entity{Italy}, x)$
+    $\lambda x.\lexicalpredicate{architect}(x)~\land~\lexicalpredicate{architect\_N/N}(\entity{Italy}, x)$
   \end{minipage}
@@
       \entity{(Italy, Palladio)}: & $\phi$: &[-.8, .2, \ldots] \\
-      & $\omega$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ 1 \\
+      & $\psi$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ 1 \\
       &           & \textsc{/structure/architect} $\rightarrow$ 0 \\
@@
       \entity{(Italy, Obama)}: & $\phi$: &[-.2, -.2, \ldots] \\
-      & $\omega$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ 0 \\
+      & $\psi$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ 0 \\
       &           & \textsc{/structure/architect} $\rightarrow$ 0 \\
@@
     \begin{tabular}{@{}ll}
-      $\mathrm{prob}(\entity{Palladio})$: & 0.79 \\
-      $\mathrm{prob}(\entity{Obama})$: & 0.01 \\
+      $P(\entity{Palladio})$: & 0.79 \\
+      $P(\entity{Obama})$: & 0.01 \\
       $\cdots$ \\
@@
 introduced a technique for learning semantic parsers with open
-predicate vocabularies. Instead of mapping text directly to Freebase
-queries, this method parses text to a surface logical form whose
-predicates are derived directly from the words in the text (an example
-of these logical forms is shown in \figref{overview}). Next, a
-distribution over denotations for each predicate is learned using a
-matrix factorization approach similar to that of Riedel et
+predicate vocabularies. Instead of mapping text to Freebase queries,
+this method parses text to a surface logical form whose predicates are
+derived directly from the words in the text (an example of these
+logical forms is shown in \figref{overview}). Next, a distribution
+over denotations for each predicate is learned using a matrix
+factorization approach similar to that of Riedel et
 al.~\shortcite{riedel-2013-mf-universal-schema}. This distribution is
@@
 \ref{sec:formal-and-distributional} and \ref{sec:feature-generation}
-describe our improved predicate models and the corresponding feature
-generation process. Finally, Section \ref{sec:better-candidates}
-describes an improvement on candidate entity generation for question
-answering.
-
-% In \secref{formal-and-distributional} we describe how we modify
-% Krishnamurthy and Mitchell's (K\&M's) semantic parser to include
-% features from a formal knowledge base.  In \secref{computing-pmi} we
-% describe how we select those features for each predicate.  The
-% remaining two sections then describe other improvements we made to
-% K\&M's semantic parsing model: lexicalizing preposition and
-% noun-compound predicates, and using the Freebase graph to select
-% candidate entities.
+describe our predicate models and the corresponding feature generation
+process. Finally, Section \ref{sec:better-candidates} describes an
+improvement on candidate entity generation for question answering.
 
@@
 
-As in K\&M, we generate logical forms from natural language statements
-by computing a syntactic CCG parse, then applying a collection of
-rules to produce logical forms. However, their logical form analyses
-do not model noun-mediated relations well. For example, given the
-phrase ``Italian architect Andrea Palladio,'' their system's logical
-form would include the relation
-$\lexicalpredicate{N/N}(\entity{Italy}, \entity{Andrea
+As done by Krishnamurthy and
+Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}, we
+generate logical forms from natural language statements by computing a
+syntactic CCG parse, then applying a collection of rules to produce
+logical forms. However, their logical form analyses do not model
+noun-mediated relations well. For example, given the phrase ``Italian
+architect Andrea Palladio,'' their system's logical form would include
+the relation $\lexicalpredicate{N/N}(\entity{Italy}, \entity{Andrea
 Palladio})$. Here, the \lexicalpredicate{N/N} predicate represents a
@@
 above, our system produces the relation
-\lexicalpredicate{architect\_N/N}. It does this by simply
+\lexicalpredicate{architect\_N/N}. It does this by
 concatenating all intervening noun modifiers between two entity
@@
 ``Illinois attorney general Lisa Madigan'' produces the predicate
-\lexicalpredicate{attorney\_general\_N/N}). (While it would be
+\lexicalpredicate{attorney\_general\_N/N}).\footnote{While it would be
 preferable to use actual dependency relations to determine which words
@@
 produces flat analyses of noun phrases where all noun modifiers depend
-directly on the head of the noun phrase.) We similarly improve the
+directly on the head of the noun phrase.} We similarly improve the
 analyses of prepositions and possessives to include the head noun. For
@@
 
-% TODO: ``query'' features?
+The key question in the semantic parsing framework we are using is how
+to define the predicate models that underlie the probabilistic
+database described in \secref{jayant-semparse}.  This is where
+previous work used purely distributional models, and where we wish to
+include structured information from a knowledge base to improve the
+semantics of these predicate models.
 
 We inject information from a knowledge base into our predicate models
-by augmenting the learned embeddings with features. The truth
-probability of a category instance $c(e)$ or relation instance $r(e_1,
-e_2)$ in our model is given by:
+by augmenting the learned embeddings with features. In our models, the
+truth probability of a category instance $c(e)$ or relation instance
+$r(e_1, e_2)$ is given by:
 
@@
 with the selected formal SFE features for each predicate.  All of
-these parameters are optimized jointly, using the same query ranking
-objective used by K\&M.
-
-% For each category and relation, we select a subset of the SFE features in the
-% vectors $\psi$ to have associated weights $\omega_c$ and $\omega_r$.  We then
-% add the weights $\omega_c$ and $\omega_r$ as parameters to be learned for each
-% predicate, and we add the feature vectors $\psi(e)$ and $\psi(e_1, e_2)$ as
-% observed features for each entity and entity pair.  The augmented category and
-% relation probabilities are as follows:
+these parameters are optimized jointly, using the semantic parsing
+framework described in \secref{jayant-semparse}.
 
@@
 edge sequences that connect nodes $e_1$ and $e_2$ in the Freebase
-graph, up to length 4.  For an entity $e$, we extract two kinds of
-features: (1) all edge sequences up to length two that begin at $e$,
-and (2) the same sequences paired with the entity at their
-endpoint. Features of type (1) capture the kinds of relations that an
-entity participates in, e.g., designing architectural structures,
-while features of type (2) capture relations to other particular
-entities. This second kind of feature is most helpful when the
-endpoint entity is a type, such as \entity{architect}, although there
-are some other valuable features of this kind. \figref{sfe} shows some
-example entity and entity pair features extracted from a subset of the
-Freebase graph.
-
-% For each category and relation, we select a subset of the SFE features in the
-% vectors $\psi$ to have associated weights $\omega_c$ and $\omega_r$.  We then
-% add the weights $\omega_c$ and $\omega_r$ as parameters to be learned for each
-% predicate, and we add the feature vectors $\psi(e)$ and $\psi(e_1, e_2)$ as
-% observed features for each entity and entity pair.  The augmented category and
-% relation probabilities are as follows:
-% 
-% \begin{align*}
-%   P(c(e)) &= \sigma ( \theta_c^T \phi_e + \omega_c^T \psi_c(e)) \\
-%   P(r(e_1, e_2)) &= \sigma ( \theta_r^T \phi_{(e_1, e_2)} + \omega_r^T \psi_r(e_1, e_2) )
-% \end{align*}
-% where we have added subscripts on the $\psi$ functions to indicate that each
-% predicate selects its own set of features from the SFE feature vector $\psi$.
-
-% The feature vectors returned by SFE have dimensionality in the tens of
-% millions.  We do not have near enough data to train that many parameters for
-% each of our tens of thousands of predicates, nor do we have enough RAM in our
-% machines to keep that many parameters in memory.  It is thus necessary to
-% select some small number of informative features for each predicate.  We do
-% this using pointwise mutual information (PMI).
+graph, up to length 4.  For an entity $e$, the vector $\psi(e)$
+contains two kinds of indicator features: (1) all edge sequences up to
+length two that begin at $e$, and (2) the same sequences paired with
+the entity at their endpoint. Features of type (1) capture the kinds
+of relations that an entity participates in, e.g., designing
+architectural structures, while features of type (2) capture relations
+to other particular entities. This second kind of feature is most
+helpful when the endpoint entity is a type, such as
+\entity{architect}, although there are some other valuable features of
+this kind. \figref{sfe} shows some example entity and entity pair
+features extracted from a subset of the Freebase graph.
 
@@
 feature counts for the predicates \formalpredicate{architect} and
-\formalpredicate{architect\_N/N}, respectively. Next, for each predicate
-$\pi$ and feature $f$, we use these counts to calculate three
-probabilities: $p(\pi, f)$, $p(\pi)$ and $p(f)$. (TODO: how did you
-calculate these?). The PMI of a predicate/feature pair is then $\log
-\frac{p(\pi, f)}{p(\pi)p(f)}$. After removing features with counts
-below a threshold, we pick the $k=100$ features with the highest PMI
-values for each predicate to use in our model.
-
-% PMI measures the strength of association between two variables $x$ and $y$; it
-% is computed as $\log\frac{p(x,y)}{p(x)p(y)}$.  In our case, we want to
-% associate predicates with SFE features.  However, our SFE features are for each
-% \emph{entity} and \emph{entity pair}, not each \emph{predicate}.  To associate
-% SFE features with predicates, we  For each
-% predicate $\pi$ and feature $f$, we use these counts to calculate the
-% probabilities $p(\pi, f)$, $p(\pi)$ and $p(f)$.
+\formalpredicate{architect\_N/N}, respectively. This gives a set of
+counts \formalpredicate{count}($\pi$), \formalpredicate{count}($f$),
+and \formalpredicate{count}($\pi\land f$), for each predicate $\pi$
+and feature $f$.  The features are then ranked by PMI for each feature
+by computing $\frac{\formalpredicate{count}(\pi\land
+f)}{\formalpredicate{count}(\pi)\formalpredicate{count}(f)}$.  After
+removing features with counts below a threshold, we pick the $k=100$
+features with the highest PMI values for each predicate to use in our
+model.
 
@@
 scores to entity pairs that were never seen in the training data. The
-purely-distributional model of K\&M has no basis for assigning these
-scores and therefore assumes $P(r(e_1,e_2)) = 0$ for unseen entity
-pairs $(e_1,e_2)$. This assumption limits the recall of their system
-when it is applied to question answering, as these entity pairs will
-not have been observed for many correct, but rare entity answers. In
-contrast, our predicate models can score any entity pair: the
-distributional component of an unseen pair will be zero, but the SFE
-component is always applicable. This benefit allows our model to
-considerably improve question answering performance on rare entities.
-
-% One final way in which we improved K\&M's semantic parser is in how candidate
-% entities are generated during inference.  Because the distributional-only
-% predicate models used by K\&M's semantic parser need to learn a vector of
-% parameters for each entity pair, they cannot give a non-zero score to any
-% entity pair not seen during training time.  When given a query such as
-% $\lambda(x).\lexicalpredicate{architect\_N/N}(x, \entity{Andrea
-% Palladio})$, K\&M's system only needs to consider the set of entities
-% $\entity{x}$ that have been seen at training time with \entity{Andrea
-% Palladio}; all other entities will get a score of 0.
-% 
-% Our predicate models do not have this limitation.  The distributional component
-% will still give an unseen entity pair a score of 0, as it is identical to K\&M's
-% model, but the formal component of our models simply computes an observed
-% feature vector from Freebase for the entity pair.  As long as both entities
-% appear in Freebase, our model can compute a feature vector and give a non-zero
-% score.
+purely distributional model of Krishnamurthy and Mitchell has no basis
+for assigning these scores and therefore assumes $P(r(e_1,e_2)) = 0$
+for unseen entity pairs $(e_1,e_2)$. This assumption limits the recall
+of their system when it is applied to question answering, as these
+entity pairs will not have been observed for many correct, but rare
+entity answers. In contrast, our predicate models can score any entity
+pair: the distributional component of an unseen pair will be zero, but
+the SFE component is always applicable. This benefit allows our model
+to considerably improve question answering performance on rare
+entities.
 
@@
 is slow, and furthermore makes it more difficult to identify correct
-answers (as their frequency in the candidate set
-decreases). Therefore, when answering a query, we compute a set of
-candidate entities and only score these candidates. Our candidate set
-consists of all entities seen with the query entities in the training
-set as well as all entities directly connected to the query entities
-in Freebase, or connected by a mediator node.\footnote{Mediators in
+answers (as their relative frequency in the candidate set decreases).
+Therefore, when answering a query, we compute a set of candidate
+entities and only score these candidates. Our candidate set consists
+of all entities seen with the query entities in the training set as
+well as all entities directly connected to the query entities in
+Freebase, or connected by a mediator node.\footnote{Mediators in
 Freebase are used to capture relations with more than two arguments,
@@
 start date, and an end date.}
-
-% While this improvement allows us to handle queries over rare entities much
-% better than a distributional-only model, it also complicates inference, as we
-% cannot just score entity pairs seen at training time.  Optimizing every query's
-% score over all of the millions of entities in Freebase is not computationally
-% feasible.  To make inference tractable, for a given query we restrict
-% candidates to all entities seen with the query entities during training (as
-% done by K\&M), as well as all entities directly connected to the query entities
-% in Freebase, or connected by a mediator node.\footnote{Mediators in Freebase are
-% used to capture relations with more than two arguments, such as employment
-% tenure, which has an employer, and employee, a start date, and an end date.}
 
@@
 
-We evaluate our models of predicate semantics on a fill-in-the-blank
+We evaluate our open-vocabulary semantic parser on a fill-in-the-blank
 natural language query task.  Each test example is a natural language
@@
 184k entities.  After removing infrequently-seen predicates (seen
-fewer than 6 times), there were 25k categories and 4.2k relations.
-The differences in numbers reported here versus those reported by
-Krishnamurthy and
+fewer than 6 times), there were 25k categories and 4.2k
+relations.\footnote{The differences in numbers reported here versus
+those reported by Krishnamurthy and
 Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} are
 due to our improved logical form generation, discussed in
-\secref{better-lfs}.
+\secref{better-lfs}.}
 
@@
 data from a separate section of ClueWeb.  However, as they did not
-release a development set in with their data, we used this set as a
+release a development set with their data, we used this set as a
 development set.  For a final evaluation, we generated another,
@@
 function for whether the $k$th answer is correct, and $m$ is number of
-returned answers (up to 100 in this evaluation).  Reciprocal rank is
-computed by first finding the rank $r$ of the first correct prediction
-made by a system.  Reciprocal rank is then $\frac{1}{r}$, ranging from
-1 (if the first prediction is correct) to 0 (if there is no correct
-answer returned).  In the tables below we report \emph{mean} average
-precision (MAP) and reciprocal rank (MRR), averaged over all of the
-queries in the test set.  We also report a weighted version of MAP,
-where the AP of each query is scaled by the number of annotated
-correct answers to the query (shown as W-MAP in the tables for space
-considerations).
+returned answers (up to 100 in this evaluation).  AP is equivalent to
+calculating the area under a precision-recall curve.  Reciprocal rank
+is computed by first finding the rank $r$ of the first correct
+prediction made by a system.  Reciprocal rank is then $\frac{1}{r}$,
+ranging from 1 (if the first prediction is correct) to 0 (if there is
+no correct answer returned).  In the tables below we report
+\emph{mean} average precision (MAP) and \emph{mean} reciprocal rank
+(MRR), averaged over all of the queries in the test set.  We also
+report a weighted version of MAP, where the AP of each query is scaled
+by the number of annotated correct answers to the query (shown as
+W-MAP in the tables for space considerations).
 
@@
 entity generation outlined in \secref{better-candidates}.  By simply
-appending the list of connected entities to the end of the rankings
-returned by the distributional model, MAP improves by 40\% (see
-\tabref{better-candidates}).  The connectedness of an entity pair in
-Freebase is very informative, especially for rare entities that are
+appending the list of connected entities in Freebase to the end of the
+rankings returned by the distributional model, MAP improves by 40\%
+(see \tabref{better-candidates}).  The connectedness of an entity pair
+in Freebase is very informative, especially for rare entities that are
 not seen together during training.
@@
 
-\tabref{dev-results} shows the results of our experiments on the
-development set.  As can be seen, the combined model significantly
-improves performance over prior work, giving a relative gain in
-weighted MAP of 29\%.
+\tabref{dev-results} shows a comparison between the semantic parsing
+models we have discussed on the development set.  As can be seen, the
+combined model significantly improves performance over prior work,
+giving a relative gain in weighted MAP of 29\%.
 
@@
 combined model is actually larger on this set, with gains on our
-metrics ranging from 50\% to 97\%.
+metrics ranging from 50\% to 87\%.
 
@@
 prime minister \blank{},'' both of which can be exactly expressed in
-Freebase. (TODO: do these relations get high weights in the features?)
+Freebase.  The top features for \lexicalpredicate{newspaper}($x$) all
+indicate that $x$ has type \formalpredicate{newspaper} in Freebase,
+and the top features for \lexicalpredicate{newspaper\_N/N}($x$, $y$)
+indicate that $y$ is a newspaper, and that $x$ is either the
+circulation area of $y$ or the language of $y$.
+
 The model also performs well on queries with partial Freebase
@@
 rocktaschel-2015-logical-embeddings,schwartz-2016-symmetric-patterns-w2v,%
-yu-2014-w2v-with-semantic-knowledge}.
-A key difference between these approaches and ours is that they use
-the structured information only to modify distributional
-representations, while we include the structured information directly
-in our models, training weights for structured information jointly
-with distributional representations.
+yu-2014-w2v-with-semantic-knowledge}.  A key difference between these
+approaches and ours is that they use the structured information only
+to modify distributional representations, while we include the
+structured information directly in our models, training feature
+weights jointly with distributional representations.
 
@@
 achieved relative gains of over 50\% in mean average precision and
-mean reciprocal rank versus prior work.  We also introduced a better
-mapping from surface text to logical forms, and a simple method for
-using Freebase to find candidate entities during inference.  Taken
-together, the methods introduced in this paper improved mean average
-precision on our task from .163 to .370, a 127\% relative improvement.
+mean reciprocal rank versus a purely distributional approach.  We also
+introduced a better mapping from surface text to logical forms, and a
+simple method for using Freebase to find candidate entities during
+inference.  Taken together, the methods introduced in this paper
+improved mean average precision on our task from .163 to .370, a 127\%
+relative improvement over prior work.
 

### 2016-03-21 papers/acl2016/paper.tex
Fix text width and remove commented-out text
Former-commit-id: 2ea804b60d3534a40b77dc2478323c370288cca5

@@
 
-  We consider the problem of mapping language onto meaning
-  representations that are executable, returning truth values for
-  complete statements and distributions over entities for queries.
-  The typical approach to solve this problem is semantic parsing;
-  however, this approach fails when the language cannot be represented
-  by a single query over the Freebase schema.  Instead, our approach
-  represents language as a \emph{weighted combination} of queries over
-  the formal schema, along with a distributional component similar to
-  a word embedding.  This technique combines the advantages of
-  traditional semantic parsing (compositionality and the ability to
-  leverage a structured knowledge base) with the broad coverage
-  obtained by distributional methods.  We present relative gains of
-  over 120\% in mean average precision versus prior work on an
-  open-vocabulary fill-in-the-blank question answering task.
+  We consider the problem of mapping language onto meaning representations that
+  are executable, returning truth values for complete statements and
+  distributions over entities for queries.  The typical approach to solve this
+  problem is semantic parsing; however, this approach fails when the language
+  cannot be represented by a single query over the Freebase schema.  Instead,
+  our approach represents language as a \emph{weighted combination} of queries
+  over the formal schema, along with a distributional component similar to a
+  word embedding.  This technique combines the advantages of traditional
+  semantic parsing (compositionality and the ability to leverage a structured
+  knowledge base) with the broad coverage obtained by distributional methods.
+  We present relative gains of over 120\% in mean average precision versus
+  prior work on an open-vocabulary fill-in-the-blank question answering task.
 
@@
 
-How should a computer program represent the meaning of a word or a
-phrase? Recent work has suggested two vastly different
-approaches---distributional vector space models and semantic
-parsing---each with its own advantages and disadvantages. On one hand,
-distributional models produce a vector representation of the meaning
-of each word from a large unlabeled text corpus. These models have
-broad coverage, but only a shallow semantics centered around word
-similarity. On the other hand, semantic parsing translates natural
+How should a computer program represent the meaning of a word or a phrase?
+Recent work has suggested two vastly different approaches---distributional
+vector space models and semantic parsing---each with its own advantages and
+disadvantages. On one hand, distributional models produce a vector
+representation of the meaning of each word from a large unlabeled text corpus.
+These models have broad coverage, but only a shallow semantics centered around
+word similarity. On the other hand, semantic parsing translates natural
 language into logical queries against a formal knowledge base, such as
-Freebase. This approach produces a rich compositional semantics and
-can leverage structured information from the knowledge base. However,
-semantic parsers have limited coverage as they can only represent the
-meanings of words that can be mapped to knowledge base predicates. A
-critical question is \emph{how do we obtain the benefits of both of
-these approaches?}
+Freebase. This approach produces a rich compositional semantics and can
+leverage structured information from the knowledge base. However, semantic
+parsers have limited coverage as they can only represent the meanings of words
+that can be mapped to knowledge base predicates. A critical question is
+\emph{how do we obtain the benefits of both of these approaches?}
 
@@
   \vspace{-.1in}
-  \caption{Overview of the components of our model.  Given an input
-  text, we use a CCG parser and an entity linker to produce a logical
-  form that is a conjunction of predicates involving the entities in
-  the text.  For each predicate (both categories and relations), we
-  learn a distributional vector $\theta$, as well as weights $\omega$
-  associated with formal features from Freebase (which are shortened
-  to fit in the figure).  For each entity and entity pair, we also
-  learn a distributional vector $\phi$, and we extract a feature
-  vector $\psi$ from Freebase.  These models are combined to assign a
+  \caption{Overview of the components of our model.  Given an input text, we
+  use a CCG parser and an entity linker to produce a logical form that is a
+  conjunction of predicates involving the entities in the text.  For each
+  predicate (both categories and relations), we learn a distributional vector
+  $\theta$, as well as weights $\omega$ associated with formal features from
+  Freebase (which are shortened to fit in the figure).  For each entity and
+  entity pair, we also learn a distributional vector $\phi$, and we extract a
+  feature vector $\psi$ from Freebase.  These models are combined to assign a
   probability to candidate entities, assigning a high probability to
-  \entity{Andrea Palladio} and a low probability to \entity{Barack
-  Obama}.}
+  \entity{Andrea Palladio} and a low probability to \entity{Barack Obama}.}
   \label{fig:overview}
@@
 Krishnamurthy and
-Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}
-provide a partial answer to this question with their open-vocabulary
-semantic parser. This system answers compositional, fill-in-the-blank
-natural language queries against Freebase, such as ``Hollywood honcho
-\blank{},'' using \emph{distributional} models of predicate
-semantics. The method semantically parses text to a surface logical
-form containing predicates derived from the text itself, such as
-$\lambda x.\lexicalpredicate{honcho}(x) \land
+Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} provide a
+partial answer to this question with their open-vocabulary semantic parser.
+This system answers compositional, fill-in-the-blank natural language queries
+against Freebase, such as ``Hollywood honcho \blank{},'' using
+\emph{distributional} models of predicate semantics. The method semantically
+parses text to a surface logical form containing predicates derived from the
+text itself, such as $\lambda x.\lexicalpredicate{honcho}(x) \land
 \lexicalpredicate{honcho\_N/N}(\entity{Hollywood}, x)$, then learns the
-denotations of these predicates using distributional information from
-a large, entity-linked corpus. This method combines the broad coverage
-of distributional approaches with the compositionality of semantic
-parsing; however, it does not use structured information from Freebase
-to assist with its predictions.
+denotations of these predicates using distributional information from a large,
+entity-linked corpus. This method combines the broad coverage of distributional
+approaches with the compositionality of semantic parsing; however, it does not
+use structured information from Freebase to assist with its predictions.
 
-In this work, we introduce new models of predicate semantics that
-leverage both structured information from Freebase and distributional
-information from a corpus. Our key observation is that, while there is
-no Freebase predicate that corresponds exactly to the meaning of
-``honcho,'' Freebase \emph{does} contain predicates that
-\emph{partially} represent its meaning. For example, an entity that
-can be called ``honcho'' is likely to have type
-\formalpredicate{person}. We therefore incorporate \emph{features}
-based on Freebase paths into the predicate models of Krishnamurthy and
-Mitchell and learn per-predicate weights for these features using
-distributional information (\figref{overview}). This approach
-effectively learns the meaning of a word as a distributional vector
-plus a \emph{weighted combination of Freebase queries}, a considerably
-more expressive representation than either traditional semantic parsers
-or the work by Krishnamurthy and Mitchell.
+In this work, we introduce new models of predicate semantics that leverage both
+structured information from Freebase and distributional information from a
+corpus. Our key observation is that, while there is no Freebase predicate that
+corresponds exactly to the meaning of ``honcho,'' Freebase \emph{does} contain
+predicates that \emph{partially} represent its meaning. For example, an entity
+that can be called ``honcho'' is likely to have type \formalpredicate{person}.
+We therefore incorporate \emph{features} based on Freebase paths into the
+predicate models of Krishnamurthy and Mitchell and learn per-predicate weights
+for these features using distributional information (\figref{overview}). This
+approach effectively learns the meaning of a word as a distributional vector
+plus a \emph{weighted combination of Freebase queries}, a considerably more
+expressive representation than either traditional semantic parsers or the work
+by Krishnamurthy and Mitchell.
 
-We demonstrate our approach on the task of answering fill-in-the-blank
-natural language queries.  We first present two simple improvements to
-the distributional models of Krishnamurthy and Mitchell (an improved
-surface logical form representation, and better candidate generation
-during inference), improving the performance of that system by over
-40\%.  We then show that our approach improves mean average precision
-by 62\% over this improved baseline.  Taken together, the methods
-presented in this paper give a relative gain over prior work of more
-than 120\%.
+We demonstrate our approach on the task of answering fill-in-the-blank natural
+language queries.  We first present two simple improvements to the
+distributional models of Krishnamurthy and Mitchell (an improved surface
+logical form representation, and better candidate generation during inference),
+improving the performance of that system by over 40\%.  We then show that our
+approach improves mean average precision by 62\% over this improved baseline.
+Taken together, the methods presented in this paper give a relative gain over
+prior work of more than 120\%.
 
@@
 
-In this work, we make heavy use of the open-vocabulary semantic parser
-of Krishnamurthy and
-Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}, as
-well as features derived from a knowledge base using a technique
-called subgraph feature extraction~\cite{gardner-2015-sfe}.  We
-briefly describe both of these techniques.
+In this work, we make heavy use of the open-vocabulary semantic parser of
+Krishnamurthy and
+Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}, as well as
+features derived from a knowledge base using a technique called subgraph
+feature extraction~\cite{gardner-2015-sfe}.  We briefly describe both of these
+techniques.
 
@@
 Krishnamurthy and
-Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}
-introduced a technique for learning semantic parsers with open
-predicate vocabularies. Instead of mapping text to Freebase queries,
-this method parses text to a surface logical form whose predicates are
-derived directly from the words in the text (an example of these
-logical forms is shown in \figref{overview}). Next, a distribution
-over denotations for each predicate is learned using a matrix
-factorization approach similar to that of Riedel et
-al.~\shortcite{riedel-2013-mf-universal-schema}. This distribution is
-concisely represented using a probabilistic database, which also
-enables efficient probabilistic execution of logical form queries.
+Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} introduced a
+technique for learning semantic parsers with open predicate vocabularies.
+Instead of mapping text to Freebase queries, this method parses text to a
+surface logical form whose predicates are derived directly from the words in
+the text (an example of these logical forms is shown in \figref{overview}).
+Next, a distribution over denotations for each predicate is learned using a
+matrix factorization approach similar to that of Riedel et
+al.~\shortcite{riedel-2013-mf-universal-schema}. This distribution is concisely
+represented using a probabilistic database, which also enables efficient
+probabilistic execution of logical form queries.
 
@@
 probabilistic matrix factorization. This factorization has two sets of
-parameters: each category or relation has a learned $k$-dimensional
-embedding $\theta$, and each entity or entity pair has a learned
-$k$-dimensional embedding $\phi$. The probability assigned to a
-category instance $c(e)$ or relation instance $r(e_1, e_2)$ is given
-by:
+parameters: each category or relation has a learned $k$-dimensional embedding
+$\theta$, and each entity or entity pair has a learned $k$-dimensional
+embedding $\phi$. The probability assigned to a category instance $c(e)$ or
+relation instance $r(e_1, e_2)$ is given by:
 
@@
 
-The probability of a predicate instance is the (sigmoided) inner
-product of the corresponding predicate and entity embeddings. Thus,
-predicates with nearby embeddings will have similar distributions over
-the entities in their denotation. The parameters $\theta$ and $\phi$
-are learned using a query ranking objective that optimizes them to
-rank entities observed in the denotation of a logical form above
-unobserved entities. Note that this approach is similar to modern
-techniques for constructing word embeddings in that it factors a
-cooccurrence matrix between predicates and
-entities~\cite{levy-2014-w2v-as-mf}. Given the trained predicate and
-entity parameters, the system is capable of efficiently computing the
-marginal probability that an entity is an element of a logical form's
-denotation using approximate inference algorithms for probabilistic
-databases.
+The probability of a predicate instance is the (sigmoided) inner product of the
+corresponding predicate and entity embeddings. Thus, predicates with nearby
+embeddings will have similar distributions over the entities in their
+denotation. The parameters $\theta$ and $\phi$ are learned using a query
+ranking objective that optimizes them to rank entities observed in the
+denotation of a logical form above unobserved entities. Note that this approach
+is similar to modern techniques for constructing word embeddings in that it
+factors a cooccurrence matrix between predicates and
+entities~\cite{levy-2014-w2v-as-mf}. Given the trained predicate and entity
+parameters, the system is capable of efficiently computing the marginal
+probability that an entity is an element of a logical form's denotation using
+approximate inference algorithms for probabilistic databases.
 
-In this paper, we use the open-vocabulary semantic parsing framework
-outlined in this section.  However, where Krishnamurthy and Mitchell
-used only distributional methods to compute $P(c(e))$ and $P(r(e_1,
-e_2))$, we augment these models with features derived from a formal
-knowledge base, as described in \secref{method}.
+In this paper, we use the open-vocabulary semantic parsing framework outlined
+in this section.  However, where Krishnamurthy and Mitchell used only
+distributional methods to compute $P(c(e))$ and $P(r(e_1, e_2))$, we augment
+these models with features derived from a formal knowledge base, as described
+in \secref{method}.
 
@@
 
-  \caption{A subset of the Freebase graph, and some example extracted
-  features.  The actual Freebase relations and entity identifiers used
-  are modified here to aid readability.}
+  \caption{A subset of the Freebase graph, and some example extracted features.
+  The actual Freebase relations and entity identifiers used are modified here
+  to aid readability.}
   \label{fig:sfe}
@@
 
-Subgraph feature extraction (SFE) is a technique introduced by Gardner
-and Mitchell~\shortcite{gardner-2015-sfe} for generating feature
-matrices over node pairs in a graph with labeled edges.  Given a pair
-of nodes in a graph, SFE performs a search to characterize and extract
-features from a subgraph around those two nodes.  Example features
-include the set of edge sequences that connect the two nodes.
-\figref{sfe} shows an example subgraph for the pair \entity{Andrea
-Pallado} and \entity{Italy}, and features that would be extracted for
-that entity pair.  Gardner and Mitchell used these features to perform
-link prediction in the graph, using characteristics of the subgraph
-around two nodes to determine if an edge of a particular type should
-exist between those nodes.\footnote{When the graph corresponds to a
-knowledge base like Freebase, this task is also known as knowledge
-base completion.}
+Subgraph feature extraction (SFE) is a technique introduced by Gardner and
+Mitchell~\shortcite{gardner-2015-sfe} for generating feature matrices over node
+pairs in a graph with labeled edges.  Given a pair of nodes in a graph, SFE
+performs a search to characterize and extract features from a subgraph around
+those two nodes.  Example features include the set of edge sequences that
+connect the two nodes.  \figref{sfe} shows an example subgraph for the pair
+\entity{Andrea Pallado} and \entity{Italy}, and features that would be
+extracted for that entity pair.  Gardner and Mitchell used these features to
+perform link prediction in the graph, using characteristics of the subgraph
+around two nodes to determine if an edge of a particular type should exist
+between those nodes.\footnote{When the graph corresponds to a knowledge base
+like Freebase, this task is also known as knowledge base completion.}
 
-We differ from the work done by Gardner and Mitchell in two ways.
-First, we apply these features to models of natural language, instead
-of to the link prediction task.  Second, Gardner and Mitchell only
-considered generating feature matrices over node \emph{pairs} in a
-graph, with which one can model binary relations.  The natural
-language queries we wish to answer also involve unary predicates.  We
-thus extend SFE to also generate feature matrices over \emph{nodes} in
-a graph, a straightforward extension that is described in
+We differ from the work done by Gardner and Mitchell in two ways.  First, we
+apply these features to models of natural language, instead of to the link
+prediction task.  Second, Gardner and Mitchell only considered generating
+feature matrices over node \emph{pairs} in a graph, with which one can model
+binary relations.  The natural language queries we wish to answer also involve
+unary predicates.  We thus extend SFE to also generate feature matrices over
+\emph{nodes} in a graph, a straightforward extension that is described in
 \secref{method}.
@@
 
-This section presents our approach to open vocabulary semantic
-parsing. Our approach follows the same structure as described in
-Section \ref{sec:jayant-semparse}: we generate a surface logical form
-from a query, then evaluate it against a probabilistic database with
-learned predicate instance probabilities. Section \ref{sec:better-lfs}
-describes our logical form generation, which improves the analyses of
-noun-mediated relations relative to prior work. Sections
-\ref{sec:formal-and-distributional} and \ref{sec:feature-generation}
-describe our predicate models and the corresponding feature generation
-process. Finally, Section \ref{sec:better-candidates} describes an
-improvement on candidate entity generation for question answering.
+This section presents our approach to open vocabulary semantic parsing. Our
+approach follows the same structure as described in Section
+\ref{sec:jayant-semparse}: we generate a surface logical form from a query,
+then evaluate it against a probabilistic database with learned predicate
+instance probabilities. Section \ref{sec:better-lfs} describes our logical form
+generation, which improves the analyses of noun-mediated relations relative to
+prior work. Sections \ref{sec:formal-and-distributional} and
+\ref{sec:feature-generation} describe our predicate models and the
+corresponding feature generation process. Finally, Section
+\ref{sec:better-candidates} describes an improvement on candidate entity
+generation for question answering.
 
@@
 As done by Krishnamurthy and
-Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}, we
-generate logical forms from natural language statements by computing a
-syntactic CCG parse, then applying a collection of rules to produce
-logical forms. However, their logical form analyses do not model
-noun-mediated relations well. For example, given the phrase ``Italian
-architect Andrea Palladio,'' their system's logical form would include
-the relation $\lexicalpredicate{N/N}(\entity{Italy}, \entity{Andrea
-Palladio})$. Here, the \lexicalpredicate{N/N} predicate represents a
-generic noun modifier relation; however, this relation is too vague
-for the predicate model to accurately learn its denotation. A similar
-problem occurs with prepositions and possessives, e.g., it is
-similarly hard to learn the denotation of the predicate
-\lexicalpredicate{of}.
+Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}, we generate
+logical forms from natural language statements by computing a syntactic CCG
+parse, then applying a collection of rules to produce logical forms. However,
+their logical form analyses do not model noun-mediated relations well. For
+example, given the phrase ``Italian architect Andrea Palladio,'' their system's
+logical form would include the relation $\lexicalpredicate{N/N}(\entity{Italy},
+\entity{Andrea Palladio})$. Here, the \lexicalpredicate{N/N} predicate
+represents a generic noun modifier relation; however, this relation is too
+vague for the predicate model to accurately learn its denotation. A similar
+problem occurs with prepositions and possessives, e.g., it is similarly hard to
+learn the denotation of the predicate \lexicalpredicate{of}.
 
-Our system improves the analysis of noun-mediated relations by simply
-including the noun in the predicate name. In the architect example
-above, our system produces the relation
-\lexicalpredicate{architect\_N/N}. It does this by
-concatenating all intervening noun modifiers between two entity
-mentions and including them in the predicate name; for example,
-``Illinois attorney general Lisa Madigan'' produces the predicate
+Our system improves the analysis of noun-mediated relations by simply including
+the noun in the predicate name. In the architect example above, our system
+produces the relation \lexicalpredicate{architect\_N/N}. It does this by
+concatenating all intervening noun modifiers between two entity mentions and
+including them in the predicate name; for example, ``Illinois attorney general
+Lisa Madigan'' produces the predicate
 \lexicalpredicate{attorney\_general\_N/N}).\footnote{While it would be
-preferable to use actual dependency relations to determine which words
-to add to the predicate, this is not possible because our parser
-produces flat analyses of noun phrases where all noun modifiers depend
-directly on the head of the noun phrase.} We similarly improve the
-analyses of prepositions and possessives to include the head noun. For
-example, ``Barack Obama, president of the U.S.'' produces the
-predicate instance $\lexicalpredicate{president\_of}(\entity{Barack
-  Obama}, \entity{U.S.})$, and ``Rome, Italy's capital'' produces the
-predicate \lexicalpredicate{'s\_capital}. This process generates more
-specific predicates that we empirically found were easier for the
-predicate models to learn.
-
-% While we largely follow the semantic parsing framework introduced by K\&M, we
-% made one important change in how logical forms are generated.  For the running
-% example we have been using this paper, ``Italian architect Andrea Palladio'',
-% the relation predicate produced by K\&M's system is
-% $\lexicalpredicate{N/N}(\entity{Italy}, \entity{Andrea Palladio})$.
-% \lexicalpredicate{N/N}
-% does correctly capture the fact that \entity{Italy} is used syntactically as a
-% noun modifier of \entity{Andrea Palladio}, but it leaves out the additional
-% information contained in the syntax that ``architect'' was mediating that
-% noun-noun dependency.  This means that ``U.S. president Barack Obama'' and
-% ``Italian architect Andrea Palladio'' are both modeled using the same relation
-% predicate, which leads to a very generic and largely useless model for the
-% predicate \lexicalpredicate{N/N}.  By splitting \lexicalpredicate{N/N} into separate
-% predicates (\lexicalpredicate{architect\_N/N} and \lexicalpredicate{president\_N/N}), we give
-% the model the opportunity to learn more fine-grained relation semantics, and we
-% allow our feature selection pipeline to find much more useful features for
-% relation predicates.  While it would be ideal to use actual dependency
-% relations to determine which words to add to the predicate in complex noun
-% phrases, most current parsers treat these kinds of noun phrases as flat, with
-% all noun modifiers depending directly on the head of the noun phrase.  We
-% approximate this ideal by simply taking all words in between the two entities
-% in a noun phrase as the predicate (e.g., ``Illinois attorney general Lisa
-% Madigan'' would produce the predicate \lexicalpredicate{attorney\_general\_N/N}).
-
-% A similar issue arises with prepositions and possessives.  For a phrase such as
-% ``Barack Obama, president of the U.S.'', K\&M's system would produce the
-% following relation predicate: $\lexicalpredicate{of}(\entity{Barack Obama},
-% \entity{U.S.})$.  Because this same predicate (\lexicalpredicate{of}) is used for all
-% instances of this preposition, the predicate is forced to model too much and
-% becomes overly generic.  When there is a common noun mediating a prepositional
-% dependency between two entities, as in the phrase above, we add that noun to
-% the predicate, giving the instance $\lexicalpredicate{president\_of}(\entity{Barack
-% Obama}, \entity{U.S.})$.  We do the same for possessives in phrases such as
-% ``Rome, Italy's capital'', producing the predicate \lexicalpredicate{'s\_capital}.
+preferable to use actual dependency relations to determine which words to add
+to the predicate, this is not possible because our parser produces flat
+analyses of noun phrases where all noun modifiers depend directly on the head
+of the noun phrase.} We similarly improve the analyses of prepositions and
+possessives to include the head noun. For example, ``Barack Obama, president of
+the U.S.'' produces the predicate instance
+$\lexicalpredicate{president\_of}(\entity{Barack Obama}, \entity{U.S.})$, and
+``Rome, Italy's capital'' produces the predicate
+\lexicalpredicate{'s\_capital}. This process generates more specific predicates
+that we empirically found were easier for the predicate models to learn.
 
@@
 
-The key question in the semantic parsing framework we are using is how
-to define the predicate models that underlie the probabilistic
-database described in \secref{jayant-semparse}.  This is where
-previous work used purely distributional models, and where we wish to
-include structured information from a knowledge base to improve the
-semantics of these predicate models.
+The key question in the semantic parsing framework we are using is how to
+define the predicate models that underlie the probabilistic database described
+in \secref{jayant-semparse}.  This is where previous work used purely
+distributional models, and where we wish to include structured information from
+a knowledge base to improve the semantics of these predicate models.
 
-We inject information from a knowledge base into our predicate models
-by augmenting the learned embeddings with features. In our models, the
-truth probability of a category instance $c(e)$ or relation instance
-$r(e_1, e_2)$ is given by:
+We inject information from a knowledge base into our predicate models by
+augmenting the learned embeddings with features. In our models, the truth
+probability of a category instance $c(e)$ or relation instance $r(e_1, e_2)$ is
+given by:
 
@@
 
-In the above equation, the $\theta$ and $\phi$ terms are learned
-predicate and entity embeddings, as described in Section
-\ref{sec:jayant-semparse}. The second term in the sum represents our
-new features and their learned weights. $\psi_c(e)$ and $\psi_r(e_1,
-e_2)$ are SFE feature vectors for each entity and entity pair; a
-different set of features is chosen for each predicate $c$ and $r$ in
-order to maximize their usefulness. The terms $\omega_c$ and
-$\omega_r$ represent learned weights for these features.
+In the above equation, the $\theta$ and $\phi$ terms are learned predicate and
+entity embeddings, as described in Section \ref{sec:jayant-semparse}. The
+second term in the sum represents our new features and their learned weights.
+$\psi_c(e)$ and $\psi_r(e_1, e_2)$ are SFE feature vectors for each entity and
+entity pair; a different set of features is chosen for each predicate $c$ and
+$r$ in order to maximize their usefulness. The terms $\omega_c$ and $\omega_r$
+represent learned weights for these features.
 
-Each SFE feature can be viewed as either a Freebase query or a horn
-clause implication rule using the Freebase schema. In both cases, the
-feature defines a set of entities (or entity pairs), and the
-associated feature weight measures the likelihood that an entity in
-this set is also in the denotation of the surface predicate. Our
-models include \emph{many} such features for each surface predicate,
-effectively mapping each surface predicate onto a \emph{weighted
-  combination of Freebase queries}. This approach is fundamentally
-different from typical semantic parsers that map language to a single
-Freebase query.
+Each SFE feature can be viewed as either a Freebase query or a horn clause
+implication rule using the Freebase schema. In both cases, the feature defines
+a set of entities (or entity pairs), and the associated feature weight measures
+the likelihood that an entity in this set is also in the denotation of the
+surface predicate. Our models include \emph{many} such features for each
+surface predicate, effectively mapping each surface predicate onto a
+\emph{weighted combination of Freebase queries}. This approach is fundamentally
+different from typical semantic parsers that map language to a single Freebase
+query.
 
-In our model, there are now three sets of parameters to be learned:
-(1) $\theta$, low-dimensional distributional vectors trained for each
-predicate; (2) $\phi$, low-dimensional distributional vectors trained
-for each entity and entity pair; and (3) $\omega$, weights associated
-with the selected formal SFE features for each predicate.  All of
-these parameters are optimized jointly, using the semantic parsing
-framework described in \secref{jayant-semparse}.
+In our model, there are now three sets of parameters to be learned: (1)
+$\theta$, low-dimensional distributional vectors trained for each predicate;
+(2) $\phi$, low-dimensional distributional vectors trained for each entity and
+entity pair; and (3) $\omega$, weights associated with the selected formal SFE
+features for each predicate.  All of these parameters are optimized jointly,
+using the semantic parsing framework described in \secref{jayant-semparse}.
 
@@
 
-The feature vectors $\psi_c(e)$ and $\psi_r(e_1, e_2)$ are constructed
-using a two-stage process. First, we generate a predicate-independent
-feature vector $\psi(e)$ for each entity $e$ and $\psi(e_1, e_2)$ for
-each entity pair $(e_1, e_2)$ using SFE. This step generates very
-high-dimensional feature vectors, where most of the
-features are not relevant for any given predicate. Next, we perform
-per-predicate feature selection to identify a subset of these features
+The feature vectors $\psi_c(e)$ and $\psi_r(e_1, e_2)$ are constructed using a
+two-stage process. First, we generate a predicate-independent feature vector
+$\psi(e)$ for each entity $e$ and $\psi(e_1, e_2)$ for each entity pair $(e_1,
+e_2)$ using SFE. This step generates very high-dimensional feature vectors,
+where most of the features are not relevant for any given predicate. Next, we
+perform per-predicate feature selection to identify a subset of these features
 that are relevant for each category and relation predicate.
 
-The predicate-independent feature extraction stage computes the
-following feature vectors. For entity pairs, the vector $\psi(e_1,
-e_2)$ is a sparse binary vector containing indicator features for all
-edge sequences that connect nodes $e_1$ and $e_2$ in the Freebase
-graph, up to length 4.  For an entity $e$, the vector $\psi(e)$
-contains two kinds of indicator features: (1) all edge sequences up to
-length two that begin at $e$, and (2) the same sequences paired with
-the entity at their endpoint. Features of type (1) capture the kinds
-of relations that an entity participates in, e.g., designing
-architectural structures, while features of type (2) capture relations
-to other particular entities. This second kind of feature is most
-helpful when the endpoint entity is a type, such as
-\entity{architect}, although there are some other valuable features of
-this kind. \figref{sfe} shows some example entity and entity pair
-features extracted from a subset of the Freebase graph.
+The predicate-independent feature extraction stage computes the following
+feature vectors. For entity pairs, the vector $\psi(e_1, e_2)$ is a sparse
+binary vector containing indicator features for all edge sequences that connect
+nodes $e_1$ and $e_2$ in the Freebase graph, up to length 4.  For an entity
+$e$, the vector $\psi(e)$ contains two kinds of indicator features: (1) all
+edge sequences up to length two that begin at $e$, and (2) the same sequences
+paired with the entity at their endpoint. Features of type (1) capture the
+kinds of relations that an entity participates in, e.g., designing
+architectural structures, while features of type (2) capture relations to other
+particular entities. This second kind of feature is most helpful when the
+endpoint entity is a type, such as \entity{architect}, although there are some
+other valuable features of this kind. \figref{sfe} shows some example entity
+and entity pair features extracted from a subset of the Freebase graph.
 
-The feature selection step uses pointwise mutual information (PMI) to
-reduce the number of features considered by the model for each
-predicate. The feature vectors generated above have tens of millions
-of dimensions, but, for any given surface predicate, only a handful of
-these dimensions represent relevant Freebase queries. We select
-features by first summing the entity and entity pair feature vectors
-seen with each predicate in the training data. For example, the phrase
-``Italian architect Andrea Palladio'' is considered a positive
-training example for the instantiated predicates
+The feature selection step uses pointwise mutual information (PMI) to reduce
+the number of features considered by the model for each predicate. The feature
+vectors generated above have tens of millions of dimensions, but, for any given
+surface predicate, only a handful of these dimensions represent relevant
+Freebase queries. We select features by first summing the entity and entity
+pair feature vectors seen with each predicate in the training data. For
+example, the phrase ``Italian architect Andrea Palladio'' is considered a
+positive training example for the instantiated predicates
 $\formalpredicate{architect}(\entity{Andrea Palladio})$ and
-$\formalpredicate{architect\_N/N}(\entity{Italy}, \entity{Andrea
-Palladio})$. We then add the feature vectors for \entity{Andrea
-Palladio} and (\entity{Italy}, \entity{Andrea Palladio}) to the
-feature counts for the predicates \formalpredicate{architect} and
-\formalpredicate{architect\_N/N}, respectively. This gives a set of
-counts \formalpredicate{count}($\pi$), \formalpredicate{count}($f$),
-and \formalpredicate{count}($\pi\land f$), for each predicate $\pi$
-and feature $f$.  The features are then ranked by PMI for each feature
-by computing $\frac{\formalpredicate{count}(\pi\land
-f)}{\formalpredicate{count}(\pi)\formalpredicate{count}(f)}$.  After
-removing features with counts below a threshold, we pick the $k=100$
-features with the highest PMI values for each predicate to use in our
-model.
+$\formalpredicate{architect\_N/N}(\entity{Italy}, \entity{Andrea Palladio})$.
+We then add the feature vectors for \entity{Andrea Palladio} and
+(\entity{Italy}, \entity{Andrea Palladio}) to the feature counts for the
+predicates \formalpredicate{architect} and \formalpredicate{architect\_N/N},
+respectively. This gives a set of counts \formalpredicate{count}($\pi$),
+\formalpredicate{count}($f$), and \formalpredicate{count}($\pi\land f$), for
+each predicate $\pi$ and feature $f$.  The features are then ranked by PMI for
+each feature by computing $\frac{\formalpredicate{count}(\pi\land
+f)}{\formalpredicate{count}(\pi)\formalpredicate{count}(f)}$.  After removing
+features with counts below a threshold, we pick the $k=100$ features with the
+highest PMI values for each predicate to use in our model.
 
@@
 
-A key benefit of our predicate models is that they are able to assign
-scores to entity pairs that were never seen in the training data. The
-purely distributional model of Krishnamurthy and Mitchell has no basis
-for assigning these scores and therefore assumes $P(r(e_1,e_2)) = 0$
-for unseen entity pairs $(e_1,e_2)$. This assumption limits the recall
-of their system when it is applied to question answering, as these
-entity pairs will not have been observed for many correct, but rare
-entity answers. In contrast, our predicate models can score any entity
-pair: the distributional component of an unseen pair will be zero, but
-the SFE component is always applicable. This benefit allows our model
-to considerably improve question answering performance on rare
+A key benefit of our predicate models is that they are able to assign scores to
+entity pairs that were never seen in the training data. The purely
+distributional model of Krishnamurthy and Mitchell has no basis for assigning
+these scores and therefore assumes $P(r(e_1,e_2)) = 0$ for unseen entity pairs
+$(e_1,e_2)$. This assumption limits the recall of their system when it is
+applied to question answering, as these entity pairs will not have been
+observed for many correct, but rare entity answers. In contrast, our predicate
+models can score any entity pair: the distributional component of an unseen
+pair will be zero, but the SFE component is always applicable. This benefit
+allows our model to considerably improve question answering performance on rare
 entities.
 
-However, this benefit has an associated drawback: given a logical form
-query, it is computationally and statistically undesirable to consider
-\emph{all} Freebase entities as answers. Scoring millions of entities
-is slow, and furthermore makes it more difficult to identify correct
-answers (as their relative frequency in the candidate set decreases).
-Therefore, when answering a query, we compute a set of candidate
-entities and only score these candidates. Our candidate set consists
-of all entities seen with the query entities in the training set as
-well as all entities directly connected to the query entities in
-Freebase, or connected by a mediator node.\footnote{Mediators in
-Freebase are used to capture relations with more than two arguments,
-such as employment tenure, which has an employer, and employee, a
-start date, and an end date.}
+However, this benefit has an associated drawback: given a logical form query,
+it is computationally and statistically undesirable to consider \emph{all}
+Freebase entities as answers. Scoring millions of entities is slow, and
+furthermore makes it more difficult to identify correct answers (as their
+relative frequency in the candidate set decreases).  Therefore, when answering
+a query, we compute a set of candidate entities and only score these
+candidates. Our candidate set consists of all entities seen with the query
+entities in the training set as well as all entities directly connected to the
+query entities in Freebase, or connected by a mediator node.\footnote{Mediators
+in Freebase are used to capture relations with more than two arguments, such as
+employment tenure, which has an employer, and employee, a start date, and an
+end date.}
 
-Unfortunately, for some entities, such as the United States, the set
-of connected entities can be intractably large; we therefore limit
-this expansion to only those entities with fewer than 100 directly
-connected entities.  Our motivation for this is that this candidate
-entity generation is most useful for rarely seen entities, for which
-we have few or no related entities seen during training.  These
-entities also tend to have relatively few connected entities in
-Freebase.
+Unfortunately, for some entities, such as the United States, the set of
+connected entities can be intractably large; we therefore limit this expansion
+to only those entities with fewer than 100 directly connected entities.  Our
+motivation for this is that this candidate entity generation is most useful for
+rarely seen entities, for which we have few or no related entities seen during
+training.  These entities also tend to have relatively few connected entities
+in Freebase.
 
@@
 
-We evaluate our open-vocabulary semantic parser on a fill-in-the-blank
-natural language query task.  Each test example is a natural language
-phrase containing at least two Freebase entities, one of which is held
-out.  The system must propose a ranked list of Freebase entities to
-fill in the blank left by the held out entity, and the predicted
-entities are then judged manually for correctness.  We compare our
-proposed models, which combine distributional and formal elements,
-with a purely distributional baseline from prior work.  All of the
-data and code used in these experiments is available at [url withheld
-for review].
+We evaluate our open-vocabulary semantic parser on a fill-in-the-blank natural
+language query task.  Each test example is a natural language phrase containing
+at least two Freebase entities, one of which is held out.  The system must
+propose a ranked list of Freebase entities to fill in the blank left by the
+held out entity, and the predicted entities are then judged manually for
+correctness.  We compare our proposed models, which combine distributional and
+formal elements, with a purely distributional baseline from prior work.  All of
+the data and code used in these experiments is available at [url withheld for
+review].
 
@@
 We use the dataset introduced by Krishnamurthy and
-Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary},
-which consists of the ClueWeb09 web
-corpus\footnote{http://www.lemuproject.org/clueweb09.php} along with
-Google's FACC entity linking of that corpus to
-Freebase~\cite{gabrilovich-2013-clueweb-entity-linking}.  For training
-data, 3 million webpages from this corpus were processed with a CCG
-parser to produce logical forms~\cite{krishnamurthy-2014-joint-ccg}.
-This produced 2.1m predicate instances involving 142k entity pairs and
-184k entities.  After removing infrequently-seen predicates (seen
-fewer than 6 times), there were 25k categories and 4.2k
-relations.\footnote{The differences in numbers reported here versus
-those reported by Krishnamurthy and
-Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} are
-due to our improved logical form generation, discussed in
-\secref{better-lfs}.}
+Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}, which
+consists of the ClueWeb09 web
+corpus\footnote{http://www.lemuproject.org/clueweb09.php} along with Google's
+FACC entity linking of that corpus to
+Freebase~\cite{gabrilovich-2013-clueweb-entity-linking}.  For training data, 3
+million webpages from this corpus were processed with a CCG parser to produce
+logical forms~\cite{krishnamurthy-2014-joint-ccg}.  This produced 2.1m
+predicate instances involving 142k entity pairs and 184k entities.  After
+removing infrequently-seen predicates (seen fewer than 6 times), there were 25k
+categories and 4.2k relations.\footnote{The differences in numbers reported
+here versus those reported by Krishnamurthy and
+Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} are due to our
+improved logical form generation, discussed in \secref{better-lfs}.}
 
-We also used the test set created by Krishnamurthy and Mitchell, which
-contains 220 queries generated in the same fashion as the training
-data from a separate section of ClueWeb.  However, as they did not
-release a development set with their data, we used this set as a
-development set.  For a final evaluation, we generated another,
-similar test set from a different held out section of ClueWeb, in the
-same fashion as done by Krishnamurthy and Mitchell.  This final test
-set contains 307 queries.  We report results on both of these sets
-below.
+We also used the test set created by Krishnamurthy and Mitchell, which contains
+220 queries generated in the same fashion as the training data from a separate
+section of ClueWeb.  However, as they did not release a development set with
+their data, we used this set as a development set.  For a final evaluation, we
+generated another, similar test set from a different held out section of
+ClueWeb, in the same fashion as done by Krishnamurthy and Mitchell.  This final
+test set contains 307 queries.  We report results on both of these sets below.
 
@@
 
-We compare three models in our experiments: (1) a distributional model
-(the prior work of Krishnamurthy and
-Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}); (2)
-a formal model (new to this work), where the distributional parameters
-$\theta$ and $\phi$ in \secref{formal-and-distributional} are fixed at
-zero; and (3) the combined model described in
-\secref{formal-and-distributional} (also new to this work).  Except
-where noted, all experiments use our modified logical forms
+We compare three models in our experiments: (1) a distributional model (the
+prior work of Krishnamurthy and
+Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}); (2) a formal
+model (new to this work), where the distributional parameters $\theta$ and
+$\phi$ in \secref{formal-and-distributional} are fixed at zero; and (3) the
+combined model described in \secref{formal-and-distributional} (also new to
+this work).  Except where noted, all experiments use our modified logical forms
 (\secref{better-lfs}) and our entity proposal mechanism
@@
 
-Given a fill-in-the-blank query such as ``Italian architect
-\blank{}'', each system produces a ranked list of 100 candidate
-entities.  To compare the output of the systems, we follow a pooled
-evaluation protocol commonly used in relation extraction and
-information
-retrieval~\cite{west-2014-kbc-via-qa,riedel-2013-mf-universal-schema}.
-We take the top 30 predictions from each system and manually annotate
-whether they are correct, and use those annotations to compute the
-average precision (AP) and reciprocal rank (RR) of each system on the
-query.  Average precision is defined as $\frac{1}{m}\sum^m_{k=1}
-\mathrm{Prec}(k) \times \mathrm{Correct}(k)$, where $\mathrm{Prec}(k)$
-is the precision at rank $k$, $\mathrm{Correct}(k)$ is an indicator
-function for whether the $k$th answer is correct, and $m$ is number of
-returned answers (up to 100 in this evaluation).  AP is equivalent to
-calculating the area under a precision-recall curve.  Reciprocal rank
-is computed by first finding the rank $r$ of the first correct
-prediction made by a system.  Reciprocal rank is then $\frac{1}{r}$,
-ranging from 1 (if the first prediction is correct) to 0 (if there is
-no correct answer returned).  In the tables below we report
-\emph{mean} average precision (MAP) and \emph{mean} reciprocal rank
-(MRR), averaged over all of the queries in the test set.  We also
-report a weighted version of MAP, where the AP of each query is scaled
-by the number of annotated correct answers to the query (shown as
-W-MAP in the tables for space considerations).
+Given a fill-in-the-blank query such as ``Italian architect \blank{}'', each
+system produces a ranked list of 100 candidate entities.  To compare the output
+of the systems, we follow a pooled evaluation protocol commonly used in
+relation extraction and information
+retrieval~\cite{west-2014-kbc-via-qa,riedel-2013-mf-universal-schema}.  We take
+the top 30 predictions from each system and manually annotate whether they are
+correct, and use those annotations to compute the average precision (AP) and
+reciprocal rank (RR) of each system on the query.  Average precision is defined
+as $\frac{1}{m}\sum^m_{k=1} \mathrm{Prec}(k) \times \mathrm{Correct}(k)$, where
+$\mathrm{Prec}(k)$ is the precision at rank $k$, $\mathrm{Correct}(k)$ is an
+indicator function for whether the $k$th answer is correct, and $m$ is number
+of returned answers (up to 100 in this evaluation).  AP is equivalent to
+calculating the area under a precision-recall curve.  Reciprocal rank is
+computed by first finding the rank $r$ of the first correct prediction made by
+a system.  Reciprocal rank is then $\frac{1}{r}$, ranging from 1 (if the first
+prediction is correct) to 0 (if there is no correct answer returned).  In the
+tables below we report \emph{mean} average precision (MAP) and \emph{mean}
+reciprocal rank (MRR), averaged over all of the queries in the test set.  We
+also report a weighted version of MAP, where the AP of each query is scaled by
+the number of annotated correct answers to the query (shown as W-MAP in the
+tables for space considerations).
 
@@
   }
-  \caption{Comparison of models using logical forms from prior work
-  versus those introduced in this paper.  The metric shown is mean
-  average precision on the dev set.  With our logical forms,
-  performance of all models improves, quite substantially in the case
-  of the formal model.}
+  \caption{Comparison of models using logical forms from prior work versus
+  those introduced in this paper.  The metric shown is mean average precision
+  on the dev set.  With our logical forms, performance of all models improves,
+  quite substantially in the case of the formal model.}
   \label{tab:better-lfs}
@@
 We first show the effect of using the new logical forms introduced in
-\secref{better-lfs}.  As can be seen in \tabref{better-lfs}, with
-improved logical forms, all models are better able to capture the
-semantics of language.  This improvement is more pronounced in the
-formal models, which have more capacity to get specific features from
-Freebase with the new logical forms.  As our logical forms are able to
-give all models better performance, the remaining experiments we
-present all use these logical forms.
+\secref{better-lfs}.  As can be seen in \tabref{better-lfs}, with improved
+logical forms, all models are better able to capture the semantics of language.
+This improvement is more pronounced in the formal models, which have more
+capacity to get specific features from Freebase with the new logical forms.  As
+our logical forms are able to give all models better performance, the remaining
+experiments we present all use these logical forms.
 
@@
   }
-  \caption{Allowing Krishnamurthy and Mitchell's model to propose
-  candidate entities from Freebase improves mean average precision
-  substantially, by allowing the model to have higher recall.}
+  \caption{Allowing Krishnamurthy and Mitchell's model to propose candidate
+  entities from Freebase improves mean average precision substantially, by
+  allowing the model to have higher recall.}
   \label{tab:better-candidates}
@@
 
-We next show the improvement gained by using the simple candidate
-entity generation outlined in \secref{better-candidates}.  By simply
-appending the list of connected entities in Freebase to the end of the
-rankings returned by the distributional model, MAP improves by 40\%
-(see \tabref{better-candidates}).  The connectedness of an entity pair
-in Freebase is very informative, especially for rare entities that are
-not seen together during training.
+We next show the improvement gained by using the simple candidate entity
+generation outlined in \secref{better-candidates}.  By simply appending the
+list of connected entities in Freebase to the end of the rankings returned by
+the distributional model, MAP improves by 40\% (see
+\tabref{better-candidates}).  The connectedness of an entity pair in Freebase
+is very informative, especially for rare entities that are not seen together
+during training.
 
@@
 
-\tabref{dev-results} shows a comparison between the semantic parsing
-models we have discussed on the development set.  As can be seen, the
-combined model significantly improves performance over prior work,
-giving a relative gain in weighted MAP of 29\%.
+\tabref{dev-results} shows a comparison between the semantic parsing models we
+have discussed on the development set.  As can be seen, the combined model
+significantly improves performance over prior work, giving a relative gain in
+weighted MAP of 29\%.
 
@@
   }
-  \caption{Results on the final test set for our fill-in-the-blank
-  task.  The combined model improves over prior work by 50--87\% on
-  our metrics.  Note that these improvements over the baseline are
-  \emph{after} the baseline has been improved by the methods developed
-  in this paper, shown in \tabref{better-lfs} and
-  \tabref{better-candidates}.  The cumulative effect of the methods
-  presented in this work is an improvement of over 120\% in MAP.}
+  \caption{Results on the final test set for our fill-in-the-blank task.  The
+  combined model improves over prior work by 50--87\% on our metrics.  Note
+  that these improvements over the baseline are \emph{after} the baseline has
+  been improved by the methods developed in this paper, shown in
+  \tabref{better-lfs} and \tabref{better-candidates}.  The cumulative effect of
+  the methods presented in this work is an improvement of over 120\% in MAP.}
   \label{tab:final-results}
@@
 
-\tabref{final-results} shows that these improvements are consistent on
-the final test set, as well.  The performance improvement seen by the
-combined model is actually larger on this set, with gains on our
-metrics ranging from 50\% to 87\%.
+\tabref{final-results} shows that these improvements are consistent on the
+final test set, as well.  The performance improvement seen by the combined
+model is actually larger on this set, with gains on our metrics ranging from
+50\% to 87\%.
 
-On both of these datasets, the difference in MAP between the combined
-model and the distributional model is statistically significant (by a
-paired permutation test, $p < 0.05$).  The differences between the
-combined model and the formal model, and between the formal model and
-the distributional model, are not statistically significant, as each
-method has certain kinds of queries that it performs well on.  Only
-the combined model is able to consistently outperform the
-distributional model on all kinds of queries.
+On both of these datasets, the difference in MAP between the combined model and
+the distributional model is statistically significant (by a paired permutation
+test, $p < 0.05$).  The differences between the combined model and the formal
+model, and between the formal model and the distributional model, are not
+statistically significant, as each method has certain kinds of queries that it
+performs well on.  Only the combined model is able to consistently outperform
+the distributional model on all kinds of queries.
 
@@
 
-Our model tends to outperform the distributional model on queries
-containing predicates with exact or partial correlates in
-Freebase. For example, our model obtains nearly perfect average
-precision on the queries ``French newspaper \blank{}'' and ``Israeli
-prime minister \blank{},'' both of which can be exactly expressed in
-Freebase.  The top features for \lexicalpredicate{newspaper}($x$) all
-indicate that $x$ has type \formalpredicate{newspaper} in Freebase,
-and the top features for \lexicalpredicate{newspaper\_N/N}($x$, $y$)
-indicate that $y$ is a newspaper, and that $x$ is either the
-circulation area of $y$ or the language of $y$.
+Our model tends to outperform the distributional model on queries containing
+predicates with exact or partial correlates in Freebase. For example, our model
+obtains nearly perfect average precision on the queries ``French newspaper
+\blank{}'' and ``Israeli prime minister \blank{},'' both of which can be
+exactly expressed in Freebase.  The top features for
+\lexicalpredicate{newspaper}($x$) all indicate that $x$ has type
+\formalpredicate{newspaper} in Freebase, and the top features for
+\lexicalpredicate{newspaper\_N/N}($x$, $y$) indicate that $y$ is a newspaper,
+and that $x$ is either the circulation area of $y$ or the language of $y$.
 
-The model also performs well on queries with partial Freebase
-correlates, such as ``Microsoft head honcho \blank{}'', ``The United
-States, \blank{}'s closest ally'', and ``Patriots linebacker
-\blank{},'' although with somewhat lower average precision. The high
-weight features in these cases tend to provide useful hints, even
-though there is no direct correlate; for example, the model learns
-that ``honchos'' are people, and that they tend to be CEOs and film
+The model also performs well on queries with partial Freebase correlates, such
+as ``Microsoft head honcho \blank{}'', ``The United States, \blank{}'s closest
+ally'', and ``Patriots linebacker \blank{},'' although with somewhat lower
+average precision. The high weight features in these cases tend to provide
+useful hints, even though there is no direct correlate; for example, the model
+learns that ``honchos'' are people, and that they tend to be CEOs and film
 producers.
 
-There are also some areas where our model can be improved. First, in
-some cases, the edge sequence features used by the model are not
-expressive enough to identify the correct relation in Freebase. An
-example of this problem is the ``linebacker'' example above, where the
-features for \lexicalpredicate{linebacker\_N/N} can capture which athletes
-play for which teams, but not the \emph{positions} of those
-athletes. Second, our model can underperform on predicates with no
-close mapping to Freebase. An example where this problem occurs is the
-query ``\blank{} is a NASA mission.'' Third, there remains room to
-further improve the logical forms produced by the semantic parser,
-specifically for multi-word expressions. One problem occurs with
-multi-word noun modifiers, e.g., ``Vice president Al Gore'' is mapped
-to $\lexicalpredicate{vice}(\entity{Al Gore}) \land
-\lexicalpredicate{president}(\entity{Al Gore})$. Another problem is that
-there is no backoff with multi-word relations. For example, the
-predicate \lexicalpredicate{head\_honcho\_N/N} was never seen in the training
-data, so it is replaced with \lexicalpredicate{unknown}; however, it would be
-better to replace it with \lexicalpredicate{honcho\_N/N}, which \emph{was}
-seen in the training data. Finally, although using connected entities
-in Freebase as additional candidates during inference is helpful, it
-often over- or under-generates candidates. A more tailored, per-query
-search process could improve performance.
+There are also some areas where our model can be improved. First, in some
+cases, the edge sequence features used by the model are not expressive enough
+to identify the correct relation in Freebase. An example of this problem is the
+``linebacker'' example above, where the features for
+\lexicalpredicate{linebacker\_N/N} can capture which athletes play for which
+teams, but not the \emph{positions} of those athletes. Second, our model can
+underperform on predicates with no close mapping to Freebase. An example where
+this problem occurs is the query ``\blank{} is a NASA mission.'' Third, there
+remains room to further improve the logical forms produced by the semantic
+parser, specifically for multi-word expressions. One problem occurs with
+multi-word noun modifiers, e.g., ``Vice president Al Gore'' is mapped to
+$\lexicalpredicate{vice}(\entity{Al Gore}) \land
+\lexicalpredicate{president}(\entity{Al Gore})$. Another problem is that there
+is no backoff with multi-word relations. For example, the predicate
+\lexicalpredicate{head\_honcho\_N/N} was never seen in the training data, so it
+is replaced with \lexicalpredicate{unknown}; however, it would be better to
+replace it with \lexicalpredicate{honcho\_N/N}, which \emph{was} seen in the
+training data. Finally, although using connected entities in Freebase as
+additional candidates during inference is helpful, it often over- or
+under-generates candidates. A more tailored, per-query search process could
+improve performance.
 
@@
 
-In addition to the work described in \secref{background}, there are
-three broad classes of work that are related to what we have presented
-in this paper.
+In addition to the work described in \secref{background}, there are three broad
+classes of work that are related to what we have presented in this paper.
 
-The first line of research that our work is related to is knowledge
-base completion.  In addition to SFE~\cite{gardner-2015-sfe}, our work
-draws inspiration from work on embedding the entities and relations in
-a knowledge base~\cite{riedel-2013-mf-universal-schema,%
+The first line of research that our work is related to is knowledge base
+completion.  In addition to SFE~\cite{gardner-2015-sfe}, our work draws
+inspiration from work on embedding the entities and relations in a knowledge
+base~\cite{riedel-2013-mf-universal-schema,%
 nickel-2011-rescal,bordes-2013-transe,nickel-2014-are,%
-toutanova-2015-joint-text-kb-embedding}, as well as work on
-graph-based methods for reasoning with knowledge
+toutanova-2015-joint-text-kb-embedding}, as well as work on graph-based methods
+for reasoning with knowledge
 bases~\cite{lao-2010-original-pra,gardner-2014-vector-space-pra,%
@@
 
-Second, our work is conceptually related to many methods that aim to
-learn word embeddings that are informed by some kind of external
+Second, our work is conceptually related to many methods that aim to learn word
+embeddings that are informed by some kind of external
 knowledge~\cite{faruqui-2015-retrofitting-word-vectors,%
@@
 yu-2014-w2v-with-semantic-knowledge}.  A key difference between these
-approaches and ours is that they use the structured information only
-to modify distributional representations, while we include the
-structured information directly in our models, training feature
-weights jointly with distributional representations.
+approaches and ours is that they use the structured information only to modify
+distributional representations, while we include the structured information
+directly in our models, training feature weights jointly with distributional
+representations.
 
-Lastly, there is an extensive literature on building semantic parsers
-to answer questions against a structured knowledge
+Lastly, there is an extensive literature on building semantic parsers to answer
+questions against a structured knowledge
 base~\cite{zettlemoyer-2005-ccg,berant-2013-semantic-parsing-qa,%
 kwiatkowski-2013-ontology-matching,krishnamurthy-2012-semantic-parsing,%
-li-2015-semantic-parsing-scfg}.  The vast majority of this work is
-focused on matching natural language text to statements in a specific
-schema, with no hope of assigning meaning to language that falls
-outside of that schema.  Only very recently has there been work
-attempting to learn broad coverage meaning representations in semantic
-parsers.  In addition to the work by Krishnamurthy and Mitchell
-discussed in \secref{background}, and work by Lewis and
+li-2015-semantic-parsing-scfg}.  The vast majority of this work is focused on
+matching natural language text to statements in a specific schema, with no hope
+of assigning meaning to language that falls outside of that schema.  Only very
+recently has there been work attempting to learn broad coverage meaning
+representations in semantic parsers.  In addition to the work by Krishnamurthy
+and Mitchell discussed in \secref{background}, and work by Lewis and
 Steedman~\shortcite{lewis-2013-combined-distributional-and-logical-semantics}
 which Krishnamurthy and Mitchell extended, Choi et
-al.~\shortcite{choi-2015-semantic-parsing-partial-ontologies},
-extended a traditional semantic parser with the notion of ``open''
-predicates not contained in the Freebase ontology.  A key difference
-between their work and ours is that, while their system might learn
-that ``front-runner'' should be modeled as an open predicate that has
-no representation in Freebase, they have no method to assign any
-further meaning to that predicate, whereas our models learn both
-distributional and formal information about the meaning of
+al.~\shortcite{choi-2015-semantic-parsing-partial-ontologies}, extended a
+traditional semantic parser with the notion of ``open'' predicates not
+contained in the Freebase ontology.  A key difference between their work and
+ours is that, while their system might learn that ``front-runner'' should be
+modeled as an open predicate that has no representation in Freebase, they have
+no method to assign any further meaning to that predicate, whereas our models
+learn both distributional and formal information about the meaning of
 ``front-runner''.
@@
 
-This paper considers the problem of assigning meaning to predicates
-(both categories and relations) in natural language using both
-distributional information and information from a formal knowledge
-base. Our model represents words as a weighted combination of
-knowledge base queries plus a distributional component. Both of these
-components are jointly trained to correctly predict entity answers to
-fill-in-the-blank natural language queries. This combined model
-achieved relative gains of over 50\% in mean average precision and
-mean reciprocal rank versus a purely distributional approach.  We also
-introduced a better mapping from surface text to logical forms, and a
-simple method for using Freebase to find candidate entities during
-inference.  Taken together, the methods introduced in this paper
-improved mean average precision on our task from .163 to .370, a 127\%
-relative improvement over prior work.
+This paper considers the problem of assigning meaning to predicates (both
+categories and relations) in natural language using both distributional
+information and information from a formal knowledge base. Our model represents
+words as a weighted combination of knowledge base queries plus a distributional
+component. Both of these components are jointly trained to correctly predict
+entity answers to fill-in-the-blank natural language queries. This combined
+model achieved relative gains of over 50\% in mean average precision and mean
+reciprocal rank versus a purely distributional approach.  We also introduced a
+better mapping from surface text to logical forms, and a simple method for
+using Freebase to find candidate entities during inference.  Taken together,
+the methods introduced in this paper improved mean average precision on our
+task from .163 to .370, a 127\% relative improvement over prior work.
 
-A consequence of this work is that it suggests a new direction for
-semantic parsing research. Existing semantic parsers map language to a
-single knowledge base query, an approach that successfully leverages a
-knowledge base's predicate instances, but is fundamentally limited by
-its schema. In contrast, our approach maps language to a
-\emph{weighted combination of queries} plus a distributional
-component; this approach is capable of representing a much broader
-class of concepts while still using the knowledge base when it is
-helpful. Furthermore, it is capable of using the knowledge base even
-when the meaning of the language cannot be exactly represented by a
-knowledge base predicate, which is a common occurrence. We believe
-that this kind of approach could significantly expand the
-applicability of semantic parsing techniques to more complex domains
-where the assumptions of traditional techniques are too limiting.
+A consequence of this work is that it suggests a new direction for semantic
+parsing research. Existing semantic parsers map language to a single knowledge
+base query, an approach that successfully leverages a knowledge base's
+predicate instances, but is fundamentally limited by its schema. In contrast,
+our approach maps language to a \emph{weighted combination of queries} plus a
+distributional component; this approach is capable of representing a much
+broader class of concepts while still using the knowledge base when it is
+helpful. Furthermore, it is capable of using the knowledge base even when the
+meaning of the language cannot be exactly represented by a knowledge base
+predicate, which is a common occurrence. We believe that this kind of approach
+could significantly expand the applicability of semantic parsing techniques to
+more complex domains where the assumptions of traditional techniques are too
+limiting.
 

### 2016-03-21 src/main/scala/org/allenai/semparse/pipeline/Tester.scala
Fixed a couple of small bugs in the pipeline
It looks like it's working!


Former-commit-id: 858ab841b6bec7ddf010c9da833db8b53ba17d99
Former-commit-id: 526c5be71d9b5b3a9c25a5ad75dcb0c40aa523c4

@@ -39,21 +39,23 @@ class Tester(
   val modelType = trainer.modelType
   val trainingDataFile = processor.trainingDataFile
 
+  val lispBase = "src/main/lisp"
+
   // These are code files that are common to all models, and just specify the base lisp
   // environment.
-  val baseEnvFile = "src/main/lisp/environment.lisp"
-  val uschemaEnvFile = "src/main/lisp/uschema_environment.lisp"
+  val baseEnvFile = s"$lispBase/environment.lisp"
+  val uschemaEnvFile = s"$lispBase/uschema_environment.lisp"
 
   // These are code files, specifying the model we're using.
   val lispModelFiles = if (ensembledEvaluation) {
     if (modelType == "baseline") throw new IllegalStateException("You can't ensemble the baseline...")
-    Seq("src/main/lisp/model_baseline", s"src/main/lisp/model_${modelType}.lisp")
+    Seq(s"$lispBase/model_baseline", s"$lispBase/model_${modelType}.lisp")
   } else {
-    Seq(s"src/main/lisp/model_${modelType}.lisp")
+    Seq(s"$lispBase/model_${modelType}.lisp")
   }
   val evalLispFile = modelType match {
-    case "baseline" => "eval_baseline.lisp"
-    case _ => if (ensembledEvaluation) "eval_ensemble.lisp" else "eval_uschema.lisp"
+    case "baseline" => s"$lispBase/eval_baseline.lisp"
+    case _ => if (ensembledEvaluation) s"$lispBase/eval_ensemble.lisp" else s"$lispBase/eval_uschema.lisp"
   }
 
   val handwrittenLispFiles = Seq(baseEnvFile, uschemaEnvFile) ++ lispModelFiles ++ Seq(evalLispFile)

### 2016-03-21 src/main/scala/org/allenai/semparse/pipeline/Experiments.scala
Put in (almost) all of the ACL 2016 experiment configs
Former-commit-id: 5e132135bbb7e8873a283ca52dcbf28d1111e368
Former-commit-id: 8a4fe6a0c868cffa4991270055ab81cdb548408f

@@ -11,7 +11,7 @@ object Experiments {
 
   val NEW_LF_TRAINING_DATA_FILE = "data/acl2016-training.txt"
   val NEW_LF_TRAINING_DATA_NAME = "acl2016"
-  val OLD_LF_TRAINING_DATA_FILE = "data/tacl2015/tacl2015-training.txt"
+  val OLD_LF_TRAINING_DATA_FILE = "data/tacl2015-training.txt"
   val OLD_LF_TRAINING_DATA_NAME = "tacl2015"
 
   val newLfTrainingDataParams: JValue =
@@ -85,6 +85,16 @@ object Experiments {
     ("model type" -> "combined") ~
     ("feature computer" -> newLfTrainingDataPmiParams)
 
+  val oldLfFormalModelParams: JValue =
+    ("model type" -> "formal") ~
+    ("feature computer" -> oldLfTrainingDataPmiParams)
+  val oldLfDistributionalModelParams: JValue =
+    ("model type" -> "distributional") ~
+    ("feature computer" -> oldLfTrainingDataPmiParams)
+  val oldLfCombinedModelParams: JValue =
+    ("model type" -> "combined") ~
+    ("feature computer" -> oldLfTrainingDataPmiParams)
+
   val newLfSampleFormalModelParams: JValue =
     ("model type" -> "formal") ~
     ("feature computer" -> newLfTrainingDataSamplePmiParams)
@@ -99,50 +109,105 @@ object Experiments {
   // STEP 5: TESTING
   // *********************************
 
-  val FINAL_TEST_SET = "src/main/resources/acl2016_final_test_set_annotated.json"
-  val DEV_SET = "src/main/resources/acl2016_dev_set_annotated.json"
-  val DEV_SET_OLD_LFS = "src/main/resources/acl2016_dev_set_old_lfs_annotated.json"
+  // TODO(matt): Make the test set expansion with Freebase an option here; it currently is just
+  // hard-coded to always happen.  So Table 2 doesn't have a nice experiment set up...
+
+  val FINAL_TEST_SET = ("acl2016_test", "src/main/resources/acl2016_final_test_set_annotated.json")
+  val DEV_SET = ("acl2016_dev", "src/main/resources/acl2016_dev_set_annotated.json")
+  val DEV_SET_OLD_LFS = ("tacl2015_test", "src/main/resources/acl2016_dev_set_old_lfs_annotated.json")
 
[…]

### 2016-03-21 src/main/scala/org/allenai/semparse/pipeline/Tester.scala

@@ -23,10 +23,11 @@ class Tester(
 ) extends Step(Some(params), fileUtil) {
   implicit val formats = DefaultFormats
 
-  val validParams = Seq("test query file", "pool depth", "ensembled evaluation", "model")
+  val validParams = Seq("test name", "test query file", "pool depth", "ensembled evaluation", "model")
   JsonHelper.ensureNoExtras(params, "tester", validParams)
 
-  // Parameters we take.  Only the query file is required.
+  // Parameters we take.  Only the test name and query file are required.
+  val testName = (params \ "test name").extract[String]
   val queryFile = (params \ "test query file").extract[String]
   val poolDepth = JsonHelper.extractWithDefault(params, "pool depth", 100)
   val ensembledEvaluation = JsonHelper.extractWithDefault(params, "ensembled evaluation", false)
@@ -91,8 +92,8 @@ class Tester(
     modelType match {
       // ACK!  I need to make this more general...  The dataset should not be just "large" and
       // "small"
-      case "baseline" => s"results/${dataName}/baseline/output.txt"
-      case other => s"results/${dataName}/${modelType}/${ranking}/${ensemble}/output.txt"
+      case "baseline" => s"results/${testName}/${dataName}/baseline/output.txt"
+      case other => s"results/${testName}/${dataName}/${modelType}/${ranking}/${ensemble}/output.txt"
     }
   }
 

### 2016-03-24 src/main/scala/org/allenai/semparse/ccg/Lexicon.scala
Working on getting logical forms for general text
Former-commit-id: 4cd8f2ab1f8f69ef9115400b63e92b43500c3158
Former-commit-id: f28e2c1228cd4ea17ed941d7c144be4a295fb9ab

@@ -1,0 +1,164 @@
+package org.allenai.semparse.ccg
+
+import java.io.File
+import java.util.Optional
+
+import edu.uw.easysrl.dependencies.Coindexation
+import edu.uw.easysrl.semantics._
+import edu.uw.easysrl.semantics.lexicon._
+import edu.uw.easysrl.syntax.grammar.Category
+import edu.uw.easysrl.syntax.grammar.SyntaxTreeNode
+import edu.uw.easysrl.syntax.parser.SRLParser.CCGandSRLparse
+
+object ScienceQuestionLexicon {
+  def getDefault(lexiconFile: File) = {
+    println("Loading lexicon")
+    lazy val manualLexicon: Option[Lexicon] = if (lexiconFile.exists()) Some(new ManualLexicon(lexiconFile)) else None
+    lazy val lexica = Seq(
+      new DeterminerLexicon,
+      new NounLexicon,
+      new AdjectiveLexicon,
+      new VerbLexicon,
+      new CopulaLexicon,
+      new NumbersLexicon,
+      new DefaultLexicon
+    ) ++ manualLexicon.toList
+    new CompositeLexicon(lexica)
+  }
+}
+
+// I basically have to duplicate the CompositeLexicon that exists in the EasySRL code, because Mike
+// made the constructor private...
+class CompositeLexicon(lexica: Seq[Lexicon]) extends Lexicon {
+  override def getEntry(
+    word: String,
+    pos: String,
+    category: Category,
+    coindexation: Coindexation,
+    parse: Optional[CCGandSRLparse],
+    wordIndex: Int
+  ) = {
+    lexica.view.map(lexicon => {
+      lexicon.getEntry(word, pos, category, coindexation, parse, wordIndex)
+    }).filter(_ != null).headOption match {
+      case None => null
+      case Some(logic) => {
+        println("Composite matched something:")
+        println(s"word: $word")
+        println(s"pos: $pos")
+        println(s"category: $category")
+        println(s"logic: $logic")
+        logic
+      }
+    }
+  }
+
+  override def isMultiWordExpression(node: SyntaxTreeNode) = {
+    lexica.exists(_.isMultiWordExpression(node))
+  }
+}
+
+class VerbLexicon extends Lexicon {
+  override def getEntry(
+    word: String,
+    pos: String,
+    category: Category,
+    coindexation: Coindexation,
+    parse: Optional[CCGandSRLparse],
+    wordIndex: Int
+  ) = {
[…]

### 2016-03-24 src/main/scala/org/allenai/semparse/ccg/ScienceQuestionParser.scala

@@ -12,7 +12,6 @@ import edu.uw.easysrl.main.InputReader
 import edu.uw.easysrl.main.ParsePrinter
 import edu.uw.easysrl.semantics._
 import edu.uw.easysrl.semantics.Logic.LogicVisitor
-import edu.uw.easysrl.semantics.lexicon.CompositeLexicon
 import edu.uw.easysrl.syntax.grammar.Category
 import edu.uw.easysrl.syntax.model.CutoffsDictionary
 import edu.uw.easysrl.syntax.model.SRLFactoredModel.SRLFactoredModelFactory
@@ -76,9 +75,11 @@ class ScienceQuestionParser(params: JValue) {
     val labelClassifier = new File(pipelineDir, "labelClassifier")
     val classifier = Util.deserialize[LabelClassifier](labelClassifier)
 
+    val lexicalCategories = TaggerEmbeddings.loadCategories(new File(modelDir, "categories"))
+
     // ACK!  Did he really just save global state in this static Coindexation object?  Bleh...
     Coindexation.parseMarkedUpFile(new File(pipelineDir, "markedup"))
-    val modelFactory = new SupertagFactoredModelFactory(Tagger.make(pipelineDir, supertaggerBeam, 50, null), nBest > 1)
+    val modelFactory = new SupertagFactoredModelFactory(Tagger.make(pipelineDir, supertaggerBeam, 50, null), lexicalCategories, nBest > 1)
     val aStarParser = new ParserAStar(modelFactory, maxLength, nBest, rootCategories, pipelineDir, 100000)
 
     new PipelineSRLParser(aStarParser, classifier, posTagger)
@@ -100,10 +101,7 @@ class ScienceQuestionParser(params: JValue) {
     val aStarParser = new ParserAStar(modelFactory, maxLength, nBest, rootCategories, modelDir, 20000)
     new BackoffSRLParser(new JointSRLParser(aStarParser, posTagger), pipeline)
   }
-  lazy val lexicon = {
-    println("Loading lexicon")
-    if(lexiconFile.exists()) CompositeLexicon.makeDefault(lexiconFile) else CompositeLexicon.makeDefault()
-  }
+  lazy val lexicon = ScienceQuestionLexicon.getDefault(lexiconFile)
   lazy val parser = {
     println("Making final parser")
     new SemanticParser(backoffParser, lexicon)
@@ -223,11 +221,19 @@ object test_easysrl {
   def main(args: Array[String]) {
[…]

### 2016-03-24 src/test/scala/org/allenai/semparse/EvaluatorSpec.scala

@@ -1,29 +1,0 @@
-package org.allenai.semparse
-
-import org.scalatest._
-
-import com.mattg.util.FakeFileUtil
-
-class EvaluationSpec extends FlatSpecLike with Matchers {
-
-  val dataFile = "/data/file"
-  val dataFileContents = """/m/01cb_k /m/03z3fl	"H. pylori" "J. Robin Warren"		discovered_by	((word-rel "discovered_by") "/m/01cb_k" "/m/03z3fl")	[["discovered_by","/m/01cb_k","/m/03z3fl"], ["discovered_by","/m/01cb_k","/m/023fbk"]]
-/m/0gkq30	"Car Service"	best		((word-cat "best") "/m/0gkq30")	[["best","/m/0gkq30"]]
-/m/03rt9	"Ireland"	the		((word-cat "the") "/m/03rt9")	[["throughout","/m/03rt9"], ["the","/m/03rt9"], ["uk,","/m/03rt9"], ["operating","/m/03rt9"]]
-/m/0f8l9c /m/03xp6r	"French" "AF"		special:N/N	((word-rel "special:N/N") "/m/0f8l9c" "/m/03xp6r")	[["special:N/N","/m/0f8l9c","/m/03xp6r"]]
-/m/0f8l9c /m/03xp6r	"France" "Air Force"		special:N/N	((word-rel "special:N/N") "/m/0f8l9c" "/m/03xp6r")	[["special:N/N","/m/0f8l9c","/m/03xp6r"]]
-"""
-
-  val fileUtil = new FakeFileUtil
-  fileUtil.addFileToBeRead(dataFile, dataFileContents)
-
-  "readEntityNames" should "pull entity names out of a data file and sort them" in {
-    val names = Evaluator.loadEntityNames(dataFile, fileUtil)
-    names("/m/01cb_k") should be("\"H. pylori\"")
-    names("/m/03z3fl") should be("\"J. Robin Warren\"")
-    names("/m/0gkq30") should be("\"Car Service\"")
-    names("/m/03rt9") should be("\"Ireland\"")
-    names("/m/0f8l9c") should be("\"France\" \"French\"")
-    names("/m/03xp6r") should be("\"AF\" \"Air Force\"")
-  }
-}

### 2016-03-24 src/test/scala/org/allenai/semparse/ccg/LexiconSpec.scala

@@ -1,0 +1,119 @@
+package org.allenai.semparse.ccg
+
+import org.scalatest._
+
+import java.io.File
+import java.util.Optional
+
+import edu.uw.easysrl.dependencies.Coindexation
+import edu.uw.easysrl.semantics.Logic
+import edu.uw.easysrl.semantics.LogicParser
+import edu.uw.easysrl.semantics.lexicon.Lexicon
+import edu.uw.easysrl.syntax.grammar.Category
+import edu.uw.easysrl.syntax.grammar.Combinator.RuleType
+import edu.uw.easysrl.syntax.grammar.SyntaxTreeNode
+import edu.uw.easysrl.syntax.grammar.SyntaxTreeNode._
+import edu.uw.easysrl.syntax.parser.AbstractParser.UnaryRule
+import edu.uw.easysrl.syntax.parser.SRLParser.CCGandSRLparse
+
+class CompositeLexiconSpec extends FlatSpecLike with Matchers {
+  val logic1 = LogicParser.fromString("#y.y", Category.valueOf("N"))
+  val logic2 = LogicParser.fromString("#x.x", Category.valueOf("S"))
+  val logic3 = LogicParser.fromString("#z.z", Category.valueOf("N"))
+  class FakeLexicon(_word: Option[String], _category: Category, logic: Logic) extends Lexicon {
+    override def getEntry(
+      word: String,
+      pos: String,
+      category: Category,
+      coindexation: Coindexation,
+      parse: Optional[CCGandSRLparse],
+      wordIndex: Int
+    ) = {
+      if (_category.matches(category)) {
+        _word match {
+          case None => logic
+          case Some(w) => if (word == w) logic else null
+        }
+      } else {
+        null
+      }
+    }
+    override def isMultiWordExpression(node: SyntaxTreeNode) = false
+  }
+  val lexicon1 = new FakeLexicon(Some("one"), Category.valueOf("N"), logic1)
+  val lexicon2 = new FakeLexicon(None, Category.valueOf("S"), logic2)
+  val lexicon3 = new FakeLexicon(None, Category.valueOf("N"), logic3)
+
+  "getEntry" should "ask each lexicon in turn and return the first match" in {
+    val lexicon = new CompositeLexicon(Seq(lexicon1, lexicon2, lexicon3))
[…]
